---
title: "Recent Candidate Articles for PBPath Journal Watch"
author:
  - name: Serdar Balcı 
    url: https://www.serdarbalci.com/
    affiliation: MD Pathologist
    affiliation_url: https://sbalci.github.io/
date: "`r Sys.Date()`"
output: blastula::blastula_email 
--- 

Dear PBPath Educational Committee Member,

Below are the recent candidate articles for PBPath Journal Watch. Please review them and select the ones to be included in the upcoming *Journal Watch*. 


Best regards


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(cache = TRUE)
```

```{r}
suppressPackageStartupMessages(library("dplyr"))
suppressPackageStartupMessages(library("RefManageR"))
```


```{r strings , include=FALSE}
PubMedString <- "PubMed: https://www.ncbi.nlm.nih.gov/pubmed/?term="

doiString <- "doi: https://doi.org/"

```




For all candidate articles please visit: http://pbpath.org/journal-watch-upcoming-issue/


### New Pancreas Articles




---

```{r pancreas 31862231, include=FALSE}

PMID_31862231 <- RefManageR::ReadPubMed('31862231', database = 'PubMed')

citation_31862231 <- paste0(PMID_31862231$journal,' ', PMID_31862231$year, ' ', PMID_31862231$month,';', PMID_31862231$volume,'(', PMID_31862231$number,'):', PMID_31862231$pages)

PubMed_31862231 <- paste0(PubMedString, PMID_31862231$eprint)

doi_31862231 <- paste0(doiString, PMID_31862231$doi)

Sys.sleep(1)

```

<details open> <summary>
- **`r PMID_31862231$title`**
</summary> 

*`r citation_31862231`*

`r PubMed_31862231`

`r PMID_31862231$abstract`

`r doi_31862231`

</details>

---




---

```{r pancreas 31862230, include=FALSE}

PMID_31862230 <- RefManageR::ReadPubMed('31862230', database = 'PubMed')

citation_31862230 <- paste0(PMID_31862230$journal,' ', PMID_31862230$year, ' ', PMID_31862230$month,';', PMID_31862230$volume,'(', PMID_31862230$number,'):', PMID_31862230$pages)

PubMed_31862230 <- paste0(PubMedString, PMID_31862230$eprint)

doi_31862230 <- paste0(doiString, PMID_31862230$doi)

Sys.sleep(1)

```

<details open> <summary>
- **`r PMID_31862230$title`**
</summary> 

*`r citation_31862230`*

`r PubMed_31862230`

`r PMID_31862230$abstract`

`r doi_31862230`

</details>

---




### New GallBladder Articles


Today there is no new Gallbladder Article.


### New BileDuct Articles


Today there is no new Bile Duct Article.


### New Ampulla Articles


Today there is no new Ampulla Article.




For all candidate articles please visit: http://pbpath.org/journal-watch-upcoming-issue/


