---
title: "Recent Candidate Articles for PBPath Journal Watch"
author:
  - name: Serdar Balcı 
    url: https://www.serdarbalci.com/
    affiliation: MD Pathologist
    affiliation_url: https://sbalci.github.io/
date: "`r Sys.Date()`"
output: blastula::blastula_email 
--- 

Dear PBPath Educational Committee Member,

Below are the recent candidate articles for PBPath Journal Watch. Please review them and select the ones to be included in the upcoming *Journal Watch*. 


Best regards


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(cache = TRUE)
```

```{r}
suppressPackageStartupMessages(library("dplyr"))
suppressPackageStartupMessages(library("RefManageR"))
```


```{r strings , include=FALSE}
PubMedString <- "PubMed: https://www.ncbi.nlm.nih.gov/pubmed/?term="

doiString <- "doi: https://doi.org/"

dimensionString1 <- "<script async='' charset='utf-8' src='https://badge.dimensions.ai/badge.js'></script> <span class='__dimensions_badge_embed__' data-doi='"

dimensionString2 <- "' data-style='small_circle' data-hide-zero-citations='true' data-legend='always'></span>"

altmetricString1 <-"<script type='text/javascript' src='https://d1bxh8uas1mnw7.cloudfront.net/assets/embed.js'></script> <span class='altmetric-embed' data-link-target='_blank' data-badge-details='right' data-badge-type='donut' data-doi='"

altmetricString2 <- "' data-hide-no-mentions='true'></span>"

```




For all candidate articles please visit: http://pbpath.org/journal-watch-upcoming-issue/


### New Pancreas Articles




---

```{r pancreas 31838609, include=FALSE}

PMID_31838609 <- RefManageR::ReadPubMed('31838609', database = 'PubMed')

citation_31838609 <- paste0(PMID_31838609$journal,' ', PMID_31838609$year, ' ', PMID_31838609$month,';', PMID_31838609$volume,'(', PMID_31838609$number,'):', PMID_31838609$pages)

PubMed_31838609 <- paste0(PubMedString, PMID_31838609$eprint)

doi_31838609 <- paste0(doiString, PMID_31838609$doi)

dimensionBadge_31838609 <- paste0(dimensionString1, PMID_31838609$doi,dimensionString2)

altmetricBadge_31838609 <- paste0(altmetricString1, PMID_31838609$doi, altmetricString2 )

Sys.sleep(2)

```

<details open> <summary>
- **`r PMID_31838609$title`**
</summary> 

*`r citation_31838609`*

`r PubMed_31838609`

`r PMID_31838609$abstract`

`r doi_31838609`

`r dimensionBadge_31838609`

`r altmetricBadge_31838609`

</details>

---




### New GallBladder Articles




---

```{r gallbladder 31838585, include=FALSE}

PMID_31838585 <- RefManageR::ReadPubMed('31838585', database = 'PubMed')

citation_31838585 <- paste0(PMID_31838585$journal,' ', PMID_31838585$year, ' ', PMID_31838585$month,';', PMID_31838585$volume,'(', PMID_31838585$number,'):', PMID_31838585$pages)

PubMed_31838585 <- paste0(PubMedString, PMID_31838585$eprint)

doi_31838585 <- paste0(doiString, PMID_31838585$doi)

dimensionBadge_31838585 <- paste0(dimensionString1, PMID_31838585$doi,dimensionString2)

altmetricBadge_31838585 <- paste0(altmetricString1, PMID_31838585$doi, altmetricString2 )

Sys.sleep(2)

```

<details open> <summary>
- **`r PMID_31838585$title`**
</summary> 

*`r citation_31838585`*

`r PubMed_31838585`

`r PMID_31838585$abstract`

`r doi_31838585`

`r dimensionBadge_31838585`

`r altmetricBadge_31838585`

</details>

---




### New BileDuct Articles


Today there is no new Bile Duct Article.


### New Ampulla Articles


Today there is no new Ampulla Article.




For all candidate articles please visit: http://pbpath.org/journal-watch-upcoming-issue/


