---
title: "Recent Candidate Articles for PBPath Journal Watch"
author:
  - name: Serdar Balcı 
    url: https://www.serdarbalci.com/
    affiliation: MD Pathologist
    affiliation_url: https://sbalci.github.io/
date: "`r Sys.Date()`"
output: blastula::blastula_email 
--- 

Dear PBPath Educational Committee Member,

Below are the recent candidate articles for PBPath Journal Watch. Please review them and select the ones to be included in the upcoming *Journal Watch*. 


Best regards




```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(cache = TRUE)
```

```{r}
suppressPackageStartupMessages(library("dplyr"))
suppressPackageStartupMessages(library("RefManageR"))
```



```{r strings , include=FALSE}
PubMedString <- "PubMed: https://www.ncbi.nlm.nih.gov/pubmed/?term="

doiString <- "doi: https://doi.org/"

dimensionString1 <- "<script async='' charset='utf-8' src='https://badge.dimensions.ai/badge.js'></script> <span class='__dimensions_badge_embed__' data-doi='"

dimensionString2 <- "' data-style='small_circle' data-hide-zero-citations='true' data-legend='always'></span>"

altmetricString1 <-"<script type='text/javascript' src='https://d1bxh8uas1mnw7.cloudfront.net/assets/embed.js'></script> <span class='altmetric-embed' data-link-target='_blank' data-badge-details='right' data-badge-type='donut' data-doi='"

altmetricString2 <- "' data-hide-no-mentions='true'></span>"

addthis_String1 <- "<div class='addthis_inline_share_toolbox' data-url='pbpath.org/current-journal-watch/' data-title='See this abstract on #PBPath #JournalWatch : "

addthis_String2 <- "'></div>"

```




### New Pancreas Articles


Today there is no new Pancreas Article.


### New GallBladder Articles


Today there is no new Gallbladder Article.


### New BileDuct Articles


Today there is no new Bile Duct Article.


### New Ampulla Articles


Today there is no new Ampulla Article.




For all candidate articles please visit: http://pbpath.org/journal-watch-upcoming-issue/


