

---

```{r ampulla 31743737, include=FALSE}

articles <- readRDS('~/JournalWatchPBPath/articles.rds')


PMID_31743737 <- RefManageR::ReadPubMed('31743737', database = 'PubMed')

citation_31743737 <- paste0(PMID_31743737$journal,' ', PMID_31743737$year, ' ', PMID_31743737$month,';', PMID_31743737$volume,'(', PMID_31743737$number,'):', PMID_31743737$pages)

PubMed_31743737 <- paste0(PubMedString, PMID_31743737$eprint)

doi_31743737 <- paste0(doiString, PMID_31743737$doi)

dimensionBadge_31743737 <- paste0(dimensionString1, PMID_31743737$doi,dimensionString2)

altmetricBadge_31743737 <- paste0(altmetricString1, PMID_31743737$doi, altmetricString2 )

addthis_inline_31743737 <- paste0(addthis_String1, PMID_31743737$title , " PMID: 31743737" , addthis_String2)

Sys.sleep(1)


articles <- articles %>%

add_row(

ArticleCitation = PMID_31743737,
PMID = PMID_31743737$eprint,
Title = PMID_31743737$title,
# Author = PMID_31743737$author,
# Abstract = PMID_31743737$abstract,
Journal = PMID_31743737$journal,
Year = PMID_31743737$year,
Month = PMID_31743737$month,
# Volume = PMID_31743737$volume,
# Number = PMID_31743737$number,
# Pages = PMID_31743737$pages,
PubMedLink = paste0('https://www.ncbi.nlm.nih.gov/pubmed/?term=', PMID_31743737$eprint),
DoiNumber = PMID_31743737$doi,
DoiLink = paste0('https://doi.org/', PMID_31743737$doi),
Language = PMID_31743737$language,
ISSN = PMID_31743737$issn
) %>%

unique()


Sys.sleep(1)

saveRDS(articles, '~/JournalWatchPBPath/articles.rds')

```

<details open> <summary>
- **`r PMID_31743737$title`**
</summary> 

*`r citation_31743737`*

`r PubMed_31743737`

<!-- `r addthis_inline_31743737` -->

`r PMID_31743737$abstract`

`r doi_31743737`

<!-- `r dimensionBadge_31743737` -->

<!-- `r altmetricBadge_31743737` -->

</details>

---




---

```{r ampulla 31722071, include=FALSE}

articles <- readRDS('~/JournalWatchPBPath/articles.rds')


PMID_31722071 <- RefManageR::ReadPubMed('31722071', database = 'PubMed')

citation_31722071 <- paste0(PMID_31722071$journal,' ', PMID_31722071$year, ' ', PMID_31722071$month,';', PMID_31722071$volume,'(', PMID_31722071$number,'):', PMID_31722071$pages)

PubMed_31722071 <- paste0(PubMedString, PMID_31722071$eprint)

doi_31722071 <- paste0(doiString, PMID_31722071$doi)

dimensionBadge_31722071 <- paste0(dimensionString1, PMID_31722071$doi,dimensionString2)

altmetricBadge_31722071 <- paste0(altmetricString1, PMID_31722071$doi, altmetricString2 )

addthis_inline_31722071 <- paste0(addthis_String1, PMID_31722071$title , " PMID: 31722071" , addthis_String2)

Sys.sleep(1)


articles <- articles %>%

add_row(

ArticleCitation = PMID_31722071,
PMID = PMID_31722071$eprint,
Title = PMID_31722071$title,
# Author = PMID_31722071$author,
# Abstract = PMID_31722071$abstract,
Journal = PMID_31722071$journal,
Year = PMID_31722071$year,
Month = PMID_31722071$month,
# Volume = PMID_31722071$volume,
# Number = PMID_31722071$number,
# Pages = PMID_31722071$pages,
PubMedLink = paste0('https://www.ncbi.nlm.nih.gov/pubmed/?term=', PMID_31722071$eprint),
DoiNumber = PMID_31722071$doi,
DoiLink = paste0('https://doi.org/', PMID_31722071$doi),
Language = PMID_31722071$language,
ISSN = PMID_31722071$issn
) %>%

unique()


Sys.sleep(1)

saveRDS(articles, '~/JournalWatchPBPath/articles.rds')

```

<details open> <summary>
- **`r PMID_31722071$title`**
</summary> 

*`r citation_31722071`*

`r PubMed_31722071`

<!-- `r addthis_inline_31722071` -->

`r PMID_31722071$abstract`

`r doi_31722071`

<!-- `r dimensionBadge_31722071` -->

<!-- `r altmetricBadge_31722071` -->

</details>

---




---

```{r ampulla 31698512, include=FALSE}

articles <- readRDS('~/JournalWatchPBPath/articles.rds')


PMID_31698512 <- RefManageR::ReadPubMed('31698512', database = 'PubMed')

citation_31698512 <- paste0(PMID_31698512$journal,' ', PMID_31698512$year, ' ', PMID_31698512$month,';', PMID_31698512$volume,'(', PMID_31698512$number,'):', PMID_31698512$pages)

PubMed_31698512 <- paste0(PubMedString, PMID_31698512$eprint)

doi_31698512 <- paste0(doiString, PMID_31698512$doi)

dimensionBadge_31698512 <- paste0(dimensionString1, PMID_31698512$doi,dimensionString2)

altmetricBadge_31698512 <- paste0(altmetricString1, PMID_31698512$doi, altmetricString2 )

addthis_inline_31698512 <- paste0(addthis_String1, PMID_31698512$title , " PMID: 31698512" , addthis_String2)

Sys.sleep(1)


articles <- articles %>%

add_row(

ArticleCitation = PMID_31698512,
PMID = PMID_31698512$eprint,
Title = PMID_31698512$title,
# Author = PMID_31698512$author,
# Abstract = PMID_31698512$abstract,
Journal = PMID_31698512$journal,
Year = PMID_31698512$year,
Month = PMID_31698512$month,
# Volume = PMID_31698512$volume,
# Number = PMID_31698512$number,
# Pages = PMID_31698512$pages,
PubMedLink = paste0('https://www.ncbi.nlm.nih.gov/pubmed/?term=', PMID_31698512$eprint),
DoiNumber = PMID_31698512$doi,
DoiLink = paste0('https://doi.org/', PMID_31698512$doi),
Language = PMID_31698512$language,
ISSN = PMID_31698512$issn
) %>%

unique()


Sys.sleep(1)

saveRDS(articles, '~/JournalWatchPBPath/articles.rds')

```

<details open> <summary>
- **`r PMID_31698512$title`**
</summary> 

*`r citation_31698512`*

`r PubMed_31698512`

<!-- `r addthis_inline_31698512` -->

`r PMID_31698512$abstract`

`r doi_31698512`

<!-- `r dimensionBadge_31698512` -->

<!-- `r altmetricBadge_31698512` -->

</details>

---




---

```{r ampulla 31696397, include=FALSE}

articles <- readRDS('~/JournalWatchPBPath/articles.rds')


PMID_31696397 <- RefManageR::ReadPubMed('31696397', database = 'PubMed')

citation_31696397 <- paste0(PMID_31696397$journal,' ', PMID_31696397$year, ' ', PMID_31696397$month,';', PMID_31696397$volume,'(', PMID_31696397$number,'):', PMID_31696397$pages)

PubMed_31696397 <- paste0(PubMedString, PMID_31696397$eprint)

doi_31696397 <- paste0(doiString, PMID_31696397$doi)

dimensionBadge_31696397 <- paste0(dimensionString1, PMID_31696397$doi,dimensionString2)

altmetricBadge_31696397 <- paste0(altmetricString1, PMID_31696397$doi, altmetricString2 )

addthis_inline_31696397 <- paste0(addthis_String1, PMID_31696397$title , " PMID: 31696397" , addthis_String2)

Sys.sleep(1)


articles <- articles %>%

add_row(

ArticleCitation = PMID_31696397,
PMID = PMID_31696397$eprint,
Title = PMID_31696397$title,
# Author = PMID_31696397$author,
# Abstract = PMID_31696397$abstract,
Journal = PMID_31696397$journal,
Year = PMID_31696397$year,
Month = PMID_31696397$month,
# Volume = PMID_31696397$volume,
# Number = PMID_31696397$number,
# Pages = PMID_31696397$pages,
PubMedLink = paste0('https://www.ncbi.nlm.nih.gov/pubmed/?term=', PMID_31696397$eprint),
DoiNumber = PMID_31696397$doi,
DoiLink = paste0('https://doi.org/', PMID_31696397$doi),
Language = PMID_31696397$language,
ISSN = PMID_31696397$issn
) %>%

unique()


Sys.sleep(1)

saveRDS(articles, '~/JournalWatchPBPath/articles.rds')

```

<details open> <summary>
- **`r PMID_31696397$title`**
</summary> 

*`r citation_31696397`*

`r PubMed_31696397`

<!-- `r addthis_inline_31696397` -->

`r PMID_31696397$abstract`

`r doi_31696397`

<!-- `r dimensionBadge_31696397` -->

<!-- `r altmetricBadge_31696397` -->

</details>

---




---

```{r ampulla 31407176, include=FALSE}

articles <- readRDS('~/JournalWatchPBPath/articles.rds')


PMID_31407176 <- RefManageR::ReadPubMed('31407176', database = 'PubMed')

citation_31407176 <- paste0(PMID_31407176$journal,' ', PMID_31407176$year, ' ', PMID_31407176$month,';', PMID_31407176$volume,'(', PMID_31407176$number,'):', PMID_31407176$pages)

PubMed_31407176 <- paste0(PubMedString, PMID_31407176$eprint)

doi_31407176 <- paste0(doiString, PMID_31407176$doi)

dimensionBadge_31407176 <- paste0(dimensionString1, PMID_31407176$doi,dimensionString2)

altmetricBadge_31407176 <- paste0(altmetricString1, PMID_31407176$doi, altmetricString2 )

addthis_inline_31407176 <- paste0(addthis_String1, PMID_31407176$title , " PMID: 31407176" , addthis_String2)

Sys.sleep(1)


articles <- articles %>%

add_row(

ArticleCitation = PMID_31407176,
PMID = PMID_31407176$eprint,
Title = PMID_31407176$title,
# Author = PMID_31407176$author,
# Abstract = PMID_31407176$abstract,
Journal = PMID_31407176$journal,
Year = PMID_31407176$year,
Month = PMID_31407176$month,
# Volume = PMID_31407176$volume,
# Number = PMID_31407176$number,
# Pages = PMID_31407176$pages,
PubMedLink = paste0('https://www.ncbi.nlm.nih.gov/pubmed/?term=', PMID_31407176$eprint),
DoiNumber = PMID_31407176$doi,
DoiLink = paste0('https://doi.org/', PMID_31407176$doi),
Language = PMID_31407176$language,
ISSN = PMID_31407176$issn
) %>%

unique()


Sys.sleep(1)

saveRDS(articles, '~/JournalWatchPBPath/articles.rds')

```

<details open> <summary>
- **`r PMID_31407176$title`**
</summary> 

*`r citation_31407176`*

`r PubMed_31407176`

<!-- `r addthis_inline_31407176` -->

`r PMID_31407176$abstract`

`r doi_31407176`

<!-- `r dimensionBadge_31407176` -->

<!-- `r altmetricBadge_31407176` -->

</details>

---




---

```{r ampulla 31332425, include=FALSE}

articles <- readRDS('~/JournalWatchPBPath/articles.rds')


PMID_31332425 <- RefManageR::ReadPubMed('31332425', database = 'PubMed')

citation_31332425 <- paste0(PMID_31332425$journal,' ', PMID_31332425$year, ' ', PMID_31332425$month,';', PMID_31332425$volume,'(', PMID_31332425$number,'):', PMID_31332425$pages)

PubMed_31332425 <- paste0(PubMedString, PMID_31332425$eprint)

doi_31332425 <- paste0(doiString, PMID_31332425$doi)

dimensionBadge_31332425 <- paste0(dimensionString1, PMID_31332425$doi,dimensionString2)

altmetricBadge_31332425 <- paste0(altmetricString1, PMID_31332425$doi, altmetricString2 )

addthis_inline_31332425 <- paste0(addthis_String1, PMID_31332425$title , " PMID: 31332425" , addthis_String2)

Sys.sleep(1)


articles <- articles %>%

add_row(

ArticleCitation = PMID_31332425,
PMID = PMID_31332425$eprint,
Title = PMID_31332425$title,
# Author = PMID_31332425$author,
# Abstract = PMID_31332425$abstract,
Journal = PMID_31332425$journal,
Year = PMID_31332425$year,
Month = PMID_31332425$month,
# Volume = PMID_31332425$volume,
# Number = PMID_31332425$number,
# Pages = PMID_31332425$pages,
PubMedLink = paste0('https://www.ncbi.nlm.nih.gov/pubmed/?term=', PMID_31332425$eprint),
DoiNumber = PMID_31332425$doi,
DoiLink = paste0('https://doi.org/', PMID_31332425$doi),
Language = PMID_31332425$language,
ISSN = PMID_31332425$issn
) %>%

unique()


Sys.sleep(1)

saveRDS(articles, '~/JournalWatchPBPath/articles.rds')

```

<details open> <summary>
- **`r PMID_31332425$title`**
</summary> 

*`r citation_31332425`*

`r PubMed_31332425`

<!-- `r addthis_inline_31332425` -->

`r PMID_31332425$abstract`

`r doi_31332425`

<!-- `r dimensionBadge_31332425` -->

<!-- `r altmetricBadge_31332425` -->

</details>

---




---

```{r ampulla 31256008, include=FALSE}

articles <- readRDS('~/JournalWatchPBPath/articles.rds')


PMID_31256008 <- RefManageR::ReadPubMed('31256008', database = 'PubMed')

citation_31256008 <- paste0(PMID_31256008$journal,' ', PMID_31256008$year, ' ', PMID_31256008$month,';', PMID_31256008$volume,'(', PMID_31256008$number,'):', PMID_31256008$pages)

PubMed_31256008 <- paste0(PubMedString, PMID_31256008$eprint)

doi_31256008 <- paste0(doiString, PMID_31256008$doi)

dimensionBadge_31256008 <- paste0(dimensionString1, PMID_31256008$doi,dimensionString2)

altmetricBadge_31256008 <- paste0(altmetricString1, PMID_31256008$doi, altmetricString2 )

addthis_inline_31256008 <- paste0(addthis_String1, PMID_31256008$title , " PMID: 31256008" , addthis_String2)

Sys.sleep(1)


articles <- articles %>%

add_row(

ArticleCitation = PMID_31256008,
PMID = PMID_31256008$eprint,
Title = PMID_31256008$title,
# Author = PMID_31256008$author,
# Abstract = PMID_31256008$abstract,
Journal = PMID_31256008$journal,
Year = PMID_31256008$year,
Month = PMID_31256008$month,
# Volume = PMID_31256008$volume,
# Number = PMID_31256008$number,
# Pages = PMID_31256008$pages,
PubMedLink = paste0('https://www.ncbi.nlm.nih.gov/pubmed/?term=', PMID_31256008$eprint),
DoiNumber = PMID_31256008$doi,
DoiLink = paste0('https://doi.org/', PMID_31256008$doi),
Language = PMID_31256008$language,
ISSN = PMID_31256008$issn
) %>%

unique()


Sys.sleep(1)

saveRDS(articles, '~/JournalWatchPBPath/articles.rds')

```

<details open> <summary>
- **`r PMID_31256008$title`**
</summary> 

*`r citation_31256008`*

`r PubMed_31256008`

<!-- `r addthis_inline_31256008` -->

`r PMID_31256008$abstract`

`r doi_31256008`

<!-- `r dimensionBadge_31256008` -->

<!-- `r altmetricBadge_31256008` -->

</details>

---




---

```{r ampulla 31612756, include=FALSE}

articles <- readRDS('~/JournalWatchPBPath/articles.rds')


PMID_31612756 <- RefManageR::ReadPubMed('31612756', database = 'PubMed')

citation_31612756 <- paste0(PMID_31612756$journal,' ', PMID_31612756$year, ' ', PMID_31612756$month,';', PMID_31612756$volume,'(', PMID_31612756$number,'):', PMID_31612756$pages)

PubMed_31612756 <- paste0(PubMedString, PMID_31612756$eprint)

doi_31612756 <- paste0(doiString, PMID_31612756$doi)

dimensionBadge_31612756 <- paste0(dimensionString1, PMID_31612756$doi,dimensionString2)

altmetricBadge_31612756 <- paste0(altmetricString1, PMID_31612756$doi, altmetricString2 )

addthis_inline_31612756 <- paste0(addthis_String1, PMID_31612756$title , " PMID: 31612756" , addthis_String2)

Sys.sleep(1)


articles <- articles %>%

add_row(

ArticleCitation = PMID_31612756,
PMID = PMID_31612756$eprint,
Title = PMID_31612756$title,
# Author = PMID_31612756$author,
# Abstract = PMID_31612756$abstract,
Journal = PMID_31612756$journal,
Year = PMID_31612756$year,
Month = PMID_31612756$month,
# Volume = PMID_31612756$volume,
# Number = PMID_31612756$number,
# Pages = PMID_31612756$pages,
PubMedLink = paste0('https://www.ncbi.nlm.nih.gov/pubmed/?term=', PMID_31612756$eprint),
DoiNumber = PMID_31612756$doi,
DoiLink = paste0('https://doi.org/', PMID_31612756$doi),
Language = PMID_31612756$language,
ISSN = PMID_31612756$issn
) %>%

unique()


Sys.sleep(1)

saveRDS(articles, '~/JournalWatchPBPath/articles.rds')

```

<details open> <summary>
- **`r PMID_31612756$title`**
</summary> 

*`r citation_31612756`*

`r PubMed_31612756`

<!-- `r addthis_inline_31612756` -->

`r PMID_31612756$abstract`

`r doi_31612756`

<!-- `r dimensionBadge_31612756` -->

<!-- `r altmetricBadge_31612756` -->

</details>

---




---

```{r ampulla 31605347, include=FALSE}

articles <- readRDS('~/JournalWatchPBPath/articles.rds')


PMID_31605347 <- RefManageR::ReadPubMed('31605347', database = 'PubMed')

citation_31605347 <- paste0(PMID_31605347$journal,' ', PMID_31605347$year, ' ', PMID_31605347$month,';', PMID_31605347$volume,'(', PMID_31605347$number,'):', PMID_31605347$pages)

PubMed_31605347 <- paste0(PubMedString, PMID_31605347$eprint)

doi_31605347 <- paste0(doiString, PMID_31605347$doi)

dimensionBadge_31605347 <- paste0(dimensionString1, PMID_31605347$doi,dimensionString2)

altmetricBadge_31605347 <- paste0(altmetricString1, PMID_31605347$doi, altmetricString2 )

addthis_inline_31605347 <- paste0(addthis_String1, PMID_31605347$title , " PMID: 31605347" , addthis_String2)

Sys.sleep(1)


articles <- articles %>%

add_row(

ArticleCitation = PMID_31605347,
PMID = PMID_31605347$eprint,
Title = PMID_31605347$title,
# Author = PMID_31605347$author,
# Abstract = PMID_31605347$abstract,
Journal = PMID_31605347$journal,
Year = PMID_31605347$year,
Month = PMID_31605347$month,
# Volume = PMID_31605347$volume,
# Number = PMID_31605347$number,
# Pages = PMID_31605347$pages,
PubMedLink = paste0('https://www.ncbi.nlm.nih.gov/pubmed/?term=', PMID_31605347$eprint),
DoiNumber = PMID_31605347$doi,
DoiLink = paste0('https://doi.org/', PMID_31605347$doi),
Language = PMID_31605347$language,
ISSN = PMID_31605347$issn
) %>%

unique()


Sys.sleep(1)

saveRDS(articles, '~/JournalWatchPBPath/articles.rds')

```

<details open> <summary>
- **`r PMID_31605347$title`**
</summary> 

*`r citation_31605347`*

`r PubMed_31605347`

<!-- `r addthis_inline_31605347` -->

`r PMID_31605347$abstract`

`r doi_31605347`

<!-- `r dimensionBadge_31605347` -->

<!-- `r altmetricBadge_31605347` -->

</details>

---




---

```{r ampulla 31425333, include=FALSE}

articles <- readRDS('~/JournalWatchPBPath/articles.rds')


PMID_31425333 <- RefManageR::ReadPubMed('31425333', database = 'PubMed')

citation_31425333 <- paste0(PMID_31425333$journal,' ', PMID_31425333$year, ' ', PMID_31425333$month,';', PMID_31425333$volume,'(', PMID_31425333$number,'):', PMID_31425333$pages)

PubMed_31425333 <- paste0(PubMedString, PMID_31425333$eprint)

doi_31425333 <- paste0(doiString, PMID_31425333$doi)

dimensionBadge_31425333 <- paste0(dimensionString1, PMID_31425333$doi,dimensionString2)

altmetricBadge_31425333 <- paste0(altmetricString1, PMID_31425333$doi, altmetricString2 )

addthis_inline_31425333 <- paste0(addthis_String1, PMID_31425333$title , " PMID: 31425333" , addthis_String2)

Sys.sleep(1)


articles <- articles %>%

add_row(

ArticleCitation = PMID_31425333,
PMID = PMID_31425333$eprint,
Title = PMID_31425333$title,
# Author = PMID_31425333$author,
# Abstract = PMID_31425333$abstract,
Journal = PMID_31425333$journal,
Year = PMID_31425333$year,
Month = PMID_31425333$month,
# Volume = PMID_31425333$volume,
# Number = PMID_31425333$number,
# Pages = PMID_31425333$pages,
PubMedLink = paste0('https://www.ncbi.nlm.nih.gov/pubmed/?term=', PMID_31425333$eprint),
DoiNumber = PMID_31425333$doi,
DoiLink = paste0('https://doi.org/', PMID_31425333$doi),
Language = PMID_31425333$language,
ISSN = PMID_31425333$issn
) %>%

unique()


Sys.sleep(1)

saveRDS(articles, '~/JournalWatchPBPath/articles.rds')

```

<details open> <summary>
- **`r PMID_31425333$title`**
</summary> 

*`r citation_31425333`*

`r PubMed_31425333`

<!-- `r addthis_inline_31425333` -->

`r PMID_31425333$abstract`

`r doi_31425333`

<!-- `r dimensionBadge_31425333` -->

<!-- `r altmetricBadge_31425333` -->

</details>

---


