

---

```{r bileducts 31611450, include=FALSE}

articles <- readRDS('~/JournalWatchPBPath/articles.rds')


PMID_31611450 <- RefManageR::ReadPubMed('31611450', database = 'PubMed')

citation_31611450 <- paste0(PMID_31611450$journal,' ', PMID_31611450$year, ' ', PMID_31611450$month,';', PMID_31611450$volume,'(', PMID_31611450$number,'):', PMID_31611450$pages)

PubMed_31611450 <- paste0(PubMedString, PMID_31611450$eprint)

doi_31611450 <- paste0(doiString, PMID_31611450$doi)

dimensionBadge_31611450 <- paste0(dimensionString1, PMID_31611450$doi,dimensionString2)

altmetricBadge_31611450 <- paste0(altmetricString1, PMID_31611450$doi, altmetricString2 )

addthis_inline_31611450 <- paste0(addthis_String1, PMID_31611450$title , " PMID: 31611450" , addthis_String2)

Sys.sleep(1)


articles <- articles %>%

add_row(

ArticleCitation = PMID_31611450,
PMID = PMID_31611450$eprint,
Title = PMID_31611450$title,
# Author = PMID_31611450$author,
# Abstract = PMID_31611450$abstract,
Journal = PMID_31611450$journal,
Year = PMID_31611450$year,
Month = PMID_31611450$month,
# Volume = PMID_31611450$volume,
# Number = PMID_31611450$number,
# Pages = PMID_31611450$pages,
PubMedLink = paste0('https://www.ncbi.nlm.nih.gov/pubmed/?term=', PMID_31611450$eprint),
DoiNumber = PMID_31611450$doi,
DoiLink = paste0('https://doi.org/', PMID_31611450$doi),
Language = PMID_31611450$language,
ISSN = PMID_31611450$issn
) %>%

unique()


Sys.sleep(1)

saveRDS(articles, '~/JournalWatchPBPath/articles.rds')

```

<details open> <summary>
- **`r PMID_31611450$title`**
</summary> 

*`r citation_31611450`*

`r PubMed_31611450`

`r addthis_inline_31611450`

`r PMID_31611450$abstract`

`r doi_31611450`

`r dimensionBadge_31611450`

`r altmetricBadge_31611450`

</details>

---




---

```{r bileducts 31608763, include=FALSE}

articles <- readRDS('~/JournalWatchPBPath/articles.rds')


PMID_31608763 <- RefManageR::ReadPubMed('31608763', database = 'PubMed')

citation_31608763 <- paste0(PMID_31608763$journal,' ', PMID_31608763$year, ' ', PMID_31608763$month,';', PMID_31608763$volume,'(', PMID_31608763$number,'):', PMID_31608763$pages)

PubMed_31608763 <- paste0(PubMedString, PMID_31608763$eprint)

doi_31608763 <- paste0(doiString, PMID_31608763$doi)

dimensionBadge_31608763 <- paste0(dimensionString1, PMID_31608763$doi,dimensionString2)

altmetricBadge_31608763 <- paste0(altmetricString1, PMID_31608763$doi, altmetricString2 )

addthis_inline_31608763 <- paste0(addthis_String1, PMID_31608763$title , " PMID: 31608763" , addthis_String2)

Sys.sleep(1)


articles <- articles %>%

add_row(

ArticleCitation = PMID_31608763,
PMID = PMID_31608763$eprint,
Title = PMID_31608763$title,
# Author = PMID_31608763$author,
# Abstract = PMID_31608763$abstract,
Journal = PMID_31608763$journal,
Year = PMID_31608763$year,
Month = PMID_31608763$month,
# Volume = PMID_31608763$volume,
# Number = PMID_31608763$number,
# Pages = PMID_31608763$pages,
PubMedLink = paste0('https://www.ncbi.nlm.nih.gov/pubmed/?term=', PMID_31608763$eprint),
DoiNumber = PMID_31608763$doi,
DoiLink = paste0('https://doi.org/', PMID_31608763$doi),
Language = PMID_31608763$language,
ISSN = PMID_31608763$issn
) %>%

unique()


Sys.sleep(1)

saveRDS(articles, '~/JournalWatchPBPath/articles.rds')

```

<details open> <summary>
- **`r PMID_31608763$title`**
</summary> 

*`r citation_31608763`*

`r PubMed_31608763`

`r addthis_inline_31608763`

`r PMID_31608763$abstract`

`r doi_31608763`

`r dimensionBadge_31608763`

`r altmetricBadge_31608763`

</details>

---




---

```{r bileducts 31584623, include=FALSE}

articles <- readRDS('~/JournalWatchPBPath/articles.rds')


PMID_31584623 <- RefManageR::ReadPubMed('31584623', database = 'PubMed')

citation_31584623 <- paste0(PMID_31584623$journal,' ', PMID_31584623$year, ' ', PMID_31584623$month,';', PMID_31584623$volume,'(', PMID_31584623$number,'):', PMID_31584623$pages)

PubMed_31584623 <- paste0(PubMedString, PMID_31584623$eprint)

doi_31584623 <- paste0(doiString, PMID_31584623$doi)

dimensionBadge_31584623 <- paste0(dimensionString1, PMID_31584623$doi,dimensionString2)

altmetricBadge_31584623 <- paste0(altmetricString1, PMID_31584623$doi, altmetricString2 )

addthis_inline_31584623 <- paste0(addthis_String1, PMID_31584623$title , " PMID: 31584623" , addthis_String2)

Sys.sleep(1)


articles <- articles %>%

add_row(

ArticleCitation = PMID_31584623,
PMID = PMID_31584623$eprint,
Title = PMID_31584623$title,
# Author = PMID_31584623$author,
# Abstract = PMID_31584623$abstract,
Journal = PMID_31584623$journal,
Year = PMID_31584623$year,
Month = PMID_31584623$month,
# Volume = PMID_31584623$volume,
# Number = PMID_31584623$number,
# Pages = PMID_31584623$pages,
PubMedLink = paste0('https://www.ncbi.nlm.nih.gov/pubmed/?term=', PMID_31584623$eprint),
DoiNumber = PMID_31584623$doi,
DoiLink = paste0('https://doi.org/', PMID_31584623$doi),
Language = PMID_31584623$language,
ISSN = PMID_31584623$issn
) %>%

unique()


Sys.sleep(1)

saveRDS(articles, '~/JournalWatchPBPath/articles.rds')

```

<details open> <summary>
- **`r PMID_31584623$title`**
</summary> 

*`r citation_31584623`*

`r PubMed_31584623`

`r addthis_inline_31584623`

`r PMID_31584623$abstract`

`r doi_31584623`

`r dimensionBadge_31584623`

`r altmetricBadge_31584623`

</details>

---




---

```{r bileducts 31550713, include=FALSE}

articles <- readRDS('~/JournalWatchPBPath/articles.rds')


PMID_31550713 <- RefManageR::ReadPubMed('31550713', database = 'PubMed')

citation_31550713 <- paste0(PMID_31550713$journal,' ', PMID_31550713$year, ' ', PMID_31550713$month,';', PMID_31550713$volume,'(', PMID_31550713$number,'):', PMID_31550713$pages)

PubMed_31550713 <- paste0(PubMedString, PMID_31550713$eprint)

doi_31550713 <- paste0(doiString, PMID_31550713$doi)

dimensionBadge_31550713 <- paste0(dimensionString1, PMID_31550713$doi,dimensionString2)

altmetricBadge_31550713 <- paste0(altmetricString1, PMID_31550713$doi, altmetricString2 )

addthis_inline_31550713 <- paste0(addthis_String1, PMID_31550713$title , " PMID: 31550713" , addthis_String2)

Sys.sleep(1)


articles <- articles %>%

add_row(

ArticleCitation = PMID_31550713,
PMID = PMID_31550713$eprint,
Title = PMID_31550713$title,
# Author = PMID_31550713$author,
# Abstract = PMID_31550713$abstract,
Journal = PMID_31550713$journal,
Year = PMID_31550713$year,
Month = PMID_31550713$month,
# Volume = PMID_31550713$volume,
# Number = PMID_31550713$number,
# Pages = PMID_31550713$pages,
PubMedLink = paste0('https://www.ncbi.nlm.nih.gov/pubmed/?term=', PMID_31550713$eprint),
DoiNumber = PMID_31550713$doi,
DoiLink = paste0('https://doi.org/', PMID_31550713$doi),
Language = PMID_31550713$language,
ISSN = PMID_31550713$issn
) %>%

unique()


Sys.sleep(1)

saveRDS(articles, '~/JournalWatchPBPath/articles.rds')

```

<details open> <summary>
- **`r PMID_31550713$title`**
</summary> 

*`r citation_31550713`*

`r PubMed_31550713`

`r addthis_inline_31550713`

`r PMID_31550713$abstract`

`r doi_31550713`

`r dimensionBadge_31550713`

`r altmetricBadge_31550713`

</details>

---




---

```{r bileducts 31530714, include=FALSE}

articles <- readRDS('~/JournalWatchPBPath/articles.rds')


PMID_31530714 <- RefManageR::ReadPubMed('31530714', database = 'PubMed')

citation_31530714 <- paste0(PMID_31530714$journal,' ', PMID_31530714$year, ' ', PMID_31530714$month,';', PMID_31530714$volume,'(', PMID_31530714$number,'):', PMID_31530714$pages)

PubMed_31530714 <- paste0(PubMedString, PMID_31530714$eprint)

doi_31530714 <- paste0(doiString, PMID_31530714$doi)

dimensionBadge_31530714 <- paste0(dimensionString1, PMID_31530714$doi,dimensionString2)

altmetricBadge_31530714 <- paste0(altmetricString1, PMID_31530714$doi, altmetricString2 )

addthis_inline_31530714 <- paste0(addthis_String1, PMID_31530714$title , " PMID: 31530714" , addthis_String2)

Sys.sleep(1)


articles <- articles %>%

add_row(

ArticleCitation = PMID_31530714,
PMID = PMID_31530714$eprint,
Title = PMID_31530714$title,
# Author = PMID_31530714$author,
# Abstract = PMID_31530714$abstract,
Journal = PMID_31530714$journal,
Year = PMID_31530714$year,
Month = PMID_31530714$month,
# Volume = PMID_31530714$volume,
# Number = PMID_31530714$number,
# Pages = PMID_31530714$pages,
PubMedLink = paste0('https://www.ncbi.nlm.nih.gov/pubmed/?term=', PMID_31530714$eprint),
DoiNumber = PMID_31530714$doi,
DoiLink = paste0('https://doi.org/', PMID_31530714$doi),
Language = PMID_31530714$language,
ISSN = PMID_31530714$issn
) %>%

unique()


Sys.sleep(1)

saveRDS(articles, '~/JournalWatchPBPath/articles.rds')

```

<details open> <summary>
- **`r PMID_31530714$title`**
</summary> 

*`r citation_31530714`*

`r PubMed_31530714`

`r addthis_inline_31530714`

`r PMID_31530714$abstract`

`r doi_31530714`

`r dimensionBadge_31530714`

`r altmetricBadge_31530714`

</details>

---




---

```{r bileducts 31371396, include=FALSE}

articles <- readRDS('~/JournalWatchPBPath/articles.rds')


PMID_31371396 <- RefManageR::ReadPubMed('31371396', database = 'PubMed')

citation_31371396 <- paste0(PMID_31371396$journal,' ', PMID_31371396$year, ' ', PMID_31371396$month,';', PMID_31371396$volume,'(', PMID_31371396$number,'):', PMID_31371396$pages)

PubMed_31371396 <- paste0(PubMedString, PMID_31371396$eprint)

doi_31371396 <- paste0(doiString, PMID_31371396$doi)

dimensionBadge_31371396 <- paste0(dimensionString1, PMID_31371396$doi,dimensionString2)

altmetricBadge_31371396 <- paste0(altmetricString1, PMID_31371396$doi, altmetricString2 )

addthis_inline_31371396 <- paste0(addthis_String1, PMID_31371396$title , " PMID: 31371396" , addthis_String2)

Sys.sleep(1)


articles <- articles %>%

add_row(

ArticleCitation = PMID_31371396,
PMID = PMID_31371396$eprint,
Title = PMID_31371396$title,
# Author = PMID_31371396$author,
# Abstract = PMID_31371396$abstract,
Journal = PMID_31371396$journal,
Year = PMID_31371396$year,
Month = PMID_31371396$month,
# Volume = PMID_31371396$volume,
# Number = PMID_31371396$number,
# Pages = PMID_31371396$pages,
PubMedLink = paste0('https://www.ncbi.nlm.nih.gov/pubmed/?term=', PMID_31371396$eprint),
DoiNumber = PMID_31371396$doi,
DoiLink = paste0('https://doi.org/', PMID_31371396$doi),
Language = PMID_31371396$language,
ISSN = PMID_31371396$issn
) %>%

unique()


Sys.sleep(1)

saveRDS(articles, '~/JournalWatchPBPath/articles.rds')

```

<details open> <summary>
- **`r PMID_31371396$title`**
</summary> 

*`r citation_31371396`*

`r PubMed_31371396`

`r addthis_inline_31371396`

`r PMID_31371396$abstract`

`r doi_31371396`

`r dimensionBadge_31371396`

`r altmetricBadge_31371396`

</details>

---




---

```{r bileducts 31229495, include=FALSE}

articles <- readRDS('~/JournalWatchPBPath/articles.rds')


PMID_31229495 <- RefManageR::ReadPubMed('31229495', database = 'PubMed')

citation_31229495 <- paste0(PMID_31229495$journal,' ', PMID_31229495$year, ' ', PMID_31229495$month,';', PMID_31229495$volume,'(', PMID_31229495$number,'):', PMID_31229495$pages)

PubMed_31229495 <- paste0(PubMedString, PMID_31229495$eprint)

doi_31229495 <- paste0(doiString, PMID_31229495$doi)

dimensionBadge_31229495 <- paste0(dimensionString1, PMID_31229495$doi,dimensionString2)

altmetricBadge_31229495 <- paste0(altmetricString1, PMID_31229495$doi, altmetricString2 )

addthis_inline_31229495 <- paste0(addthis_String1, PMID_31229495$title , " PMID: 31229495" , addthis_String2)

Sys.sleep(1)


articles <- articles %>%

add_row(

ArticleCitation = PMID_31229495,
PMID = PMID_31229495$eprint,
Title = PMID_31229495$title,
# Author = PMID_31229495$author,
# Abstract = PMID_31229495$abstract,
Journal = PMID_31229495$journal,
Year = PMID_31229495$year,
Month = PMID_31229495$month,
# Volume = PMID_31229495$volume,
# Number = PMID_31229495$number,
# Pages = PMID_31229495$pages,
PubMedLink = paste0('https://www.ncbi.nlm.nih.gov/pubmed/?term=', PMID_31229495$eprint),
DoiNumber = PMID_31229495$doi,
DoiLink = paste0('https://doi.org/', PMID_31229495$doi),
Language = PMID_31229495$language,
ISSN = PMID_31229495$issn
) %>%

unique()


Sys.sleep(1)

saveRDS(articles, '~/JournalWatchPBPath/articles.rds')

```

<details open> <summary>
- **`r PMID_31229495$title`**
</summary> 

*`r citation_31229495`*

`r PubMed_31229495`

`r addthis_inline_31229495`

`r PMID_31229495$abstract`

`r doi_31229495`

`r dimensionBadge_31229495`

`r altmetricBadge_31229495`

</details>

---




---

```{r bileducts 31228442, include=FALSE}

articles <- readRDS('~/JournalWatchPBPath/articles.rds')


PMID_31228442 <- RefManageR::ReadPubMed('31228442', database = 'PubMed')

citation_31228442 <- paste0(PMID_31228442$journal,' ', PMID_31228442$year, ' ', PMID_31228442$month,';', PMID_31228442$volume,'(', PMID_31228442$number,'):', PMID_31228442$pages)

PubMed_31228442 <- paste0(PubMedString, PMID_31228442$eprint)

doi_31228442 <- paste0(doiString, PMID_31228442$doi)

dimensionBadge_31228442 <- paste0(dimensionString1, PMID_31228442$doi,dimensionString2)

altmetricBadge_31228442 <- paste0(altmetricString1, PMID_31228442$doi, altmetricString2 )

addthis_inline_31228442 <- paste0(addthis_String1, PMID_31228442$title , " PMID: 31228442" , addthis_String2)

Sys.sleep(1)


articles <- articles %>%

add_row(

ArticleCitation = PMID_31228442,
PMID = PMID_31228442$eprint,
Title = PMID_31228442$title,
# Author = PMID_31228442$author,
# Abstract = PMID_31228442$abstract,
Journal = PMID_31228442$journal,
Year = PMID_31228442$year,
Month = PMID_31228442$month,
# Volume = PMID_31228442$volume,
# Number = PMID_31228442$number,
# Pages = PMID_31228442$pages,
PubMedLink = paste0('https://www.ncbi.nlm.nih.gov/pubmed/?term=', PMID_31228442$eprint),
DoiNumber = PMID_31228442$doi,
DoiLink = paste0('https://doi.org/', PMID_31228442$doi),
Language = PMID_31228442$language,
ISSN = PMID_31228442$issn
) %>%

unique()


Sys.sleep(1)

saveRDS(articles, '~/JournalWatchPBPath/articles.rds')

```

<details open> <summary>
- **`r PMID_31228442$title`**
</summary> 

*`r citation_31228442`*

`r PubMed_31228442`

`r addthis_inline_31228442`

`r PMID_31228442$abstract`

`r doi_31228442`

`r dimensionBadge_31228442`

`r altmetricBadge_31228442`

</details>

---




---

```{r bileducts 31081949, include=FALSE}

articles <- readRDS('~/JournalWatchPBPath/articles.rds')


PMID_31081949 <- RefManageR::ReadPubMed('31081949', database = 'PubMed')

citation_31081949 <- paste0(PMID_31081949$journal,' ', PMID_31081949$year, ' ', PMID_31081949$month,';', PMID_31081949$volume,'(', PMID_31081949$number,'):', PMID_31081949$pages)

PubMed_31081949 <- paste0(PubMedString, PMID_31081949$eprint)

doi_31081949 <- paste0(doiString, PMID_31081949$doi)

dimensionBadge_31081949 <- paste0(dimensionString1, PMID_31081949$doi,dimensionString2)

altmetricBadge_31081949 <- paste0(altmetricString1, PMID_31081949$doi, altmetricString2 )

addthis_inline_31081949 <- paste0(addthis_String1, PMID_31081949$title , " PMID: 31081949" , addthis_String2)

Sys.sleep(1)


articles <- articles %>%

add_row(

ArticleCitation = PMID_31081949,
PMID = PMID_31081949$eprint,
Title = PMID_31081949$title,
# Author = PMID_31081949$author,
# Abstract = PMID_31081949$abstract,
Journal = PMID_31081949$journal,
Year = PMID_31081949$year,
Month = PMID_31081949$month,
# Volume = PMID_31081949$volume,
# Number = PMID_31081949$number,
# Pages = PMID_31081949$pages,
PubMedLink = paste0('https://www.ncbi.nlm.nih.gov/pubmed/?term=', PMID_31081949$eprint),
DoiNumber = PMID_31081949$doi,
DoiLink = paste0('https://doi.org/', PMID_31081949$doi),
Language = PMID_31081949$language,
ISSN = PMID_31081949$issn
) %>%

unique()


Sys.sleep(1)

saveRDS(articles, '~/JournalWatchPBPath/articles.rds')

```

<details open> <summary>
- **`r PMID_31081949$title`**
</summary> 

*`r citation_31081949`*

`r PubMed_31081949`

`r addthis_inline_31081949`

`r PMID_31081949$abstract`

`r doi_31081949`

`r dimensionBadge_31081949`

`r altmetricBadge_31081949`

</details>

---




---

```{r bileducts 30228218, include=FALSE}

articles <- readRDS('~/JournalWatchPBPath/articles.rds')


PMID_30228218 <- RefManageR::ReadPubMed('30228218', database = 'PubMed')

citation_30228218 <- paste0(PMID_30228218$journal,' ', PMID_30228218$year, ' ', PMID_30228218$month,';', PMID_30228218$volume,'(', PMID_30228218$number,'):', PMID_30228218$pages)

PubMed_30228218 <- paste0(PubMedString, PMID_30228218$eprint)

doi_30228218 <- paste0(doiString, PMID_30228218$doi)

dimensionBadge_30228218 <- paste0(dimensionString1, PMID_30228218$doi,dimensionString2)

altmetricBadge_30228218 <- paste0(altmetricString1, PMID_30228218$doi, altmetricString2 )

addthis_inline_30228218 <- paste0(addthis_String1, PMID_30228218$title , " PMID: 30228218" , addthis_String2)

Sys.sleep(1)


articles <- articles %>%

add_row(

ArticleCitation = PMID_30228218,
PMID = PMID_30228218$eprint,
Title = PMID_30228218$title,
# Author = PMID_30228218$author,
# Abstract = PMID_30228218$abstract,
Journal = PMID_30228218$journal,
Year = PMID_30228218$year,
Month = PMID_30228218$month,
# Volume = PMID_30228218$volume,
# Number = PMID_30228218$number,
# Pages = PMID_30228218$pages,
PubMedLink = paste0('https://www.ncbi.nlm.nih.gov/pubmed/?term=', PMID_30228218$eprint),
DoiNumber = PMID_30228218$doi,
DoiLink = paste0('https://doi.org/', PMID_30228218$doi),
Language = PMID_30228218$language,
ISSN = PMID_30228218$issn
) %>%

unique()


Sys.sleep(1)

saveRDS(articles, '~/JournalWatchPBPath/articles.rds')

```

<details open> <summary>
- **`r PMID_30228218$title`**
</summary> 

*`r citation_30228218`*

`r PubMed_30228218`

`r addthis_inline_30228218`

`r PMID_30228218$abstract`

`r doi_30228218`

`r dimensionBadge_30228218`

`r altmetricBadge_30228218`

</details>

---




---

```{r bileducts 31518056, include=FALSE}

articles <- readRDS('~/JournalWatchPBPath/articles.rds')


PMID_31518056 <- RefManageR::ReadPubMed('31518056', database = 'PubMed')

citation_31518056 <- paste0(PMID_31518056$journal,' ', PMID_31518056$year, ' ', PMID_31518056$month,';', PMID_31518056$volume,'(', PMID_31518056$number,'):', PMID_31518056$pages)

PubMed_31518056 <- paste0(PubMedString, PMID_31518056$eprint)

doi_31518056 <- paste0(doiString, PMID_31518056$doi)

dimensionBadge_31518056 <- paste0(dimensionString1, PMID_31518056$doi,dimensionString2)

altmetricBadge_31518056 <- paste0(altmetricString1, PMID_31518056$doi, altmetricString2 )

addthis_inline_31518056 <- paste0(addthis_String1, PMID_31518056$title , " PMID: 31518056" , addthis_String2)

Sys.sleep(1)


articles <- articles %>%

add_row(

ArticleCitation = PMID_31518056,
PMID = PMID_31518056$eprint,
Title = PMID_31518056$title,
# Author = PMID_31518056$author,
# Abstract = PMID_31518056$abstract,
Journal = PMID_31518056$journal,
Year = PMID_31518056$year,
Month = PMID_31518056$month,
# Volume = PMID_31518056$volume,
# Number = PMID_31518056$number,
# Pages = PMID_31518056$pages,
PubMedLink = paste0('https://www.ncbi.nlm.nih.gov/pubmed/?term=', PMID_31518056$eprint),
DoiNumber = PMID_31518056$doi,
DoiLink = paste0('https://doi.org/', PMID_31518056$doi),
Language = PMID_31518056$language,
ISSN = PMID_31518056$issn
) %>%

unique()


Sys.sleep(1)

saveRDS(articles, '~/JournalWatchPBPath/articles.rds')

```

<details open> <summary>
- **`r PMID_31518056$title`**
</summary> 

*`r citation_31518056`*

`r PubMed_31518056`

`r addthis_inline_31518056`

`r PMID_31518056$abstract`

`r doi_31518056`

`r dimensionBadge_31518056`

`r altmetricBadge_31518056`

</details>

---




---

```{r bileducts 31425486, include=FALSE}

articles <- readRDS('~/JournalWatchPBPath/articles.rds')


PMID_31425486 <- RefManageR::ReadPubMed('31425486', database = 'PubMed')

citation_31425486 <- paste0(PMID_31425486$journal,' ', PMID_31425486$year, ' ', PMID_31425486$month,';', PMID_31425486$volume,'(', PMID_31425486$number,'):', PMID_31425486$pages)

PubMed_31425486 <- paste0(PubMedString, PMID_31425486$eprint)

doi_31425486 <- paste0(doiString, PMID_31425486$doi)

dimensionBadge_31425486 <- paste0(dimensionString1, PMID_31425486$doi,dimensionString2)

altmetricBadge_31425486 <- paste0(altmetricString1, PMID_31425486$doi, altmetricString2 )

addthis_inline_31425486 <- paste0(addthis_String1, PMID_31425486$title , " PMID: 31425486" , addthis_String2)

Sys.sleep(1)


articles <- articles %>%

add_row(

ArticleCitation = PMID_31425486,
PMID = PMID_31425486$eprint,
Title = PMID_31425486$title,
# Author = PMID_31425486$author,
# Abstract = PMID_31425486$abstract,
Journal = PMID_31425486$journal,
Year = PMID_31425486$year,
Month = PMID_31425486$month,
# Volume = PMID_31425486$volume,
# Number = PMID_31425486$number,
# Pages = PMID_31425486$pages,
PubMedLink = paste0('https://www.ncbi.nlm.nih.gov/pubmed/?term=', PMID_31425486$eprint),
DoiNumber = PMID_31425486$doi,
DoiLink = paste0('https://doi.org/', PMID_31425486$doi),
Language = PMID_31425486$language,
ISSN = PMID_31425486$issn
) %>%

unique()


Sys.sleep(1)

saveRDS(articles, '~/JournalWatchPBPath/articles.rds')

```

<details open> <summary>
- **`r PMID_31425486$title`**
</summary> 

*`r citation_31425486`*

`r PubMed_31425486`

`r addthis_inline_31425486`

`r PMID_31425486$abstract`

`r doi_31425486`

`r dimensionBadge_31425486`

`r altmetricBadge_31425486`

</details>

---




---

```{r bileducts 31400934, include=FALSE}

articles <- readRDS('~/JournalWatchPBPath/articles.rds')


PMID_31400934 <- RefManageR::ReadPubMed('31400934', database = 'PubMed')

citation_31400934 <- paste0(PMID_31400934$journal,' ', PMID_31400934$year, ' ', PMID_31400934$month,';', PMID_31400934$volume,'(', PMID_31400934$number,'):', PMID_31400934$pages)

PubMed_31400934 <- paste0(PubMedString, PMID_31400934$eprint)

doi_31400934 <- paste0(doiString, PMID_31400934$doi)

dimensionBadge_31400934 <- paste0(dimensionString1, PMID_31400934$doi,dimensionString2)

altmetricBadge_31400934 <- paste0(altmetricString1, PMID_31400934$doi, altmetricString2 )

addthis_inline_31400934 <- paste0(addthis_String1, PMID_31400934$title , " PMID: 31400934" , addthis_String2)

Sys.sleep(1)


articles <- articles %>%

add_row(

ArticleCitation = PMID_31400934,
PMID = PMID_31400934$eprint,
Title = PMID_31400934$title,
# Author = PMID_31400934$author,
# Abstract = PMID_31400934$abstract,
Journal = PMID_31400934$journal,
Year = PMID_31400934$year,
Month = PMID_31400934$month,
# Volume = PMID_31400934$volume,
# Number = PMID_31400934$number,
# Pages = PMID_31400934$pages,
PubMedLink = paste0('https://www.ncbi.nlm.nih.gov/pubmed/?term=', PMID_31400934$eprint),
DoiNumber = PMID_31400934$doi,
DoiLink = paste0('https://doi.org/', PMID_31400934$doi),
Language = PMID_31400934$language,
ISSN = PMID_31400934$issn
) %>%

unique()


Sys.sleep(1)

saveRDS(articles, '~/JournalWatchPBPath/articles.rds')

```

<details open> <summary>
- **`r PMID_31400934$title`**
</summary> 

*`r citation_31400934`*

`r PubMed_31400934`

`r addthis_inline_31400934`

`r PMID_31400934$abstract`

`r doi_31400934`

`r dimensionBadge_31400934`

`r altmetricBadge_31400934`

</details>

---




---

```{r bileducts 31378393, include=FALSE}

articles <- readRDS('~/JournalWatchPBPath/articles.rds')


PMID_31378393 <- RefManageR::ReadPubMed('31378393', database = 'PubMed')

citation_31378393 <- paste0(PMID_31378393$journal,' ', PMID_31378393$year, ' ', PMID_31378393$month,';', PMID_31378393$volume,'(', PMID_31378393$number,'):', PMID_31378393$pages)

PubMed_31378393 <- paste0(PubMedString, PMID_31378393$eprint)

doi_31378393 <- paste0(doiString, PMID_31378393$doi)

dimensionBadge_31378393 <- paste0(dimensionString1, PMID_31378393$doi,dimensionString2)

altmetricBadge_31378393 <- paste0(altmetricString1, PMID_31378393$doi, altmetricString2 )

addthis_inline_31378393 <- paste0(addthis_String1, PMID_31378393$title , " PMID: 31378393" , addthis_String2)

Sys.sleep(1)


articles <- articles %>%

add_row(

ArticleCitation = PMID_31378393,
PMID = PMID_31378393$eprint,
Title = PMID_31378393$title,
# Author = PMID_31378393$author,
# Abstract = PMID_31378393$abstract,
Journal = PMID_31378393$journal,
Year = PMID_31378393$year,
Month = PMID_31378393$month,
# Volume = PMID_31378393$volume,
# Number = PMID_31378393$number,
# Pages = PMID_31378393$pages,
PubMedLink = paste0('https://www.ncbi.nlm.nih.gov/pubmed/?term=', PMID_31378393$eprint),
DoiNumber = PMID_31378393$doi,
DoiLink = paste0('https://doi.org/', PMID_31378393$doi),
Language = PMID_31378393$language,
ISSN = PMID_31378393$issn
) %>%

unique()


Sys.sleep(1)

saveRDS(articles, '~/JournalWatchPBPath/articles.rds')

```

<details open> <summary>
- **`r PMID_31378393$title`**
</summary> 

*`r citation_31378393`*

`r PubMed_31378393`

`r addthis_inline_31378393`

`r PMID_31378393$abstract`

`r doi_31378393`

`r dimensionBadge_31378393`

`r altmetricBadge_31378393`

</details>

---




---

```{r bileducts 31377276, include=FALSE}

articles <- readRDS('~/JournalWatchPBPath/articles.rds')


PMID_31377276 <- RefManageR::ReadPubMed('31377276', database = 'PubMed')

citation_31377276 <- paste0(PMID_31377276$journal,' ', PMID_31377276$year, ' ', PMID_31377276$month,';', PMID_31377276$volume,'(', PMID_31377276$number,'):', PMID_31377276$pages)

PubMed_31377276 <- paste0(PubMedString, PMID_31377276$eprint)

doi_31377276 <- paste0(doiString, PMID_31377276$doi)

dimensionBadge_31377276 <- paste0(dimensionString1, PMID_31377276$doi,dimensionString2)

altmetricBadge_31377276 <- paste0(altmetricString1, PMID_31377276$doi, altmetricString2 )

addthis_inline_31377276 <- paste0(addthis_String1, PMID_31377276$title , " PMID: 31377276" , addthis_String2)

Sys.sleep(1)


articles <- articles %>%

add_row(

ArticleCitation = PMID_31377276,
PMID = PMID_31377276$eprint,
Title = PMID_31377276$title,
# Author = PMID_31377276$author,
# Abstract = PMID_31377276$abstract,
Journal = PMID_31377276$journal,
Year = PMID_31377276$year,
Month = PMID_31377276$month,
# Volume = PMID_31377276$volume,
# Number = PMID_31377276$number,
# Pages = PMID_31377276$pages,
PubMedLink = paste0('https://www.ncbi.nlm.nih.gov/pubmed/?term=', PMID_31377276$eprint),
DoiNumber = PMID_31377276$doi,
DoiLink = paste0('https://doi.org/', PMID_31377276$doi),
Language = PMID_31377276$language,
ISSN = PMID_31377276$issn
) %>%

unique()


Sys.sleep(1)

saveRDS(articles, '~/JournalWatchPBPath/articles.rds')

```

<details open> <summary>
- **`r PMID_31377276$title`**
</summary> 

*`r citation_31377276`*

`r PubMed_31377276`

`r addthis_inline_31377276`

`r PMID_31377276$abstract`

`r doi_31377276`

`r dimensionBadge_31377276`

`r altmetricBadge_31377276`

</details>

---




---

```{r bileducts 31240450, include=FALSE}

articles <- readRDS('~/JournalWatchPBPath/articles.rds')


PMID_31240450 <- RefManageR::ReadPubMed('31240450', database = 'PubMed')

citation_31240450 <- paste0(PMID_31240450$journal,' ', PMID_31240450$year, ' ', PMID_31240450$month,';', PMID_31240450$volume,'(', PMID_31240450$number,'):', PMID_31240450$pages)

PubMed_31240450 <- paste0(PubMedString, PMID_31240450$eprint)

doi_31240450 <- paste0(doiString, PMID_31240450$doi)

dimensionBadge_31240450 <- paste0(dimensionString1, PMID_31240450$doi,dimensionString2)

altmetricBadge_31240450 <- paste0(altmetricString1, PMID_31240450$doi, altmetricString2 )

addthis_inline_31240450 <- paste0(addthis_String1, PMID_31240450$title , " PMID: 31240450" , addthis_String2)

Sys.sleep(1)


articles <- articles %>%

add_row(

ArticleCitation = PMID_31240450,
PMID = PMID_31240450$eprint,
Title = PMID_31240450$title,
# Author = PMID_31240450$author,
# Abstract = PMID_31240450$abstract,
Journal = PMID_31240450$journal,
Year = PMID_31240450$year,
Month = PMID_31240450$month,
# Volume = PMID_31240450$volume,
# Number = PMID_31240450$number,
# Pages = PMID_31240450$pages,
PubMedLink = paste0('https://www.ncbi.nlm.nih.gov/pubmed/?term=', PMID_31240450$eprint),
DoiNumber = PMID_31240450$doi,
DoiLink = paste0('https://doi.org/', PMID_31240450$doi),
Language = PMID_31240450$language,
ISSN = PMID_31240450$issn
) %>%

unique()


Sys.sleep(1)

saveRDS(articles, '~/JournalWatchPBPath/articles.rds')

```

<details open> <summary>
- **`r PMID_31240450$title`**
</summary> 

*`r citation_31240450`*

`r PubMed_31240450`

`r addthis_inline_31240450`

`r PMID_31240450$abstract`

`r doi_31240450`

`r dimensionBadge_31240450`

`r altmetricBadge_31240450`

</details>

---




---

```{r bileducts 31170413, include=FALSE}

articles <- readRDS('~/JournalWatchPBPath/articles.rds')


PMID_31170413 <- RefManageR::ReadPubMed('31170413', database = 'PubMed')

citation_31170413 <- paste0(PMID_31170413$journal,' ', PMID_31170413$year, ' ', PMID_31170413$month,';', PMID_31170413$volume,'(', PMID_31170413$number,'):', PMID_31170413$pages)

PubMed_31170413 <- paste0(PubMedString, PMID_31170413$eprint)

doi_31170413 <- paste0(doiString, PMID_31170413$doi)

dimensionBadge_31170413 <- paste0(dimensionString1, PMID_31170413$doi,dimensionString2)

altmetricBadge_31170413 <- paste0(altmetricString1, PMID_31170413$doi, altmetricString2 )

addthis_inline_31170413 <- paste0(addthis_String1, PMID_31170413$title , " PMID: 31170413" , addthis_String2)

Sys.sleep(1)


articles <- articles %>%

add_row(

ArticleCitation = PMID_31170413,
PMID = PMID_31170413$eprint,
Title = PMID_31170413$title,
# Author = PMID_31170413$author,
# Abstract = PMID_31170413$abstract,
Journal = PMID_31170413$journal,
Year = PMID_31170413$year,
Month = PMID_31170413$month,
# Volume = PMID_31170413$volume,
# Number = PMID_31170413$number,
# Pages = PMID_31170413$pages,
PubMedLink = paste0('https://www.ncbi.nlm.nih.gov/pubmed/?term=', PMID_31170413$eprint),
DoiNumber = PMID_31170413$doi,
DoiLink = paste0('https://doi.org/', PMID_31170413$doi),
Language = PMID_31170413$language,
ISSN = PMID_31170413$issn
) %>%

unique()


Sys.sleep(1)

saveRDS(articles, '~/JournalWatchPBPath/articles.rds')

```

<details open> <summary>
- **`r PMID_31170413$title`**
</summary> 

*`r citation_31170413`*

`r PubMed_31170413`

`r addthis_inline_31170413`

`r PMID_31170413$abstract`

`r doi_31170413`

`r dimensionBadge_31170413`

`r altmetricBadge_31170413`

</details>

---




---

```{r bileducts 31166202, include=FALSE}

articles <- readRDS('~/JournalWatchPBPath/articles.rds')


PMID_31166202 <- RefManageR::ReadPubMed('31166202', database = 'PubMed')

citation_31166202 <- paste0(PMID_31166202$journal,' ', PMID_31166202$year, ' ', PMID_31166202$month,';', PMID_31166202$volume,'(', PMID_31166202$number,'):', PMID_31166202$pages)

PubMed_31166202 <- paste0(PubMedString, PMID_31166202$eprint)

doi_31166202 <- paste0(doiString, PMID_31166202$doi)

dimensionBadge_31166202 <- paste0(dimensionString1, PMID_31166202$doi,dimensionString2)

altmetricBadge_31166202 <- paste0(altmetricString1, PMID_31166202$doi, altmetricString2 )

addthis_inline_31166202 <- paste0(addthis_String1, PMID_31166202$title , " PMID: 31166202" , addthis_String2)

Sys.sleep(1)


articles <- articles %>%

add_row(

ArticleCitation = PMID_31166202,
PMID = PMID_31166202$eprint,
Title = PMID_31166202$title,
# Author = PMID_31166202$author,
# Abstract = PMID_31166202$abstract,
Journal = PMID_31166202$journal,
Year = PMID_31166202$year,
Month = PMID_31166202$month,
# Volume = PMID_31166202$volume,
# Number = PMID_31166202$number,
# Pages = PMID_31166202$pages,
PubMedLink = paste0('https://www.ncbi.nlm.nih.gov/pubmed/?term=', PMID_31166202$eprint),
DoiNumber = PMID_31166202$doi,
DoiLink = paste0('https://doi.org/', PMID_31166202$doi),
Language = PMID_31166202$language,
ISSN = PMID_31166202$issn
) %>%

unique()


Sys.sleep(1)

saveRDS(articles, '~/JournalWatchPBPath/articles.rds')

```

<details open> <summary>
- **`r PMID_31166202$title`**
</summary> 

*`r citation_31166202`*

`r PubMed_31166202`

`r addthis_inline_31166202`

`r PMID_31166202$abstract`

`r doi_31166202`

`r dimensionBadge_31166202`

`r altmetricBadge_31166202`

</details>

---




---

```{r bileducts 31147989, include=FALSE}

articles <- readRDS('~/JournalWatchPBPath/articles.rds')


PMID_31147989 <- RefManageR::ReadPubMed('31147989', database = 'PubMed')

citation_31147989 <- paste0(PMID_31147989$journal,' ', PMID_31147989$year, ' ', PMID_31147989$month,';', PMID_31147989$volume,'(', PMID_31147989$number,'):', PMID_31147989$pages)

PubMed_31147989 <- paste0(PubMedString, PMID_31147989$eprint)

doi_31147989 <- paste0(doiString, PMID_31147989$doi)

dimensionBadge_31147989 <- paste0(dimensionString1, PMID_31147989$doi,dimensionString2)

altmetricBadge_31147989 <- paste0(altmetricString1, PMID_31147989$doi, altmetricString2 )

addthis_inline_31147989 <- paste0(addthis_String1, PMID_31147989$title , " PMID: 31147989" , addthis_String2)

Sys.sleep(1)


articles <- articles %>%

add_row(

ArticleCitation = PMID_31147989,
PMID = PMID_31147989$eprint,
Title = PMID_31147989$title,
# Author = PMID_31147989$author,
# Abstract = PMID_31147989$abstract,
Journal = PMID_31147989$journal,
Year = PMID_31147989$year,
Month = PMID_31147989$month,
# Volume = PMID_31147989$volume,
# Number = PMID_31147989$number,
# Pages = PMID_31147989$pages,
PubMedLink = paste0('https://www.ncbi.nlm.nih.gov/pubmed/?term=', PMID_31147989$eprint),
DoiNumber = PMID_31147989$doi,
DoiLink = paste0('https://doi.org/', PMID_31147989$doi),
Language = PMID_31147989$language,
ISSN = PMID_31147989$issn
) %>%

unique()


Sys.sleep(1)

saveRDS(articles, '~/JournalWatchPBPath/articles.rds')

```

<details open> <summary>
- **`r PMID_31147989$title`**
</summary> 

*`r citation_31147989`*

`r PubMed_31147989`

`r addthis_inline_31147989`

`r PMID_31147989$abstract`

`r doi_31147989`

`r dimensionBadge_31147989`

`r altmetricBadge_31147989`

</details>

---




---

```{r bileducts 31116517, include=FALSE}

articles <- readRDS('~/JournalWatchPBPath/articles.rds')


PMID_31116517 <- RefManageR::ReadPubMed('31116517', database = 'PubMed')

citation_31116517 <- paste0(PMID_31116517$journal,' ', PMID_31116517$year, ' ', PMID_31116517$month,';', PMID_31116517$volume,'(', PMID_31116517$number,'):', PMID_31116517$pages)

PubMed_31116517 <- paste0(PubMedString, PMID_31116517$eprint)

doi_31116517 <- paste0(doiString, PMID_31116517$doi)

dimensionBadge_31116517 <- paste0(dimensionString1, PMID_31116517$doi,dimensionString2)

altmetricBadge_31116517 <- paste0(altmetricString1, PMID_31116517$doi, altmetricString2 )

addthis_inline_31116517 <- paste0(addthis_String1, PMID_31116517$title , " PMID: 31116517" , addthis_String2)

Sys.sleep(1)


articles <- articles %>%

add_row(

ArticleCitation = PMID_31116517,
PMID = PMID_31116517$eprint,
Title = PMID_31116517$title,
# Author = PMID_31116517$author,
# Abstract = PMID_31116517$abstract,
Journal = PMID_31116517$journal,
Year = PMID_31116517$year,
Month = PMID_31116517$month,
# Volume = PMID_31116517$volume,
# Number = PMID_31116517$number,
# Pages = PMID_31116517$pages,
PubMedLink = paste0('https://www.ncbi.nlm.nih.gov/pubmed/?term=', PMID_31116517$eprint),
DoiNumber = PMID_31116517$doi,
DoiLink = paste0('https://doi.org/', PMID_31116517$doi),
Language = PMID_31116517$language,
ISSN = PMID_31116517$issn
) %>%

unique()


Sys.sleep(1)

saveRDS(articles, '~/JournalWatchPBPath/articles.rds')

```

<details open> <summary>
- **`r PMID_31116517$title`**
</summary> 

*`r citation_31116517`*

`r PubMed_31116517`

`r addthis_inline_31116517`

`r PMID_31116517$abstract`

`r doi_31116517`

`r dimensionBadge_31116517`

`r altmetricBadge_31116517`

</details>

---




---

```{r bileducts 31033491, include=FALSE}

articles <- readRDS('~/JournalWatchPBPath/articles.rds')


PMID_31033491 <- RefManageR::ReadPubMed('31033491', database = 'PubMed')

citation_31033491 <- paste0(PMID_31033491$journal,' ', PMID_31033491$year, ' ', PMID_31033491$month,';', PMID_31033491$volume,'(', PMID_31033491$number,'):', PMID_31033491$pages)

PubMed_31033491 <- paste0(PubMedString, PMID_31033491$eprint)

doi_31033491 <- paste0(doiString, PMID_31033491$doi)

dimensionBadge_31033491 <- paste0(dimensionString1, PMID_31033491$doi,dimensionString2)

altmetricBadge_31033491 <- paste0(altmetricString1, PMID_31033491$doi, altmetricString2 )

addthis_inline_31033491 <- paste0(addthis_String1, PMID_31033491$title , " PMID: 31033491" , addthis_String2)

Sys.sleep(1)


articles <- articles %>%

add_row(

ArticleCitation = PMID_31033491,
PMID = PMID_31033491$eprint,
Title = PMID_31033491$title,
# Author = PMID_31033491$author,
# Abstract = PMID_31033491$abstract,
Journal = PMID_31033491$journal,
Year = PMID_31033491$year,
Month = PMID_31033491$month,
# Volume = PMID_31033491$volume,
# Number = PMID_31033491$number,
# Pages = PMID_31033491$pages,
PubMedLink = paste0('https://www.ncbi.nlm.nih.gov/pubmed/?term=', PMID_31033491$eprint),
DoiNumber = PMID_31033491$doi,
DoiLink = paste0('https://doi.org/', PMID_31033491$doi),
Language = PMID_31033491$language,
ISSN = PMID_31033491$issn
) %>%

unique()


Sys.sleep(1)

saveRDS(articles, '~/JournalWatchPBPath/articles.rds')

```

<details open> <summary>
- **`r PMID_31033491$title`**
</summary> 

*`r citation_31033491`*

`r PubMed_31033491`

`r addthis_inline_31033491`

`r PMID_31033491$abstract`

`r doi_31033491`

`r dimensionBadge_31033491`

`r altmetricBadge_31033491`

</details>

---




---

```{r bileducts 30615872, include=FALSE}

articles <- readRDS('~/JournalWatchPBPath/articles.rds')


PMID_30615872 <- RefManageR::ReadPubMed('30615872', database = 'PubMed')

citation_30615872 <- paste0(PMID_30615872$journal,' ', PMID_30615872$year, ' ', PMID_30615872$month,';', PMID_30615872$volume,'(', PMID_30615872$number,'):', PMID_30615872$pages)

PubMed_30615872 <- paste0(PubMedString, PMID_30615872$eprint)

doi_30615872 <- paste0(doiString, PMID_30615872$doi)

dimensionBadge_30615872 <- paste0(dimensionString1, PMID_30615872$doi,dimensionString2)

altmetricBadge_30615872 <- paste0(altmetricString1, PMID_30615872$doi, altmetricString2 )

addthis_inline_30615872 <- paste0(addthis_String1, PMID_30615872$title , " PMID: 30615872" , addthis_String2)

Sys.sleep(1)


articles <- articles %>%

add_row(

ArticleCitation = PMID_30615872,
PMID = PMID_30615872$eprint,
Title = PMID_30615872$title,
# Author = PMID_30615872$author,
# Abstract = PMID_30615872$abstract,
Journal = PMID_30615872$journal,
Year = PMID_30615872$year,
Month = PMID_30615872$month,
# Volume = PMID_30615872$volume,
# Number = PMID_30615872$number,
# Pages = PMID_30615872$pages,
PubMedLink = paste0('https://www.ncbi.nlm.nih.gov/pubmed/?term=', PMID_30615872$eprint),
DoiNumber = PMID_30615872$doi,
DoiLink = paste0('https://doi.org/', PMID_30615872$doi),
Language = PMID_30615872$language,
ISSN = PMID_30615872$issn
) %>%

unique()


Sys.sleep(1)

saveRDS(articles, '~/JournalWatchPBPath/articles.rds')

```

<details open> <summary>
- **`r PMID_30615872$title`**
</summary> 

*`r citation_30615872`*

`r PubMed_30615872`

`r addthis_inline_30615872`

`r PMID_30615872$abstract`

`r doi_30615872`

`r dimensionBadge_30615872`

`r altmetricBadge_30615872`

</details>

---




---

```{r bileducts 31454426, include=FALSE}

articles <- readRDS('~/JournalWatchPBPath/articles.rds')


PMID_31454426 <- RefManageR::ReadPubMed('31454426', database = 'PubMed')

citation_31454426 <- paste0(PMID_31454426$journal,' ', PMID_31454426$year, ' ', PMID_31454426$month,';', PMID_31454426$volume,'(', PMID_31454426$number,'):', PMID_31454426$pages)

PubMed_31454426 <- paste0(PubMedString, PMID_31454426$eprint)

doi_31454426 <- paste0(doiString, PMID_31454426$doi)

dimensionBadge_31454426 <- paste0(dimensionString1, PMID_31454426$doi,dimensionString2)

altmetricBadge_31454426 <- paste0(altmetricString1, PMID_31454426$doi, altmetricString2 )

addthis_inline_31454426 <- paste0(addthis_String1, PMID_31454426$title , " PMID: 31454426" , addthis_String2)

Sys.sleep(1)


articles <- articles %>%

add_row(

ArticleCitation = PMID_31454426,
PMID = PMID_31454426$eprint,
Title = PMID_31454426$title,
# Author = PMID_31454426$author,
# Abstract = PMID_31454426$abstract,
Journal = PMID_31454426$journal,
Year = PMID_31454426$year,
Month = PMID_31454426$month,
# Volume = PMID_31454426$volume,
# Number = PMID_31454426$number,
# Pages = PMID_31454426$pages,
PubMedLink = paste0('https://www.ncbi.nlm.nih.gov/pubmed/?term=', PMID_31454426$eprint),
DoiNumber = PMID_31454426$doi,
DoiLink = paste0('https://doi.org/', PMID_31454426$doi),
Language = PMID_31454426$language,
ISSN = PMID_31454426$issn
) %>%

unique()


Sys.sleep(1)

saveRDS(articles, '~/JournalWatchPBPath/articles.rds')

```

<details open> <summary>
- **`r PMID_31454426$title`**
</summary> 

*`r citation_31454426`*

`r PubMed_31454426`

`r addthis_inline_31454426`

`r PMID_31454426$abstract`

`r doi_31454426`

`r dimensionBadge_31454426`

`r altmetricBadge_31454426`

</details>

---




---

```{r bileducts 31437071, include=FALSE}

articles <- readRDS('~/JournalWatchPBPath/articles.rds')


PMID_31437071 <- RefManageR::ReadPubMed('31437071', database = 'PubMed')

citation_31437071 <- paste0(PMID_31437071$journal,' ', PMID_31437071$year, ' ', PMID_31437071$month,';', PMID_31437071$volume,'(', PMID_31437071$number,'):', PMID_31437071$pages)

PubMed_31437071 <- paste0(PubMedString, PMID_31437071$eprint)

doi_31437071 <- paste0(doiString, PMID_31437071$doi)

dimensionBadge_31437071 <- paste0(dimensionString1, PMID_31437071$doi,dimensionString2)

altmetricBadge_31437071 <- paste0(altmetricString1, PMID_31437071$doi, altmetricString2 )

addthis_inline_31437071 <- paste0(addthis_String1, PMID_31437071$title , " PMID: 31437071" , addthis_String2)

Sys.sleep(1)


articles <- articles %>%

add_row(

ArticleCitation = PMID_31437071,
PMID = PMID_31437071$eprint,
Title = PMID_31437071$title,
# Author = PMID_31437071$author,
# Abstract = PMID_31437071$abstract,
Journal = PMID_31437071$journal,
Year = PMID_31437071$year,
Month = PMID_31437071$month,
# Volume = PMID_31437071$volume,
# Number = PMID_31437071$number,
# Pages = PMID_31437071$pages,
PubMedLink = paste0('https://www.ncbi.nlm.nih.gov/pubmed/?term=', PMID_31437071$eprint),
DoiNumber = PMID_31437071$doi,
DoiLink = paste0('https://doi.org/', PMID_31437071$doi),
Language = PMID_31437071$language,
ISSN = PMID_31437071$issn
) %>%

unique()


Sys.sleep(1)

saveRDS(articles, '~/JournalWatchPBPath/articles.rds')

```

<details open> <summary>
- **`r PMID_31437071$title`**
</summary> 

*`r citation_31437071`*

`r PubMed_31437071`

`r addthis_inline_31437071`

`r PMID_31437071$abstract`

`r doi_31437071`

`r dimensionBadge_31437071`

`r altmetricBadge_31437071`

</details>

---




---

```{r bileducts 31433924, include=FALSE}

articles <- readRDS('~/JournalWatchPBPath/articles.rds')


PMID_31433924 <- RefManageR::ReadPubMed('31433924', database = 'PubMed')

citation_31433924 <- paste0(PMID_31433924$journal,' ', PMID_31433924$year, ' ', PMID_31433924$month,';', PMID_31433924$volume,'(', PMID_31433924$number,'):', PMID_31433924$pages)

PubMed_31433924 <- paste0(PubMedString, PMID_31433924$eprint)

doi_31433924 <- paste0(doiString, PMID_31433924$doi)

dimensionBadge_31433924 <- paste0(dimensionString1, PMID_31433924$doi,dimensionString2)

altmetricBadge_31433924 <- paste0(altmetricString1, PMID_31433924$doi, altmetricString2 )

addthis_inline_31433924 <- paste0(addthis_String1, PMID_31433924$title , " PMID: 31433924" , addthis_String2)

Sys.sleep(1)


articles <- articles %>%

add_row(

ArticleCitation = PMID_31433924,
PMID = PMID_31433924$eprint,
Title = PMID_31433924$title,
# Author = PMID_31433924$author,
# Abstract = PMID_31433924$abstract,
Journal = PMID_31433924$journal,
Year = PMID_31433924$year,
Month = PMID_31433924$month,
# Volume = PMID_31433924$volume,
# Number = PMID_31433924$number,
# Pages = PMID_31433924$pages,
PubMedLink = paste0('https://www.ncbi.nlm.nih.gov/pubmed/?term=', PMID_31433924$eprint),
DoiNumber = PMID_31433924$doi,
DoiLink = paste0('https://doi.org/', PMID_31433924$doi),
Language = PMID_31433924$language,
ISSN = PMID_31433924$issn
) %>%

unique()


Sys.sleep(1)

saveRDS(articles, '~/JournalWatchPBPath/articles.rds')

```

<details open> <summary>
- **`r PMID_31433924$title`**
</summary> 

*`r citation_31433924`*

`r PubMed_31433924`

`r addthis_inline_31433924`

`r PMID_31433924$abstract`

`r doi_31433924`

`r dimensionBadge_31433924`

`r altmetricBadge_31433924`

</details>

---




---

```{r bileducts 31272691, include=FALSE}

articles <- readRDS('~/JournalWatchPBPath/articles.rds')


PMID_31272691 <- RefManageR::ReadPubMed('31272691', database = 'PubMed')

citation_31272691 <- paste0(PMID_31272691$journal,' ', PMID_31272691$year, ' ', PMID_31272691$month,';', PMID_31272691$volume,'(', PMID_31272691$number,'):', PMID_31272691$pages)

PubMed_31272691 <- paste0(PubMedString, PMID_31272691$eprint)

doi_31272691 <- paste0(doiString, PMID_31272691$doi)

dimensionBadge_31272691 <- paste0(dimensionString1, PMID_31272691$doi,dimensionString2)

altmetricBadge_31272691 <- paste0(altmetricString1, PMID_31272691$doi, altmetricString2 )

addthis_inline_31272691 <- paste0(addthis_String1, PMID_31272691$title , " PMID: 31272691" , addthis_String2)

Sys.sleep(1)


articles <- articles %>%

add_row(

ArticleCitation = PMID_31272691,
PMID = PMID_31272691$eprint,
Title = PMID_31272691$title,
# Author = PMID_31272691$author,
# Abstract = PMID_31272691$abstract,
Journal = PMID_31272691$journal,
Year = PMID_31272691$year,
Month = PMID_31272691$month,
# Volume = PMID_31272691$volume,
# Number = PMID_31272691$number,
# Pages = PMID_31272691$pages,
PubMedLink = paste0('https://www.ncbi.nlm.nih.gov/pubmed/?term=', PMID_31272691$eprint),
DoiNumber = PMID_31272691$doi,
DoiLink = paste0('https://doi.org/', PMID_31272691$doi),
Language = PMID_31272691$language,
ISSN = PMID_31272691$issn
) %>%

unique()


Sys.sleep(1)

saveRDS(articles, '~/JournalWatchPBPath/articles.rds')

```

<details open> <summary>
- **`r PMID_31272691$title`**
</summary> 

*`r citation_31272691`*

`r PubMed_31272691`

`r addthis_inline_31272691`

`r PMID_31272691$abstract`

`r doi_31272691`

`r dimensionBadge_31272691`

`r altmetricBadge_31272691`

</details>

---




---

```{r bileducts 31272690, include=FALSE}

articles <- readRDS('~/JournalWatchPBPath/articles.rds')


PMID_31272690 <- RefManageR::ReadPubMed('31272690', database = 'PubMed')

citation_31272690 <- paste0(PMID_31272690$journal,' ', PMID_31272690$year, ' ', PMID_31272690$month,';', PMID_31272690$volume,'(', PMID_31272690$number,'):', PMID_31272690$pages)

PubMed_31272690 <- paste0(PubMedString, PMID_31272690$eprint)

doi_31272690 <- paste0(doiString, PMID_31272690$doi)

dimensionBadge_31272690 <- paste0(dimensionString1, PMID_31272690$doi,dimensionString2)

altmetricBadge_31272690 <- paste0(altmetricString1, PMID_31272690$doi, altmetricString2 )

addthis_inline_31272690 <- paste0(addthis_String1, PMID_31272690$title , " PMID: 31272690" , addthis_String2)

Sys.sleep(1)


articles <- articles %>%

add_row(

ArticleCitation = PMID_31272690,
PMID = PMID_31272690$eprint,
Title = PMID_31272690$title,
# Author = PMID_31272690$author,
# Abstract = PMID_31272690$abstract,
Journal = PMID_31272690$journal,
Year = PMID_31272690$year,
Month = PMID_31272690$month,
# Volume = PMID_31272690$volume,
# Number = PMID_31272690$number,
# Pages = PMID_31272690$pages,
PubMedLink = paste0('https://www.ncbi.nlm.nih.gov/pubmed/?term=', PMID_31272690$eprint),
DoiNumber = PMID_31272690$doi,
DoiLink = paste0('https://doi.org/', PMID_31272690$doi),
Language = PMID_31272690$language,
ISSN = PMID_31272690$issn
) %>%

unique()


Sys.sleep(1)

saveRDS(articles, '~/JournalWatchPBPath/articles.rds')

```

<details open> <summary>
- **`r PMID_31272690$title`**
</summary> 

*`r citation_31272690`*

`r PubMed_31272690`

`r addthis_inline_31272690`

`r PMID_31272690$abstract`

`r doi_31272690`

`r dimensionBadge_31272690`

`r altmetricBadge_31272690`

</details>

---




---

```{r bileducts 31409605, include=FALSE}

articles <- readRDS('~/JournalWatchPBPath/articles.rds')


PMID_31409605 <- RefManageR::ReadPubMed('31409605', database = 'PubMed')

citation_31409605 <- paste0(PMID_31409605$journal,' ', PMID_31409605$year, ' ', PMID_31409605$month,';', PMID_31409605$volume,'(', PMID_31409605$number,'):', PMID_31409605$pages)

PubMed_31409605 <- paste0(PubMedString, PMID_31409605$eprint)

doi_31409605 <- paste0(doiString, PMID_31409605$doi)

dimensionBadge_31409605 <- paste0(dimensionString1, PMID_31409605$doi,dimensionString2)

altmetricBadge_31409605 <- paste0(altmetricString1, PMID_31409605$doi, altmetricString2 )

addthis_inline_31409605 <- paste0(addthis_String1, PMID_31409605$title , " PMID: 31409605" , addthis_String2)

Sys.sleep(1)


articles <- articles %>%

add_row(

ArticleCitation = PMID_31409605,
PMID = PMID_31409605$eprint,
Title = PMID_31409605$title,
# Author = PMID_31409605$author,
# Abstract = PMID_31409605$abstract,
Journal = PMID_31409605$journal,
Year = PMID_31409605$year,
Month = PMID_31409605$month,
# Volume = PMID_31409605$volume,
# Number = PMID_31409605$number,
# Pages = PMID_31409605$pages,
PubMedLink = paste0('https://www.ncbi.nlm.nih.gov/pubmed/?term=', PMID_31409605$eprint),
DoiNumber = PMID_31409605$doi,
DoiLink = paste0('https://doi.org/', PMID_31409605$doi),
Language = PMID_31409605$language,
ISSN = PMID_31409605$issn
) %>%

unique()


Sys.sleep(1)

saveRDS(articles, '~/JournalWatchPBPath/articles.rds')

```

<details open> <summary>
- **`r PMID_31409605$title`**
</summary> 

*`r citation_31409605`*

`r PubMed_31409605`

`r addthis_inline_31409605`

`r PMID_31409605$abstract`

`r doi_31409605`

`r dimensionBadge_31409605`

`r altmetricBadge_31409605`

</details>

---




---

```{r bileducts 31395017, include=FALSE}

articles <- readRDS('~/JournalWatchPBPath/articles.rds')


PMID_31395017 <- RefManageR::ReadPubMed('31395017', database = 'PubMed')

citation_31395017 <- paste0(PMID_31395017$journal,' ', PMID_31395017$year, ' ', PMID_31395017$month,';', PMID_31395017$volume,'(', PMID_31395017$number,'):', PMID_31395017$pages)

PubMed_31395017 <- paste0(PubMedString, PMID_31395017$eprint)

doi_31395017 <- paste0(doiString, PMID_31395017$doi)

dimensionBadge_31395017 <- paste0(dimensionString1, PMID_31395017$doi,dimensionString2)

altmetricBadge_31395017 <- paste0(altmetricString1, PMID_31395017$doi, altmetricString2 )

addthis_inline_31395017 <- paste0(addthis_String1, PMID_31395017$title , " PMID: 31395017" , addthis_String2)

Sys.sleep(1)


articles <- articles %>%

add_row(

ArticleCitation = PMID_31395017,
PMID = PMID_31395017$eprint,
Title = PMID_31395017$title,
# Author = PMID_31395017$author,
# Abstract = PMID_31395017$abstract,
Journal = PMID_31395017$journal,
Year = PMID_31395017$year,
Month = PMID_31395017$month,
# Volume = PMID_31395017$volume,
# Number = PMID_31395017$number,
# Pages = PMID_31395017$pages,
PubMedLink = paste0('https://www.ncbi.nlm.nih.gov/pubmed/?term=', PMID_31395017$eprint),
DoiNumber = PMID_31395017$doi,
DoiLink = paste0('https://doi.org/', PMID_31395017$doi),
Language = PMID_31395017$language,
ISSN = PMID_31395017$issn
) %>%

unique()


Sys.sleep(1)

saveRDS(articles, '~/JournalWatchPBPath/articles.rds')

```

<details open> <summary>
- **`r PMID_31395017$title`**
</summary> 

*`r citation_31395017`*

`r PubMed_31395017`

`r addthis_inline_31395017`

`r PMID_31395017$abstract`

`r doi_31395017`

`r dimensionBadge_31395017`

`r altmetricBadge_31395017`

</details>

---




---

```{r bileducts 31382888, include=FALSE}

articles <- readRDS('~/JournalWatchPBPath/articles.rds')


PMID_31382888 <- RefManageR::ReadPubMed('31382888', database = 'PubMed')

citation_31382888 <- paste0(PMID_31382888$journal,' ', PMID_31382888$year, ' ', PMID_31382888$month,';', PMID_31382888$volume,'(', PMID_31382888$number,'):', PMID_31382888$pages)

PubMed_31382888 <- paste0(PubMedString, PMID_31382888$eprint)

doi_31382888 <- paste0(doiString, PMID_31382888$doi)

dimensionBadge_31382888 <- paste0(dimensionString1, PMID_31382888$doi,dimensionString2)

altmetricBadge_31382888 <- paste0(altmetricString1, PMID_31382888$doi, altmetricString2 )

addthis_inline_31382888 <- paste0(addthis_String1, PMID_31382888$title , " PMID: 31382888" , addthis_String2)

Sys.sleep(1)


articles <- articles %>%

add_row(

ArticleCitation = PMID_31382888,
PMID = PMID_31382888$eprint,
Title = PMID_31382888$title,
# Author = PMID_31382888$author,
# Abstract = PMID_31382888$abstract,
Journal = PMID_31382888$journal,
Year = PMID_31382888$year,
Month = PMID_31382888$month,
# Volume = PMID_31382888$volume,
# Number = PMID_31382888$number,
# Pages = PMID_31382888$pages,
PubMedLink = paste0('https://www.ncbi.nlm.nih.gov/pubmed/?term=', PMID_31382888$eprint),
DoiNumber = PMID_31382888$doi,
DoiLink = paste0('https://doi.org/', PMID_31382888$doi),
Language = PMID_31382888$language,
ISSN = PMID_31382888$issn
) %>%

unique()


Sys.sleep(1)

saveRDS(articles, '~/JournalWatchPBPath/articles.rds')

```

<details open> <summary>
- **`r PMID_31382888$title`**
</summary> 

*`r citation_31382888`*

`r PubMed_31382888`

`r addthis_inline_31382888`

`r PMID_31382888$abstract`

`r doi_31382888`

`r dimensionBadge_31382888`

`r altmetricBadge_31382888`

</details>

---




---

```{r bileducts 31154395, include=FALSE}

articles <- readRDS('~/JournalWatchPBPath/articles.rds')


PMID_31154395 <- RefManageR::ReadPubMed('31154395', database = 'PubMed')

citation_31154395 <- paste0(PMID_31154395$journal,' ', PMID_31154395$year, ' ', PMID_31154395$month,';', PMID_31154395$volume,'(', PMID_31154395$number,'):', PMID_31154395$pages)

PubMed_31154395 <- paste0(PubMedString, PMID_31154395$eprint)

doi_31154395 <- paste0(doiString, PMID_31154395$doi)

dimensionBadge_31154395 <- paste0(dimensionString1, PMID_31154395$doi,dimensionString2)

altmetricBadge_31154395 <- paste0(altmetricString1, PMID_31154395$doi, altmetricString2 )

addthis_inline_31154395 <- paste0(addthis_String1, PMID_31154395$title , " PMID: 31154395" , addthis_String2)

Sys.sleep(1)


articles <- articles %>%

add_row(

ArticleCitation = PMID_31154395,
PMID = PMID_31154395$eprint,
Title = PMID_31154395$title,
# Author = PMID_31154395$author,
# Abstract = PMID_31154395$abstract,
Journal = PMID_31154395$journal,
Year = PMID_31154395$year,
Month = PMID_31154395$month,
# Volume = PMID_31154395$volume,
# Number = PMID_31154395$number,
# Pages = PMID_31154395$pages,
PubMedLink = paste0('https://www.ncbi.nlm.nih.gov/pubmed/?term=', PMID_31154395$eprint),
DoiNumber = PMID_31154395$doi,
DoiLink = paste0('https://doi.org/', PMID_31154395$doi),
Language = PMID_31154395$language,
ISSN = PMID_31154395$issn
) %>%

unique()


Sys.sleep(1)

saveRDS(articles, '~/JournalWatchPBPath/articles.rds')

```

<details open> <summary>
- **`r PMID_31154395$title`**
</summary> 

*`r citation_31154395`*

`r PubMed_31154395`

`r addthis_inline_31154395`

`r PMID_31154395$abstract`

`r doi_31154395`

`r dimensionBadge_31154395`

`r altmetricBadge_31154395`

</details>

---




---

```{r bileducts 31109808, include=FALSE}

articles <- readRDS('~/JournalWatchPBPath/articles.rds')


PMID_31109808 <- RefManageR::ReadPubMed('31109808', database = 'PubMed')

citation_31109808 <- paste0(PMID_31109808$journal,' ', PMID_31109808$year, ' ', PMID_31109808$month,';', PMID_31109808$volume,'(', PMID_31109808$number,'):', PMID_31109808$pages)

PubMed_31109808 <- paste0(PubMedString, PMID_31109808$eprint)

doi_31109808 <- paste0(doiString, PMID_31109808$doi)

dimensionBadge_31109808 <- paste0(dimensionString1, PMID_31109808$doi,dimensionString2)

altmetricBadge_31109808 <- paste0(altmetricString1, PMID_31109808$doi, altmetricString2 )

addthis_inline_31109808 <- paste0(addthis_String1, PMID_31109808$title , " PMID: 31109808" , addthis_String2)

Sys.sleep(1)


articles <- articles %>%

add_row(

ArticleCitation = PMID_31109808,
PMID = PMID_31109808$eprint,
Title = PMID_31109808$title,
# Author = PMID_31109808$author,
# Abstract = PMID_31109808$abstract,
Journal = PMID_31109808$journal,
Year = PMID_31109808$year,
Month = PMID_31109808$month,
# Volume = PMID_31109808$volume,
# Number = PMID_31109808$number,
# Pages = PMID_31109808$pages,
PubMedLink = paste0('https://www.ncbi.nlm.nih.gov/pubmed/?term=', PMID_31109808$eprint),
DoiNumber = PMID_31109808$doi,
DoiLink = paste0('https://doi.org/', PMID_31109808$doi),
Language = PMID_31109808$language,
ISSN = PMID_31109808$issn
) %>%

unique()


Sys.sleep(1)

saveRDS(articles, '~/JournalWatchPBPath/articles.rds')

```

<details open> <summary>
- **`r PMID_31109808$title`**
</summary> 

*`r citation_31109808`*

`r PubMed_31109808`

`r addthis_inline_31109808`

`r PMID_31109808$abstract`

`r doi_31109808`

`r dimensionBadge_31109808`

`r altmetricBadge_31109808`

</details>

---




---

```{r bileducts 31075300, include=FALSE}

articles <- readRDS('~/JournalWatchPBPath/articles.rds')


PMID_31075300 <- RefManageR::ReadPubMed('31075300', database = 'PubMed')

citation_31075300 <- paste0(PMID_31075300$journal,' ', PMID_31075300$year, ' ', PMID_31075300$month,';', PMID_31075300$volume,'(', PMID_31075300$number,'):', PMID_31075300$pages)

PubMed_31075300 <- paste0(PubMedString, PMID_31075300$eprint)

doi_31075300 <- paste0(doiString, PMID_31075300$doi)

dimensionBadge_31075300 <- paste0(dimensionString1, PMID_31075300$doi,dimensionString2)

altmetricBadge_31075300 <- paste0(altmetricString1, PMID_31075300$doi, altmetricString2 )

addthis_inline_31075300 <- paste0(addthis_String1, PMID_31075300$title , " PMID: 31075300" , addthis_String2)

Sys.sleep(1)


articles <- articles %>%

add_row(

ArticleCitation = PMID_31075300,
PMID = PMID_31075300$eprint,
Title = PMID_31075300$title,
# Author = PMID_31075300$author,
# Abstract = PMID_31075300$abstract,
Journal = PMID_31075300$journal,
Year = PMID_31075300$year,
Month = PMID_31075300$month,
# Volume = PMID_31075300$volume,
# Number = PMID_31075300$number,
# Pages = PMID_31075300$pages,
PubMedLink = paste0('https://www.ncbi.nlm.nih.gov/pubmed/?term=', PMID_31075300$eprint),
DoiNumber = PMID_31075300$doi,
DoiLink = paste0('https://doi.org/', PMID_31075300$doi),
Language = PMID_31075300$language,
ISSN = PMID_31075300$issn
) %>%

unique()


Sys.sleep(1)

saveRDS(articles, '~/JournalWatchPBPath/articles.rds')

```

<details open> <summary>
- **`r PMID_31075300$title`**
</summary> 

*`r citation_31075300`*

`r PubMed_31075300`

`r addthis_inline_31075300`

`r PMID_31075300$abstract`

`r doi_31075300`

`r dimensionBadge_31075300`

`r altmetricBadge_31075300`

</details>

---




---

```{r bileducts 31065963, include=FALSE}

articles <- readRDS('~/JournalWatchPBPath/articles.rds')


PMID_31065963 <- RefManageR::ReadPubMed('31065963', database = 'PubMed')

citation_31065963 <- paste0(PMID_31065963$journal,' ', PMID_31065963$year, ' ', PMID_31065963$month,';', PMID_31065963$volume,'(', PMID_31065963$number,'):', PMID_31065963$pages)

PubMed_31065963 <- paste0(PubMedString, PMID_31065963$eprint)

doi_31065963 <- paste0(doiString, PMID_31065963$doi)

dimensionBadge_31065963 <- paste0(dimensionString1, PMID_31065963$doi,dimensionString2)

altmetricBadge_31065963 <- paste0(altmetricString1, PMID_31065963$doi, altmetricString2 )

addthis_inline_31065963 <- paste0(addthis_String1, PMID_31065963$title , " PMID: 31065963" , addthis_String2)

Sys.sleep(1)


articles <- articles %>%

add_row(

ArticleCitation = PMID_31065963,
PMID = PMID_31065963$eprint,
Title = PMID_31065963$title,
# Author = PMID_31065963$author,
# Abstract = PMID_31065963$abstract,
Journal = PMID_31065963$journal,
Year = PMID_31065963$year,
Month = PMID_31065963$month,
# Volume = PMID_31065963$volume,
# Number = PMID_31065963$number,
# Pages = PMID_31065963$pages,
PubMedLink = paste0('https://www.ncbi.nlm.nih.gov/pubmed/?term=', PMID_31065963$eprint),
DoiNumber = PMID_31065963$doi,
DoiLink = paste0('https://doi.org/', PMID_31065963$doi),
Language = PMID_31065963$language,
ISSN = PMID_31065963$issn
) %>%

unique()


Sys.sleep(1)

saveRDS(articles, '~/JournalWatchPBPath/articles.rds')

```

<details open> <summary>
- **`r PMID_31065963$title`**
</summary> 

*`r citation_31065963`*

`r PubMed_31065963`

`r addthis_inline_31065963`

`r PMID_31065963$abstract`

`r doi_31065963`

`r dimensionBadge_31065963`

`r altmetricBadge_31065963`

</details>

---




---

```{r bileducts 31028154, include=FALSE}

articles <- readRDS('~/JournalWatchPBPath/articles.rds')


PMID_31028154 <- RefManageR::ReadPubMed('31028154', database = 'PubMed')

citation_31028154 <- paste0(PMID_31028154$journal,' ', PMID_31028154$year, ' ', PMID_31028154$month,';', PMID_31028154$volume,'(', PMID_31028154$number,'):', PMID_31028154$pages)

PubMed_31028154 <- paste0(PubMedString, PMID_31028154$eprint)

doi_31028154 <- paste0(doiString, PMID_31028154$doi)

dimensionBadge_31028154 <- paste0(dimensionString1, PMID_31028154$doi,dimensionString2)

altmetricBadge_31028154 <- paste0(altmetricString1, PMID_31028154$doi, altmetricString2 )

addthis_inline_31028154 <- paste0(addthis_String1, PMID_31028154$title , " PMID: 31028154" , addthis_String2)

Sys.sleep(1)


articles <- articles %>%

add_row(

ArticleCitation = PMID_31028154,
PMID = PMID_31028154$eprint,
Title = PMID_31028154$title,
# Author = PMID_31028154$author,
# Abstract = PMID_31028154$abstract,
Journal = PMID_31028154$journal,
Year = PMID_31028154$year,
Month = PMID_31028154$month,
# Volume = PMID_31028154$volume,
# Number = PMID_31028154$number,
# Pages = PMID_31028154$pages,
PubMedLink = paste0('https://www.ncbi.nlm.nih.gov/pubmed/?term=', PMID_31028154$eprint),
DoiNumber = PMID_31028154$doi,
DoiLink = paste0('https://doi.org/', PMID_31028154$doi),
Language = PMID_31028154$language,
ISSN = PMID_31028154$issn
) %>%

unique()


Sys.sleep(1)

saveRDS(articles, '~/JournalWatchPBPath/articles.rds')

```

<details open> <summary>
- **`r PMID_31028154$title`**
</summary> 

*`r citation_31028154`*

`r PubMed_31028154`

`r addthis_inline_31028154`

`r PMID_31028154$abstract`

`r doi_31028154`

`r dimensionBadge_31028154`

`r altmetricBadge_31028154`

</details>

---




---

```{r bileducts 30959037, include=FALSE}

articles <- readRDS('~/JournalWatchPBPath/articles.rds')


PMID_30959037 <- RefManageR::ReadPubMed('30959037', database = 'PubMed')

citation_30959037 <- paste0(PMID_30959037$journal,' ', PMID_30959037$year, ' ', PMID_30959037$month,';', PMID_30959037$volume,'(', PMID_30959037$number,'):', PMID_30959037$pages)

PubMed_30959037 <- paste0(PubMedString, PMID_30959037$eprint)

doi_30959037 <- paste0(doiString, PMID_30959037$doi)

dimensionBadge_30959037 <- paste0(dimensionString1, PMID_30959037$doi,dimensionString2)

altmetricBadge_30959037 <- paste0(altmetricString1, PMID_30959037$doi, altmetricString2 )

addthis_inline_30959037 <- paste0(addthis_String1, PMID_30959037$title , " PMID: 30959037" , addthis_String2)

Sys.sleep(1)


articles <- articles %>%

add_row(

ArticleCitation = PMID_30959037,
PMID = PMID_30959037$eprint,
Title = PMID_30959037$title,
# Author = PMID_30959037$author,
# Abstract = PMID_30959037$abstract,
Journal = PMID_30959037$journal,
Year = PMID_30959037$year,
Month = PMID_30959037$month,
# Volume = PMID_30959037$volume,
# Number = PMID_30959037$number,
# Pages = PMID_30959037$pages,
PubMedLink = paste0('https://www.ncbi.nlm.nih.gov/pubmed/?term=', PMID_30959037$eprint),
DoiNumber = PMID_30959037$doi,
DoiLink = paste0('https://doi.org/', PMID_30959037$doi),
Language = PMID_30959037$language,
ISSN = PMID_30959037$issn
) %>%

unique()


Sys.sleep(1)

saveRDS(articles, '~/JournalWatchPBPath/articles.rds')

```

<details open> <summary>
- **`r PMID_30959037$title`**
</summary> 

*`r citation_30959037`*

`r PubMed_30959037`

`r addthis_inline_30959037`

`r PMID_30959037$abstract`

`r doi_30959037`

`r dimensionBadge_30959037`

`r altmetricBadge_30959037`

</details>

---




---

```{r bileducts 30959031, include=FALSE}

articles <- readRDS('~/JournalWatchPBPath/articles.rds')


PMID_30959031 <- RefManageR::ReadPubMed('30959031', database = 'PubMed')

citation_30959031 <- paste0(PMID_30959031$journal,' ', PMID_30959031$year, ' ', PMID_30959031$month,';', PMID_30959031$volume,'(', PMID_30959031$number,'):', PMID_30959031$pages)

PubMed_30959031 <- paste0(PubMedString, PMID_30959031$eprint)

doi_30959031 <- paste0(doiString, PMID_30959031$doi)

dimensionBadge_30959031 <- paste0(dimensionString1, PMID_30959031$doi,dimensionString2)

altmetricBadge_30959031 <- paste0(altmetricString1, PMID_30959031$doi, altmetricString2 )

addthis_inline_30959031 <- paste0(addthis_String1, PMID_30959031$title , " PMID: 30959031" , addthis_String2)

Sys.sleep(1)


articles <- articles %>%

add_row(

ArticleCitation = PMID_30959031,
PMID = PMID_30959031$eprint,
Title = PMID_30959031$title,
# Author = PMID_30959031$author,
# Abstract = PMID_30959031$abstract,
Journal = PMID_30959031$journal,
Year = PMID_30959031$year,
Month = PMID_30959031$month,
# Volume = PMID_30959031$volume,
# Number = PMID_30959031$number,
# Pages = PMID_30959031$pages,
PubMedLink = paste0('https://www.ncbi.nlm.nih.gov/pubmed/?term=', PMID_30959031$eprint),
DoiNumber = PMID_30959031$doi,
DoiLink = paste0('https://doi.org/', PMID_30959031$doi),
Language = PMID_30959031$language,
ISSN = PMID_30959031$issn
) %>%

unique()


Sys.sleep(1)

saveRDS(articles, '~/JournalWatchPBPath/articles.rds')

```

<details open> <summary>
- **`r PMID_30959031$title`**
</summary> 

*`r citation_30959031`*

`r PubMed_30959031`

`r addthis_inline_30959031`

`r PMID_30959031$abstract`

`r doi_30959031`

`r dimensionBadge_30959031`

`r altmetricBadge_30959031`

</details>

---




---

```{r bileducts 30872395, include=FALSE}

articles <- readRDS('~/JournalWatchPBPath/articles.rds')


PMID_30872395 <- RefManageR::ReadPubMed('30872395', database = 'PubMed')

citation_30872395 <- paste0(PMID_30872395$journal,' ', PMID_30872395$year, ' ', PMID_30872395$month,';', PMID_30872395$volume,'(', PMID_30872395$number,'):', PMID_30872395$pages)

PubMed_30872395 <- paste0(PubMedString, PMID_30872395$eprint)

doi_30872395 <- paste0(doiString, PMID_30872395$doi)

dimensionBadge_30872395 <- paste0(dimensionString1, PMID_30872395$doi,dimensionString2)

altmetricBadge_30872395 <- paste0(altmetricString1, PMID_30872395$doi, altmetricString2 )

addthis_inline_30872395 <- paste0(addthis_String1, PMID_30872395$title , " PMID: 30872395" , addthis_String2)

Sys.sleep(1)


articles <- articles %>%

add_row(

ArticleCitation = PMID_30872395,
PMID = PMID_30872395$eprint,
Title = PMID_30872395$title,
# Author = PMID_30872395$author,
# Abstract = PMID_30872395$abstract,
Journal = PMID_30872395$journal,
Year = PMID_30872395$year,
Month = PMID_30872395$month,
# Volume = PMID_30872395$volume,
# Number = PMID_30872395$number,
# Pages = PMID_30872395$pages,
PubMedLink = paste0('https://www.ncbi.nlm.nih.gov/pubmed/?term=', PMID_30872395$eprint),
DoiNumber = PMID_30872395$doi,
DoiLink = paste0('https://doi.org/', PMID_30872395$doi),
Language = PMID_30872395$language,
ISSN = PMID_30872395$issn
) %>%

unique()


Sys.sleep(1)

saveRDS(articles, '~/JournalWatchPBPath/articles.rds')

```

<details open> <summary>
- **`r PMID_30872395$title`**
</summary> 

*`r citation_30872395`*

`r PubMed_30872395`

`r addthis_inline_30872395`

`r PMID_30872395$abstract`

`r doi_30872395`

`r dimensionBadge_30872395`

`r altmetricBadge_30872395`

</details>

---




---

```{r bileducts 30448774, include=FALSE}

articles <- readRDS('~/JournalWatchPBPath/articles.rds')


PMID_30448774 <- RefManageR::ReadPubMed('30448774', database = 'PubMed')

citation_30448774 <- paste0(PMID_30448774$journal,' ', PMID_30448774$year, ' ', PMID_30448774$month,';', PMID_30448774$volume,'(', PMID_30448774$number,'):', PMID_30448774$pages)

PubMed_30448774 <- paste0(PubMedString, PMID_30448774$eprint)

doi_30448774 <- paste0(doiString, PMID_30448774$doi)

dimensionBadge_30448774 <- paste0(dimensionString1, PMID_30448774$doi,dimensionString2)

altmetricBadge_30448774 <- paste0(altmetricString1, PMID_30448774$doi, altmetricString2 )

addthis_inline_30448774 <- paste0(addthis_String1, PMID_30448774$title , " PMID: 30448774" , addthis_String2)

Sys.sleep(1)


articles <- articles %>%

add_row(

ArticleCitation = PMID_30448774,
PMID = PMID_30448774$eprint,
Title = PMID_30448774$title,
# Author = PMID_30448774$author,
# Abstract = PMID_30448774$abstract,
Journal = PMID_30448774$journal,
Year = PMID_30448774$year,
Month = PMID_30448774$month,
# Volume = PMID_30448774$volume,
# Number = PMID_30448774$number,
# Pages = PMID_30448774$pages,
PubMedLink = paste0('https://www.ncbi.nlm.nih.gov/pubmed/?term=', PMID_30448774$eprint),
DoiNumber = PMID_30448774$doi,
DoiLink = paste0('https://doi.org/', PMID_30448774$doi),
Language = PMID_30448774$language,
ISSN = PMID_30448774$issn
) %>%

unique()


Sys.sleep(1)

saveRDS(articles, '~/JournalWatchPBPath/articles.rds')

```

<details open> <summary>
- **`r PMID_30448774$title`**
</summary> 

*`r citation_30448774`*

`r PubMed_30448774`

`r addthis_inline_30448774`

`r PMID_30448774$abstract`

`r doi_30448774`

`r dimensionBadge_30448774`

`r altmetricBadge_30448774`

</details>

---




---

```{r bileducts 30131321, include=FALSE}

articles <- readRDS('~/JournalWatchPBPath/articles.rds')


PMID_30131321 <- RefManageR::ReadPubMed('30131321', database = 'PubMed')

citation_30131321 <- paste0(PMID_30131321$journal,' ', PMID_30131321$year, ' ', PMID_30131321$month,';', PMID_30131321$volume,'(', PMID_30131321$number,'):', PMID_30131321$pages)

PubMed_30131321 <- paste0(PubMedString, PMID_30131321$eprint)

doi_30131321 <- paste0(doiString, PMID_30131321$doi)

dimensionBadge_30131321 <- paste0(dimensionString1, PMID_30131321$doi,dimensionString2)

altmetricBadge_30131321 <- paste0(altmetricString1, PMID_30131321$doi, altmetricString2 )

addthis_inline_30131321 <- paste0(addthis_String1, PMID_30131321$title , " PMID: 30131321" , addthis_String2)

Sys.sleep(1)


articles <- articles %>%

add_row(

ArticleCitation = PMID_30131321,
PMID = PMID_30131321$eprint,
Title = PMID_30131321$title,
# Author = PMID_30131321$author,
# Abstract = PMID_30131321$abstract,
Journal = PMID_30131321$journal,
Year = PMID_30131321$year,
Month = PMID_30131321$month,
# Volume = PMID_30131321$volume,
# Number = PMID_30131321$number,
# Pages = PMID_30131321$pages,
PubMedLink = paste0('https://www.ncbi.nlm.nih.gov/pubmed/?term=', PMID_30131321$eprint),
DoiNumber = PMID_30131321$doi,
DoiLink = paste0('https://doi.org/', PMID_30131321$doi),
Language = PMID_30131321$language,
ISSN = PMID_30131321$issn
) %>%

unique()


Sys.sleep(1)

saveRDS(articles, '~/JournalWatchPBPath/articles.rds')

```

<details open> <summary>
- **`r PMID_30131321$title`**
</summary> 

*`r citation_30131321`*

`r PubMed_30131321`

`r addthis_inline_30131321`

`r PMID_30131321$abstract`

`r doi_30131321`

`r dimensionBadge_30131321`

`r altmetricBadge_30131321`

</details>

---




---

```{r bileducts 31349795, include=FALSE}

articles <- readRDS('~/JournalWatchPBPath/articles.rds')


PMID_31349795 <- RefManageR::ReadPubMed('31349795', database = 'PubMed')

citation_31349795 <- paste0(PMID_31349795$journal,' ', PMID_31349795$year, ' ', PMID_31349795$month,';', PMID_31349795$volume,'(', PMID_31349795$number,'):', PMID_31349795$pages)

PubMed_31349795 <- paste0(PubMedString, PMID_31349795$eprint)

doi_31349795 <- paste0(doiString, PMID_31349795$doi)

dimensionBadge_31349795 <- paste0(dimensionString1, PMID_31349795$doi,dimensionString2)

altmetricBadge_31349795 <- paste0(altmetricString1, PMID_31349795$doi, altmetricString2 )

addthis_inline_31349795 <- paste0(addthis_String1, PMID_31349795$title , " PMID: 31349795" , addthis_String2)

Sys.sleep(1)


articles <- articles %>%

add_row(

ArticleCitation = PMID_31349795,
PMID = PMID_31349795$eprint,
Title = PMID_31349795$title,
# Author = PMID_31349795$author,
# Abstract = PMID_31349795$abstract,
Journal = PMID_31349795$journal,
Year = PMID_31349795$year,
Month = PMID_31349795$month,
# Volume = PMID_31349795$volume,
# Number = PMID_31349795$number,
# Pages = PMID_31349795$pages,
PubMedLink = paste0('https://www.ncbi.nlm.nih.gov/pubmed/?term=', PMID_31349795$eprint),
DoiNumber = PMID_31349795$doi,
DoiLink = paste0('https://doi.org/', PMID_31349795$doi),
Language = PMID_31349795$language,
ISSN = PMID_31349795$issn
) %>%

unique()


Sys.sleep(1)

saveRDS(articles, '~/JournalWatchPBPath/articles.rds')

```

<details open> <summary>
- **`r PMID_31349795$title`**
</summary> 

*`r citation_31349795`*

`r PubMed_31349795`

`r addthis_inline_31349795`

`r PMID_31349795$abstract`

`r doi_31349795`

`r dimensionBadge_31349795`

`r altmetricBadge_31349795`

</details>

---




---

```{r bileducts 31358425, include=FALSE}

articles <- readRDS('~/JournalWatchPBPath/articles.rds')


PMID_31358425 <- RefManageR::ReadPubMed('31358425', database = 'PubMed')

citation_31358425 <- paste0(PMID_31358425$journal,' ', PMID_31358425$year, ' ', PMID_31358425$month,';', PMID_31358425$volume,'(', PMID_31358425$number,'):', PMID_31358425$pages)

PubMed_31358425 <- paste0(PubMedString, PMID_31358425$eprint)

doi_31358425 <- paste0(doiString, PMID_31358425$doi)

dimensionBadge_31358425 <- paste0(dimensionString1, PMID_31358425$doi,dimensionString2)

altmetricBadge_31358425 <- paste0(altmetricString1, PMID_31358425$doi, altmetricString2 )

addthis_inline_31358425 <- paste0(addthis_String1, PMID_31358425$title , " PMID: 31358425" , addthis_String2)

Sys.sleep(1)


articles <- articles %>%

add_row(

ArticleCitation = PMID_31358425,
PMID = PMID_31358425$eprint,
Title = PMID_31358425$title,
# Author = PMID_31358425$author,
# Abstract = PMID_31358425$abstract,
Journal = PMID_31358425$journal,
Year = PMID_31358425$year,
Month = PMID_31358425$month,
# Volume = PMID_31358425$volume,
# Number = PMID_31358425$number,
# Pages = PMID_31358425$pages,
PubMedLink = paste0('https://www.ncbi.nlm.nih.gov/pubmed/?term=', PMID_31358425$eprint),
DoiNumber = PMID_31358425$doi,
DoiLink = paste0('https://doi.org/', PMID_31358425$doi),
Language = PMID_31358425$language,
ISSN = PMID_31358425$issn
) %>%

unique()


Sys.sleep(1)

saveRDS(articles, '~/JournalWatchPBPath/articles.rds')

```

<details open> <summary>
- **`r PMID_31358425$title`**
</summary> 

*`r citation_31358425`*

`r PubMed_31358425`

`r addthis_inline_31358425`

`r PMID_31358425$abstract`

`r doi_31358425`

`r dimensionBadge_31358425`

`r altmetricBadge_31358425`

</details>

---




---

```{r bileducts 31358424, include=FALSE}

articles <- readRDS('~/JournalWatchPBPath/articles.rds')


PMID_31358424 <- RefManageR::ReadPubMed('31358424', database = 'PubMed')

citation_31358424 <- paste0(PMID_31358424$journal,' ', PMID_31358424$year, ' ', PMID_31358424$month,';', PMID_31358424$volume,'(', PMID_31358424$number,'):', PMID_31358424$pages)

PubMed_31358424 <- paste0(PubMedString, PMID_31358424$eprint)

doi_31358424 <- paste0(doiString, PMID_31358424$doi)

dimensionBadge_31358424 <- paste0(dimensionString1, PMID_31358424$doi,dimensionString2)

altmetricBadge_31358424 <- paste0(altmetricString1, PMID_31358424$doi, altmetricString2 )

addthis_inline_31358424 <- paste0(addthis_String1, PMID_31358424$title , " PMID: 31358424" , addthis_String2)

Sys.sleep(1)


articles <- articles %>%

add_row(

ArticleCitation = PMID_31358424,
PMID = PMID_31358424$eprint,
Title = PMID_31358424$title,
# Author = PMID_31358424$author,
# Abstract = PMID_31358424$abstract,
Journal = PMID_31358424$journal,
Year = PMID_31358424$year,
Month = PMID_31358424$month,
# Volume = PMID_31358424$volume,
# Number = PMID_31358424$number,
# Pages = PMID_31358424$pages,
PubMedLink = paste0('https://www.ncbi.nlm.nih.gov/pubmed/?term=', PMID_31358424$eprint),
DoiNumber = PMID_31358424$doi,
DoiLink = paste0('https://doi.org/', PMID_31358424$doi),
Language = PMID_31358424$language,
ISSN = PMID_31358424$issn
) %>%

unique()


Sys.sleep(1)

saveRDS(articles, '~/JournalWatchPBPath/articles.rds')

```

<details open> <summary>
- **`r PMID_31358424$title`**
</summary> 

*`r citation_31358424`*

`r PubMed_31358424`

`r addthis_inline_31358424`

`r PMID_31358424$abstract`

`r doi_31358424`

`r dimensionBadge_31358424`

`r altmetricBadge_31358424`

</details>

---




---

```{r bileducts 31337646, include=FALSE}

articles <- readRDS('~/JournalWatchPBPath/articles.rds')


PMID_31337646 <- RefManageR::ReadPubMed('31337646', database = 'PubMed')

citation_31337646 <- paste0(PMID_31337646$journal,' ', PMID_31337646$year, ' ', PMID_31337646$month,';', PMID_31337646$volume,'(', PMID_31337646$number,'):', PMID_31337646$pages)

PubMed_31337646 <- paste0(PubMedString, PMID_31337646$eprint)

doi_31337646 <- paste0(doiString, PMID_31337646$doi)

dimensionBadge_31337646 <- paste0(dimensionString1, PMID_31337646$doi,dimensionString2)

altmetricBadge_31337646 <- paste0(altmetricString1, PMID_31337646$doi, altmetricString2 )

addthis_inline_31337646 <- paste0(addthis_String1, PMID_31337646$title , " PMID: 31337646" , addthis_String2)

Sys.sleep(1)


articles <- articles %>%

add_row(

ArticleCitation = PMID_31337646,
PMID = PMID_31337646$eprint,
Title = PMID_31337646$title,
# Author = PMID_31337646$author,
# Abstract = PMID_31337646$abstract,
Journal = PMID_31337646$journal,
Year = PMID_31337646$year,
Month = PMID_31337646$month,
# Volume = PMID_31337646$volume,
# Number = PMID_31337646$number,
# Pages = PMID_31337646$pages,
PubMedLink = paste0('https://www.ncbi.nlm.nih.gov/pubmed/?term=', PMID_31337646$eprint),
DoiNumber = PMID_31337646$doi,
DoiLink = paste0('https://doi.org/', PMID_31337646$doi),
Language = PMID_31337646$language,
ISSN = PMID_31337646$issn
) %>%

unique()


Sys.sleep(1)

saveRDS(articles, '~/JournalWatchPBPath/articles.rds')

```

<details open> <summary>
- **`r PMID_31337646$title`**
</summary> 

*`r citation_31337646`*

`r PubMed_31337646`

`r addthis_inline_31337646`

`r PMID_31337646$abstract`

`r doi_31337646`

`r dimensionBadge_31337646`

`r altmetricBadge_31337646`

</details>

---


