

---

```{r gallbladder 31725469, include=FALSE}

articles <- readRDS('~/JournalWatchPBPath/articles.rds')


PMID_31725469 <- RefManageR::ReadPubMed('31725469', database = 'PubMed')

citation_31725469 <- paste0(PMID_31725469$journal,' ', PMID_31725469$year, ' ', PMID_31725469$month,';', PMID_31725469$volume,'(', PMID_31725469$number,'):', PMID_31725469$pages)

PubMed_31725469 <- paste0(PubMedString, PMID_31725469$eprint)

doi_31725469 <- paste0(doiString, PMID_31725469$doi)

dimensionBadge_31725469 <- paste0(dimensionString1, PMID_31725469$doi,dimensionString2)

altmetricBadge_31725469 <- paste0(altmetricString1, PMID_31725469$doi, altmetricString2 )

addthis_inline_31725469 <- paste0(addthis_String1, PMID_31725469$title , " PMID: 31725469" , addthis_String2)

Sys.sleep(1)


articles <- articles %>%

add_row(

ArticleCitation = PMID_31725469,
PMID = PMID_31725469$eprint,
Title = PMID_31725469$title,
# Author = PMID_31725469$author,
# Abstract = PMID_31725469$abstract,
Journal = PMID_31725469$journal,
Year = PMID_31725469$year,
Month = PMID_31725469$month,
# Volume = PMID_31725469$volume,
# Number = PMID_31725469$number,
# Pages = PMID_31725469$pages,
PubMedLink = paste0('https://www.ncbi.nlm.nih.gov/pubmed/?term=', PMID_31725469$eprint),
DoiNumber = PMID_31725469$doi,
DoiLink = paste0('https://doi.org/', PMID_31725469$doi),
Language = PMID_31725469$language,
ISSN = PMID_31725469$issn
) %>%

unique()


Sys.sleep(1)

saveRDS(articles, '~/JournalWatchPBPath/articles.rds')

```

<details open> <summary>
- **`r PMID_31725469$title`**
</summary> 

*`r citation_31725469`*

`r PubMed_31725469`

<!-- `r addthis_inline_31725469` -->

`r PMID_31725469$abstract`

`r doi_31725469`

<!-- `r dimensionBadge_31725469` -->

<!-- `r altmetricBadge_31725469` -->

</details>

---




---

```{r gallbladder 31722073, include=FALSE}

articles <- readRDS('~/JournalWatchPBPath/articles.rds')


PMID_31722073 <- RefManageR::ReadPubMed('31722073', database = 'PubMed')

citation_31722073 <- paste0(PMID_31722073$journal,' ', PMID_31722073$year, ' ', PMID_31722073$month,';', PMID_31722073$volume,'(', PMID_31722073$number,'):', PMID_31722073$pages)

PubMed_31722073 <- paste0(PubMedString, PMID_31722073$eprint)

doi_31722073 <- paste0(doiString, PMID_31722073$doi)

dimensionBadge_31722073 <- paste0(dimensionString1, PMID_31722073$doi,dimensionString2)

altmetricBadge_31722073 <- paste0(altmetricString1, PMID_31722073$doi, altmetricString2 )

addthis_inline_31722073 <- paste0(addthis_String1, PMID_31722073$title , " PMID: 31722073" , addthis_String2)

Sys.sleep(1)


articles <- articles %>%

add_row(

ArticleCitation = PMID_31722073,
PMID = PMID_31722073$eprint,
Title = PMID_31722073$title,
# Author = PMID_31722073$author,
# Abstract = PMID_31722073$abstract,
Journal = PMID_31722073$journal,
Year = PMID_31722073$year,
Month = PMID_31722073$month,
# Volume = PMID_31722073$volume,
# Number = PMID_31722073$number,
# Pages = PMID_31722073$pages,
PubMedLink = paste0('https://www.ncbi.nlm.nih.gov/pubmed/?term=', PMID_31722073$eprint),
DoiNumber = PMID_31722073$doi,
DoiLink = paste0('https://doi.org/', PMID_31722073$doi),
Language = PMID_31722073$language,
ISSN = PMID_31722073$issn
) %>%

unique()


Sys.sleep(1)

saveRDS(articles, '~/JournalWatchPBPath/articles.rds')

```

<details open> <summary>
- **`r PMID_31722073$title`**
</summary> 

*`r citation_31722073`*

`r PubMed_31722073`

<!-- `r addthis_inline_31722073` -->

`r PMID_31722073$abstract`

`r doi_31722073`

<!-- `r dimensionBadge_31722073` -->

<!-- `r altmetricBadge_31722073` -->

</details>

---




---

```{r gallbladder 31640627, include=FALSE}

articles <- readRDS('~/JournalWatchPBPath/articles.rds')


PMID_31640627 <- RefManageR::ReadPubMed('31640627', database = 'PubMed')

citation_31640627 <- paste0(PMID_31640627$journal,' ', PMID_31640627$year, ' ', PMID_31640627$month,';', PMID_31640627$volume,'(', PMID_31640627$number,'):', PMID_31640627$pages)

PubMed_31640627 <- paste0(PubMedString, PMID_31640627$eprint)

doi_31640627 <- paste0(doiString, PMID_31640627$doi)

dimensionBadge_31640627 <- paste0(dimensionString1, PMID_31640627$doi,dimensionString2)

altmetricBadge_31640627 <- paste0(altmetricString1, PMID_31640627$doi, altmetricString2 )

addthis_inline_31640627 <- paste0(addthis_String1, PMID_31640627$title , " PMID: 31640627" , addthis_String2)

Sys.sleep(1)


articles <- articles %>%

add_row(

ArticleCitation = PMID_31640627,
PMID = PMID_31640627$eprint,
Title = PMID_31640627$title,
# Author = PMID_31640627$author,
# Abstract = PMID_31640627$abstract,
Journal = PMID_31640627$journal,
Year = PMID_31640627$year,
Month = PMID_31640627$month,
# Volume = PMID_31640627$volume,
# Number = PMID_31640627$number,
# Pages = PMID_31640627$pages,
PubMedLink = paste0('https://www.ncbi.nlm.nih.gov/pubmed/?term=', PMID_31640627$eprint),
DoiNumber = PMID_31640627$doi,
DoiLink = paste0('https://doi.org/', PMID_31640627$doi),
Language = PMID_31640627$language,
ISSN = PMID_31640627$issn
) %>%

unique()


Sys.sleep(1)

saveRDS(articles, '~/JournalWatchPBPath/articles.rds')

```

<details open> <summary>
- **`r PMID_31640627$title`**
</summary> 

*`r citation_31640627`*

`r PubMed_31640627`

<!-- `r addthis_inline_31640627` -->

`r PMID_31640627$abstract`

`r doi_31640627`

<!-- `r dimensionBadge_31640627` -->

<!-- `r altmetricBadge_31640627` -->

</details>

---




---

```{r gallbladder 31634153, include=FALSE}

articles <- readRDS('~/JournalWatchPBPath/articles.rds')


PMID_31634153 <- RefManageR::ReadPubMed('31634153', database = 'PubMed')

citation_31634153 <- paste0(PMID_31634153$journal,' ', PMID_31634153$year, ' ', PMID_31634153$month,';', PMID_31634153$volume,'(', PMID_31634153$number,'):', PMID_31634153$pages)

PubMed_31634153 <- paste0(PubMedString, PMID_31634153$eprint)

doi_31634153 <- paste0(doiString, PMID_31634153$doi)

dimensionBadge_31634153 <- paste0(dimensionString1, PMID_31634153$doi,dimensionString2)

altmetricBadge_31634153 <- paste0(altmetricString1, PMID_31634153$doi, altmetricString2 )

addthis_inline_31634153 <- paste0(addthis_String1, PMID_31634153$title , " PMID: 31634153" , addthis_String2)

Sys.sleep(1)


articles <- articles %>%

add_row(

ArticleCitation = PMID_31634153,
PMID = PMID_31634153$eprint,
Title = PMID_31634153$title,
# Author = PMID_31634153$author,
# Abstract = PMID_31634153$abstract,
Journal = PMID_31634153$journal,
Year = PMID_31634153$year,
Month = PMID_31634153$month,
# Volume = PMID_31634153$volume,
# Number = PMID_31634153$number,
# Pages = PMID_31634153$pages,
PubMedLink = paste0('https://www.ncbi.nlm.nih.gov/pubmed/?term=', PMID_31634153$eprint),
DoiNumber = PMID_31634153$doi,
DoiLink = paste0('https://doi.org/', PMID_31634153$doi),
Language = PMID_31634153$language,
ISSN = PMID_31634153$issn
) %>%

unique()


Sys.sleep(1)

saveRDS(articles, '~/JournalWatchPBPath/articles.rds')

```

<details open> <summary>
- **`r PMID_31634153$title`**
</summary> 

*`r citation_31634153`*

`r PubMed_31634153`

<!-- `r addthis_inline_31634153` -->

`r PMID_31634153$abstract`

`r doi_31634153`

<!-- `r dimensionBadge_31634153` -->

<!-- `r altmetricBadge_31634153` -->

</details>

---




---

```{r gallbladder 31600399, include=FALSE}

articles <- readRDS('~/JournalWatchPBPath/articles.rds')


PMID_31600399 <- RefManageR::ReadPubMed('31600399', database = 'PubMed')

citation_31600399 <- paste0(PMID_31600399$journal,' ', PMID_31600399$year, ' ', PMID_31600399$month,';', PMID_31600399$volume,'(', PMID_31600399$number,'):', PMID_31600399$pages)

PubMed_31600399 <- paste0(PubMedString, PMID_31600399$eprint)

doi_31600399 <- paste0(doiString, PMID_31600399$doi)

dimensionBadge_31600399 <- paste0(dimensionString1, PMID_31600399$doi,dimensionString2)

altmetricBadge_31600399 <- paste0(altmetricString1, PMID_31600399$doi, altmetricString2 )

addthis_inline_31600399 <- paste0(addthis_String1, PMID_31600399$title , " PMID: 31600399" , addthis_String2)

Sys.sleep(1)


articles <- articles %>%

add_row(

ArticleCitation = PMID_31600399,
PMID = PMID_31600399$eprint,
Title = PMID_31600399$title,
# Author = PMID_31600399$author,
# Abstract = PMID_31600399$abstract,
Journal = PMID_31600399$journal,
Year = PMID_31600399$year,
Month = PMID_31600399$month,
# Volume = PMID_31600399$volume,
# Number = PMID_31600399$number,
# Pages = PMID_31600399$pages,
PubMedLink = paste0('https://www.ncbi.nlm.nih.gov/pubmed/?term=', PMID_31600399$eprint),
DoiNumber = PMID_31600399$doi,
DoiLink = paste0('https://doi.org/', PMID_31600399$doi),
Language = PMID_31600399$language,
ISSN = PMID_31600399$issn
) %>%

unique()


Sys.sleep(1)

saveRDS(articles, '~/JournalWatchPBPath/articles.rds')

```

<details open> <summary>
- **`r PMID_31600399$title`**
</summary> 

*`r citation_31600399`*

`r PubMed_31600399`

<!-- `r addthis_inline_31600399` -->

`r PMID_31600399$abstract`

`r doi_31600399`

<!-- `r dimensionBadge_31600399` -->

<!-- `r altmetricBadge_31600399` -->

</details>

---




---

```{r gallbladder 31567508, include=FALSE}

articles <- readRDS('~/JournalWatchPBPath/articles.rds')


PMID_31567508 <- RefManageR::ReadPubMed('31567508', database = 'PubMed')

citation_31567508 <- paste0(PMID_31567508$journal,' ', PMID_31567508$year, ' ', PMID_31567508$month,';', PMID_31567508$volume,'(', PMID_31567508$number,'):', PMID_31567508$pages)

PubMed_31567508 <- paste0(PubMedString, PMID_31567508$eprint)

doi_31567508 <- paste0(doiString, PMID_31567508$doi)

dimensionBadge_31567508 <- paste0(dimensionString1, PMID_31567508$doi,dimensionString2)

altmetricBadge_31567508 <- paste0(altmetricString1, PMID_31567508$doi, altmetricString2 )

addthis_inline_31567508 <- paste0(addthis_String1, PMID_31567508$title , " PMID: 31567508" , addthis_String2)

Sys.sleep(1)


articles <- articles %>%

add_row(

ArticleCitation = PMID_31567508,
PMID = PMID_31567508$eprint,
Title = PMID_31567508$title,
# Author = PMID_31567508$author,
# Abstract = PMID_31567508$abstract,
Journal = PMID_31567508$journal,
Year = PMID_31567508$year,
Month = PMID_31567508$month,
# Volume = PMID_31567508$volume,
# Number = PMID_31567508$number,
# Pages = PMID_31567508$pages,
PubMedLink = paste0('https://www.ncbi.nlm.nih.gov/pubmed/?term=', PMID_31567508$eprint),
DoiNumber = PMID_31567508$doi,
DoiLink = paste0('https://doi.org/', PMID_31567508$doi),
Language = PMID_31567508$language,
ISSN = PMID_31567508$issn
) %>%

unique()


Sys.sleep(1)

saveRDS(articles, '~/JournalWatchPBPath/articles.rds')

```

<details open> <summary>
- **`r PMID_31567508$title`**
</summary> 

*`r citation_31567508`*

`r PubMed_31567508`

<!-- `r addthis_inline_31567508` -->

`r PMID_31567508$abstract`

`r doi_31567508`

<!-- `r dimensionBadge_31567508` -->

<!-- `r altmetricBadge_31567508` -->

</details>

---




---

```{r gallbladder 31551021, include=FALSE}

articles <- readRDS('~/JournalWatchPBPath/articles.rds')


PMID_31551021 <- RefManageR::ReadPubMed('31551021', database = 'PubMed')

citation_31551021 <- paste0(PMID_31551021$journal,' ', PMID_31551021$year, ' ', PMID_31551021$month,';', PMID_31551021$volume,'(', PMID_31551021$number,'):', PMID_31551021$pages)

PubMed_31551021 <- paste0(PubMedString, PMID_31551021$eprint)

doi_31551021 <- paste0(doiString, PMID_31551021$doi)

dimensionBadge_31551021 <- paste0(dimensionString1, PMID_31551021$doi,dimensionString2)

altmetricBadge_31551021 <- paste0(altmetricString1, PMID_31551021$doi, altmetricString2 )

addthis_inline_31551021 <- paste0(addthis_String1, PMID_31551021$title , " PMID: 31551021" , addthis_String2)

Sys.sleep(1)


articles <- articles %>%

add_row(

ArticleCitation = PMID_31551021,
PMID = PMID_31551021$eprint,
Title = PMID_31551021$title,
# Author = PMID_31551021$author,
# Abstract = PMID_31551021$abstract,
Journal = PMID_31551021$journal,
Year = PMID_31551021$year,
Month = PMID_31551021$month,
# Volume = PMID_31551021$volume,
# Number = PMID_31551021$number,
# Pages = PMID_31551021$pages,
PubMedLink = paste0('https://www.ncbi.nlm.nih.gov/pubmed/?term=', PMID_31551021$eprint),
DoiNumber = PMID_31551021$doi,
DoiLink = paste0('https://doi.org/', PMID_31551021$doi),
Language = PMID_31551021$language,
ISSN = PMID_31551021$issn
) %>%

unique()


Sys.sleep(1)

saveRDS(articles, '~/JournalWatchPBPath/articles.rds')

```

<details open> <summary>
- **`r PMID_31551021$title`**
</summary> 

*`r citation_31551021`*

`r PubMed_31551021`

<!-- `r addthis_inline_31551021` -->

`r PMID_31551021$abstract`

`r doi_31551021`

<!-- `r dimensionBadge_31551021` -->

<!-- `r altmetricBadge_31551021` -->

</details>

---




---

```{r gallbladder 31403962, include=FALSE}

articles <- readRDS('~/JournalWatchPBPath/articles.rds')


PMID_31403962 <- RefManageR::ReadPubMed('31403962', database = 'PubMed')

citation_31403962 <- paste0(PMID_31403962$journal,' ', PMID_31403962$year, ' ', PMID_31403962$month,';', PMID_31403962$volume,'(', PMID_31403962$number,'):', PMID_31403962$pages)

PubMed_31403962 <- paste0(PubMedString, PMID_31403962$eprint)

doi_31403962 <- paste0(doiString, PMID_31403962$doi)

dimensionBadge_31403962 <- paste0(dimensionString1, PMID_31403962$doi,dimensionString2)

altmetricBadge_31403962 <- paste0(altmetricString1, PMID_31403962$doi, altmetricString2 )

addthis_inline_31403962 <- paste0(addthis_String1, PMID_31403962$title , " PMID: 31403962" , addthis_String2)

Sys.sleep(1)


articles <- articles %>%

add_row(

ArticleCitation = PMID_31403962,
PMID = PMID_31403962$eprint,
Title = PMID_31403962$title,
# Author = PMID_31403962$author,
# Abstract = PMID_31403962$abstract,
Journal = PMID_31403962$journal,
Year = PMID_31403962$year,
Month = PMID_31403962$month,
# Volume = PMID_31403962$volume,
# Number = PMID_31403962$number,
# Pages = PMID_31403962$pages,
PubMedLink = paste0('https://www.ncbi.nlm.nih.gov/pubmed/?term=', PMID_31403962$eprint),
DoiNumber = PMID_31403962$doi,
DoiLink = paste0('https://doi.org/', PMID_31403962$doi),
Language = PMID_31403962$language,
ISSN = PMID_31403962$issn
) %>%

unique()


Sys.sleep(1)

saveRDS(articles, '~/JournalWatchPBPath/articles.rds')

```

<details open> <summary>
- **`r PMID_31403962$title`**
</summary> 

*`r citation_31403962`*

`r PubMed_31403962`

<!-- `r addthis_inline_31403962` -->

`r PMID_31403962$abstract`

`r doi_31403962`

<!-- `r dimensionBadge_31403962` -->

<!-- `r altmetricBadge_31403962` -->

</details>

---




---

```{r gallbladder 31102094, include=FALSE}

articles <- readRDS('~/JournalWatchPBPath/articles.rds')


PMID_31102094 <- RefManageR::ReadPubMed('31102094', database = 'PubMed')

citation_31102094 <- paste0(PMID_31102094$journal,' ', PMID_31102094$year, ' ', PMID_31102094$month,';', PMID_31102094$volume,'(', PMID_31102094$number,'):', PMID_31102094$pages)

PubMed_31102094 <- paste0(PubMedString, PMID_31102094$eprint)

doi_31102094 <- paste0(doiString, PMID_31102094$doi)

dimensionBadge_31102094 <- paste0(dimensionString1, PMID_31102094$doi,dimensionString2)

altmetricBadge_31102094 <- paste0(altmetricString1, PMID_31102094$doi, altmetricString2 )

addthis_inline_31102094 <- paste0(addthis_String1, PMID_31102094$title , " PMID: 31102094" , addthis_String2)

Sys.sleep(1)


articles <- articles %>%

add_row(

ArticleCitation = PMID_31102094,
PMID = PMID_31102094$eprint,
Title = PMID_31102094$title,
# Author = PMID_31102094$author,
# Abstract = PMID_31102094$abstract,
Journal = PMID_31102094$journal,
Year = PMID_31102094$year,
Month = PMID_31102094$month,
# Volume = PMID_31102094$volume,
# Number = PMID_31102094$number,
# Pages = PMID_31102094$pages,
PubMedLink = paste0('https://www.ncbi.nlm.nih.gov/pubmed/?term=', PMID_31102094$eprint),
DoiNumber = PMID_31102094$doi,
DoiLink = paste0('https://doi.org/', PMID_31102094$doi),
Language = PMID_31102094$language,
ISSN = PMID_31102094$issn
) %>%

unique()


Sys.sleep(1)

saveRDS(articles, '~/JournalWatchPBPath/articles.rds')

```

<details open> <summary>
- **`r PMID_31102094$title`**
</summary> 

*`r citation_31102094`*

`r PubMed_31102094`

<!-- `r addthis_inline_31102094` -->

`r PMID_31102094$abstract`

`r doi_31102094`

<!-- `r dimensionBadge_31102094` -->

<!-- `r altmetricBadge_31102094` -->

</details>

---




---

```{r gallbladder 30969156, include=FALSE}

articles <- readRDS('~/JournalWatchPBPath/articles.rds')


PMID_30969156 <- RefManageR::ReadPubMed('30969156', database = 'PubMed')

citation_30969156 <- paste0(PMID_30969156$journal,' ', PMID_30969156$year, ' ', PMID_30969156$month,';', PMID_30969156$volume,'(', PMID_30969156$number,'):', PMID_30969156$pages)

PubMed_30969156 <- paste0(PubMedString, PMID_30969156$eprint)

doi_30969156 <- paste0(doiString, PMID_30969156$doi)

dimensionBadge_30969156 <- paste0(dimensionString1, PMID_30969156$doi,dimensionString2)

altmetricBadge_30969156 <- paste0(altmetricString1, PMID_30969156$doi, altmetricString2 )

addthis_inline_30969156 <- paste0(addthis_String1, PMID_30969156$title , " PMID: 30969156" , addthis_String2)

Sys.sleep(1)


articles <- articles %>%

add_row(

ArticleCitation = PMID_30969156,
PMID = PMID_30969156$eprint,
Title = PMID_30969156$title,
# Author = PMID_30969156$author,
# Abstract = PMID_30969156$abstract,
Journal = PMID_30969156$journal,
Year = PMID_30969156$year,
Month = PMID_30969156$month,
# Volume = PMID_30969156$volume,
# Number = PMID_30969156$number,
# Pages = PMID_30969156$pages,
PubMedLink = paste0('https://www.ncbi.nlm.nih.gov/pubmed/?term=', PMID_30969156$eprint),
DoiNumber = PMID_30969156$doi,
DoiLink = paste0('https://doi.org/', PMID_30969156$doi),
Language = PMID_30969156$language,
ISSN = PMID_30969156$issn
) %>%

unique()


Sys.sleep(1)

saveRDS(articles, '~/JournalWatchPBPath/articles.rds')

```

<details open> <summary>
- **`r PMID_30969156$title`**
</summary> 

*`r citation_30969156`*

`r PubMed_30969156`

<!-- `r addthis_inline_30969156` -->

`r PMID_30969156$abstract`

`r doi_30969156`

<!-- `r dimensionBadge_30969156` -->

<!-- `r altmetricBadge_30969156` -->

</details>

---




---

```{r gallbladder 31356229, include=FALSE}

articles <- readRDS('~/JournalWatchPBPath/articles.rds')


PMID_31356229 <- RefManageR::ReadPubMed('31356229', database = 'PubMed')

citation_31356229 <- paste0(PMID_31356229$journal,' ', PMID_31356229$year, ' ', PMID_31356229$month,';', PMID_31356229$volume,'(', PMID_31356229$number,'):', PMID_31356229$pages)

PubMed_31356229 <- paste0(PubMedString, PMID_31356229$eprint)

doi_31356229 <- paste0(doiString, PMID_31356229$doi)

dimensionBadge_31356229 <- paste0(dimensionString1, PMID_31356229$doi,dimensionString2)

altmetricBadge_31356229 <- paste0(altmetricString1, PMID_31356229$doi, altmetricString2 )

addthis_inline_31356229 <- paste0(addthis_String1, PMID_31356229$title , " PMID: 31356229" , addthis_String2)

Sys.sleep(1)


articles <- articles %>%

add_row(

ArticleCitation = PMID_31356229,
PMID = PMID_31356229$eprint,
Title = PMID_31356229$title,
# Author = PMID_31356229$author,
# Abstract = PMID_31356229$abstract,
Journal = PMID_31356229$journal,
Year = PMID_31356229$year,
Month = PMID_31356229$month,
# Volume = PMID_31356229$volume,
# Number = PMID_31356229$number,
# Pages = PMID_31356229$pages,
PubMedLink = paste0('https://www.ncbi.nlm.nih.gov/pubmed/?term=', PMID_31356229$eprint),
DoiNumber = PMID_31356229$doi,
DoiLink = paste0('https://doi.org/', PMID_31356229$doi),
Language = PMID_31356229$language,
ISSN = PMID_31356229$issn
) %>%

unique()


Sys.sleep(1)

saveRDS(articles, '~/JournalWatchPBPath/articles.rds')

```

<details open> <summary>
- **`r PMID_31356229$title`**
</summary> 

*`r citation_31356229`*

`r PubMed_31356229`

<!-- `r addthis_inline_31356229` -->

`r PMID_31356229$abstract`

`r doi_31356229`

<!-- `r dimensionBadge_31356229` -->

<!-- `r altmetricBadge_31356229` -->

</details>

---




---

```{r gallbladder 31240450, include=FALSE}

articles <- readRDS('~/JournalWatchPBPath/articles.rds')


PMID_31240450 <- RefManageR::ReadPubMed('31240450', database = 'PubMed')

citation_31240450 <- paste0(PMID_31240450$journal,' ', PMID_31240450$year, ' ', PMID_31240450$month,';', PMID_31240450$volume,'(', PMID_31240450$number,'):', PMID_31240450$pages)

PubMed_31240450 <- paste0(PubMedString, PMID_31240450$eprint)

doi_31240450 <- paste0(doiString, PMID_31240450$doi)

dimensionBadge_31240450 <- paste0(dimensionString1, PMID_31240450$doi,dimensionString2)

altmetricBadge_31240450 <- paste0(altmetricString1, PMID_31240450$doi, altmetricString2 )

addthis_inline_31240450 <- paste0(addthis_String1, PMID_31240450$title , " PMID: 31240450" , addthis_String2)

Sys.sleep(1)


articles <- articles %>%

add_row(

ArticleCitation = PMID_31240450,
PMID = PMID_31240450$eprint,
Title = PMID_31240450$title,
# Author = PMID_31240450$author,
# Abstract = PMID_31240450$abstract,
Journal = PMID_31240450$journal,
Year = PMID_31240450$year,
Month = PMID_31240450$month,
# Volume = PMID_31240450$volume,
# Number = PMID_31240450$number,
# Pages = PMID_31240450$pages,
PubMedLink = paste0('https://www.ncbi.nlm.nih.gov/pubmed/?term=', PMID_31240450$eprint),
DoiNumber = PMID_31240450$doi,
DoiLink = paste0('https://doi.org/', PMID_31240450$doi),
Language = PMID_31240450$language,
ISSN = PMID_31240450$issn
) %>%

unique()


Sys.sleep(1)

saveRDS(articles, '~/JournalWatchPBPath/articles.rds')

```

<details open> <summary>
- **`r PMID_31240450$title`**
</summary> 

*`r citation_31240450`*

`r PubMed_31240450`

<!-- `r addthis_inline_31240450` -->

`r PMID_31240450$abstract`

`r doi_31240450`

<!-- `r dimensionBadge_31240450` -->

<!-- `r altmetricBadge_31240450` -->

</details>

---




---

```{r gallbladder 31044440, include=FALSE}

articles <- readRDS('~/JournalWatchPBPath/articles.rds')


PMID_31044440 <- RefManageR::ReadPubMed('31044440', database = 'PubMed')

citation_31044440 <- paste0(PMID_31044440$journal,' ', PMID_31044440$year, ' ', PMID_31044440$month,';', PMID_31044440$volume,'(', PMID_31044440$number,'):', PMID_31044440$pages)

PubMed_31044440 <- paste0(PubMedString, PMID_31044440$eprint)

doi_31044440 <- paste0(doiString, PMID_31044440$doi)

dimensionBadge_31044440 <- paste0(dimensionString1, PMID_31044440$doi,dimensionString2)

altmetricBadge_31044440 <- paste0(altmetricString1, PMID_31044440$doi, altmetricString2 )

addthis_inline_31044440 <- paste0(addthis_String1, PMID_31044440$title , " PMID: 31044440" , addthis_String2)

Sys.sleep(1)


articles <- articles %>%

add_row(

ArticleCitation = PMID_31044440,
PMID = PMID_31044440$eprint,
Title = PMID_31044440$title,
# Author = PMID_31044440$author,
# Abstract = PMID_31044440$abstract,
Journal = PMID_31044440$journal,
Year = PMID_31044440$year,
Month = PMID_31044440$month,
# Volume = PMID_31044440$volume,
# Number = PMID_31044440$number,
# Pages = PMID_31044440$pages,
PubMedLink = paste0('https://www.ncbi.nlm.nih.gov/pubmed/?term=', PMID_31044440$eprint),
DoiNumber = PMID_31044440$doi,
DoiLink = paste0('https://doi.org/', PMID_31044440$doi),
Language = PMID_31044440$language,
ISSN = PMID_31044440$issn
) %>%

unique()


Sys.sleep(1)

saveRDS(articles, '~/JournalWatchPBPath/articles.rds')

```

<details open> <summary>
- **`r PMID_31044440$title`**
</summary> 

*`r citation_31044440`*

`r PubMed_31044440`

<!-- `r addthis_inline_31044440` -->

`r PMID_31044440$abstract`

`r doi_31044440`

<!-- `r dimensionBadge_31044440` -->

<!-- `r altmetricBadge_31044440` -->

</details>

---




---

```{r gallbladder 30882917, include=FALSE}

articles <- readRDS('~/JournalWatchPBPath/articles.rds')


PMID_30882917 <- RefManageR::ReadPubMed('30882917', database = 'PubMed')

citation_30882917 <- paste0(PMID_30882917$journal,' ', PMID_30882917$year, ' ', PMID_30882917$month,';', PMID_30882917$volume,'(', PMID_30882917$number,'):', PMID_30882917$pages)

PubMed_30882917 <- paste0(PubMedString, PMID_30882917$eprint)

doi_30882917 <- paste0(doiString, PMID_30882917$doi)

dimensionBadge_30882917 <- paste0(dimensionString1, PMID_30882917$doi,dimensionString2)

altmetricBadge_30882917 <- paste0(altmetricString1, PMID_30882917$doi, altmetricString2 )

addthis_inline_30882917 <- paste0(addthis_String1, PMID_30882917$title , " PMID: 30882917" , addthis_String2)

Sys.sleep(1)


articles <- articles %>%

add_row(

ArticleCitation = PMID_30882917,
PMID = PMID_30882917$eprint,
Title = PMID_30882917$title,
# Author = PMID_30882917$author,
# Abstract = PMID_30882917$abstract,
Journal = PMID_30882917$journal,
Year = PMID_30882917$year,
Month = PMID_30882917$month,
# Volume = PMID_30882917$volume,
# Number = PMID_30882917$number,
# Pages = PMID_30882917$pages,
PubMedLink = paste0('https://www.ncbi.nlm.nih.gov/pubmed/?term=', PMID_30882917$eprint),
DoiNumber = PMID_30882917$doi,
DoiLink = paste0('https://doi.org/', PMID_30882917$doi),
Language = PMID_30882917$language,
ISSN = PMID_30882917$issn
) %>%

unique()


Sys.sleep(1)

saveRDS(articles, '~/JournalWatchPBPath/articles.rds')

```

<details open> <summary>
- **`r PMID_30882917$title`**
</summary> 

*`r citation_30882917`*

`r PubMed_30882917`

<!-- `r addthis_inline_30882917` -->

`r PMID_30882917$abstract`

`r doi_30882917`

<!-- `r dimensionBadge_30882917` -->

<!-- `r altmetricBadge_30882917` -->

</details>

---




---

```{r gallbladder 31464710, include=FALSE}

articles <- readRDS('~/JournalWatchPBPath/articles.rds')


PMID_31464710 <- RefManageR::ReadPubMed('31464710', database = 'PubMed')

citation_31464710 <- paste0(PMID_31464710$journal,' ', PMID_31464710$year, ' ', PMID_31464710$month,';', PMID_31464710$volume,'(', PMID_31464710$number,'):', PMID_31464710$pages)

PubMed_31464710 <- paste0(PubMedString, PMID_31464710$eprint)

doi_31464710 <- paste0(doiString, PMID_31464710$doi)

dimensionBadge_31464710 <- paste0(dimensionString1, PMID_31464710$doi,dimensionString2)

altmetricBadge_31464710 <- paste0(altmetricString1, PMID_31464710$doi, altmetricString2 )

addthis_inline_31464710 <- paste0(addthis_String1, PMID_31464710$title , " PMID: 31464710" , addthis_String2)

Sys.sleep(1)


articles <- articles %>%

add_row(

ArticleCitation = PMID_31464710,
PMID = PMID_31464710$eprint,
Title = PMID_31464710$title,
# Author = PMID_31464710$author,
# Abstract = PMID_31464710$abstract,
Journal = PMID_31464710$journal,
Year = PMID_31464710$year,
Month = PMID_31464710$month,
# Volume = PMID_31464710$volume,
# Number = PMID_31464710$number,
# Pages = PMID_31464710$pages,
PubMedLink = paste0('https://www.ncbi.nlm.nih.gov/pubmed/?term=', PMID_31464710$eprint),
DoiNumber = PMID_31464710$doi,
DoiLink = paste0('https://doi.org/', PMID_31464710$doi),
Language = PMID_31464710$language,
ISSN = PMID_31464710$issn
) %>%

unique()


Sys.sleep(1)

saveRDS(articles, '~/JournalWatchPBPath/articles.rds')

```

<details open> <summary>
- **`r PMID_31464710$title`**
</summary> 

*`r citation_31464710`*

`r PubMed_31464710`

<!-- `r addthis_inline_31464710` -->

`r PMID_31464710$abstract`

`r doi_31464710`

<!-- `r dimensionBadge_31464710` -->

<!-- `r altmetricBadge_31464710` -->

</details>

---




---

```{r gallbladder 31454426, include=FALSE}

articles <- readRDS('~/JournalWatchPBPath/articles.rds')


PMID_31454426 <- RefManageR::ReadPubMed('31454426', database = 'PubMed')

citation_31454426 <- paste0(PMID_31454426$journal,' ', PMID_31454426$year, ' ', PMID_31454426$month,';', PMID_31454426$volume,'(', PMID_31454426$number,'):', PMID_31454426$pages)

PubMed_31454426 <- paste0(PubMedString, PMID_31454426$eprint)

doi_31454426 <- paste0(doiString, PMID_31454426$doi)

dimensionBadge_31454426 <- paste0(dimensionString1, PMID_31454426$doi,dimensionString2)

altmetricBadge_31454426 <- paste0(altmetricString1, PMID_31454426$doi, altmetricString2 )

addthis_inline_31454426 <- paste0(addthis_String1, PMID_31454426$title , " PMID: 31454426" , addthis_String2)

Sys.sleep(1)


articles <- articles %>%

add_row(

ArticleCitation = PMID_31454426,
PMID = PMID_31454426$eprint,
Title = PMID_31454426$title,
# Author = PMID_31454426$author,
# Abstract = PMID_31454426$abstract,
Journal = PMID_31454426$journal,
Year = PMID_31454426$year,
Month = PMID_31454426$month,
# Volume = PMID_31454426$volume,
# Number = PMID_31454426$number,
# Pages = PMID_31454426$pages,
PubMedLink = paste0('https://www.ncbi.nlm.nih.gov/pubmed/?term=', PMID_31454426$eprint),
DoiNumber = PMID_31454426$doi,
DoiLink = paste0('https://doi.org/', PMID_31454426$doi),
Language = PMID_31454426$language,
ISSN = PMID_31454426$issn
) %>%

unique()


Sys.sleep(1)

saveRDS(articles, '~/JournalWatchPBPath/articles.rds')

```

<details open> <summary>
- **`r PMID_31454426$title`**
</summary> 

*`r citation_31454426`*

`r PubMed_31454426`

<!-- `r addthis_inline_31454426` -->

`r PMID_31454426$abstract`

`r doi_31454426`

<!-- `r dimensionBadge_31454426` -->

<!-- `r altmetricBadge_31454426` -->

</details>

---




---

```{r gallbladder 31433924, include=FALSE}

articles <- readRDS('~/JournalWatchPBPath/articles.rds')


PMID_31433924 <- RefManageR::ReadPubMed('31433924', database = 'PubMed')

citation_31433924 <- paste0(PMID_31433924$journal,' ', PMID_31433924$year, ' ', PMID_31433924$month,';', PMID_31433924$volume,'(', PMID_31433924$number,'):', PMID_31433924$pages)

PubMed_31433924 <- paste0(PubMedString, PMID_31433924$eprint)

doi_31433924 <- paste0(doiString, PMID_31433924$doi)

dimensionBadge_31433924 <- paste0(dimensionString1, PMID_31433924$doi,dimensionString2)

altmetricBadge_31433924 <- paste0(altmetricString1, PMID_31433924$doi, altmetricString2 )

addthis_inline_31433924 <- paste0(addthis_String1, PMID_31433924$title , " PMID: 31433924" , addthis_String2)

Sys.sleep(1)


articles <- articles %>%

add_row(

ArticleCitation = PMID_31433924,
PMID = PMID_31433924$eprint,
Title = PMID_31433924$title,
# Author = PMID_31433924$author,
# Abstract = PMID_31433924$abstract,
Journal = PMID_31433924$journal,
Year = PMID_31433924$year,
Month = PMID_31433924$month,
# Volume = PMID_31433924$volume,
# Number = PMID_31433924$number,
# Pages = PMID_31433924$pages,
PubMedLink = paste0('https://www.ncbi.nlm.nih.gov/pubmed/?term=', PMID_31433924$eprint),
DoiNumber = PMID_31433924$doi,
DoiLink = paste0('https://doi.org/', PMID_31433924$doi),
Language = PMID_31433924$language,
ISSN = PMID_31433924$issn
) %>%

unique()


Sys.sleep(1)

saveRDS(articles, '~/JournalWatchPBPath/articles.rds')

```

<details open> <summary>
- **`r PMID_31433924$title`**
</summary> 

*`r citation_31433924`*

`r PubMed_31433924`

<!-- `r addthis_inline_31433924` -->

`r PMID_31433924$abstract`

`r doi_31433924`

<!-- `r dimensionBadge_31433924` -->

<!-- `r altmetricBadge_31433924` -->

</details>

---




---

```{r gallbladder 31433838, include=FALSE}

articles <- readRDS('~/JournalWatchPBPath/articles.rds')


PMID_31433838 <- RefManageR::ReadPubMed('31433838', database = 'PubMed')

citation_31433838 <- paste0(PMID_31433838$journal,' ', PMID_31433838$year, ' ', PMID_31433838$month,';', PMID_31433838$volume,'(', PMID_31433838$number,'):', PMID_31433838$pages)

PubMed_31433838 <- paste0(PubMedString, PMID_31433838$eprint)

doi_31433838 <- paste0(doiString, PMID_31433838$doi)

dimensionBadge_31433838 <- paste0(dimensionString1, PMID_31433838$doi,dimensionString2)

altmetricBadge_31433838 <- paste0(altmetricString1, PMID_31433838$doi, altmetricString2 )

addthis_inline_31433838 <- paste0(addthis_String1, PMID_31433838$title , " PMID: 31433838" , addthis_String2)

Sys.sleep(1)


articles <- articles %>%

add_row(

ArticleCitation = PMID_31433838,
PMID = PMID_31433838$eprint,
Title = PMID_31433838$title,
# Author = PMID_31433838$author,
# Abstract = PMID_31433838$abstract,
Journal = PMID_31433838$journal,
Year = PMID_31433838$year,
Month = PMID_31433838$month,
# Volume = PMID_31433838$volume,
# Number = PMID_31433838$number,
# Pages = PMID_31433838$pages,
PubMedLink = paste0('https://www.ncbi.nlm.nih.gov/pubmed/?term=', PMID_31433838$eprint),
DoiNumber = PMID_31433838$doi,
DoiLink = paste0('https://doi.org/', PMID_31433838$doi),
Language = PMID_31433838$language,
ISSN = PMID_31433838$issn
) %>%

unique()


Sys.sleep(1)

saveRDS(articles, '~/JournalWatchPBPath/articles.rds')

```

<details open> <summary>
- **`r PMID_31433838$title`**
</summary> 

*`r citation_31433838`*

`r PubMed_31433838`

<!-- `r addthis_inline_31433838` -->

`r PMID_31433838$abstract`

`r doi_31433838`

<!-- `r dimensionBadge_31433838` -->

<!-- `r altmetricBadge_31433838` -->

</details>

---




---

```{r gallbladder 31432248, include=FALSE}

articles <- readRDS('~/JournalWatchPBPath/articles.rds')


PMID_31432248 <- RefManageR::ReadPubMed('31432248', database = 'PubMed')

citation_31432248 <- paste0(PMID_31432248$journal,' ', PMID_31432248$year, ' ', PMID_31432248$month,';', PMID_31432248$volume,'(', PMID_31432248$number,'):', PMID_31432248$pages)

PubMed_31432248 <- paste0(PubMedString, PMID_31432248$eprint)

doi_31432248 <- paste0(doiString, PMID_31432248$doi)

dimensionBadge_31432248 <- paste0(dimensionString1, PMID_31432248$doi,dimensionString2)

altmetricBadge_31432248 <- paste0(altmetricString1, PMID_31432248$doi, altmetricString2 )

addthis_inline_31432248 <- paste0(addthis_String1, PMID_31432248$title , " PMID: 31432248" , addthis_String2)

Sys.sleep(1)


articles <- articles %>%

add_row(

ArticleCitation = PMID_31432248,
PMID = PMID_31432248$eprint,
Title = PMID_31432248$title,
# Author = PMID_31432248$author,
# Abstract = PMID_31432248$abstract,
Journal = PMID_31432248$journal,
Year = PMID_31432248$year,
Month = PMID_31432248$month,
# Volume = PMID_31432248$volume,
# Number = PMID_31432248$number,
# Pages = PMID_31432248$pages,
PubMedLink = paste0('https://www.ncbi.nlm.nih.gov/pubmed/?term=', PMID_31432248$eprint),
DoiNumber = PMID_31432248$doi,
DoiLink = paste0('https://doi.org/', PMID_31432248$doi),
Language = PMID_31432248$language,
ISSN = PMID_31432248$issn
) %>%

unique()


Sys.sleep(1)

saveRDS(articles, '~/JournalWatchPBPath/articles.rds')

```

<details open> <summary>
- **`r PMID_31432248$title`**
</summary> 

*`r citation_31432248`*

`r PubMed_31432248`

<!-- `r addthis_inline_31432248` -->

`r PMID_31432248$abstract`

`r doi_31432248`

<!-- `r dimensionBadge_31432248` -->

<!-- `r altmetricBadge_31432248` -->

</details>

---




---

```{r gallbladder 30988082, include=FALSE}

articles <- readRDS('~/JournalWatchPBPath/articles.rds')


PMID_30988082 <- RefManageR::ReadPubMed('30988082', database = 'PubMed')

citation_30988082 <- paste0(PMID_30988082$journal,' ', PMID_30988082$year, ' ', PMID_30988082$month,';', PMID_30988082$volume,'(', PMID_30988082$number,'):', PMID_30988082$pages)

PubMed_30988082 <- paste0(PubMedString, PMID_30988082$eprint)

doi_30988082 <- paste0(doiString, PMID_30988082$doi)

dimensionBadge_30988082 <- paste0(dimensionString1, PMID_30988082$doi,dimensionString2)

altmetricBadge_30988082 <- paste0(altmetricString1, PMID_30988082$doi, altmetricString2 )

addthis_inline_30988082 <- paste0(addthis_String1, PMID_30988082$title , " PMID: 30988082" , addthis_String2)

Sys.sleep(1)


articles <- articles %>%

add_row(

ArticleCitation = PMID_30988082,
PMID = PMID_30988082$eprint,
Title = PMID_30988082$title,
# Author = PMID_30988082$author,
# Abstract = PMID_30988082$abstract,
Journal = PMID_30988082$journal,
Year = PMID_30988082$year,
Month = PMID_30988082$month,
# Volume = PMID_30988082$volume,
# Number = PMID_30988082$number,
# Pages = PMID_30988082$pages,
PubMedLink = paste0('https://www.ncbi.nlm.nih.gov/pubmed/?term=', PMID_30988082$eprint),
DoiNumber = PMID_30988082$doi,
DoiLink = paste0('https://doi.org/', PMID_30988082$doi),
Language = PMID_30988082$language,
ISSN = PMID_30988082$issn
) %>%

unique()


Sys.sleep(1)

saveRDS(articles, '~/JournalWatchPBPath/articles.rds')

```

<details open> <summary>
- **`r PMID_30988082$title`**
</summary> 

*`r citation_30988082`*

`r PubMed_30988082`

<!-- `r addthis_inline_30988082` -->

`r PMID_30988082$abstract`

`r doi_30988082`

<!-- `r dimensionBadge_30988082` -->

<!-- `r altmetricBadge_30988082` -->

</details>

---




---

```{r gallbladder 31391032, include=FALSE}

articles <- readRDS('~/JournalWatchPBPath/articles.rds')


PMID_31391032 <- RefManageR::ReadPubMed('31391032', database = 'PubMed')

citation_31391032 <- paste0(PMID_31391032$journal,' ', PMID_31391032$year, ' ', PMID_31391032$month,';', PMID_31391032$volume,'(', PMID_31391032$number,'):', PMID_31391032$pages)

PubMed_31391032 <- paste0(PubMedString, PMID_31391032$eprint)

doi_31391032 <- paste0(doiString, PMID_31391032$doi)

dimensionBadge_31391032 <- paste0(dimensionString1, PMID_31391032$doi,dimensionString2)

altmetricBadge_31391032 <- paste0(altmetricString1, PMID_31391032$doi, altmetricString2 )

addthis_inline_31391032 <- paste0(addthis_String1, PMID_31391032$title , " PMID: 31391032" , addthis_String2)

Sys.sleep(1)


articles <- articles %>%

add_row(

ArticleCitation = PMID_31391032,
PMID = PMID_31391032$eprint,
Title = PMID_31391032$title,
# Author = PMID_31391032$author,
# Abstract = PMID_31391032$abstract,
Journal = PMID_31391032$journal,
Year = PMID_31391032$year,
Month = PMID_31391032$month,
# Volume = PMID_31391032$volume,
# Number = PMID_31391032$number,
# Pages = PMID_31391032$pages,
PubMedLink = paste0('https://www.ncbi.nlm.nih.gov/pubmed/?term=', PMID_31391032$eprint),
DoiNumber = PMID_31391032$doi,
DoiLink = paste0('https://doi.org/', PMID_31391032$doi),
Language = PMID_31391032$language,
ISSN = PMID_31391032$issn
) %>%

unique()


Sys.sleep(1)

saveRDS(articles, '~/JournalWatchPBPath/articles.rds')

```

<details open> <summary>
- **`r PMID_31391032$title`**
</summary> 

*`r citation_31391032`*

`r PubMed_31391032`

<!-- `r addthis_inline_31391032` -->

`r PMID_31391032$abstract`

`r doi_31391032`

<!-- `r dimensionBadge_31391032` -->

<!-- `r altmetricBadge_31391032` -->

</details>

---




---

```{r gallbladder 31382888, include=FALSE}

articles <- readRDS('~/JournalWatchPBPath/articles.rds')


PMID_31382888 <- RefManageR::ReadPubMed('31382888', database = 'PubMed')

citation_31382888 <- paste0(PMID_31382888$journal,' ', PMID_31382888$year, ' ', PMID_31382888$month,';', PMID_31382888$volume,'(', PMID_31382888$number,'):', PMID_31382888$pages)

PubMed_31382888 <- paste0(PubMedString, PMID_31382888$eprint)

doi_31382888 <- paste0(doiString, PMID_31382888$doi)

dimensionBadge_31382888 <- paste0(dimensionString1, PMID_31382888$doi,dimensionString2)

altmetricBadge_31382888 <- paste0(altmetricString1, PMID_31382888$doi, altmetricString2 )

addthis_inline_31382888 <- paste0(addthis_String1, PMID_31382888$title , " PMID: 31382888" , addthis_String2)

Sys.sleep(1)


articles <- articles %>%

add_row(

ArticleCitation = PMID_31382888,
PMID = PMID_31382888$eprint,
Title = PMID_31382888$title,
# Author = PMID_31382888$author,
# Abstract = PMID_31382888$abstract,
Journal = PMID_31382888$journal,
Year = PMID_31382888$year,
Month = PMID_31382888$month,
# Volume = PMID_31382888$volume,
# Number = PMID_31382888$number,
# Pages = PMID_31382888$pages,
PubMedLink = paste0('https://www.ncbi.nlm.nih.gov/pubmed/?term=', PMID_31382888$eprint),
DoiNumber = PMID_31382888$doi,
DoiLink = paste0('https://doi.org/', PMID_31382888$doi),
Language = PMID_31382888$language,
ISSN = PMID_31382888$issn
) %>%

unique()


Sys.sleep(1)

saveRDS(articles, '~/JournalWatchPBPath/articles.rds')

```

<details open> <summary>
- **`r PMID_31382888$title`**
</summary> 

*`r citation_31382888`*

`r PubMed_31382888`

<!-- `r addthis_inline_31382888` -->

`r PMID_31382888$abstract`

`r doi_31382888`

<!-- `r dimensionBadge_31382888` -->

<!-- `r altmetricBadge_31382888` -->

</details>

---




---

```{r gallbladder 31268981, include=FALSE}

articles <- readRDS('~/JournalWatchPBPath/articles.rds')


PMID_31268981 <- RefManageR::ReadPubMed('31268981', database = 'PubMed')

citation_31268981 <- paste0(PMID_31268981$journal,' ', PMID_31268981$year, ' ', PMID_31268981$month,';', PMID_31268981$volume,'(', PMID_31268981$number,'):', PMID_31268981$pages)

PubMed_31268981 <- paste0(PubMedString, PMID_31268981$eprint)

doi_31268981 <- paste0(doiString, PMID_31268981$doi)

dimensionBadge_31268981 <- paste0(dimensionString1, PMID_31268981$doi,dimensionString2)

altmetricBadge_31268981 <- paste0(altmetricString1, PMID_31268981$doi, altmetricString2 )

addthis_inline_31268981 <- paste0(addthis_String1, PMID_31268981$title , " PMID: 31268981" , addthis_String2)

Sys.sleep(1)


articles <- articles %>%

add_row(

ArticleCitation = PMID_31268981,
PMID = PMID_31268981$eprint,
Title = PMID_31268981$title,
# Author = PMID_31268981$author,
# Abstract = PMID_31268981$abstract,
Journal = PMID_31268981$journal,
Year = PMID_31268981$year,
Month = PMID_31268981$month,
# Volume = PMID_31268981$volume,
# Number = PMID_31268981$number,
# Pages = PMID_31268981$pages,
PubMedLink = paste0('https://www.ncbi.nlm.nih.gov/pubmed/?term=', PMID_31268981$eprint),
DoiNumber = PMID_31268981$doi,
DoiLink = paste0('https://doi.org/', PMID_31268981$doi),
Language = PMID_31268981$language,
ISSN = PMID_31268981$issn
) %>%

unique()


Sys.sleep(1)

saveRDS(articles, '~/JournalWatchPBPath/articles.rds')

```

<details open> <summary>
- **`r PMID_31268981$title`**
</summary> 

*`r citation_31268981`*

`r PubMed_31268981`

<!-- `r addthis_inline_31268981` -->

`r PMID_31268981$abstract`

`r doi_31268981`

<!-- `r dimensionBadge_31268981` -->

<!-- `r altmetricBadge_31268981` -->

</details>

---




---

```{r gallbladder 31189015, include=FALSE}

articles <- readRDS('~/JournalWatchPBPath/articles.rds')


PMID_31189015 <- RefManageR::ReadPubMed('31189015', database = 'PubMed')

citation_31189015 <- paste0(PMID_31189015$journal,' ', PMID_31189015$year, ' ', PMID_31189015$month,';', PMID_31189015$volume,'(', PMID_31189015$number,'):', PMID_31189015$pages)

PubMed_31189015 <- paste0(PubMedString, PMID_31189015$eprint)

doi_31189015 <- paste0(doiString, PMID_31189015$doi)

dimensionBadge_31189015 <- paste0(dimensionString1, PMID_31189015$doi,dimensionString2)

altmetricBadge_31189015 <- paste0(altmetricString1, PMID_31189015$doi, altmetricString2 )

addthis_inline_31189015 <- paste0(addthis_String1, PMID_31189015$title , " PMID: 31189015" , addthis_String2)

Sys.sleep(1)


articles <- articles %>%

add_row(

ArticleCitation = PMID_31189015,
PMID = PMID_31189015$eprint,
Title = PMID_31189015$title,
# Author = PMID_31189015$author,
# Abstract = PMID_31189015$abstract,
Journal = PMID_31189015$journal,
Year = PMID_31189015$year,
Month = PMID_31189015$month,
# Volume = PMID_31189015$volume,
# Number = PMID_31189015$number,
# Pages = PMID_31189015$pages,
PubMedLink = paste0('https://www.ncbi.nlm.nih.gov/pubmed/?term=', PMID_31189015$eprint),
DoiNumber = PMID_31189015$doi,
DoiLink = paste0('https://doi.org/', PMID_31189015$doi),
Language = PMID_31189015$language,
ISSN = PMID_31189015$issn
) %>%

unique()


Sys.sleep(1)

saveRDS(articles, '~/JournalWatchPBPath/articles.rds')

```

<details open> <summary>
- **`r PMID_31189015$title`**
</summary> 

*`r citation_31189015`*

`r PubMed_31189015`

<!-- `r addthis_inline_31189015` -->

`r PMID_31189015$abstract`

`r doi_31189015`

<!-- `r dimensionBadge_31189015` -->

<!-- `r altmetricBadge_31189015` -->

</details>

---




---

```{r gallbladder 31109808, include=FALSE}

articles <- readRDS('~/JournalWatchPBPath/articles.rds')


PMID_31109808 <- RefManageR::ReadPubMed('31109808', database = 'PubMed')

citation_31109808 <- paste0(PMID_31109808$journal,' ', PMID_31109808$year, ' ', PMID_31109808$month,';', PMID_31109808$volume,'(', PMID_31109808$number,'):', PMID_31109808$pages)

PubMed_31109808 <- paste0(PubMedString, PMID_31109808$eprint)

doi_31109808 <- paste0(doiString, PMID_31109808$doi)

dimensionBadge_31109808 <- paste0(dimensionString1, PMID_31109808$doi,dimensionString2)

altmetricBadge_31109808 <- paste0(altmetricString1, PMID_31109808$doi, altmetricString2 )

addthis_inline_31109808 <- paste0(addthis_String1, PMID_31109808$title , " PMID: 31109808" , addthis_String2)

Sys.sleep(1)


articles <- articles %>%

add_row(

ArticleCitation = PMID_31109808,
PMID = PMID_31109808$eprint,
Title = PMID_31109808$title,
# Author = PMID_31109808$author,
# Abstract = PMID_31109808$abstract,
Journal = PMID_31109808$journal,
Year = PMID_31109808$year,
Month = PMID_31109808$month,
# Volume = PMID_31109808$volume,
# Number = PMID_31109808$number,
# Pages = PMID_31109808$pages,
PubMedLink = paste0('https://www.ncbi.nlm.nih.gov/pubmed/?term=', PMID_31109808$eprint),
DoiNumber = PMID_31109808$doi,
DoiLink = paste0('https://doi.org/', PMID_31109808$doi),
Language = PMID_31109808$language,
ISSN = PMID_31109808$issn
) %>%

unique()


Sys.sleep(1)

saveRDS(articles, '~/JournalWatchPBPath/articles.rds')

```

<details open> <summary>
- **`r PMID_31109808$title`**
</summary> 

*`r citation_31109808`*

`r PubMed_31109808`

<!-- `r addthis_inline_31109808` -->

`r PMID_31109808$abstract`

`r doi_31109808`

<!-- `r dimensionBadge_31109808` -->

<!-- `r altmetricBadge_31109808` -->

</details>

---




---

```{r gallbladder 30912695, include=FALSE}

articles <- readRDS('~/JournalWatchPBPath/articles.rds')


PMID_30912695 <- RefManageR::ReadPubMed('30912695', database = 'PubMed')

citation_30912695 <- paste0(PMID_30912695$journal,' ', PMID_30912695$year, ' ', PMID_30912695$month,';', PMID_30912695$volume,'(', PMID_30912695$number,'):', PMID_30912695$pages)

PubMed_30912695 <- paste0(PubMedString, PMID_30912695$eprint)

doi_30912695 <- paste0(doiString, PMID_30912695$doi)

dimensionBadge_30912695 <- paste0(dimensionString1, PMID_30912695$doi,dimensionString2)

altmetricBadge_30912695 <- paste0(altmetricString1, PMID_30912695$doi, altmetricString2 )

addthis_inline_30912695 <- paste0(addthis_String1, PMID_30912695$title , " PMID: 30912695" , addthis_String2)

Sys.sleep(1)


articles <- articles %>%

add_row(

ArticleCitation = PMID_30912695,
PMID = PMID_30912695$eprint,
Title = PMID_30912695$title,
# Author = PMID_30912695$author,
# Abstract = PMID_30912695$abstract,
Journal = PMID_30912695$journal,
Year = PMID_30912695$year,
Month = PMID_30912695$month,
# Volume = PMID_30912695$volume,
# Number = PMID_30912695$number,
# Pages = PMID_30912695$pages,
PubMedLink = paste0('https://www.ncbi.nlm.nih.gov/pubmed/?term=', PMID_30912695$eprint),
DoiNumber = PMID_30912695$doi,
DoiLink = paste0('https://doi.org/', PMID_30912695$doi),
Language = PMID_30912695$language,
ISSN = PMID_30912695$issn
) %>%

unique()


Sys.sleep(1)

saveRDS(articles, '~/JournalWatchPBPath/articles.rds')

```

<details open> <summary>
- **`r PMID_30912695$title`**
</summary> 

*`r citation_30912695`*

`r PubMed_30912695`

<!-- `r addthis_inline_30912695` -->

`r PMID_30912695$abstract`

`r doi_30912695`

<!-- `r dimensionBadge_30912695` -->

<!-- `r altmetricBadge_30912695` -->

</details>

---




---

```{r gallbladder 30520351, include=FALSE}

articles <- readRDS('~/JournalWatchPBPath/articles.rds')


PMID_30520351 <- RefManageR::ReadPubMed('30520351', database = 'PubMed')

citation_30520351 <- paste0(PMID_30520351$journal,' ', PMID_30520351$year, ' ', PMID_30520351$month,';', PMID_30520351$volume,'(', PMID_30520351$number,'):', PMID_30520351$pages)

PubMed_30520351 <- paste0(PubMedString, PMID_30520351$eprint)

doi_30520351 <- paste0(doiString, PMID_30520351$doi)

dimensionBadge_30520351 <- paste0(dimensionString1, PMID_30520351$doi,dimensionString2)

altmetricBadge_30520351 <- paste0(altmetricString1, PMID_30520351$doi, altmetricString2 )

addthis_inline_30520351 <- paste0(addthis_String1, PMID_30520351$title , " PMID: 30520351" , addthis_String2)

Sys.sleep(1)


articles <- articles %>%

add_row(

ArticleCitation = PMID_30520351,
PMID = PMID_30520351$eprint,
Title = PMID_30520351$title,
# Author = PMID_30520351$author,
# Abstract = PMID_30520351$abstract,
Journal = PMID_30520351$journal,
Year = PMID_30520351$year,
Month = PMID_30520351$month,
# Volume = PMID_30520351$volume,
# Number = PMID_30520351$number,
# Pages = PMID_30520351$pages,
PubMedLink = paste0('https://www.ncbi.nlm.nih.gov/pubmed/?term=', PMID_30520351$eprint),
DoiNumber = PMID_30520351$doi,
DoiLink = paste0('https://doi.org/', PMID_30520351$doi),
Language = PMID_30520351$language,
ISSN = PMID_30520351$issn
) %>%

unique()


Sys.sleep(1)

saveRDS(articles, '~/JournalWatchPBPath/articles.rds')

```

<details open> <summary>
- **`r PMID_30520351$title`**
</summary> 

*`r citation_30520351`*

`r PubMed_30520351`

<!-- `r addthis_inline_30520351` -->

`r PMID_30520351$abstract`

`r doi_30520351`

<!-- `r dimensionBadge_30520351` -->

<!-- `r altmetricBadge_30520351` -->

</details>

---




---

```{r gallbladder 29464551, include=FALSE}

articles <- readRDS('~/JournalWatchPBPath/articles.rds')


PMID_29464551 <- RefManageR::ReadPubMed('29464551', database = 'PubMed')

citation_29464551 <- paste0(PMID_29464551$journal,' ', PMID_29464551$year, ' ', PMID_29464551$month,';', PMID_29464551$volume,'(', PMID_29464551$number,'):', PMID_29464551$pages)

PubMed_29464551 <- paste0(PubMedString, PMID_29464551$eprint)

doi_29464551 <- paste0(doiString, PMID_29464551$doi)

dimensionBadge_29464551 <- paste0(dimensionString1, PMID_29464551$doi,dimensionString2)

altmetricBadge_29464551 <- paste0(altmetricString1, PMID_29464551$doi, altmetricString2 )

addthis_inline_29464551 <- paste0(addthis_String1, PMID_29464551$title , " PMID: 29464551" , addthis_String2)

Sys.sleep(1)


articles <- articles %>%

add_row(

ArticleCitation = PMID_29464551,
PMID = PMID_29464551$eprint,
Title = PMID_29464551$title,
# Author = PMID_29464551$author,
# Abstract = PMID_29464551$abstract,
Journal = PMID_29464551$journal,
Year = PMID_29464551$year,
Month = PMID_29464551$month,
# Volume = PMID_29464551$volume,
# Number = PMID_29464551$number,
# Pages = PMID_29464551$pages,
PubMedLink = paste0('https://www.ncbi.nlm.nih.gov/pubmed/?term=', PMID_29464551$eprint),
DoiNumber = PMID_29464551$doi,
DoiLink = paste0('https://doi.org/', PMID_29464551$doi),
Language = PMID_29464551$language,
ISSN = PMID_29464551$issn
) %>%

unique()


Sys.sleep(1)

saveRDS(articles, '~/JournalWatchPBPath/articles.rds')

```

<details open> <summary>
- **`r PMID_29464551$title`**
</summary> 

*`r citation_29464551`*

`r PubMed_29464551`

<!-- `r addthis_inline_29464551` -->

`r PMID_29464551$abstract`

`r doi_29464551`

<!-- `r dimensionBadge_29464551` -->

<!-- `r altmetricBadge_29464551` -->

</details>

---




---

```{r gallbladder 31741109, include=FALSE}

articles <- readRDS('~/JournalWatchPBPath/articles.rds')


PMID_31741109 <- RefManageR::ReadPubMed('31741109', database = 'PubMed')

citation_31741109 <- paste0(PMID_31741109$journal,' ', PMID_31741109$year, ' ', PMID_31741109$month,';', PMID_31741109$volume,'(', PMID_31741109$number,'):', PMID_31741109$pages)

PubMed_31741109 <- paste0(PubMedString, PMID_31741109$eprint)

doi_31741109 <- paste0(doiString, PMID_31741109$doi)

dimensionBadge_31741109 <- paste0(dimensionString1, PMID_31741109$doi,dimensionString2)

altmetricBadge_31741109 <- paste0(altmetricString1, PMID_31741109$doi, altmetricString2 )

addthis_inline_31741109 <- paste0(addthis_String1, PMID_31741109$title , " PMID: 31741109" , addthis_String2)

Sys.sleep(1)


articles <- articles %>%

add_row(

ArticleCitation = PMID_31741109,
PMID = PMID_31741109$eprint,
Title = PMID_31741109$title,
# Author = PMID_31741109$author,
# Abstract = PMID_31741109$abstract,
Journal = PMID_31741109$journal,
Year = PMID_31741109$year,
Month = PMID_31741109$month,
# Volume = PMID_31741109$volume,
# Number = PMID_31741109$number,
# Pages = PMID_31741109$pages,
PubMedLink = paste0('https://www.ncbi.nlm.nih.gov/pubmed/?term=', PMID_31741109$eprint),
DoiNumber = PMID_31741109$doi,
DoiLink = paste0('https://doi.org/', PMID_31741109$doi),
Language = PMID_31741109$language,
ISSN = PMID_31741109$issn
) %>%

unique()


Sys.sleep(1)

saveRDS(articles, '~/JournalWatchPBPath/articles.rds')

```

<details open> <summary>
- **`r PMID_31741109$title`**
</summary> 

*`r citation_31741109`*

`r PubMed_31741109`

<!-- `r addthis_inline_31741109` -->

`r PMID_31741109$abstract`

`r doi_31741109`

<!-- `r dimensionBadge_31741109` -->

<!-- `r altmetricBadge_31741109` -->

</details>

---




---

```{r gallbladder 31745968, include=FALSE}

articles <- readRDS('~/JournalWatchPBPath/articles.rds')


PMID_31745968 <- RefManageR::ReadPubMed('31745968', database = 'PubMed')

citation_31745968 <- paste0(PMID_31745968$journal,' ', PMID_31745968$year, ' ', PMID_31745968$month,';', PMID_31745968$volume,'(', PMID_31745968$number,'):', PMID_31745968$pages)

PubMed_31745968 <- paste0(PubMedString, PMID_31745968$eprint)

doi_31745968 <- paste0(doiString, PMID_31745968$doi)

dimensionBadge_31745968 <- paste0(dimensionString1, PMID_31745968$doi,dimensionString2)

altmetricBadge_31745968 <- paste0(altmetricString1, PMID_31745968$doi, altmetricString2 )

addthis_inline_31745968 <- paste0(addthis_String1, PMID_31745968$title , " PMID: 31745968" , addthis_String2)

Sys.sleep(1)


articles <- articles %>%

add_row(

ArticleCitation = PMID_31745968,
PMID = PMID_31745968$eprint,
Title = PMID_31745968$title,
# Author = PMID_31745968$author,
# Abstract = PMID_31745968$abstract,
Journal = PMID_31745968$journal,
Year = PMID_31745968$year,
Month = PMID_31745968$month,
# Volume = PMID_31745968$volume,
# Number = PMID_31745968$number,
# Pages = PMID_31745968$pages,
PubMedLink = paste0('https://www.ncbi.nlm.nih.gov/pubmed/?term=', PMID_31745968$eprint),
DoiNumber = PMID_31745968$doi,
DoiLink = paste0('https://doi.org/', PMID_31745968$doi),
Language = PMID_31745968$language,
ISSN = PMID_31745968$issn
) %>%

unique()


Sys.sleep(1)

saveRDS(articles, '~/JournalWatchPBPath/articles.rds')

```

<details open> <summary>
- **`r PMID_31745968$title`**
</summary> 

*`r citation_31745968`*

`r PubMed_31745968`

<!-- `r addthis_inline_31745968` -->

`r PMID_31745968$abstract`

`r doi_31745968`

<!-- `r dimensionBadge_31745968` -->

<!-- `r altmetricBadge_31745968` -->

</details>

---


