---
title: "Animal Studies"
output: html_notebook
---



### Animal Studies


```{r Pancreas Animal Studies, eval=FALSE, include=FALSE}
```


---

```{r 30474270, include=FALSE}

PMID_30474270 <- RefManageR::ReadPubMed('30474270', database = 'PubMed')

citation_30474270 <- paste0(PMID_30474270$journal,' ', PMID_30474270$year, ' ', PMID_30474270$month,';', PMID_30474270$volume,'(', PMID_30474270$number,'):', PMID_30474270$pages)

PubMed_30474270 <- paste0(PubMedString, PMID_30474270$eprint)

doi_30474270 <- paste0(doiString, PMID_30474270$doi)

dimensionBadge_30474270 <- paste0(dimensionString1, PMID_30474270$doi,dimensionString2)

altmetricBadge_30474270 <- paste0(altmetricString1, PMID_30474270$doi, altmetricString2 )

addthis_inline_30474270 <- paste0(addthis_String1, PMID_30474270$title , " PMID: 30474270 " , addthis_String2)

Sys.sleep(1)

```

<details open> <summary>
- **`r PMID_30474270$title`**
</summary> 

*`r citation_30474270`*

`r PubMed_30474270`

`r addthis_inline_30474270`

`r PMID_30474270$abstract`

<!-- `r doi_30474270` -->

`r dimensionBadge_30474270`

`r altmetricBadge_30474270`

</details>



---

```{r 30315093, include=FALSE}

PMID_30315093 <- RefManageR::ReadPubMed('30315093', database = 'PubMed')

citation_30315093 <- paste0(PMID_30315093$journal,' ', PMID_30315093$year, ' ', PMID_30315093$month,';', PMID_30315093$volume,'(', PMID_30315093$number,'):', PMID_30315093$pages)

PubMed_30315093 <- paste0(PubMedString, PMID_30315093$eprint)

doi_30315093 <- paste0(doiString, PMID_30315093$doi)

dimensionBadge_30315093 <- paste0(dimensionString1, PMID_30315093$doi,dimensionString2)

altmetricBadge_30315093 <- paste0(altmetricString1, PMID_30315093$doi, altmetricString2 )

addthis_inline_30315093 <- paste0(addthis_String1, PMID_30315093$title , " PMID: 30315093 " , addthis_String2)

Sys.sleep(1)


```

<details open> <summary>
- **`r PMID_30315093$title`**
</summary> 

*`r citation_30315093`*

`r PubMed_30315093`

`r addthis_inline_30315093`

`r PMID_30315093$abstract`

<!-- `r doi_30315093` -->

`r dimensionBadge_30315093`

`r altmetricBadge_30315093`

</details>

---


```{r 30405106, include=FALSE}

PMID_30405106 <- RefManageR::ReadPubMed('30405106', database = 'PubMed')

citation_30405106 <- paste0(PMID_30405106$journal,' ', PMID_30405106$year, ' ', PMID_30405106$month,';', PMID_30405106$volume,'(', PMID_30405106$number,'):', PMID_30405106$pages)

PubMed_30405106 <- paste0(PubMedString, PMID_30405106$eprint)

doi_30405106 <- paste0(doiString, PMID_30405106$doi)

dimensionBadge_30405106 <- paste0(dimensionString1, PMID_30405106$doi,dimensionString2)

altmetricBadge_30405106 <- paste0(altmetricString1, PMID_30405106$doi, altmetricString2 )

addthis_inline_30405106 <- paste0(addthis_String1, PMID_30405106$title , " PMID: 30405106 " , addthis_String2)

Sys.sleep(1)


```

<details open> <summary>
- **`r PMID_30405106$title`**
</summary> 

*`r citation_30405106`*

`r PubMed_30405106`

`r addthis_inline_30405106`

`r PMID_30405106$abstract`

<!-- `r doi_30405106` -->

`r dimensionBadge_30405106`

`r altmetricBadge_30405106`

</details>



---

```{r 30423296, include=FALSE}

PMID_30423296 <- RefManageR::ReadPubMed('30423296', database = 'PubMed')

citation_30423296 <- paste0(PMID_30423296$journal,' ', PMID_30423296$year, ' ', PMID_30423296$month,';', PMID_30423296$volume,'(', PMID_30423296$number,'):', PMID_30423296$pages)

PubMed_30423296 <- paste0(PubMedString, PMID_30423296$eprint)

doi_30423296 <- paste0(doiString, PMID_30423296$doi)

dimensionBadge_30423296 <- paste0(dimensionString1, PMID_30423296$doi,dimensionString2)

altmetricBadge_30423296 <- paste0(altmetricString1, PMID_30423296$doi, altmetricString2 )

addthis_inline_30423296 <- paste0(addthis_String1, PMID_30423296$title , " PMID: 30423296 " , addthis_String2)

Sys.sleep(1)

```

<details open> <summary>
- **`r PMID_30423296$title`**
</summary> 

*`r citation_30423296`*

`r PubMed_30423296`

`r addthis_inline_30423296`

`r PMID_30423296$abstract`

<!-- `r doi_30423296` -->

`r dimensionBadge_30423296`

`r altmetricBadge_30423296`

</details>

---

```{r 29249692, include=FALSE}

PMID_29249692 <- RefManageR::ReadPubMed('29249692', database = 'PubMed')

citation_29249692 <- paste0(PMID_29249692$journal,' ', PMID_29249692$year, ' ', PMID_29249692$month,';', PMID_29249692$volume,'(', PMID_29249692$number,'):', PMID_29249692$pages)

PubMed_29249692 <- paste0(PubMedString, PMID_29249692$eprint)

doi_29249692 <- paste0(doiString, PMID_29249692$doi)

dimensionBadge_29249692 <- paste0(dimensionString1, PMID_29249692$doi,dimensionString2)

altmetricBadge_29249692 <- paste0(altmetricString1, PMID_29249692$doi, altmetricString2 )

addthis_inline_29249692 <- paste0(addthis_String1, PMID_29249692$title , " PMID: 29249692 " , addthis_String2)

Sys.sleep(1)

```

<details open> <summary>
- **`r PMID_29249692$title`**
</summary> 

*`r citation_29249692`*

`r PubMed_29249692`

`r addthis_inline_29249692`

`r PMID_29249692$abstract`

<!-- `r doi_29249692` -->

`r dimensionBadge_29249692`

`r altmetricBadge_29249692`

</details>

---


```{r 30266763, include=FALSE}

PMID_30266763 <- RefManageR::ReadPubMed('30266763', database = 'PubMed')

citation_30266763 <- paste0(PMID_30266763$journal,' ', PMID_30266763$year, ' ', PMID_30266763$month,';', PMID_30266763$volume,'(', PMID_30266763$number,'):', PMID_30266763$pages)

PubMed_30266763 <- paste0(PubMedString, PMID_30266763$eprint)

doi_30266763 <- paste0(doiString, PMID_30266763$doi)

dimensionBadge_30266763 <- paste0(dimensionString1, PMID_30266763$doi,dimensionString2)

altmetricBadge_30266763 <- paste0(altmetricString1, PMID_30266763$doi, altmetricString2 )

addthis_inline_30266763 <- paste0(addthis_String1, PMID_30266763$title , " PMID: 30266763 " , addthis_String2)

Sys.sleep(1)

```

<details open> <summary>
- **`r PMID_30266763$title`**
</summary> 

*`r citation_30266763`*

`r PubMed_30266763`

`r addthis_inline_30266763`

`r PMID_30266763$abstract`

<!-- `r doi_30266763` -->

`r dimensionBadge_30266763`

`r altmetricBadge_30266763`

</details>



---



```{r 30296435, include=FALSE}

PMID_30296435 <- RefManageR::ReadPubMed('30296435', database = 'PubMed')

citation_30296435 <- paste0(PMID_30296435$journal,' ', PMID_30296435$year, ' ', PMID_30296435$month,';', PMID_30296435$volume,'(', PMID_30296435$number,'):', PMID_30296435$pages)

PubMed_30296435 <- paste0(PubMedString, PMID_30296435$eprint)

doi_30296435 <- paste0(doiString, PMID_30296435$doi)

dimensionBadge_30296435 <- paste0(dimensionString1, PMID_30296435$doi,dimensionString2)

altmetricBadge_30296435 <- paste0(altmetricString1, PMID_30296435$doi, altmetricString2 )

addthis_inline_30296435 <- paste0(addthis_String1, PMID_30296435$title , " PMID: 30296435 " , addthis_String2)

Sys.sleep(1)

```

<details open> <summary>
- **`r PMID_30296435$title`**
</summary> 

*`r citation_30296435`*

`r PubMed_30296435`

`r addthis_inline_30296435`

`r PMID_30296435$abstract`

<!-- `r doi_30296435` -->

`r dimensionBadge_30296435`

`r altmetricBadge_30296435`

</details>


---


```{r 30342032, include=FALSE}

PMID_30342032 <- RefManageR::ReadPubMed('30342032', database = 'PubMed')

citation_30342032 <- paste0(PMID_30342032$journal,' ', PMID_30342032$year, ' ', PMID_30342032$month,';', PMID_30342032$volume,'(', PMID_30342032$number,'):', PMID_30342032$pages)

PubMed_30342032 <- paste0(PubMedString, PMID_30342032$eprint)

doi_30342032 <- paste0(doiString, PMID_30342032$doi)

dimensionBadge_30342032 <- paste0(dimensionString1, PMID_30342032$doi,dimensionString2)

altmetricBadge_30342032 <- paste0(altmetricString1, PMID_30342032$doi, altmetricString2 )

addthis_inline_30342032 <- paste0(addthis_String1, PMID_30342032$title , " PMID: 30342032 " , addthis_String2)

Sys.sleep(1)

```

<details open> <summary>
- **`r PMID_30342032$title`**
</summary> 

*`r citation_30342032`*

`r PubMed_30342032`

`r addthis_inline_30342032`

`r PMID_30342032$abstract`

<!-- `r doi_30342032` -->

`r dimensionBadge_30342032`

`r altmetricBadge_30342032`

</details>




---



```{r 30343272, include=FALSE}

PMID_30343272 <- RefManageR::ReadPubMed('30343272', database = 'PubMed')

citation_30343272 <- paste0(PMID_30343272$journal,' ', PMID_30343272$year, ' ', PMID_30343272$month,';', PMID_30343272$volume,'(', PMID_30343272$number,'):', PMID_30343272$pages)

PubMed_30343272 <- paste0(PubMedString, PMID_30343272$eprint)

doi_30343272 <- paste0(doiString, PMID_30343272$doi)

dimensionBadge_30343272 <- paste0(dimensionString1, PMID_30343272$doi,dimensionString2)

altmetricBadge_30343272 <- paste0(altmetricString1, PMID_30343272$doi, altmetricString2 )

addthis_inline_30343272 <- paste0(addthis_String1, PMID_30343272$title , " PMID: 30343272 " , addthis_String2)

Sys.sleep(1)

```

<details open> <summary>
- **`r PMID_30343272$title`**
</summary> 

*`r citation_30343272`*

`r PubMed_30343272`

`r addthis_inline_30343272`

`r PMID_30343272$abstract`

<!-- `r doi_30343272` -->

`r dimensionBadge_30343272`

`r altmetricBadge_30343272`

</details>


---

```{r 29928898, include=FALSE}

PMID_29928898 <- RefManageR::ReadPubMed('29928898', database = 'PubMed')

citation_29928898 <- paste0(PMID_29928898$journal,' ', PMID_29928898$year, ' ', PMID_29928898$month,';', PMID_29928898$volume,'(', PMID_29928898$number,'):', PMID_29928898$pages)

PubMed_29928898 <- paste0(PubMedString, PMID_29928898$eprint)

doi_29928898 <- paste0(doiString, PMID_29928898$doi)

dimensionBadge_29928898 <- paste0(dimensionString1, PMID_29928898$doi,dimensionString2)

altmetricBadge_29928898 <- paste0(altmetricString1, PMID_29928898$doi, altmetricString2 )

addthis_inline_29928898 <- paste0(addthis_String1, PMID_29928898$title , " PMID: 29928898 " , addthis_String2)

Sys.sleep(1)

```

<details open> <summary>
- **`r PMID_29928898$title`**
</summary> 

*`r citation_29928898`*

`r PubMed_29928898`

`r addthis_inline_29928898`

`r PMID_29928898$abstract`

<!-- `r doi_29928898` -->

`r dimensionBadge_29928898`

`r altmetricBadge_29928898`

</details>



---



```{r 30352906, include=FALSE}

PMID_30352906 <- RefManageR::ReadPubMed('30352906', database = 'PubMed')

citation_30352906 <- paste0(PMID_30352906$journal,' ', PMID_30352906$year, ' ', PMID_30352906$month,';', PMID_30352906$volume,'(', PMID_30352906$number,'):', PMID_30352906$pages)

PubMed_30352906 <- paste0(PubMedString, PMID_30352906$eprint)

doi_30352906 <- paste0(doiString, PMID_30352906$doi)

dimensionBadge_30352906 <- paste0(dimensionString1, PMID_30352906$doi,dimensionString2)

altmetricBadge_30352906 <- paste0(altmetricString1, PMID_30352906$doi, altmetricString2 )

addthis_inline_30352906 <- paste0(addthis_String1, PMID_30352906$title , " PMID: 30352906 " , addthis_String2)

Sys.sleep(1)

```

<details open> <summary>
- **`r PMID_30352906$title`**
</summary> 

*`r citation_30352906`*

`r PubMed_30352906`

`r addthis_inline_30352906`

`r PMID_30352906$abstract`

<!-- `r doi_30352906` -->

`r dimensionBadge_30352906`

`r altmetricBadge_30352906`

</details>



---

<a href="#top" target="_self">Back to top</a>

---

\pagebreak





