---
title: "PBPath Journal Watch"
subtitle: "Top Articles"
date: '`r format(Sys.Date())`'
output: 
  html_notebook: 
    code_folding: hide
    fig_caption: yes
    highlight: kate
    theme: paper
    toc: yes
    toc_float: yes
  html_document: 
    df_print: kable
    toc: yes
---



---

- **Molecular Diagnostics in Pancreatic and Biliary Cytology**

https://link.springer.com/chapter/10.1007/978-3-319-97397-5_15



---

- **Molecular Cytology Applications on Pancreas and Biliary Tract**

https://link.springer.com/chapter/10.1007/978-3-319-74942-6_11


---


```{r 29882285, include=FALSE}

PMID_29882285 <- RefManageR::ReadPubMed('29882285', database = 'PubMed')

citation_29882285 <- paste0(PMID_29882285$journal,' ', PMID_29882285$year, ' ', PMID_29882285$month,';', PMID_29882285$volume,'(', PMID_29882285$number,'):', PMID_29882285$pages)

PubMed_29882285 <- paste0(PubMedString, PMID_29882285$eprint)

doi_29882285 <- paste0(doiString, PMID_29882285$doi)

dimensionBadge_29882285 <- paste0(dimensionString1, PMID_29882285$doi,dimensionString2)

altmetricBadge_29882285 <- paste0(altmetricString1, PMID_29882285$doi, altmetricString2 )

```

- **`r PMID_29882285$title`**

*`r citation_29882285`*

`r PMID_29882285$abstract`

`r PubMed_29882285`

`r doi_29882285`

`r dimensionBadge_29882285`

`r altmetricBadge_29882285`

---

```{r 30284406, include=FALSE}

PMID_30284406 <- RefManageR::ReadPubMed('30284406', database = 'PubMed')

citation_30284406 <- paste0(PMID_30284406$journal,' ', PMID_30284406$year, ' ', PMID_30284406$month,';', PMID_30284406$volume,'(', PMID_30284406$number,'):', PMID_30284406$pages)

PubMed_30284406 <- paste0(PubMedString, PMID_30284406$eprint)

doi_30284406 <- paste0(doiString, PMID_30284406$doi)

dimensionBadge_30284406 <- paste0(dimensionString1, PMID_30284406$doi,dimensionString2)

altmetricBadge_30284406 <- paste0(altmetricString1, PMID_30284406$doi, altmetricString2 )

addthis_inline_30284406 <- paste0(addthis_String1, PMID_30284406$title , " PMID: 30284406 " , addthis_String2)

Sys.sleep(1)

```

<details open> <summary>
- **`r PMID_30284406$title`**
</summary> 

*`r citation_30284406`*

`r PubMed_30284406`

`r addthis_inline_30284406`

`r PMID_30284406$abstract`

<!-- `r doi_30284406` -->

`r dimensionBadge_30284406`

`r altmetricBadge_30284406`

</details>


---


    
- **Pancreaticobiliary cytopathology: an update**

Diagnostic Histopathology Volume 24, Issue 10, October 2018, Pages 397-408

https://www.sciencedirect.com/science/article/pii/S1756231718301397


```{r 30479026, include=FALSE}

PMID_30479026 <- RefManageR::ReadPubMed('30479026', database = 'PubMed')

citation_30479026 <- paste0(PMID_30479026$journal,' ', PMID_30479026$year, ' ', PMID_30479026$month,';', PMID_30479026$volume,'(', PMID_30479026$number,'):', PMID_30479026$pages)

PubMed_30479026 <- paste0(PubMedString, PMID_30479026$eprint)

doi_30479026 <- paste0(doiString, PMID_30479026$doi)

dimensionBadge_30479026 <- paste0(dimensionString1, PMID_30479026$doi,dimensionString2)

altmetricBadge_30479026 <- paste0(altmetricString1, PMID_30479026$doi, altmetricString2 )

addthis_inline_30479026 <- paste0(addthis_String1, PMID_30479026$title , " PMID: 30479026 " , addthis_String2)

Sys.sleep(1)

```

<details open> <summary>
- **`r PMID_30479026$title`**
</summary> 

*`r citation_30479026`*

`r PubMed_30479026`

`r addthis_inline_30479026`

`r PMID_30479026$abstract`

<!-- `r doi_30479026` -->

`r dimensionBadge_30479026`

`r altmetricBadge_30479026`

</details>

---


```{r 30301772, include=FALSE}

PMID_30301772 <- RefManageR::ReadPubMed('30301772', database = 'PubMed')

citation_30301772 <- paste0(PMID_30301772$journal,' ', PMID_30301772$year, ' ', PMID_30301772$month,';', PMID_30301772$volume,'(', PMID_30301772$number,'):', PMID_30301772$pages)

PubMed_30301772 <- paste0(PubMedString, PMID_30301772$eprint)

doi_30301772 <- paste0(doiString, PMID_30301772$doi)

dimensionBadge_30301772 <- paste0(dimensionString1, PMID_30301772$doi,dimensionString2)

altmetricBadge_30301772 <- paste0(altmetricString1, PMID_30301772$doi, altmetricString2 )

addthis_inline_30301772 <- paste0(addthis_String1, PMID_30301772$title , " PMID: 30301772 " , addthis_String2)

Sys.sleep(1)

```

<details open> <summary>
- **`r PMID_30301772$title`**
</summary> 

*`r citation_30301772`*

`r PubMed_30301772`

`r addthis_inline_30301772`

`r PMID_30301772$abstract`

<!-- `r doi_30301772` -->

`r dimensionBadge_30301772`

`r altmetricBadge_30301772`

</details>


---







