---
title: "Epidemiology"
output: html_notebook
---

#### Epidemiology, Screening, Cancer Risk Factors


```{r Pancreas Epidemiology Screening Cancer Risk Factors, eval=FALSE, include=FALSE}
```





- **High prevalence of Hereditary Cancer Syndromes and Outcomes in Adults with Early-Onset Pancreatic Cancer**
    
http://cancerpreventionresearch.aacrjournals.org/content/early/2018/09/29/1940-6207.CAPR-18-0014




---

- **Identification of Cystic Lesions by Secondary Screening of Familial Pancreatic Cancer (FPC) Kindreds Is Not Associated with the Stratified Risk of Cancer**
    
https://www.nature.com/articles/s41395-018-0395-y



---

- **Coffee and pancreatic cancer risk among never‐smokers in the UK prospective Million Women Study**

https://onlinelibrary.wiley.com/doi/abs/10.1002/ijc.31994

---

- **Screening and surveillance in hereditary gastrointestinal cancers: Recommendations from the European Society of Digestive Oncology (ESDO) expert discussion at the 20th European Society for Medical Oncology (ESMO)/World Congress on Gastrointestinal Cancer, Barcelona, June 2018**
    
https://www.sciencedirect.com/science/article/pii/S0959804918313741

---

- **Pancreatic cancer and autoimmune diseases: An association sustained by computational and epidemiological case-control approaches: Autoimmune diseases and pancreatic cancer risk**
    
https://www.researchgate.net/publication/327754246_Pancreatic_cancer_and_autoimmune_diseases_An_association_sustained_by_computational_and_epidemiological_case-control_approaches_Autoimmune_diseases_and_pancreatic_cancer_risk


---

```{r 30448085, include=FALSE}

PMID_30448085 <- RefManageR::ReadPubMed('30448085', database = 'PubMed')

citation_30448085 <- paste0(PMID_30448085$journal,' ', PMID_30448085$year, ' ', PMID_30448085$month,';', PMID_30448085$volume,'(', PMID_30448085$number,'):', PMID_30448085$pages)

PubMed_30448085 <- paste0(PubMedString, PMID_30448085$eprint)

doi_30448085 <- paste0(doiString, PMID_30448085$doi)

dimensionBadge_30448085 <- paste0(dimensionString1, PMID_30448085$doi,dimensionString2)

altmetricBadge_30448085 <- paste0(altmetricString1, PMID_30448085$doi, altmetricString2 )

addthis_inline_30448085 <- paste0(addthis_String1, PMID_30448085$title , " PMID: 30448085 " , addthis_String2)

Sys.sleep(1)

```

<details open> <summary>
- **`r PMID_30448085$title`**
</summary> 

*`r citation_30448085`*

`r PubMed_30448085`

`r addthis_inline_30448085`

`r PMID_30448085$abstract`

<!-- `r doi_30448085` -->

`r dimensionBadge_30448085`

`r altmetricBadge_30448085`

</details>



---

- **Evaluating Susceptibility to Pancreatic Cancer: ASCO Provisional Clinical Opinion**

http://ascopubs.org/doi/abs/10.1200/JCO.18.01489


---

```{r 30477640, include=FALSE}

PMID_30477640 <- RefManageR::ReadPubMed('30477640', database = 'PubMed')

citation_30477640 <- paste0(PMID_30477640$journal,' ', PMID_30477640$year, ' ', PMID_30477640$month,';', PMID_30477640$volume,'(', PMID_30477640$number,'):', PMID_30477640$pages)

PubMed_30477640 <- paste0(PubMedString, PMID_30477640$eprint)

doi_30477640 <- paste0(doiString, PMID_30477640$doi)

dimensionBadge_30477640 <- paste0(dimensionString1, PMID_30477640$doi,dimensionString2)

altmetricBadge_30477640 <- paste0(altmetricString1, PMID_30477640$doi, altmetricString2 )

addthis_inline_30477640 <- paste0(addthis_String1, PMID_30477640$title , " PMID: 30477640 " , addthis_String2)

Sys.sleep(1)

```

<details open> <summary>
- **`r PMID_30477640$title`**
</summary> 

*`r citation_30477640`*

`r PubMed_30477640`

`r addthis_inline_30477640`

`r PMID_30477640$abstract`

<!-- `r doi_30477640` -->

`r dimensionBadge_30477640`

`r altmetricBadge_30477640`

</details>

---

```{r 30353057, include=FALSE}

PMID_30353057 <- RefManageR::ReadPubMed('30353057', database = 'PubMed')

citation_30353057 <- paste0(PMID_30353057$journal,' ', PMID_30353057$year, ' ', PMID_30353057$month,';', PMID_30353057$volume,'(', PMID_30353057$number,'):', PMID_30353057$pages)

PubMed_30353057 <- paste0(PubMedString, PMID_30353057$eprint)

doi_30353057 <- paste0(doiString, PMID_30353057$doi)

dimensionBadge_30353057 <- paste0(dimensionString1, PMID_30353057$doi,dimensionString2)

altmetricBadge_30353057 <- paste0(altmetricString1, PMID_30353057$doi, altmetricString2 )

addthis_inline_30353057 <- paste0(addthis_String1, PMID_30353057$title , " PMID: 30353057 " , addthis_String2)

Sys.sleep(1)

```

<details open> <summary>
- **`r PMID_30353057$title`**
</summary> 

*`r citation_30353057`*

`r PubMed_30353057`

`r addthis_inline_30353057`

`r PMID_30353057$abstract`

<!-- `r doi_30353057` -->

`r dimensionBadge_30353057`

`r altmetricBadge_30353057`

</details>


---

```{r 29395269, include=FALSE}

PMID_29395269 <- RefManageR::ReadPubMed('29395269', database = 'PubMed')

citation_29395269 <- paste0(PMID_29395269$journal,' ', PMID_29395269$year, ' ', PMID_29395269$month,';', PMID_29395269$volume,'(', PMID_29395269$number,'):', PMID_29395269$pages)

PubMed_29395269 <- paste0(PubMedString, PMID_29395269$eprint)

doi_29395269 <- paste0(doiString, PMID_29395269$doi)

dimensionBadge_29395269 <- paste0(dimensionString1, PMID_29395269$doi,dimensionString2)

altmetricBadge_29395269 <- paste0(altmetricString1, PMID_29395269$doi, altmetricString2 )

addthis_inline_29395269 <- paste0(addthis_String1, PMID_29395269$title , " PMID: 29395269 " , addthis_String2)

Sys.sleep(1)

```

<details open> <summary>
- **`r PMID_29395269$title`**
</summary> 

*`r citation_29395269`*

`r PubMed_29395269`

`r addthis_inline_29395269`

`r PMID_29395269$abstract`

<!-- `r doi_29395269` -->

`r dimensionBadge_29395269`

`r altmetricBadge_29395269`

</details>


---

```{r 29395271, include=FALSE}

PMID_29395271 <- RefManageR::ReadPubMed('29395271', database = 'PubMed')

citation_29395271 <- paste0(PMID_29395271$journal,' ', PMID_29395271$year, ' ', PMID_29395271$month,';', PMID_29395271$volume,'(', PMID_29395271$number,'):', PMID_29395271$pages)

PubMed_29395271 <- paste0(PubMedString, PMID_29395271$eprint)

doi_29395271 <- paste0(doiString, PMID_29395271$doi)

dimensionBadge_29395271 <- paste0(dimensionString1, PMID_29395271$doi,dimensionString2)

altmetricBadge_29395271 <- paste0(altmetricString1, PMID_29395271$doi, altmetricString2 )

addthis_inline_29395271 <- paste0(addthis_String1, PMID_29395271$title , " PMID: 29395271 " , addthis_String2)

Sys.sleep(1)

```

<details open> <summary>
- **`r PMID_29395271$title`**
</summary> 

*`r citation_29395271`*

`r PubMed_29395271`

`r addthis_inline_29395271`

`r PMID_29395271$abstract`

<!-- `r doi_29395271` -->

`r dimensionBadge_29395271`

`r altmetricBadge_29395271`

</details>


---

```{r 30315778, include=FALSE}

PMID_30315778 <- RefManageR::ReadPubMed('30315778', database = 'PubMed')

citation_30315778 <- paste0(PMID_30315778$journal,' ', PMID_30315778$year, ' ', PMID_30315778$month,';', PMID_30315778$volume,'(', PMID_30315778$number,'):', PMID_30315778$pages)

PubMed_30315778 <- paste0(PubMedString, PMID_30315778$eprint)

doi_30315778 <- paste0(doiString, PMID_30315778$doi)

dimensionBadge_30315778 <- paste0(dimensionString1, PMID_30315778$doi,dimensionString2)

altmetricBadge_30315778 <- paste0(altmetricString1, PMID_30315778$doi, altmetricString2 )

addthis_inline_30315778 <- paste0(addthis_String1, PMID_30315778$title , " PMID: 30315778 " , addthis_String2)

Sys.sleep(1)

```

<details open> <summary>
- **`r PMID_30315778$title`**
</summary> 

*`r citation_30315778`*

`r PubMed_30315778`

`r addthis_inline_30315778`

`r PMID_30315778$abstract`

<!-- `r doi_30315778` -->

`r dimensionBadge_30315778`

`r altmetricBadge_30315778`

</details>


---

```{r 29521943, include=FALSE}

PMID_29521943 <- RefManageR::ReadPubMed('29521943', database = 'PubMed')

citation_29521943 <- paste0(PMID_29521943$journal,' ', PMID_29521943$year, ' ', PMID_29521943$month,';', PMID_29521943$volume,'(', PMID_29521943$number,'):', PMID_29521943$pages)

PubMed_29521943 <- paste0(PubMedString, PMID_29521943$eprint)

doi_29521943 <- paste0(doiString, PMID_29521943$doi)

dimensionBadge_29521943 <- paste0(dimensionString1, PMID_29521943$doi,dimensionString2)

altmetricBadge_29521943 <- paste0(altmetricString1, PMID_29521943$doi, altmetricString2 )

addthis_inline_29521943 <- paste0(addthis_String1, PMID_29521943$title , " PMID: 29521943 " , addthis_String2)

Sys.sleep(1)

```

<details open> <summary>
- **`r PMID_29521943$title`**
</summary> 

*`r citation_29521943`*

`r PubMed_29521943`

`r addthis_inline_29521943`

`r PMID_29521943$abstract`

<!-- `r doi_29521943` -->

`r dimensionBadge_29521943`

`r altmetricBadge_29521943`

</details>


---

```{r 30417331, include=FALSE}

PMID_30417331 <- RefManageR::ReadPubMed('30417331', database = 'PubMed')

citation_30417331 <- paste0(PMID_30417331$journal,' ', PMID_30417331$year, ' ', PMID_30417331$month,';', PMID_30417331$volume,'(', PMID_30417331$number,'):', PMID_30417331$pages)

PubMed_30417331 <- paste0(PubMedString, PMID_30417331$eprint)

doi_30417331 <- paste0(doiString, PMID_30417331$doi)

dimensionBadge_30417331 <- paste0(dimensionString1, PMID_30417331$doi,dimensionString2)

altmetricBadge_30417331 <- paste0(altmetricString1, PMID_30417331$doi, altmetricString2 )

addthis_inline_30417331 <- paste0(addthis_String1, PMID_30417331$title , " PMID: 30417331 " , addthis_String2)

Sys.sleep(1)

```

<details open> <summary>
- **`r PMID_30417331$title`**
</summary> 

*`r citation_30417331`*

`r PubMed_30417331`

`r addthis_inline_30417331`

`r PMID_30417331$abstract`

<!-- `r doi_30417331` -->

`r dimensionBadge_30417331`

`r altmetricBadge_30417331`

</details>


---

    
- **A prospective clinical and biological database for pancreatic adenocarcinoma: the BACAP cohort**
    
    
https://bmccancer.biomedcentral.com/articles/10.1186/s12885-018-4906-4

