---
title: "Microenvironment"
output: html_notebook
---

---

Reversal of pancreatic desmoplasia by re-educating stellate cells with a tumour microenvironment-activated nanosystem.

https://www.ncbi.nlm.nih.gov/pubmed/30139933

---

Experimental models of pancreatic cancer desmoplasia.

https://www.ncbi.nlm.nih.gov/pubmed/29155423

---

```{r 30283732, include=FALSE}

PMID_30283732 <- RefManageR::ReadPubMed('30283732', database = 'PubMed')

citation_30283732 <- paste0(PMID_30283732$journal,' ', PMID_30283732$year, ' ', PMID_30283732$month,';', PMID_30283732$volume,'(', PMID_30283732$number,'):', PMID_30283732$pages)

PubMed_30283732 <- paste0(PubMedString, PMID_30283732$eprint)

doi_30283732 <- paste0(doiString, PMID_30283732$doi)

dimensionBadge_30283732 <- paste0(dimensionString1, PMID_30283732$doi,dimensionString2)

altmetricBadge_30283732 <- paste0(altmetricString1, PMID_30283732$doi, altmetricString2 )

addthis_inline_30283732 <- paste0(addthis_String1, PMID_30283732$title , " PMID: 30283732 " , addthis_String2)

Sys.sleep(1)


```

<details open> <summary>
- **`r PMID_30283732$title`**
</summary> 

*`r citation_30283732`*

`r PubMed_30283732`

`r addthis_inline_30283732`

`r PMID_30283732$abstract`

<!-- `r doi_30283732` -->

`r dimensionBadge_30283732`

`r altmetricBadge_30283732`

</details>


---


```{r 30415234, include=FALSE}

PMID_30415234 <- RefManageR::ReadPubMed('30415234', database = 'PubMed')

citation_30415234 <- paste0(PMID_30415234$journal,' ', PMID_30415234$year, ' ', PMID_30415234$month,';', PMID_30415234$volume,'(', PMID_30415234$number,'):', PMID_30415234$pages)

PubMed_30415234 <- paste0(PubMedString, PMID_30415234$eprint)

doi_30415234 <- paste0(doiString, PMID_30415234$doi)

dimensionBadge_30415234 <- paste0(dimensionString1, PMID_30415234$doi,dimensionString2)

altmetricBadge_30415234 <- paste0(altmetricString1, PMID_30415234$doi, altmetricString2 )

addthis_inline_30415234 <- paste0(addthis_String1, PMID_30415234$title , " PMID: 30415234 " , addthis_String2)

Sys.sleep(1)


```

<details open> <summary>
- **`r PMID_30415234$title`**
</summary> 

*`r citation_30415234`*

`r PubMed_30415234`

`r addthis_inline_30415234`

`r PMID_30415234$abstract`

<!-- `r doi_30415234` -->

`r dimensionBadge_30415234`

`r altmetricBadge_30415234`

</details>


---








