---
title: "Molecular"
output: html_notebook
---

---

- **Genetic Drivers of Pancreatic Cancer Are Identical Between the Primary Tumor and a Secondary Lesion in a Long-Term (>5 Years) Survivor After a Whipple Procedure**

https://www.liebertpub.com/doi/abs/10.1089/pancan.2018.0015


---

- **Caveolin-1 Modulates Mechanotransduction Responses to Substrate Stiffness through Actin-Dependent Control of YAP**

https://www.sciencedirect.com/science/article/pii/S2211124718316000



---



- **Rigidity controls human desmoplastic matrix anisotropy to enable pancreatic cancer cell spread via extracellular signal-regulated kinase 2**

https://www.sciencedirect.com/science/article/pii/S0945053X18302841



---




---

- **Epigenetic Targeting DNMT1 of Pancreatic Ductal Adenocarcinoma using interstitial control release biodegrading polymer reduced tumor growth through Hedgehog pathway inhibition**

https://www.sciencedirect.com/science/article/pii/S1043661818306947






---

- **IL-1-induced  JAK/STAT  signaling  is  antagonized  by  TGF-ß  to  shape  CAF  heterogeneity  in pancreatic ductal adenocarcinoma** 

http://cancerdiscovery.aacrjournals.org/content/candisc/early/2018/10/25/2159-8290.CD-18-0710.full.pdf

---

- **Therapeutic potential of targeting the Wnt/β‐catenin pathway in the treatment of pancreatic cancer**

https://onlinelibrary.wiley.com/doi/abs/10.1002/jcb.27835


---




- **Referral frequency, attrition rate, and outcomes of germline testing in patients with pancreatic adenocarcinoma**
    
    
https://link.springer.com/article/10.1007/s10689-018-0106-2




- **Response of germline BRCA2-mutated advanced pancreatic acinar cell carcinoma to olaparib**

https://journals.lww.com/md-journal/Fulltext/2018/11090/Response_of_germline_BRCA2_mutated_advanced.48.aspx




---

- **Targeting Purinergic Receptor P2Y2 prevents the growth of pancreatic ductal adenocarcinoma by inhibiting cancer cell glycolysis**

http://clincancerres.aacrjournals.org/content/early/2018/11/10/1078-0432.CCR-18-2297?papetoc=

---

- **SRC-3 Inhibition Blocks Tumor Growth of Pancreatic Ductal Adenocarcinoma**

https://www.sciencedirect.com/science/article/pii/S0304383518306761





- **Small molecule tyrosine kinase inhibitors and pancreatic cancer—Trials and troubles**
    
https://www.sciencedirect.com/science/article/pii/S1044579X18301342




---

- **Combination treatment of advanced pancreatic cancer using novel vaccine and traditional therapies**
    
https://www.tandfonline.com/doi/abs/10.1080/14737140.2018.1531707



---

    
- **Glycemic Variability Promotes Both Local Invasion and Metastatic Colonization by Pancreatic Ductal Adenocarcinoma**
    
https://www.researchgate.net/profile/Joerg_Kleeff/publication/326628000_Glycemic_Variability_Promotes_Both_Local_Invasion_and_Metastatic_Colonization_by_Pancreatic_Ductal_Adenocarcinoma/links/5b784be14585151fd11f7713/Glycemic-Variability-Promotes-Both-Local-Invasion-and-Metastatic-Colonization-by-Pancreatic-Ductal-Adenocarcinoma.pdf



```{r 30472231, include=FALSE}

PMID_30472231 <- RefManageR::ReadPubMed('30472231', database = 'PubMed')

citation_30472231 <- paste0(PMID_30472231$journal,' ', PMID_30472231$year, ' ', PMID_30472231$month,';', PMID_30472231$volume,'(', PMID_30472231$number,'):', PMID_30472231$pages)

PubMed_30472231 <- paste0(PubMedString, PMID_30472231$eprint)

doi_30472231 <- paste0(doiString, PMID_30472231$doi)

dimensionBadge_30472231 <- paste0(dimensionString1, PMID_30472231$doi,dimensionString2)

altmetricBadge_30472231 <- paste0(altmetricString1, PMID_30472231$doi, altmetricString2 )

addthis_inline_30472231 <- paste0(addthis_String1, PMID_30472231$title , " PMID: 30472231 " , addthis_String2)

Sys.sleep(1)

```

<details open> <summary>
- **`r PMID_30472231$title`**
</summary> 

*`r citation_30472231`*

`r PubMed_30472231`

`r addthis_inline_30472231`

`r PMID_30472231$abstract`

<!-- `r doi_30472231` -->

`r dimensionBadge_30472231`

`r altmetricBadge_30472231`

</details>


---
    
    
- **Metastasis and chemoresistance in CD133 expressing pancreatic cancer cells are dependent on their lipid raft integrity**
    
https://www.sciencedirect.com/science/article/pii/S0304383518305949



---



```{r 27936345, include=FALSE}

PMID_27936345 <- RefManageR::ReadPubMed('27936345', database = 'PubMed')

citation_27936345 <- paste0(PMID_27936345$journal,' ', PMID_27936345$year, ' ', PMID_27936345$month,';', PMID_27936345$volume,'(', PMID_27936345$number,'):', PMID_27936345$pages)

PubMed_27936345 <- paste0(PubMedString, PMID_27936345$eprint)

doi_27936345 <- paste0(doiString, PMID_27936345$doi)

dimensionBadge_27936345 <- paste0(dimensionString1, PMID_27936345$doi,dimensionString2)

altmetricBadge_27936345 <- paste0(altmetricString1, PMID_27936345$doi, altmetricString2 )

addthis_inline_27936345 <- paste0(addthis_String1, PMID_27936345$title , " PMID: 27936345 " , addthis_String2)

Sys.sleep(1)

```

<details open> <summary>
- **`r PMID_27936345$title`**
</summary> 

*`r citation_27936345`*

`r PubMed_27936345`

`r addthis_inline_27936345`

`r PMID_27936345$abstract`

<!-- `r doi_27936345` -->

`r dimensionBadge_27936345`

`r altmetricBadge_27936345`

</details>




```{r 30197477, include=FALSE}

PMID_30197477 <- RefManageR::ReadPubMed('30197477', database = 'PubMed')

citation_30197477 <- paste0(PMID_30197477$journal,' ', PMID_30197477$year, ' ', PMID_30197477$month,';', PMID_30197477$volume,'(', PMID_30197477$number,'):', PMID_30197477$pages)

PubMed_30197477 <- paste0(PubMedString, PMID_30197477$eprint)

doi_30197477 <- paste0(doiString, PMID_30197477$doi)

dimensionBadge_30197477 <- paste0(dimensionString1, PMID_30197477$doi,dimensionString2)

altmetricBadge_30197477 <- paste0(altmetricString1, PMID_30197477$doi, altmetricString2 )

addthis_inline_30197477 <- paste0(addthis_String1, PMID_30197477$title , " PMID: 30197477 " , addthis_String2)

Sys.sleep(1)

```

<details open> <summary>
- **`r PMID_30197477$title`**
</summary> 

*`r citation_30197477`*

`r PubMed_30197477`

`r addthis_inline_30197477`

`r PMID_30197477$abstract`

<!-- `r doi_30197477` -->

`r dimensionBadge_30197477`

`r altmetricBadge_30197477`

</details>



```{r 30416041, include=FALSE}

PMID_30416041 <- RefManageR::ReadPubMed('30416041', database = 'PubMed')

citation_30416041 <- paste0(PMID_30416041$journal,' ', PMID_30416041$year, ' ', PMID_30416041$month,';', PMID_30416041$volume,'(', PMID_30416041$number,'):', PMID_30416041$pages)

PubMed_30416041 <- paste0(PubMedString, PMID_30416041$eprint)

doi_30416041 <- paste0(doiString, PMID_30416041$doi)

dimensionBadge_30416041 <- paste0(dimensionString1, PMID_30416041$doi,dimensionString2)

altmetricBadge_30416041 <- paste0(altmetricString1, PMID_30416041$doi, altmetricString2 )

addthis_inline_30416041 <- paste0(addthis_String1, PMID_30416041$title , " PMID: 30416041 " , addthis_String2)

Sys.sleep(1)

```

<details open> <summary>
- **`r PMID_30416041$title`**
</summary> 

*`r citation_30416041`*

`r PubMed_30416041`

`r addthis_inline_30416041`

`r PMID_30416041$abstract`

<!-- `r doi_30416041` -->

`r dimensionBadge_30416041`

`r altmetricBadge_30416041`

</details>


---

- **H19 long non-coding RNA contributes to sphere formation and invasion through regulation of CD24 and integrin expression in pancreatic cancer cells**

https://www.ncbi.nlm.nih.gov/pmc/articles/PMC6205177/




---

- **Impact of Ethnicity on Somatic Mutation Rates of Pancreatic Adenocarcinoma**
    
http://iv.iiarjournals.org/content/32/6/1527.full



---

- **Chemoresistance Transmission via Exosome-Mediated EphA2 Transfer in Pancreatic Cancer**

http://www.thno.org/v08p5986.pdf



---

- **Identification of hub genes with diagnostic values in pancreatic cancer by bioinformatics analyses and supervised learning methods**

https://wjso.biomedcentral.com/articles/10.1186/s12957-018-1519-y



---

- **miRNA-1290 Promotes Aggressiveness in Pancreatic Ductal Adenocarcinoma by Targeting IKK1**

https://www.karger.com/Article/PDF/495328





---

- **New Horizons in the Treatment of Metastatic Pancreatic Cancer: A Review of the Key Biology Features and the Most Recent Advances to Treat Metastatic Pancreatic Cancer**

https://link.springer.com/article/10.1007/s11523-018-0609-7





```{r 30286473, include=FALSE}

PMID_30286473 <- RefManageR::ReadPubMed('30286473', database = 'PubMed')

citation_30286473 <- paste0(PMID_30286473$journal,' ', PMID_30286473$year, ' ', PMID_30286473$month,';', PMID_30286473$volume,'(', PMID_30286473$number,'):', PMID_30286473$pages)

PubMed_30286473 <- paste0(PubMedString, PMID_30286473$eprint)

doi_30286473 <- paste0(doiString, PMID_30286473$doi)

dimensionBadge_30286473 <- paste0(dimensionString1, PMID_30286473$doi,dimensionString2)

altmetricBadge_30286473 <- paste0(altmetricString1, PMID_30286473$doi, altmetricString2 )

addthis_inline_30286473 <- paste0(addthis_String1, PMID_30286473$title , " PMID: 30286473 " , addthis_String2)

Sys.sleep(1)

```

<details open> <summary>
- **`r PMID_30286473$title`**
</summary> 

*`r citation_30286473`*

`r PubMed_30286473`

`r addthis_inline_30286473`

`r PMID_30286473$abstract`

<!-- `r doi_30286473` -->

`r dimensionBadge_30286473`

`r altmetricBadge_30286473`

</details>


