---
title: "PBPath Journal Watch"
subtitle: "Top Articles"
date: '`r format(Sys.Date())`'
output: 
  html_notebook: 
    code_folding: hide
    fig_caption: yes
    highlight: kate
    theme: paper
    toc: yes
    toc_float: yes
  html_document: 
    df_print: kable
    toc: yes
---


---

A preliminary study on fetal lung injury in a rat model of acute pancreatitis in pregnancy.

https://www.ncbi.nlm.nih.gov/pubmed/29033186

---

```{r 30714146, include=FALSE}

articles <- readRDS('articles.rds')


PMID_30714146 <- RefManageR::ReadPubMed('30714146', database = 'PubMed')

citation_30714146 <- paste0(PMID_30714146$journal,' ', PMID_30714146$year, ' ', PMID_30714146$month,';', PMID_30714146$volume,'(', PMID_30714146$number,'):', PMID_30714146$pages)

PubMed_30714146 <- paste0(PubMedString, PMID_30714146$eprint)

doi_30714146 <- paste0(doiString, PMID_30714146$doi)

dimensionBadge_30714146 <- paste0(dimensionString1, PMID_30714146$doi,dimensionString2)

altmetricBadge_30714146 <- paste0(altmetricString1, PMID_30714146$doi, altmetricString2 )

addthis_inline_30714146 <- paste0(addthis_String1, PMID_30714146$title , " PMID: 30714146 " , addthis_String2)

Sys.sleep(1)


articles <- articles %>%

add_row(

ArticleCitation = PMID_30714146,
PMID = PMID_30714146$eprint,
Title = PMID_30714146$title,
# Author = PMID_30714146$author,
Abstract = PMID_30714146$abstract,
Journal = PMID_30714146$journal,
Year = PMID_30714146$year,
Month = PMID_30714146$month,
# Volume = PMID_30714146$volume,
# Number = PMID_30714146$number,
# Pages = PMID_30714146$pages,
PubMedLink = paste0('https://www.ncbi.nlm.nih.gov/pubmed/?term=', PMID_30714146$eprint),
DoiNumber = PMID_30714146$doi,
DoiLink = paste0('https://doi.org/', PMID_30714146$doi),
Language = PMID_30714146$language,
ISSN = PMID_30714146$issn
) %>%

unique()


Sys.sleep(1)

saveRDS(articles, 'articles.rds')

```

<details open> <summary>
- **`r PMID_30714146$title`**
</summary> 

*`r citation_30714146`*

`r PubMed_30714146`

`r addthis_inline_30714146`

`r PMID_30714146$abstract`

<!-- `r doi_30714146` -->

`r dimensionBadge_30714146`

`r altmetricBadge_30714146`

</details>

---


```{r 30315779, include=FALSE}

PMID_30315779 <- RefManageR::ReadPubMed('30315779', database = 'PubMed')

citation_30315779 <- paste0(PMID_30315779$journal,' ', PMID_30315779$year, ' ', PMID_30315779$month,';', PMID_30315779$volume,'(', PMID_30315779$number,'):', PMID_30315779$pages)

PubMed_30315779 <- paste0(PubMedString, PMID_30315779$eprint)

doi_30315779 <- paste0(doiString, PMID_30315779$doi)

dimensionBadge_30315779 <- paste0(dimensionString1, PMID_30315779$doi,dimensionString2)

altmetricBadge_30315779 <- paste0(altmetricString1, PMID_30315779$doi, altmetricString2 )

addthis_inline_30315779 <- paste0(addthis_String1, PMID_30315779$title , " PMID: 30315779 " , addthis_String2)

Sys.sleep(1)

```

<details open> <summary>
- **`r PMID_30315779$title`**
</summary> 

*`r citation_30315779`*

`r PubMed_30315779`

`r addthis_inline_30315779`

`r PMID_30315779$abstract`

<!-- `r doi_30315779` -->

`r dimensionBadge_30315779`

`r altmetricBadge_30315779`

</details>




- **Morphologic Overlap Between Inflammatory Myofibroblastic Tumor and IgG4-related Disease Lessons From Next-generation Sequencing**

https://journals.lww.com/ajsp/Abstract/publishahead/Morphologic_Overlap_Between_Inflammatory.97741.aspx



---

- **Coexisting Mucinous Cystic Neoplasm of the Pancreas and Type 1 Autoimmune Pancreatitis**

https://www.jpatholtm.org/upload/pdf/jptm-2018-10-25.pdf



