---
title: "Pancreatobiliary Pathology Society Journal Watch"
output:
  html_document:
    df_print: paged
  pdf_document:
    toc: yes
    number_sections: yes
    latex_engine: xelatex
    keep_tex: yes
  html_notebook:
    code_folding: none
    fig_caption: yes
    highlight: null
    theme: paper
date: "Last Update on `r format(Sys.Date())`"
subtitle: 'January-March 2020'
header-includes:
- \renewcommand{\linethickness}{0.05em}
- \usepackage{booktabs}
- \usepackage{sectsty} \allsectionsfont{\nohang\centering \emph}
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(cache = TRUE)
```


```{r library, include=FALSE}
suppressPackageStartupMessages(library("tidyverse"))
suppressPackageStartupMessages(library("readxl"))
suppressPackageStartupMessages(library("RefManageR"))

```


<style type="text/css">

h1{
  text-align: center;
}
h2{
  text-align: center;
}
h3{
  text-align: center;
}
h4{
  text-align: center;
}
h4.date{
  text-align: center;
}

</style>


<!-- Open all links in new tab-->
<base target="_blank"/>


---

# PBPath Journal Watch Articles {.tabset .tabset-fade .tabset-pills #pbpath_jw}


```{r strings , include=FALSE}
PubMedString <- "PubMed: https://www.ncbi.nlm.nih.gov/pubmed/?term="

doiString <- "doi: https://doi.org/"

```



```{r read PMID from this file, include=FALSE, cache=FALSE}
currentfile <- rstudioapi::getSourceEditorContext()$path

text_currentfile <- readLines(currentfile)

PMID_List <-
    stringr::str_extract(
        string = text_currentfile,
        pattern =
            "PubMed_(\\d{8})"
    )

PMID_List <- PMID_List[!is.na(PMID_List)]

PMID_List <- PMID_List %>%
  unique() %>%
  gsub(pattern = "PubMed_", replacement = "", x = .)

```


---

**Welcome to the PBPath Journal Watch!**

[![DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.3635440.svg)](https://doi.org/10.5281/zenodo.3635440)

https://doi.org/10.5281/zenodo.3635440

https://osf.io/3d67y/

This bi-monthly journal watch features exciting recently published pancreas and biliary pathology articles that will provide up to date medical knowledge in our field. These articles will be showcased in several convenient categories, including surgical pathology, cytopathology, and molecular pathology among others. The articles in each category are in no particular order. See the list of journals we search regularly [here](http://pbpath.org/pbpath-journal-watch/). Previous months’ issues may be found in our *[archive](http://pbpath.org/journal-watch-archive/)* and you may see [drafts of the upcoming issue here](http://pbpath.org/journal-watch-upcoming-issue/).

We encourage members to actively participate by recommending new articles and providing feedback using the [forms provided below.](#feedback){target="_self"}

**We hope that you will enjoy the new PBPath Journal Watch!**




---






```{r PubMed Link, include=FALSE, cache=FALSE}

PMID_Link <- PMID_List %>%
  t() %>%
  paste0("[uid] OR ", collapse = "") # add OR between PMID List

PMID_Link <- gsub(" OR $", "" , PMID_Link) # to remove last OR

PubMed_Link <- paste0("To see these selected articles in <a href = 'https://www.ncbi.nlm.nih.gov/pubmed/?term=",PMID_Link,"'> PubMed click here </a>")

write(x = PubMed_Link,
      file = here::here("data",
                        paste0(Sys.Date(), "_PubMed_Link.txt")
                        )
)

```


```{r Lens Link, include=FALSE, cache=FALSE}

PMID_Lens <- paste0("pmid:",PMID_List,"%20OR%20" ) %>%
  t() %>%
  paste0(collapse = "")

PMID_Lens <- gsub("%20OR%20$", "" , PMID_Lens)

Lens_Link <- paste0("To see these selected articles in <a href = 'https://www.lens.org/lens/scholar/search/results?q=",PMID_Lens,"&toYear=2020&fromYear=1950&dateFilterField=year_published&filterMap=%7B%7D&preview=true'> Lens.org click here </a>")

write(x = Lens_Link,
      file = here::here("data",
                        paste0(Sys.Date(), "_Lens_Link.txt"))
)

```


`r PubMed_Link`


`r Lens_Link`



---



\pagebreak



## Pancreas {#pancreas}

---


---

```{r pancreas 32234757, include=FALSE}

PMID_32234757 <- RefManageR::ReadPubMed('32234757', database = 'PubMed')

citation_32234757 <- paste0(PMID_32234757$journal,' ', PMID_32234757$year, ' ', PMID_32234757$month,';', PMID_32234757$volume,'(', PMID_32234757$number,'):', PMID_32234757$pages)

PubMed_32234757 <- paste0(PubMedString, PMID_32234757$eprint)

doi_32234757 <- paste0(doiString, PMID_32234757$doi)

Sys.sleep(2)

```

<details open> <summary>
- **`r PMID_32234757$title`**
</summary>

*`r citation_32234757`*

`r PubMed_32234757`

`r PMID_32234757$abstract`

`r doi_32234757`

</details>

---



---

```{r pancreas 32209898, include=FALSE}

PMID_32209898 <- RefManageR::ReadPubMed('32209898', database = 'PubMed')

citation_32209898 <- paste0(PMID_32209898$journal,' ', PMID_32209898$year, ' ', PMID_32209898$month,';', PMID_32209898$volume,'(', PMID_32209898$number,'):', PMID_32209898$pages)

PubMed_32209898 <- paste0(PubMedString, PMID_32209898$eprint)

doi_32209898 <- paste0(doiString, PMID_32209898$doi)

Sys.sleep(2)

```

<details open> <summary>
- **`r PMID_32209898$title`**
</summary>

*`r citation_32209898`*

`r PubMed_32209898`

`r PMID_32209898$abstract`

`r doi_32209898`

</details>

---




---

```{r pancreas 32205290, include=FALSE}

PMID_32205290 <- RefManageR::ReadPubMed('32205290', database = 'PubMed')

citation_32205290 <- paste0(PMID_32205290$journal,' ', PMID_32205290$year, ' ', PMID_32205290$month,';', PMID_32205290$volume,'(', PMID_32205290$number,'):', PMID_32205290$pages)

PubMed_32205290 <- paste0(PubMedString, PMID_32205290$eprint)

doi_32205290 <- paste0(doiString, PMID_32205290$doi)

Sys.sleep(2)

```

<details open> <summary>
- **`r PMID_32205290$title`**
</summary>

*`r citation_32205290`*

`r PubMed_32205290`

`r PMID_32205290$abstract`

`r doi_32205290`

</details>

---



---

```{r pancreas 32156747, include=FALSE}

PMID_32156747 <- RefManageR::ReadPubMed('32156747', database = 'PubMed')

citation_32156747 <- paste0(PMID_32156747$journal,' ', PMID_32156747$year, ' ', PMID_32156747$month,';', PMID_32156747$volume,'(', PMID_32156747$number,'):', PMID_32156747$pages)

PubMed_32156747 <- paste0(PubMedString, PMID_32156747$eprint)

doi_32156747 <- paste0(doiString, PMID_32156747$doi)

Sys.sleep(2)

```

<details open> <summary>
- **`r PMID_32156747$title`**
</summary>

*`r citation_32156747`*

`r PubMed_32156747`

`r PMID_32156747$abstract`

`r doi_32156747`

</details>

---



---

```{r pancreas 32138704, include=FALSE}

PMID_32138704 <- RefManageR::ReadPubMed('32138704', database = 'PubMed')

citation_32138704 <- paste0(PMID_32138704$journal,' ', PMID_32138704$year, ' ', PMID_32138704$month,';', PMID_32138704$volume,'(', PMID_32138704$number,'):', PMID_32138704$pages)

PubMed_32138704 <- paste0(PubMedString, PMID_32138704$eprint)

doi_32138704 <- paste0(doiString, PMID_32138704$doi)

Sys.sleep(2)

```

<details open> <summary>
- **`r PMID_32138704$title`**
</summary>

*`r citation_32138704`*

`r PubMed_32138704`

`r PMID_32138704$abstract`

`r doi_32138704`

</details>

---



---

```{r pancreas 32128564, include=FALSE}

PMID_32128564 <- RefManageR::ReadPubMed('32128564', database = 'PubMed')

citation_32128564 <- paste0(PMID_32128564$journal,' ', PMID_32128564$year, ' ', PMID_32128564$month,';', PMID_32128564$volume,'(', PMID_32128564$number,'):', PMID_32128564$pages)

PubMed_32128564 <- paste0(PubMedString, PMID_32128564$eprint)

doi_32128564 <- paste0(doiString, PMID_32128564$doi)

Sys.sleep(2)

```

<details open> <summary>
- **`r PMID_32128564$title`**
</summary>

*`r citation_32128564`*

`r PubMed_32128564`

`r PMID_32128564$abstract`

`r doi_32128564`

</details>

---




---

```{r pancreas 32113937, include=FALSE}

PMID_32113937 <- RefManageR::ReadPubMed('32113937', database = 'PubMed')

citation_32113937 <- paste0(PMID_32113937$journal,' ', PMID_32113937$year, ' ', PMID_32113937$month,';', PMID_32113937$volume,'(', PMID_32113937$number,'):', PMID_32113937$pages)

PubMed_32113937 <- paste0(PubMedString, PMID_32113937$eprint)

doi_32113937 <- paste0(doiString, PMID_32113937$doi)

Sys.sleep(2)

```

<details open> <summary>
- **`r PMID_32113937$title`**
</summary>

*`r citation_32113937`*

`r PubMed_32113937`

`r PMID_32113937$abstract`

`r doi_32113937`

</details>

---




---

```{r pancreas 32111396, include=FALSE}

PMID_32111396 <- RefManageR::ReadPubMed('32111396', database = 'PubMed')

citation_32111396 <- paste0(PMID_32111396$journal,' ', PMID_32111396$year, ' ', PMID_32111396$month,';', PMID_32111396$volume,'(', PMID_32111396$number,'):', PMID_32111396$pages)

PubMed_32111396 <- paste0(PubMedString, PMID_32111396$eprint)

doi_32111396 <- paste0(doiString, PMID_32111396$doi)

Sys.sleep(2)

```

<details open> <summary>
- **`r PMID_32111396$title`**
</summary>

*`r citation_32111396`*

`r PubMed_32111396`

`r PMID_32111396$abstract`

`r doi_32111396`

</details>

---




---

```{r pancreas 32108923, include=FALSE}

PMID_32108923 <- RefManageR::ReadPubMed('32108923', database = 'PubMed')

citation_32108923 <- paste0(PMID_32108923$journal,' ', PMID_32108923$year, ' ', PMID_32108923$month,';', PMID_32108923$volume,'(', PMID_32108923$number,'):', PMID_32108923$pages)

PubMed_32108923 <- paste0(PubMedString, PMID_32108923$eprint)

doi_32108923 <- paste0(doiString, PMID_32108923$doi)

Sys.sleep(2)

```

<details open> <summary>
- **`r PMID_32108923$title`**
</summary>

*`r citation_32108923`*

`r PubMed_32108923`

`r PMID_32108923$abstract`

`r doi_32108923`

</details>

---


---

```{r pancreas 32091434, include=FALSE}

PMID_32091434 <- RefManageR::ReadPubMed('32091434', database = 'PubMed')

citation_32091434 <- paste0(PMID_32091434$journal,' ', PMID_32091434$year, ' ', PMID_32091434$month,';', PMID_32091434$volume,'(', PMID_32091434$number,'):', PMID_32091434$pages)

PubMed_32091434 <- paste0(PubMedString, PMID_32091434$eprint)

doi_32091434 <- paste0(doiString, PMID_32091434$doi)

Sys.sleep(2)

```

<details open> <summary>
- **`r PMID_32091434$title`**
</summary>

*`r citation_32091434`*

`r PubMed_32091434`

`r PMID_32091434$abstract`

`r doi_32091434`

</details>

---


---

```{r pancreas 31977134, include=FALSE}

PMID_31977134 <- RefManageR::ReadPubMed('31977134', database = 'PubMed')

citation_31977134 <- paste0(PMID_31977134$journal,' ', PMID_31977134$year, ' ', PMID_31977134$month,';', PMID_31977134$volume,'(', PMID_31977134$number,'):', PMID_31977134$pages)

PubMed_31977134 <- paste0(PubMedString, PMID_31977134$eprint)

doi_31977134 <- paste0(doiString, PMID_31977134$doi)

Sys.sleep(2)

```

<details open> <summary>
- **`r PMID_31977134$title`**
</summary>

*`r citation_31977134`*

`r PubMed_31977134`

`r PMID_31977134$abstract`

`r doi_31977134`

</details>

---


---

```{r pancreas 31965618, include=FALSE}

PMID_31965618 <- RefManageR::ReadPubMed('31965618', database = 'PubMed')

citation_31965618 <- paste0(PMID_31965618$journal,' ', PMID_31965618$year, ' ', PMID_31965618$month,';', PMID_31965618$volume,'(', PMID_31965618$number,'):', PMID_31965618$pages)

PubMed_31965618 <- paste0(PubMedString, PMID_31965618$eprint)

doi_31965618 <- paste0(doiString, PMID_31965618$doi)

Sys.sleep(2)

```

<details open> <summary>
- **`r PMID_31965618$title`**
</summary>

*`r citation_31965618`*

`r PubMed_31965618`

`r PMID_31965618$abstract`

`r doi_31965618`

</details>

---


---

```{r pancreas 31676785, include=FALSE}

PMID_31676785 <- RefManageR::ReadPubMed('31676785', database = 'PubMed')

citation_31676785 <- paste0(PMID_31676785$journal,' ', PMID_31676785$year, ' ', PMID_31676785$month,';', PMID_31676785$volume,'(', PMID_31676785$number,'):', PMID_31676785$pages)

PubMed_31676785 <- paste0(PubMedString, PMID_31676785$eprint)

doi_31676785 <- paste0(doiString, PMID_31676785$doi)

Sys.sleep(2)

```

<details open> <summary>
- **`r PMID_31676785$title`**
</summary>

*`r citation_31676785`*

`r PubMed_31676785`

`r PMID_31676785$abstract`

`r doi_31676785`

</details>

---




---

```{r pancreas 31558784, include=FALSE}

PMID_31558784 <- RefManageR::ReadPubMed('31558784', database = 'PubMed')

citation_31558784 <- paste0(PMID_31558784$journal,' ', PMID_31558784$year, ' ', PMID_31558784$month,';', PMID_31558784$volume,'(', PMID_31558784$number,'):', PMID_31558784$pages)

PubMed_31558784 <- paste0(PubMedString, PMID_31558784$eprint)

doi_31558784 <- paste0(doiString, PMID_31558784$doi)

Sys.sleep(2)

```

<details open> <summary>
- **`r PMID_31558784$title`**
</summary>

*`r citation_31558784`*

`r PubMed_31558784`

`r PMID_31558784$abstract`

`r doi_31558784`

</details>

---



---

```{r pancreas 31595972, include=FALSE}

PMID_31595972 <- RefManageR::ReadPubMed('31595972', database = 'PubMed')

citation_31595972 <- paste0(PMID_31595972$journal,' ', PMID_31595972$year, ' ', PMID_31595972$month,';', PMID_31595972$volume,'(', PMID_31595972$number,'):', PMID_31595972$pages)

PubMed_31595972 <- paste0(PubMedString, PMID_31595972$eprint)

doi_31595972 <- paste0(doiString, PMID_31595972$doi)

Sys.sleep(2)

```

<details open> <summary>
- **`r PMID_31595972$title`**
</summary>

*`r citation_31595972`*

`r PubMed_31595972`

`r PMID_31595972$abstract`

`r doi_31595972`

</details>

---

---

```{r pancreas 31383964, include=FALSE}

PMID_31383964 <- RefManageR::ReadPubMed('31383964', database = 'PubMed')

citation_31383964 <- paste0(PMID_31383964$journal,' ', PMID_31383964$year, ' ', PMID_31383964$month,';', PMID_31383964$volume,'(', PMID_31383964$number,'):', PMID_31383964$pages)

PubMed_31383964 <- paste0(PubMedString, PMID_31383964$eprint)

doi_31383964 <- paste0(doiString, PMID_31383964$doi)

Sys.sleep(2)

```

<details open> <summary>
- **`r PMID_31383964$title`**
</summary>

*`r citation_31383964`*

`r PubMed_31383964`

`r PMID_31383964$abstract`

`r doi_31383964`

</details>

---

---

<a href="#top" target="_self">Back to top</a>

---

\pagebreak



## Gallbladder {#gallbladder}

---




---

```{r gallbladder 31907021, include=FALSE}

PMID_31907021 <- RefManageR::ReadPubMed('31907021', database = 'PubMed')

citation_31907021 <- paste0(PMID_31907021$journal,' ', PMID_31907021$year, ' ', PMID_31907021$month,';', PMID_31907021$volume,'(', PMID_31907021$number,'):', PMID_31907021$pages)

PubMed_31907021 <- paste0(PubMedString, PMID_31907021$eprint)

doi_31907021 <- paste0(doiString, PMID_31907021$doi)

Sys.sleep(2)

```

<details open> <summary>
- **`r PMID_31907021$title`**
</summary>

*`r citation_31907021`*

`r PubMed_31907021`

`r PMID_31907021$abstract`

`r doi_31907021`

</details>

---






---

```{r gallbladder 32111400, include=FALSE}

PMID_32111400 <- RefManageR::ReadPubMed('32111400', database = 'PubMed')

citation_32111400 <- paste0(PMID_32111400$journal,' ', PMID_32111400$year, ' ', PMID_32111400$month,';', PMID_32111400$volume,'(', PMID_32111400$number,'):', PMID_32111400$pages)

PubMed_32111400 <- paste0(PubMedString, PMID_32111400$eprint)

doi_32111400 <- paste0(doiString, PMID_32111400$doi)

Sys.sleep(2)

```

<details open> <summary>
- **`r PMID_32111400$title`**
</summary>

*`r citation_32111400`*

`r PubMed_32111400`

`r PMID_32111400$abstract`

`r doi_32111400`

</details>

---





---

```{r gallbladder 31725469, include=FALSE}

PMID_31725469 <- RefManageR::ReadPubMed('31725469', database = 'PubMed')

citation_31725469 <- paste0(PMID_31725469$journal,' ', PMID_31725469$year, ' ', PMID_31725469$month,';', PMID_31725469$volume,'(', PMID_31725469$number,'):', PMID_31725469$pages)

PubMed_31725469 <- paste0(PubMedString, PMID_31725469$eprint)

doi_31725469 <- paste0(doiString, PMID_31725469$doi)

Sys.sleep(2)

```

<details open> <summary>
- **`r PMID_31725469$title`**
</summary>

*`r citation_31725469`*

`r PubMed_31725469`

`r PMID_31725469$abstract`

`r doi_31725469`

</details>

---




---

```{r gallbladder 31755778, include=FALSE}

PMID_31755778 <- RefManageR::ReadPubMed('31755778', database = 'PubMed')

citation_31755778 <- paste0(PMID_31755778$journal,' ', PMID_31755778$year, ' ', PMID_31755778$month,';', PMID_31755778$volume,'(', PMID_31755778$number,'):', PMID_31755778$pages)

PubMed_31755778 <- paste0(PubMedString, PMID_31755778$eprint)

doi_31755778 <- paste0(doiString, PMID_31755778$doi)

Sys.sleep(2)

```

<details open> <summary>
- **`r PMID_31755778$title`**
</summary>

*`r citation_31755778`*

`r PubMed_31755778`

`r PMID_31755778$abstract`

`r doi_31755778`

</details>

---






---

```{r gallbladder 31600399, include=FALSE}

PMID_31600399 <- RefManageR::ReadPubMed('31600399', database = 'PubMed')

citation_31600399 <- paste0(PMID_31600399$journal,' ', PMID_31600399$year, ' ', PMID_31600399$month,';', PMID_31600399$volume,'(', PMID_31600399$number,'):', PMID_31600399$pages)

PubMed_31600399 <- paste0(PubMedString, PMID_31600399$eprint)

doi_31600399 <- paste0(doiString, PMID_31600399$doi)

Sys.sleep(2)

```

<details open> <summary>
- **`r PMID_31600399$title`**
</summary>

*`r citation_31600399`*

`r PubMed_31600399`

`r PMID_31600399$abstract`

`r doi_31600399`

</details>

---


---

```{r gallbladder 31922259, include=FALSE}

PMID_31922259 <- RefManageR::ReadPubMed('31922259', database = 'PubMed')

citation_31922259 <- paste0(PMID_31922259$journal,' ', PMID_31922259$year, ' ', PMID_31922259$month,';', PMID_31922259$volume,'(', PMID_31922259$number,'):', PMID_31922259$pages)

PubMed_31922259 <- paste0(PubMedString, PMID_31922259$eprint)

doi_31922259 <- paste0(doiString, PMID_31922259$doi)

Sys.sleep(2)

```

<details open> <summary>
- **`r PMID_31922259$title`**
</summary> 

*`r citation_31922259`*

`r PubMed_31922259`

`r PMID_31922259$abstract`

`r doi_31922259`

</details>

---




---

<a href="#top" target="_self">Back to top</a>

---

\pagebreak


## Bile Ducts {#bileducts}


---



---

```{r bileducts 32012241, include=FALSE}

PMID_32012241 <- RefManageR::ReadPubMed('32012241', database = 'PubMed')

citation_32012241 <- paste0(PMID_32012241$journal,' ', PMID_32012241$year, ' ', PMID_32012241$month,';', PMID_32012241$volume,'(', PMID_32012241$number,'):', PMID_32012241$pages)

PubMed_32012241 <- paste0(PubMedString, PMID_32012241$eprint)

doi_32012241 <- paste0(doiString, PMID_32012241$doi)

Sys.sleep(2)

```

<details open> <summary>
- **`r PMID_32012241$title`**
</summary>

*`r citation_32012241`*

`r PubMed_32012241`

`r PMID_32012241$abstract`

`r doi_32012241`

</details>

---




---

```{r bileducts 32272125, include=FALSE}

PMID_32272125 <- RefManageR::ReadPubMed('32272125', database = 'PubMed')

citation_32272125 <- paste0(PMID_32272125$journal,' ', PMID_32272125$year, ' ', PMID_32272125$month,';', PMID_32272125$volume,'(', PMID_32272125$number,'):', PMID_32272125$pages)

PubMed_32272125 <- paste0(PubMedString, PMID_32272125$eprint)

doi_32272125 <- paste0(doiString, PMID_32272125$doi)

Sys.sleep(2)

```

<details open> <summary>
- **`r PMID_32272125$title`**
</summary>

*`r citation_32272125`*

`r PubMed_32272125`

`r PMID_32272125$abstract`

`r doi_32272125`

</details>

---








---

```{r bileducts 32181510, include=FALSE}

PMID_32181510 <- RefManageR::ReadPubMed('32181510', database = 'PubMed')

citation_32181510 <- paste0(PMID_32181510$journal,' ', PMID_32181510$year, ' ', PMID_32181510$month,';', PMID_32181510$volume,'(', PMID_32181510$number,'):', PMID_32181510$pages)

PubMed_32181510 <- paste0(PubMedString, PMID_32181510$eprint)

doi_32181510 <- paste0(doiString, PMID_32181510$doi)

Sys.sleep(2)

```

<details open> <summary>
- **`r PMID_32181510$title`**
</summary>

*`r citation_32181510`*

`r PubMed_32181510`

`r PMID_32181510$abstract`

`r doi_32181510`

</details>

---







---

```{r bileducts 32169826, include=FALSE}

PMID_32169826 <- RefManageR::ReadPubMed('32169826', database = 'PubMed')

citation_32169826 <- paste0(PMID_32169826$journal,' ', PMID_32169826$year, ' ', PMID_32169826$month,';', PMID_32169826$volume,'(', PMID_32169826$number,'):', PMID_32169826$pages)

PubMed_32169826 <- paste0(PubMedString, PMID_32169826$eprint)

doi_32169826 <- paste0(doiString, PMID_32169826$doi)

Sys.sleep(2)

```

<details open> <summary>
- **`r PMID_32169826$title`**
</summary>

*`r citation_32169826`*

`r PubMed_32169826`

`r PMID_32169826$abstract`

`r doi_32169826`

</details>

---




---

```{r bileducts 32129902, include=FALSE}

PMID_32129902 <- RefManageR::ReadPubMed('32129902', database = 'PubMed')

citation_32129902 <- paste0(PMID_32129902$journal,' ', PMID_32129902$year, ' ', PMID_32129902$month,';', PMID_32129902$volume,'(', PMID_32129902$number,'):', PMID_32129902$pages)

PubMed_32129902 <- paste0(PubMedString, PMID_32129902$eprint)

doi_32129902 <- paste0(doiString, PMID_32129902$doi)

Sys.sleep(2)

```

<details open> <summary>
- **`r PMID_32129902$title`**
</summary>

*`r citation_32129902`*

`r PubMed_32129902`

`r PMID_32129902$abstract`

`r doi_32129902`

</details>

---




---

```{r bileducts 32100878, include=FALSE}

PMID_32100878 <- RefManageR::ReadPubMed('32100878', database = 'PubMed')

citation_32100878 <- paste0(PMID_32100878$journal,' ', PMID_32100878$year, ' ', PMID_32100878$month,';', PMID_32100878$volume,'(', PMID_32100878$number,'):', PMID_32100878$pages)

PubMed_32100878 <- paste0(PubMedString, PMID_32100878$eprint)

doi_32100878 <- paste0(doiString, PMID_32100878$doi)

Sys.sleep(2)

```

<details open> <summary>
- **`r PMID_32100878$title`**
</summary>

*`r citation_32100878`*

`r PubMed_32100878`

`r PMID_32100878$abstract`

`r doi_32100878`

</details>

---




---

```{r bileducts 31676785, include=FALSE}

PMID_31676785 <- RefManageR::ReadPubMed('31676785', database = 'PubMed')

citation_31676785 <- paste0(PMID_31676785$journal,' ', PMID_31676785$year, ' ', PMID_31676785$month,';', PMID_31676785$volume,'(', PMID_31676785$number,'):', PMID_31676785$pages)

PubMed_31676785 <- paste0(PubMedString, PMID_31676785$eprint)

doi_31676785 <- paste0(doiString, PMID_31676785$doi)

Sys.sleep(2)

```

<details open> <summary>
- **`r PMID_31676785$title`**
</summary>

*`r citation_31676785`*

`r PubMed_31676785`

`r PMID_31676785$abstract`

`r doi_31676785`

</details>

---




---

```{r bileducts 31755778, include=FALSE}

PMID_31755778 <- RefManageR::ReadPubMed('31755778', database = 'PubMed')

citation_31755778 <- paste0(PMID_31755778$journal,' ', PMID_31755778$year, ' ', PMID_31755778$month,';', PMID_31755778$volume,'(', PMID_31755778$number,'):', PMID_31755778$pages)

PubMed_31755778 <- paste0(PubMedString, PMID_31755778$eprint)

doi_31755778 <- paste0(doiString, PMID_31755778$doi)

Sys.sleep(2)

```

<details open> <summary>
- **`r PMID_31755778$title`**
</summary>

*`r citation_31755778`*

`r PubMed_31755778`

`r PMID_31755778$abstract`

`r doi_31755778`

</details>

---



---

```{r bileducts 31678302, include=FALSE}

PMID_31678302 <- RefManageR::ReadPubMed('31678302', database = 'PubMed')

citation_31678302 <- paste0(PMID_31678302$journal,' ', PMID_31678302$year, ' ', PMID_31678302$month,';', PMID_31678302$volume,'(', PMID_31678302$number,'):', PMID_31678302$pages)

PubMed_31678302 <- paste0(PubMedString, PMID_31678302$eprint)

doi_31678302 <- paste0(doiString, PMID_31678302$doi)

Sys.sleep(2)

```

<details open> <summary>
- **`r PMID_31678302$title`**
</summary>

*`r citation_31678302`*

`r PubMed_31678302`

`r PMID_31678302$abstract`

`r doi_31678302`

</details>

---



---

<a href="#top" target="_self">Back to top</a>

---

\pagebreak

## Ampulla {#ampulla}

---



---

```{r ampulla 32171280, include=FALSE}

PMID_32171280 <- RefManageR::ReadPubMed('32171280', database = 'PubMed')

citation_32171280 <- paste0(PMID_32171280$journal,' ', PMID_32171280$year, ' ', PMID_32171280$month,';', PMID_32171280$volume,'(', PMID_32171280$number,'):', PMID_32171280$pages)

PubMed_32171280 <- paste0(PubMedString, PMID_32171280$eprint)

doi_32171280 <- paste0(doiString, PMID_32171280$doi)

Sys.sleep(2)

```

<details open> <summary>
- **`r PMID_32171280$title`**
</summary>

*`r citation_32171280`*

`r PubMed_32171280`

`r PMID_32171280$abstract`

`r doi_32171280`

</details>

---




---

<a href="#top" target="_self">Back to top</a>

---

\pagebreak


# Feedback {#feedback}


[Google Feedback Form](https://docs.google.com/forms/d/e/1FAIpQLSeD3Z9J6Y7eMmiyM12f_SfAmHUlykb1zxZcwO6lg7cebGYQIQ/viewform)


<script id="dsq-count-scr" src="//pbpath-org.disqus.com/count.js" async></script>
<div id="disqus_thread"></div>
<script>

/**
*  RECOMMENDED CONFIGURATION VARIABLES: EDIT AND UNCOMMENT THE SECTION BELOW TO INSERT DYNAMIC VALUES FROM YOUR PLATFORM OR CMS.
*  LEARN WHY DEFINING THESE VARIABLES IS IMPORTANT: https://disqus.com/admin/universalcode/#configuration-variables*/
/*
var disqus_config = function () {
this.page.url = PAGE_URL;  // Replace PAGE_URL with your page's canonical URL variable
this.page.identifier = PAGE_IDENTIFIER; // Replace PAGE_IDENTIFIER with your page's unique identifier variable
};
*/
(function() { // DON'T EDIT BELOW THIS LINE
var d = document, s = d.createElement('script');
s.src = 'https://pbpath-org.disqus.com/embed.js';
s.setAttribute('data-timestamp', +new Date());
(d.head || d.body).appendChild(s);
})();
</script>
<noscript>Please enable JavaScript to view the <a href="https://disqus.com/?ref_noscript">comments powered by Disqus.</a></noscript>



---

<a href="#top" target="_self">Back to top</a>

---

\pagebreak
