---
title: "Pancreatobiliary Pathology Society Journal Watch"
output:
  html_notebook: 
    code_folding: none
    fig_caption: yes
    highlight: null
    theme: paper
  pdf_document:
    keep_tex: yes
    latex_engine: xelatex
    toc: yes
    toc_depth: 5
  html_document:
    df_print: kable
    highlight: null
    keep_md: yes
  word_document:
    toc: yes
date: "Last Update on `r format(Sys.Date())`"
subtitle: "October November December 2019"
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(cache = TRUE)
```


```{r library, include=FALSE}
suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(readxl))
```


```{r data load, include=FALSE}
articles <- readRDS("articles.rds")
```



<!-- Open all links in new tab-->  
<base target="_blank"/>  



---

# PBPath Journal Watch Articles {.tabset .tabset-fade .tabset-pills}


```{r strings , include=FALSE}
PubMedString <- "PubMed: https://www.ncbi.nlm.nih.gov/pubmed/?term="

doiString <- "doi: https://doi.org/"
```



---

**Wellcome to the PBPath Journal Watch!** 

This bi-monthly journal watch features exciting recently published pancreas and biliary pathology articles that will provide up to date medical knowledge in our field. These articles will be showcased in several convenient categories, including surgical pathology, cytopathology, and molecular pathology among others. The articles in each category are in no particular order. See the list of journals we search regularly [here](http://pbpath.org/pbpath-journal-watch/). Previous months’ issues may be found in our *[archive](http://pbpath.org/journal-watch-archive/)* and you may see [drafts of the upcoming issue here](http://pbpath.org/journal-watch-upcoming-issue/).  

We encourage members to actively participate by recommending new articles and providing feedback using the [forms provided below.](#feedback){target="_self"}  

**We hope that you will enjoy the new PBPath Journal Watch!**

---

<a href="#top" target="_self">Back to top</a>

---

\pagebreak



## Surgical Pathology {.tabset}

---

### Pancreas


---

#### Morphology, Diagnostics, IHC

Morphology, Diagnostics, IHC


```{r S Pancreas Morphology Diagnostics IHC, eval=FALSE, include=FALSE}
```



---

```{r pancreas 31802231, include=FALSE}

PMID_31802231 <- RefManageR::ReadPubMed('31802231', database = 'PubMed')

citation_31802231 <- paste0(PMID_31802231$journal,' ', PMID_31802231$year, ' ', PMID_31802231$month,';', PMID_31802231$volume,'(', PMID_31802231$number,'):', PMID_31802231$pages)

PubMed_31802231 <- paste0(PubMedString, PMID_31802231$eprint)

doi_31802231 <- paste0(doiString, PMID_31802231$doi)

Sys.sleep(2)

```

<details open> <summary>
- **`r PMID_31802231$title`**
</summary> 

*`r citation_31802231`*

`r PubMed_31802231`

`r PMID_31802231$abstract`

`r doi_31802231`

</details>


---

```{r pancreas 31786688, include=FALSE}

PMID_31786688 <- RefManageR::ReadPubMed('31786688', database = 'PubMed')

citation_31786688 <- paste0(PMID_31786688$journal,' ', PMID_31786688$year, ' ', PMID_31786688$month,';', PMID_31786688$volume,'(', PMID_31786688$number,'):', PMID_31786688$pages)

PubMed_31786688 <- paste0(PubMedString, PMID_31786688$eprint)

doi_31786688 <- paste0(doiString, PMID_31786688$doi)

Sys.sleep(2)

```

<details open> <summary>
- **`r PMID_31786688$title`**
</summary> 

*`r citation_31786688`*

`r PubMed_31786688`

`r PMID_31786688$abstract`

`r doi_31786688`

</details>



---

```{r pancreas 31338587, include=FALSE}

PMID_31338587 <- RefManageR::ReadPubMed('31338587', database = 'PubMed')

citation_31338587 <- paste0(PMID_31338587$journal,' ', PMID_31338587$year, ' ', PMID_31338587$month,';', PMID_31338587$volume,'(', PMID_31338587$number,'):', PMID_31338587$pages)

PubMed_31338587 <- paste0(PubMedString, PMID_31338587$eprint)

doi_31338587 <- paste0(doiString, PMID_31338587$doi)

Sys.sleep(2)

```

<details open> <summary>
- **`r PMID_31338587$title`**
</summary> 

*`r citation_31338587`*

`r PubMed_31338587`

`r PMID_31338587$abstract`

`r doi_31338587`

</details>


---

```{r pancreas 31285527, include=FALSE}

PMID_31285527 <- RefManageR::ReadPubMed('31285527', database = 'PubMed')

citation_31285527 <- paste0(PMID_31285527$journal,' ', PMID_31285527$year, ' ', PMID_31285527$month,';', PMID_31285527$volume,'(', PMID_31285527$number,'):', PMID_31285527$pages)

PubMed_31285527 <- paste0(PubMedString, PMID_31285527$eprint)

doi_31285527 <- paste0(doiString, PMID_31285527$doi)

Sys.sleep(2)

```

<details open> <summary>
- **`r PMID_31285527$title`**
</summary> 

*`r citation_31285527`*

`r PubMed_31285527`

`r PMID_31285527$abstract`

`r doi_31285527`

</details>

---








<a href="#top" target="_self">Back to top</a>

---

\pagebreak

#### Staging

Pancreas TNM staging, Margins, Survival

```{r S Pancreas TNM staging Margins Survival, eval=FALSE, include=FALSE}
```


---

```{r pancreas 29672406, include=FALSE}

PMID_29672406 <- RefManageR::ReadPubMed('29672406', database = 'PubMed')

citation_29672406 <- paste0(PMID_29672406$journal,' ', PMID_29672406$year, ' ', PMID_29672406$month,';', PMID_29672406$volume,'(', PMID_29672406$number,'):', PMID_29672406$pages)

PubMed_29672406 <- paste0(PubMedString, PMID_29672406$eprint)

doi_29672406 <- paste0(doiString, PMID_29672406$doi)

Sys.sleep(2)

```

<details open> <summary>
- **`r PMID_29672406$title`**
</summary> 

*`r citation_29672406`*

`r PubMed_29672406`

`r PMID_29672406$abstract`

`r doi_29672406`

</details>

---





<a href="#top" target="_self">Back to top</a>

---

\pagebreak


#### Preneoplastic and Preinvasive Lesions 

Preneoplastic and Preinvasive Lesions, PanIN, IPMN, MCN, ICPN

```{r S Pancreas Preneoplastic and Preinvasive Lesions IPMN, MCN, ITPN,  eval=FALSE, include=FALSE}
```







---

```{r pancreas 31804389, include=FALSE}

PMID_31804389 <- RefManageR::ReadPubMed('31804389', database = 'PubMed')

citation_31804389 <- paste0(PMID_31804389$journal,' ', PMID_31804389$year, ' ', PMID_31804389$month,';', PMID_31804389$volume,'(', PMID_31804389$number,'):', PMID_31804389$pages)

PubMed_31804389 <- paste0(PubMedString, PMID_31804389$eprint)

doi_31804389 <- paste0(doiString, PMID_31804389$doi)

Sys.sleep(2)

```

<details open> <summary>
- **`r PMID_31804389$title`**
</summary> 

*`r citation_31804389`*

`r PubMed_31804389`

`r PMID_31804389$abstract`

`r doi_31804389`

</details>

---








<a href="#top" target="_self">Back to top</a>

---

\pagebreak


#### Microenvironment 

Tumor Stroma Interactions, Microenvironment, Inflammatory Response

```{r S Tumor Stroma Interactions Microenvironment Inflammatory Response, eval=FALSE, include=FALSE}
```


---

---



<a href="#top" target="_self">Back to top</a>

---

\pagebreak


#### SPN

Solid Pseudopapillary Neoplasm

```{r S SPN Solid Pseudopapillary Neoplasm, eval=FALSE, include=FALSE}
```



---




<a href="#top" target="_self">Back to top</a>

---

\pagebreak


#### Analogue Tumors & Lesions


```{r S Pancreas Analogue Tumors Lesions, eval=FALSE, include=FALSE}
```


---

<a href="#top" target="_self">Back to top</a>

---

\pagebreak


#### Pancreatitis & Other Diseases

```{r Pancreas Pancreatitis & Other Diseases, eval=FALSE, include=FALSE}
```



---

```{r pancreas 31771513, include=FALSE}

PMID_31771513 <- RefManageR::ReadPubMed('31771513', database = 'PubMed')

citation_31771513 <- paste0(PMID_31771513$journal,' ', PMID_31771513$year, ' ', PMID_31771513$month,';', PMID_31771513$volume,'(', PMID_31771513$number,'):', PMID_31771513$pages)

PubMed_31771513 <- paste0(PubMedString, PMID_31771513$eprint)

doi_31771513 <- paste0(doiString, PMID_31771513$doi)

Sys.sleep(2)

```

<details open> <summary>
- **`r PMID_31771513$title`**
</summary> 

*`r citation_31771513`*

`r PubMed_31771513`

`r PMID_31771513$abstract`

`r doi_31771513`

</details>




---

```{r pancreas 31414989, include=FALSE}

PMID_31414989 <- RefManageR::ReadPubMed('31414989', database = 'PubMed')

citation_31414989 <- paste0(PMID_31414989$journal,' ', PMID_31414989$year, ' ', PMID_31414989$month,';', PMID_31414989$volume,'(', PMID_31414989$number,'):', PMID_31414989$pages)

PubMed_31414989 <- paste0(PubMedString, PMID_31414989$eprint)

doi_31414989 <- paste0(doiString, PMID_31414989$doi)

Sys.sleep(2)

```

<details open> <summary>
- **`r PMID_31414989$title`**
</summary> 

*`r citation_31414989`*

`r PubMed_31414989`

`r PMID_31414989$abstract`

`r doi_31414989`

</details>

---



<a href="#top" target="_self">Back to top</a>

---

\pagebreak




### Bile Ducts

```{r S Bile Ducts, eval=FALSE, include=FALSE}
```

---

#### Morphology, Diagnostics, IHC

Morphology, Diagnostics, IHC


```{r S Bile Ducts Morphology Diagnostics IHC, eval=FALSE, include=FALSE}
```



---

```{r bileducts 31834956, include=FALSE}

PMID_31834956 <- RefManageR::ReadPubMed('31834956', database = 'PubMed')

citation_31834956 <- paste0(PMID_31834956$journal,' ', PMID_31834956$year, ' ', PMID_31834956$month,';', PMID_31834956$volume,'(', PMID_31834956$number,'):', PMID_31834956$pages)

PubMed_31834956 <- paste0(PubMedString, PMID_31834956$eprint)

doi_31834956 <- paste0(doiString, PMID_31834956$doi)

Sys.sleep(2)

```

<details open> <summary>
- **`r PMID_31834956$title`**
</summary> 

*`r citation_31834956`*

`r PubMed_31834956`

`r PMID_31834956$abstract`

`r doi_31834956`

</details>

---




<a href="#top" target="_self">Back to top</a>

---

\pagebreak

#### Staging

Bile Ducts TNM staging, Margins, Survival

```{r Bile Ducts TNM staging Margins Survival, eval=FALSE, include=FALSE}
```



---




<a href="#top" target="_self">Back to top</a>

---

\pagebreak


### Gallbladder


```{r S Gallbladder, eval=FALSE, include=FALSE}
```


---

#### Morphology, Diagnostics, IHC

Morphology, Diagnostics, IHC


```{r S Gallbladder Morphology Diagnostics IHC, eval=FALSE, include=FALSE}
```



---

```{r gallbladder 31838585, include=FALSE}

PMID_31838585 <- RefManageR::ReadPubMed('31838585', database = 'PubMed')

citation_31838585 <- paste0(PMID_31838585$journal,' ', PMID_31838585$year, ' ', PMID_31838585$month,';', PMID_31838585$volume,'(', PMID_31838585$number,'):', PMID_31838585$pages)

PubMed_31838585 <- paste0(PubMedString, PMID_31838585$eprint)

doi_31838585 <- paste0(doiString, PMID_31838585$doi)

Sys.sleep(2)

```

<details open> <summary>
- **`r PMID_31838585$title`**
</summary> 

*`r citation_31838585`*

`r PubMed_31838585`

`r PMID_31838585$abstract`

`r doi_31838585`

</details>

---








<a href="#top" target="_self">Back to top</a>

---

\pagebreak

#### Staging

Gallbladder TNM staging, Margins, Survival

```{r Gallbladder TNM staging Margins Survival, eval=FALSE, include=FALSE}
```



---


<a href="#top" target="_self">Back to top</a>

---

\pagebreak


### Ampulla of Vater

```{r S Ampulla of Vater, eval=FALSE, include=FALSE}
```

---

#### Morphology, Diagnostics, IHC

Morphology, Diagnostics, IHC


```{r S Ampulla of Vater Morphology Diagnostics IHC, eval=FALSE, include=FALSE}
```



---

<a href="#top" target="_self">Back to top</a>

---

\pagebreak

#### Staging

Ampulla of Vater TNM staging, Margins, Survival

```{r Ampulla of Vater TNM staging Margins Survival, eval=FALSE, include=FALSE}
```


---

<a href="#top" target="_self">Back to top</a>

---

\pagebreak


### Neuroendocrine


---

#### PanNET

PanNET, Pancreatic Neuroendocrine Tumors and related neuroendocrine neoplasms

```{r S PanNET Neuroendocrine, eval=FALSE, include=FALSE}
```



---

```{r pancreas 31855317, include=FALSE}

PMID_31855317 <- RefManageR::ReadPubMed('31855317', database = 'PubMed')

citation_31855317 <- paste0(PMID_31855317$journal,' ', PMID_31855317$year, ' ', PMID_31855317$month,';', PMID_31855317$volume,'(', PMID_31855317$number,'):', PMID_31855317$pages)

PubMed_31855317 <- paste0(PubMedString, PMID_31855317$eprint)

doi_31855317 <- paste0(doiString, PMID_31855317$doi)

Sys.sleep(2)

```

<details open> <summary>
- **`r PMID_31855317$title`**
</summary> 

*`r citation_31855317`*

`r PubMed_31855317`

`r PMID_31855317$abstract`

`r doi_31855317`

</details>


---

```{r pancreas 31672292, include=FALSE}

PMID_31672292 <- RefManageR::ReadPubMed('31672292', database = 'PubMed')

citation_31672292 <- paste0(PMID_31672292$journal,' ', PMID_31672292$year, ' ', PMID_31672292$month,';', PMID_31672292$volume,'(', PMID_31672292$number,'):', PMID_31672292$pages)

PubMed_31672292 <- paste0(PubMedString, PMID_31672292$eprint)

doi_31672292 <- paste0(doiString, PMID_31672292$doi)

Sys.sleep(2)

```

<details open> <summary>
- **`r PMID_31672292$title`**
</summary> 

*`r citation_31672292`*

`r PubMed_31672292`

`r PMID_31672292$abstract`

`r doi_31672292`

</details>

---






<a href="#top" target="_self">Back to top</a>

---

\pagebreak




#### Microenvironment 

Tumor Stroma Interactions, Microenvironment, Inflammatory Response

```{r S Tumor Stroma Interactions Microenvironment Inflammatory Response, eval=FALSE, include=FALSE}
```



---

<a href="#top" target="_self">Back to top</a>

---

\pagebreak


#### Staging

PanNET TNM staging, Margins, Survival

```{r PanNET TNM staging Margins Survival, eval=FALSE, include=FALSE}
```



---

```{r pancreas 31838609, include=FALSE}

PMID_31838609 <- RefManageR::ReadPubMed('31838609', database = 'PubMed')

citation_31838609 <- paste0(PMID_31838609$journal,' ', PMID_31838609$year, ' ', PMID_31838609$month,';', PMID_31838609$volume,'(', PMID_31838609$number,'):', PMID_31838609$pages)

PubMed_31838609 <- paste0(PubMedString, PMID_31838609$eprint)

doi_31838609 <- paste0(doiString, PMID_31838609$doi)

Sys.sleep(2)

```

<details open> <summary>
- **`r PMID_31838609$title`**
</summary> 

*`r citation_31838609`*

`r PubMed_31838609`

`r PMID_31838609$abstract`

`r doi_31838609`

</details>

---






<a href="#top" target="_self">Back to top</a>

---

\pagebreak








## Cytopathology {.tabset}


---

### Pancreas

```{r C Pancreas, eval=FALSE, include=FALSE}
```


---

```{r pancreas 31825182, include=FALSE}

PMID_31825182 <- RefManageR::ReadPubMed('31825182', database = 'PubMed')

citation_31825182 <- paste0(PMID_31825182$journal,' ', PMID_31825182$year, ' ', PMID_31825182$month,';', PMID_31825182$volume,'(', PMID_31825182$number,'):', PMID_31825182$pages)

PubMed_31825182 <- paste0(PubMedString, PMID_31825182$eprint)

doi_31825182 <- paste0(doiString, PMID_31825182$doi)

Sys.sleep(2)

```

<details open> <summary>
- **`r PMID_31825182$title`**
</summary> 

*`r citation_31825182`*

`r PubMed_31825182`

`r PMID_31825182$abstract`

`r doi_31825182`

</details>



---

```{r pancreas 31788890, include=FALSE}

PMID_31788890 <- RefManageR::ReadPubMed('31788890', database = 'PubMed')

citation_31788890 <- paste0(PMID_31788890$journal,' ', PMID_31788890$year, ' ', PMID_31788890$month,';', PMID_31788890$volume,'(', PMID_31788890$number,'):', PMID_31788890$pages)

PubMed_31788890 <- paste0(PubMedString, PMID_31788890$eprint)

doi_31788890 <- paste0(doiString, PMID_31788890$doi)

Sys.sleep(2)

```

<details open> <summary>
- **`r PMID_31788890$title`**
</summary> 

*`r citation_31788890`*

`r PubMed_31788890`

`r PMID_31788890$abstract`

`r doi_31788890`

</details>


---

```{r pancreas 31785091, include=FALSE}

PMID_31785091 <- RefManageR::ReadPubMed('31785091', database = 'PubMed')

citation_31785091 <- paste0(PMID_31785091$journal,' ', PMID_31785091$year, ' ', PMID_31785091$month,';', PMID_31785091$volume,'(', PMID_31785091$number,'):', PMID_31785091$pages)

PubMed_31785091 <- paste0(PubMedString, PMID_31785091$eprint)

doi_31785091 <- paste0(doiString, PMID_31785091$doi)

Sys.sleep(2)

```

<details open> <summary>
- **`r PMID_31785091$title`**
</summary> 

*`r citation_31785091`*

`r PubMed_31785091`

`r PMID_31785091$abstract`

`r doi_31785091`

</details>



---

```{r pancreas 31774250, include=FALSE}

PMID_31774250 <- RefManageR::ReadPubMed('31774250', database = 'PubMed')

citation_31774250 <- paste0(PMID_31774250$journal,' ', PMID_31774250$year, ' ', PMID_31774250$month,';', PMID_31774250$volume,'(', PMID_31774250$number,'):', PMID_31774250$pages)

PubMed_31774250 <- paste0(PubMedString, PMID_31774250$eprint)

doi_31774250 <- paste0(doiString, PMID_31774250$doi)

Sys.sleep(2)

```

<details open> <summary>
- **`r PMID_31774250$title`**
</summary> 

*`r citation_31774250`*

`r PubMed_31774250`

`r PMID_31774250$abstract`

`r doi_31774250`

</details>




---

```{r pancreas 31599130, include=FALSE}

PMID_31599130 <- RefManageR::ReadPubMed('31599130', database = 'PubMed')

citation_31599130 <- paste0(PMID_31599130$journal,' ', PMID_31599130$year, ' ', PMID_31599130$month,';', PMID_31599130$volume,'(', PMID_31599130$number,'):', PMID_31599130$pages)

PubMed_31599130 <- paste0(PubMedString, PMID_31599130$eprint)

doi_31599130 <- paste0(doiString, PMID_31599130$doi)

Sys.sleep(2)

```

<details open> <summary>
- **`r PMID_31599130$title`**
</summary> 

*`r citation_31599130`*

`r PubMed_31599130`

`r PMID_31599130$abstract`

`r doi_31599130`

</details>


---

```{r pancreas 31407529, include=FALSE}

PMID_31407529 <- RefManageR::ReadPubMed('31407529', database = 'PubMed')

citation_31407529 <- paste0(PMID_31407529$journal,' ', PMID_31407529$year, ' ', PMID_31407529$month,';', PMID_31407529$volume,'(', PMID_31407529$number,'):', PMID_31407529$pages)

PubMed_31407529 <- paste0(PubMedString, PMID_31407529$eprint)

doi_31407529 <- paste0(doiString, PMID_31407529$doi)

Sys.sleep(2)

```

<details open> <summary>
- **`r PMID_31407529$title`**
</summary> 

*`r citation_31407529`*

`r PubMed_31407529`

`r PMID_31407529$abstract`

`r doi_31407529`

</details>

---










<a href="#top" target="_self">Back to top</a>

---

\pagebreak





### Ampulla Duodenum

```{r C Ampulla Duodenum, eval=FALSE, include=FALSE}
```



---




---


<a href="#top" target="_self">Back to top</a>

---

\pagebreak





### Bile Ducts

```{r C Bile Ducts, eval=FALSE, include=FALSE}
```



---






<a href="#top" target="_self">Back to top</a>

---

\pagebreak

### Gallbladder

```{r C Gallbladder, eval=FALSE, include=FALSE}
```













<a href="#top" target="_self">Back to top</a>

---

\pagebreak

### Neuroendocrine

```{r C Neuroendocrine, eval=FALSE, include=FALSE}
```



---

```{r pancreas 31846235, include=FALSE}

PMID_31846235 <- RefManageR::ReadPubMed('31846235', database = 'PubMed')

citation_31846235 <- paste0(PMID_31846235$journal,' ', PMID_31846235$year, ' ', PMID_31846235$month,';', PMID_31846235$volume,'(', PMID_31846235$number,'):', PMID_31846235$pages)

PubMed_31846235 <- paste0(PubMedString, PMID_31846235$eprint)

doi_31846235 <- paste0(doiString, PMID_31846235$doi)

Sys.sleep(2)

```

<details open> <summary>
- **`r PMID_31846235$title`**
</summary> 

*`r citation_31846235`*

`r PubMed_31846235`

`r PMID_31846235$abstract`

`r doi_31846235`

</details>

---


<a href="#top" target="_self">Back to top</a>

---

\pagebreak

## Molecular Pathology {.tabset}

---


### Pancreas

```{r M Pancreas, eval=FALSE, include=FALSE}
```

---

#### Pancreas



---

```{r pancreas 31848187, include=FALSE}

PMID_31848187 <- RefManageR::ReadPubMed('31848187', database = 'PubMed')

citation_31848187 <- paste0(PMID_31848187$journal,' ', PMID_31848187$year, ' ', PMID_31848187$month,';', PMID_31848187$volume,'(', PMID_31848187$number,'):', PMID_31848187$pages)

PubMed_31848187 <- paste0(PubMedString, PMID_31848187$eprint)

doi_31848187 <- paste0(doiString, PMID_31848187$doi)

Sys.sleep(2)

```

<details open> <summary>
- **`r PMID_31848187$title`**
</summary> 

*`r citation_31848187`*

`r PubMed_31848187`

`r PMID_31848187$abstract`

`r doi_31848187`

</details>

---



<a href="#top" target="_self">Back to top</a>

---

\pagebreak


#### SPN

Solid Pseudopapillary Neoplasm

```{r S SPN Solid Pseudopapillary Neoplasm, eval=FALSE, include=FALSE}
```


---

- Targeted next generation sequencing of pancreatic solid pseudopapillary neoplasms show mutations in Wnt signaling pathway genes.


https://www.ncbi.nlm.nih.gov/pubmed/30811747



---



<a href="#top" target="_self">Back to top</a>

---

\pagebreak


#### Pancreatitis & Other Diseases

Molecular Studies on Pancreatitis & Other Diseases

```{r Molecular Studies on Pancreatitis & Other Diseases, eval=FALSE, include=FALSE}
```









<a href="#top" target="_self">Back to top</a>

---

\pagebreak


#### Molecular Research on Microenvironment 

Tumor Stroma Interactions, Microenvironment, Inflammatory Response, Microbiome

```{r Molecular Tumor Stroma Interactions Microenvironment Inflammatory Response Microbiome, eval=FALSE, include=FALSE}
```




---


<a href="#top" target="_self">Back to top</a>

---

\pagebreak


#### Preneoplastic and Preinvasive Lesions 

Molecular Pathology Preneoplastic and Preinvasive Lesions, PanIN, IPMN, MCN, ICPN, IOPN

```{r Molecular Pancreas Preneoplastic and Preinvasive Lesions IPMN MCN ITPN IOPN,  eval=FALSE, include=FALSE}
```



---











<a href="#top" target="_self">Back to top</a>

---

\pagebreak


### Bile Ducts

```{r M Bile Ducts, eval=FALSE, include=FALSE}
```



---

<a href="#top" target="_self">Back to top</a>

---

\pagebreak



### Gallbladder

```{r M Gallbladder, eval=FALSE, include=FALSE}
```


---



---

<a href="#top" target="_self">Back to top</a>

---

\pagebreak

### Ampulla of Vater

```{r M Ampulla of Vater, eval=FALSE, include=FALSE}
```



---

<a href="#top" target="_self">Back to top</a>

---

\pagebreak


### Neuroendocrine


```{r M Neuroendocrine, eval=FALSE, include=FALSE}
```




---

<a href="#top" target="_self">Back to top</a>

---

\pagebreak

# Feedback


[Google Feedback Form](https://docs.google.com/forms/d/e/1FAIpQLSeD3Z9J6Y7eMmiyM12f_SfAmHUlykb1zxZcwO6lg7cebGYQIQ/viewform)  


<script id="dsq-count-scr" src="//pbpath-org.disqus.com/count.js" async></script>
<div id="disqus_thread"></div>
<script>

/**
*  RECOMMENDED CONFIGURATION VARIABLES: EDIT AND UNCOMMENT THE SECTION BELOW TO INSERT DYNAMIC VALUES FROM YOUR PLATFORM OR CMS.
*  LEARN WHY DEFINING THESE VARIABLES IS IMPORTANT: https://disqus.com/admin/universalcode/#configuration-variables*/
/*
var disqus_config = function () {
this.page.url = PAGE_URL;  // Replace PAGE_URL with your page's canonical URL variable
this.page.identifier = PAGE_IDENTIFIER; // Replace PAGE_IDENTIFIER with your page's unique identifier variable
};
*/
(function() { // DON'T EDIT BELOW THIS LINE
var d = document, s = d.createElement('script');
s.src = 'https://pbpath-org.disqus.com/embed.js';
s.setAttribute('data-timestamp', +new Date());
(d.head || d.body).appendChild(s);
})();
</script>
<noscript>Please enable JavaScript to view the <a href="https://disqus.com/?ref_noscript">comments powered by Disqus.</a></noscript>
                            


---

<a href="#top" target="_self">Back to top</a>

---

\pagebreak







