---
title: "PBPath Others December 2018 - January 2019"
output: html_notebook
---


```{r 30570546, include=FALSE}

PMID_30570546 <- RefManageR::ReadPubMed('30570546', database = 'PubMed')

citation_30570546 <- paste0(PMID_30570546$journal,' ', PMID_30570546$year, ' ', PMID_30570546$month,';', PMID_30570546$volume,'(', PMID_30570546$number,'):', PMID_30570546$pages)

PubMed_30570546 <- paste0(PubMedString, PMID_30570546$eprint)

doi_30570546 <- paste0(doiString, PMID_30570546$doi)

dimensionBadge_30570546 <- paste0(dimensionString1, PMID_30570546$doi,dimensionString2)

altmetricBadge_30570546 <- paste0(altmetricString1, PMID_30570546$doi, altmetricString2 )

addthis_inline_30570546 <- paste0(addthis_String1, PMID_30570546$title , " PMID: 30570546 " , addthis_String2)

Sys.sleep(1)


```

<details open> <summary>
- **`r PMID_30570546$title`**
</summary> 

*`r citation_30570546`*

`r PubMed_30570546`

`r addthis_inline_30570546`

`r PMID_30570546$abstract`

<!-- `r doi_30570546` -->

`r dimensionBadge_30570546`

`r altmetricBadge_30570546`

</details>

---


```{r 30562721, include=FALSE}

PMID_30562721 <- RefManageR::ReadPubMed('30562721', database = 'PubMed')

citation_30562721 <- paste0(PMID_30562721$journal,' ', PMID_30562721$year, ' ', PMID_30562721$month,';', PMID_30562721$volume,'(', PMID_30562721$number,'):', PMID_30562721$pages)

PubMed_30562721 <- paste0(PubMedString, PMID_30562721$eprint)

doi_30562721 <- paste0(doiString, PMID_30562721$doi)

dimensionBadge_30562721 <- paste0(dimensionString1, PMID_30562721$doi,dimensionString2)

altmetricBadge_30562721 <- paste0(altmetricString1, PMID_30562721$doi, altmetricString2 )

addthis_inline_30562721 <- paste0(addthis_String1, PMID_30562721$title , " PMID: 30562721 " , addthis_String2)

Sys.sleep(1)


```

<details open> <summary>
- **`r PMID_30562721$title`**
</summary> 

*`r citation_30562721`*

`r PubMed_30562721`

`r addthis_inline_30562721`

`r PMID_30562721$abstract`

<!-- `r doi_30562721` -->

`r dimensionBadge_30562721`

`r altmetricBadge_30562721`

</details>

---


```{r 30565710, include=FALSE}

PMID_30565710 <- RefManageR::ReadPubMed('30565710', database = 'PubMed')

citation_30565710 <- paste0(PMID_30565710$journal,' ', PMID_30565710$year, ' ', PMID_30565710$month,';', PMID_30565710$volume,'(', PMID_30565710$number,'):', PMID_30565710$pages)

PubMed_30565710 <- paste0(PubMedString, PMID_30565710$eprint)

doi_30565710 <- paste0(doiString, PMID_30565710$doi)

dimensionBadge_30565710 <- paste0(dimensionString1, PMID_30565710$doi,dimensionString2)

altmetricBadge_30565710 <- paste0(altmetricString1, PMID_30565710$doi, altmetricString2 )

addthis_inline_30565710 <- paste0(addthis_String1, PMID_30565710$title , " PMID: 30565710 " , addthis_String2)

Sys.sleep(1)


```

<details open> <summary>
- **`r PMID_30565710$title`**
</summary> 

*`r citation_30565710`*

`r PubMed_30565710`

`r addthis_inline_30565710`

`r PMID_30565710$abstract`

<!-- `r doi_30565710` -->

`r dimensionBadge_30565710`

`r altmetricBadge_30565710`

</details>

---


```{r 28367607, include=FALSE}

PMID_28367607 <- RefManageR::ReadPubMed('28367607', database = 'PubMed')

citation_28367607 <- paste0(PMID_28367607$journal,' ', PMID_28367607$year, ' ', PMID_28367607$month,';', PMID_28367607$volume,'(', PMID_28367607$number,'):', PMID_28367607$pages)

PubMed_28367607 <- paste0(PubMedString, PMID_28367607$eprint)

doi_28367607 <- paste0(doiString, PMID_28367607$doi)

dimensionBadge_28367607 <- paste0(dimensionString1, PMID_28367607$doi,dimensionString2)

altmetricBadge_28367607 <- paste0(altmetricString1, PMID_28367607$doi, altmetricString2 )

addthis_inline_28367607 <- paste0(addthis_String1, PMID_28367607$title , " PMID: 28367607 " , addthis_String2) 

Sys.sleep(1)

```

<details open> <summary>
- **`r PMID_28367607$title`**
</summary> 

*`r citation_28367607`*

`r PubMed_28367607`

`r addthis_inline_28367607`

`r PMID_28367607$abstract`

<!-- `r doi_28367607` -->

`r dimensionBadge_28367607`

`r altmetricBadge_28367607`

</details>

---

```{r 30499077, include=FALSE}

PMID_30499077 <- RefManageR::ReadPubMed('30499077', database = 'PubMed')

citation_30499077 <- paste0(PMID_30499077$journal,' ', PMID_30499077$year, ' ', PMID_30499077$month,';', PMID_30499077$volume,'(', PMID_30499077$number,'):', PMID_30499077$pages)

PubMed_30499077 <- paste0(PubMedString, PMID_30499077$eprint)

doi_30499077 <- paste0(doiString, PMID_30499077$doi)

dimensionBadge_30499077 <- paste0(dimensionString1, PMID_30499077$doi,dimensionString2)

altmetricBadge_30499077 <- paste0(altmetricString1, PMID_30499077$doi, altmetricString2 )

addthis_inline_30499077 <- paste0(addthis_String1, PMID_30499077$title , " PMID: 30499077 " , addthis_String2) 

Sys.sleep(1)

```

<details open> <summary>
- **`r PMID_30499077$title`**
</summary> 

*`r citation_30499077`*

`r PubMed_30499077`

`r addthis_inline_30499077`

`r PMID_30499077$abstract`

<!-- `r doi_30499077` -->

`r dimensionBadge_30499077`

`r altmetricBadge_30499077`

</details>


---


```{r 30043166, include=FALSE}

PMID_30043166 <- RefManageR::ReadPubMed('30043166', database = 'PubMed')

citation_30043166 <- paste0(PMID_30043166$journal,' ', PMID_30043166$year, ' ', PMID_30043166$month,';', PMID_30043166$volume,'(', PMID_30043166$number,'):', PMID_30043166$pages)

PubMed_30043166 <- paste0(PubMedString, PMID_30043166$eprint)

doi_30043166 <- paste0(doiString, PMID_30043166$doi)

dimensionBadge_30043166 <- paste0(dimensionString1, PMID_30043166$doi,dimensionString2)

altmetricBadge_30043166 <- paste0(altmetricString1, PMID_30043166$doi, altmetricString2 )

addthis_inline_30043166 <- paste0(addthis_String1, PMID_30043166$title , " PMID: 30043166 " , addthis_String2)

Sys.sleep(1)


```

<details open> <summary>
- **`r PMID_30043166$title`**
</summary> 

*`r citation_30043166`*

`r PubMed_30043166`

`r addthis_inline_30043166`

`r PMID_30043166$abstract`

<!-- `r doi_30043166` -->

`r dimensionBadge_30043166`

`r altmetricBadge_30043166`

</details>

---

```{r 30585820, include=FALSE}

PMID_30585820 <- RefManageR::ReadPubMed('30585820', database = 'PubMed')

citation_30585820 <- paste0(PMID_30585820$journal,' ', PMID_30585820$year, ' ', PMID_30585820$month,';', PMID_30585820$volume,'(', PMID_30585820$number,'):', PMID_30585820$pages)

PubMed_30585820 <- paste0(PubMedString, PMID_30585820$eprint)

doi_30585820 <- paste0(doiString, PMID_30585820$doi)

dimensionBadge_30585820 <- paste0(dimensionString1, PMID_30585820$doi,dimensionString2)

altmetricBadge_30585820 <- paste0(altmetricString1, PMID_30585820$doi, altmetricString2 )

addthis_inline_30585820 <- paste0(addthis_String1, PMID_30585820$title , " PMID: 30585820 " , addthis_String2)

Sys.sleep(1)


```

<details open> <summary>
- **`r PMID_30585820$title`**
</summary> 

*`r citation_30585820`*

`r PubMed_30585820`

`r addthis_inline_30585820`

`r PMID_30585820$abstract`

<!-- `r doi_30585820` -->

`r dimensionBadge_30585820`

`r altmetricBadge_30585820`

</details>


---





#### Staging

PanNET TNM staging, Margins, Survival

```{r PanNET TNM staging Margins Survival, eval=FALSE, include=FALSE}
```

---

```{r 30661921, include=FALSE}

PMID_30661921 <- RefManageR::ReadPubMed('30661921', database = 'PubMed')

citation_30661921 <- paste0(PMID_30661921$journal,' ', PMID_30661921$year, ' ', PMID_30661921$month,';', PMID_30661921$volume,'(', PMID_30661921$number,'):', PMID_30661921$pages)

PubMed_30661921 <- paste0(PubMedString, PMID_30661921$eprint)

doi_30661921 <- paste0(doiString, PMID_30661921$doi)

dimensionBadge_30661921 <- paste0(dimensionString1, PMID_30661921$doi,dimensionString2)

altmetricBadge_30661921 <- paste0(altmetricString1, PMID_30661921$doi, altmetricString2 )

addthis_inline_30661921 <- paste0(addthis_String1, PMID_30661921$title , " PMID: 30661921 " , addthis_String2)

Sys.sleep(1)


```

<details open> <summary>
- **`r PMID_30661921$title`**
</summary> 

*`r citation_30661921`*

`r PubMed_30661921`

`r addthis_inline_30661921`

`r PMID_30661921$abstract`

<!-- `r doi_30661921` -->

`r dimensionBadge_30661921`

`r altmetricBadge_30661921`

</details>

---


<a href="#top" target="_self">Back to top</a>

---

\pagebreak



---

```{r 30419209, include=FALSE}

PMID_30419209 <- RefManageR::ReadPubMed('30419209', database = 'PubMed')

citation_30419209 <- paste0(PMID_30419209$journal,' ', PMID_30419209$year, ' ', PMID_30419209$month,';', PMID_30419209$volume,'(', PMID_30419209$number,'):', PMID_30419209$pages)

PubMed_30419209 <- paste0(PubMedString, PMID_30419209$eprint)

doi_30419209 <- paste0(doiString, PMID_30419209$doi)

dimensionBadge_30419209 <- paste0(dimensionString1, PMID_30419209$doi,dimensionString2)

altmetricBadge_30419209 <- paste0(altmetricString1, PMID_30419209$doi, altmetricString2 )

addthis_inline_30419209 <- paste0(addthis_String1, PMID_30419209$title , " PMID: 30419209 " , addthis_String2)

Sys.sleep(1)


```

<details open> <summary>
- **`r PMID_30419209$title`**
</summary> 

*`r citation_30419209`*

`r PubMed_30419209`

`r addthis_inline_30419209`

`r PMID_30419209$abstract`

<!-- `r doi_30419209` -->

`r dimensionBadge_30419209`

`r altmetricBadge_30419209`

</details>

---


```{r 30613628, include=FALSE}

PMID_30613628 <- RefManageR::ReadPubMed('30613628', database = 'PubMed')

citation_30613628 <- paste0(PMID_30613628$journal,' ', PMID_30613628$year, ' ', PMID_30613628$month,';', PMID_30613628$volume,'(', PMID_30613628$number,'):', PMID_30613628$pages)

PubMed_30613628 <- paste0(PubMedString, PMID_30613628$eprint)

doi_30613628 <- paste0(doiString, PMID_30613628$doi)

dimensionBadge_30613628 <- paste0(dimensionString1, PMID_30613628$doi,dimensionString2)

altmetricBadge_30613628 <- paste0(altmetricString1, PMID_30613628$doi, altmetricString2 )

addthis_inline_30613628 <- paste0(addthis_String1, PMID_30613628$title , " PMID: 30613628 " , addthis_String2)

Sys.sleep(1)


```

<details open> <summary>
- **`r PMID_30613628$title`**
</summary> 

*`r citation_30613628`*

`r PubMed_30613628`

`r addthis_inline_30613628`

`r PMID_30613628$abstract`

<!-- `r doi_30613628` -->

`r dimensionBadge_30613628`

`r altmetricBadge_30613628`

</details>


---








## Others {.tabset}

---

### Case Reports

---

#### Pancreas

---

```{r 30531244, include=FALSE}

PMID_30531244 <- RefManageR::ReadPubMed('30531244', database = 'PubMed')

citation_30531244 <- paste0(PMID_30531244$journal,' ', PMID_30531244$year, ' ', PMID_30531244$month,';', PMID_30531244$volume,'(', PMID_30531244$number,'):', PMID_30531244$pages)

PubMed_30531244 <- paste0(PubMedString, PMID_30531244$eprint)

doi_30531244 <- paste0(doiString, PMID_30531244$doi)

dimensionBadge_30531244 <- paste0(dimensionString1, PMID_30531244$doi,dimensionString2)

altmetricBadge_30531244 <- paste0(altmetricString1, PMID_30531244$doi, altmetricString2 )

addthis_inline_30531244 <- paste0(addthis_String1, PMID_30531244$title , " PMID: 30531244 " , addthis_String2)

Sys.sleep(1)


```

<details open> <summary>
- **`r PMID_30531244$title`**
</summary> 

*`r citation_30531244`*

`r PubMed_30531244`

`r addthis_inline_30531244`

`r PMID_30531244$abstract`

<!-- `r doi_30531244` -->

`r dimensionBadge_30531244`

`r altmetricBadge_30531244`

</details>

---


#### Bile Ducts

---

#### Gallbladder

---

```{r 30587051, include=FALSE}

PMID_30587051 <- RefManageR::ReadPubMed('30587051', database = 'PubMed')

citation_30587051 <- paste0(PMID_30587051$journal,' ', PMID_30587051$year, ' ', PMID_30587051$month,';', PMID_30587051$volume,'(', PMID_30587051$number,'):', PMID_30587051$pages)

PubMed_30587051 <- paste0(PubMedString, PMID_30587051$eprint)

doi_30587051 <- paste0(doiString, PMID_30587051$doi)

dimensionBadge_30587051 <- paste0(dimensionString1, PMID_30587051$doi,dimensionString2)

altmetricBadge_30587051 <- paste0(altmetricString1, PMID_30587051$doi, altmetricString2 )

addthis_inline_30587051 <- paste0(addthis_String1, PMID_30587051$title , " PMID: 30587051 " , addthis_String2)

Sys.sleep(1)


```

<details open> <summary>
- **`r PMID_30587051$title`**
</summary> 

*`r citation_30587051`*

`r PubMed_30587051`

`r addthis_inline_30587051`

`r PMID_30587051$abstract`

<!-- `r doi_30587051` -->

`r dimensionBadge_30587051`

`r altmetricBadge_30587051`

</details>


---

```{r 28462448, include=FALSE}

PMID_28462448 <- RefManageR::ReadPubMed('28462448', database = 'PubMed')

citation_28462448 <- paste0(PMID_28462448$journal,' ', PMID_28462448$year, ' ', PMID_28462448$month,';', PMID_28462448$volume,'(', PMID_28462448$number,'):', PMID_28462448$pages)

PubMed_28462448 <- paste0(PubMedString, PMID_28462448$eprint)

doi_28462448 <- paste0(doiString, PMID_28462448$doi)

dimensionBadge_28462448 <- paste0(dimensionString1, PMID_28462448$doi,dimensionString2)

altmetricBadge_28462448 <- paste0(altmetricString1, PMID_28462448$doi, altmetricString2 )

addthis_inline_28462448 <- paste0(addthis_String1, PMID_28462448$title , " PMID: 28462448 " , addthis_String2)

Sys.sleep(1)


```

<details open> <summary>
- **`r PMID_28462448$title`**
</summary> 

*`r citation_28462448`*

`r PubMed_28462448`

`r addthis_inline_28462448`

`r PMID_28462448$abstract`

<!-- `r doi_28462448` -->

`r dimensionBadge_28462448`

`r altmetricBadge_28462448`

</details>

---

#### Ampulla of Vater

---

```{r 29618230, include=FALSE}

PMID_29618230 <- RefManageR::ReadPubMed('29618230', database = 'PubMed')

citation_29618230 <- paste0(PMID_29618230$journal,' ', PMID_29618230$year, ' ', PMID_29618230$month,';', PMID_29618230$volume,'(', PMID_29618230$number,'):', PMID_29618230$pages)

PubMed_29618230 <- paste0(PubMedString, PMID_29618230$eprint)

doi_29618230 <- paste0(doiString, PMID_29618230$doi)

dimensionBadge_29618230 <- paste0(dimensionString1, PMID_29618230$doi,dimensionString2)

altmetricBadge_29618230 <- paste0(altmetricString1, PMID_29618230$doi, altmetricString2 )

addthis_inline_29618230 <- paste0(addthis_String1, PMID_29618230$title , " PMID: 29618230 " , addthis_String2)

Sys.sleep(1)


```

<details open> <summary>
- **`r PMID_29618230$title`**
</summary> 

*`r citation_29618230`*

`r PubMed_29618230`

`r addthis_inline_29618230`

`r PMID_29618230$abstract`

<!-- `r doi_29618230` -->

`r dimensionBadge_29618230`

`r altmetricBadge_29618230`

</details>

---

```{r 30631857, include=FALSE}

PMID_30631857 <- RefManageR::ReadPubMed('30631857', database = 'PubMed')

citation_30631857 <- paste0(PMID_30631857$journal,' ', PMID_30631857$year, ' ', PMID_30631857$month,';', PMID_30631857$volume,'(', PMID_30631857$number,'):', PMID_30631857$pages)

PubMed_30631857 <- paste0(PubMedString, PMID_30631857$eprint)

doi_30631857 <- paste0(doiString, PMID_30631857$doi)

dimensionBadge_30631857 <- paste0(dimensionString1, PMID_30631857$doi,dimensionString2)

altmetricBadge_30631857 <- paste0(altmetricString1, PMID_30631857$doi, altmetricString2 )

addthis_inline_30631857 <- paste0(addthis_String1, PMID_30631857$title , " PMID: 30631857 " , addthis_String2)

Sys.sleep(1)


```

<details open> <summary>
- **`r PMID_30631857$title`**
</summary> 

*`r citation_30631857`*

`r PubMed_30631857`

`r addthis_inline_30631857`

`r PMID_30631857$abstract`

<!-- `r doi_30631857` -->

`r dimensionBadge_30631857`

`r altmetricBadge_30631857`

</details>

---


```{r 30027790, include=FALSE}

PMID_30027790 <- RefManageR::ReadPubMed('30027790', database = 'PubMed')

citation_30027790 <- paste0(PMID_30027790$journal,' ', PMID_30027790$year, ' ', PMID_30027790$month,';', PMID_30027790$volume,'(', PMID_30027790$number,'):', PMID_30027790$pages)

PubMed_30027790 <- paste0(PubMedString, PMID_30027790$eprint)

doi_30027790 <- paste0(doiString, PMID_30027790$doi)

dimensionBadge_30027790 <- paste0(dimensionString1, PMID_30027790$doi,dimensionString2)

altmetricBadge_30027790 <- paste0(altmetricString1, PMID_30027790$doi, altmetricString2 )

addthis_inline_30027790 <- paste0(addthis_String1, PMID_30027790$title , " PMID: 30027790 " , addthis_String2)

Sys.sleep(1)


```

<details open> <summary>
- **`r PMID_30027790$title`**
</summary> 

*`r citation_30027790`*

`r PubMed_30027790`

`r addthis_inline_30027790`

`r PMID_30027790$abstract`

<!-- `r doi_30027790` -->

`r dimensionBadge_30027790`

`r altmetricBadge_30027790`

</details>

---


#### Neuroendocrine


---

```{r 30635305, include=FALSE}

PMID_30635305 <- RefManageR::ReadPubMed('30635305', database = 'PubMed')

citation_30635305 <- paste0(PMID_30635305$journal,' ', PMID_30635305$year, ' ', PMID_30635305$month,';', PMID_30635305$volume,'(', PMID_30635305$number,'):', PMID_30635305$pages)

PubMed_30635305 <- paste0(PubMedString, PMID_30635305$eprint)

doi_30635305 <- paste0(doiString, PMID_30635305$doi)

dimensionBadge_30635305 <- paste0(dimensionString1, PMID_30635305$doi,dimensionString2)

altmetricBadge_30635305 <- paste0(altmetricString1, PMID_30635305$doi, altmetricString2 )

addthis_inline_30635305 <- paste0(addthis_String1, PMID_30635305$title , " PMID: 30635305 " , addthis_String2)

Sys.sleep(1)


```

<details open> <summary>
- **`r PMID_30635305$title`**
</summary> 

*`r citation_30635305`*

`r PubMed_30635305`

`r addthis_inline_30635305`

`r PMID_30635305$abstract`

<!-- `r doi_30635305` -->

`r dimensionBadge_30635305`

`r altmetricBadge_30635305`

</details>

---





<a href="#top" target="_self">Back to top</a>

---

\pagebreak

### Experimental Studies


---

```{r 30683474, include=FALSE}

PMID_30683474 <- RefManageR::ReadPubMed('30683474', database = 'PubMed')

citation_30683474 <- paste0(PMID_30683474$journal,' ', PMID_30683474$year, ' ', PMID_30683474$month,';', PMID_30683474$volume,'(', PMID_30683474$number,'):', PMID_30683474$pages)

PubMed_30683474 <- paste0(PubMedString, PMID_30683474$eprint)

doi_30683474 <- paste0(doiString, PMID_30683474$doi)

dimensionBadge_30683474 <- paste0(dimensionString1, PMID_30683474$doi,dimensionString2)

altmetricBadge_30683474 <- paste0(altmetricString1, PMID_30683474$doi, altmetricString2 )

addthis_inline_30683474 <- paste0(addthis_String1, PMID_30683474$title , " PMID: 30683474 " , addthis_String2)

Sys.sleep(1)


```

<details open> <summary>
- **`r PMID_30683474$title`**
</summary> 

*`r citation_30683474`*

`r PubMed_30683474`

`r addthis_inline_30683474`

`r PMID_30683474$abstract`

<!-- `r doi_30683474` -->

`r dimensionBadge_30683474`

`r altmetricBadge_30683474`

</details>

---

```{r 30670333, include=FALSE}

PMID_30670333 <- RefManageR::ReadPubMed('30670333', database = 'PubMed')

citation_30670333 <- paste0(PMID_30670333$journal,' ', PMID_30670333$year, ' ', PMID_30670333$month,';', PMID_30670333$volume,'(', PMID_30670333$number,'):', PMID_30670333$pages)

PubMed_30670333 <- paste0(PubMedString, PMID_30670333$eprint)

doi_30670333 <- paste0(doiString, PMID_30670333$doi)

dimensionBadge_30670333 <- paste0(dimensionString1, PMID_30670333$doi,dimensionString2)

altmetricBadge_30670333 <- paste0(altmetricString1, PMID_30670333$doi, altmetricString2 )

addthis_inline_30670333 <- paste0(addthis_String1, PMID_30670333$title , " PMID: 30670333 " , addthis_String2)

Sys.sleep(1)


```

<details open> <summary>
- **`r PMID_30670333$title`**
</summary> 

*`r citation_30670333`*

`r PubMed_30670333`

`r addthis_inline_30670333`

`r PMID_30670333$abstract`

<!-- `r doi_30670333` -->

`r dimensionBadge_30670333`

`r altmetricBadge_30670333`

</details>

---

```{r 30106154, include=FALSE}

PMID_30106154 <- RefManageR::ReadPubMed('30106154', database = 'PubMed')

citation_30106154 <- paste0(PMID_30106154$journal,' ', PMID_30106154$year, ' ', PMID_30106154$month,';', PMID_30106154$volume,'(', PMID_30106154$number,'):', PMID_30106154$pages)

PubMed_30106154 <- paste0(PubMedString, PMID_30106154$eprint)

doi_30106154 <- paste0(doiString, PMID_30106154$doi)

dimensionBadge_30106154 <- paste0(dimensionString1, PMID_30106154$doi,dimensionString2)

altmetricBadge_30106154 <- paste0(altmetricString1, PMID_30106154$doi, altmetricString2 )

addthis_inline_30106154 <- paste0(addthis_String1, PMID_30106154$title , " PMID: 30106154 " , addthis_String2)

Sys.sleep(1)


```

<details open> <summary>
- **`r PMID_30106154$title`**
</summary> 

*`r citation_30106154`*

`r PubMed_30106154`

`r addthis_inline_30106154`

`r PMID_30106154$abstract`

<!-- `r doi_30106154` -->

`r dimensionBadge_30106154`

`r altmetricBadge_30106154`

</details>

---


```{r 30538111, include=FALSE}

PMID_30538111 <- RefManageR::ReadPubMed('30538111', database = 'PubMed')

citation_30538111 <- paste0(PMID_30538111$journal,' ', PMID_30538111$year, ' ', PMID_30538111$month,';', PMID_30538111$volume,'(', PMID_30538111$number,'):', PMID_30538111$pages)

PubMed_30538111 <- paste0(PubMedString, PMID_30538111$eprint)

doi_30538111 <- paste0(doiString, PMID_30538111$doi)

dimensionBadge_30538111 <- paste0(dimensionString1, PMID_30538111$doi,dimensionString2)

altmetricBadge_30538111 <- paste0(altmetricString1, PMID_30538111$doi, altmetricString2 )

addthis_inline_30538111 <- paste0(addthis_String1, PMID_30538111$title , " PMID: 30538111 " , addthis_String2)

Sys.sleep(1)


```

<details open> <summary>
- **`r PMID_30538111$title`**
</summary> 

*`r citation_30538111`*

`r PubMed_30538111`

`r addthis_inline_30538111`

`r PMID_30538111$abstract`

<!-- `r doi_30538111` -->

`r dimensionBadge_30538111`

`r altmetricBadge_30538111`

</details>

---

```{r 30540680, include=FALSE}

PMID_30540680 <- RefManageR::ReadPubMed('30540680', database = 'PubMed')

citation_30540680 <- paste0(PMID_30540680$journal,' ', PMID_30540680$year, ' ', PMID_30540680$month,';', PMID_30540680$volume,'(', PMID_30540680$number,'):', PMID_30540680$pages)

PubMed_30540680 <- paste0(PubMedString, PMID_30540680$eprint)

doi_30540680 <- paste0(doiString, PMID_30540680$doi)

dimensionBadge_30540680 <- paste0(dimensionString1, PMID_30540680$doi,dimensionString2)

altmetricBadge_30540680 <- paste0(altmetricString1, PMID_30540680$doi, altmetricString2 )

addthis_inline_30540680 <- paste0(addthis_String1, PMID_30540680$title , " PMID: 30540680 " , addthis_String2)

Sys.sleep(1)


```

<details open> <summary>
- **`r PMID_30540680$title`**
</summary> 

*`r citation_30540680`*

`r PubMed_30540680`

`r addthis_inline_30540680`

`r PMID_30540680$abstract`

<!-- `r doi_30540680` -->

`r dimensionBadge_30540680`

`r altmetricBadge_30540680`

</details>


---


```{r 30530506, include=FALSE}

PMID_30530506 <- RefManageR::ReadPubMed('30530506', database = 'PubMed')

citation_30530506 <- paste0(PMID_30530506$journal,' ', PMID_30530506$year, ' ', PMID_30530506$month,';', PMID_30530506$volume,'(', PMID_30530506$number,'):', PMID_30530506$pages)

PubMed_30530506 <- paste0(PubMedString, PMID_30530506$eprint)

doi_30530506 <- paste0(doiString, PMID_30530506$doi)

dimensionBadge_30530506 <- paste0(dimensionString1, PMID_30530506$doi,dimensionString2)

altmetricBadge_30530506 <- paste0(altmetricString1, PMID_30530506$doi, altmetricString2 )

addthis_inline_30530506 <- paste0(addthis_String1, PMID_30530506$title , " PMID: 30530506 " , addthis_String2)

Sys.sleep(1)


```

<details open> <summary>
- **`r PMID_30530506$title`**
</summary> 

*`r citation_30530506`*

`r PubMed_30530506`

`r addthis_inline_30530506`

`r PMID_30530506$abstract`

<!-- `r doi_30530506` -->

`r dimensionBadge_30530506`

`r altmetricBadge_30530506`

</details>

---


```{r 30531247, include=FALSE}

PMID_30531247 <- RefManageR::ReadPubMed('30531247', database = 'PubMed')

citation_30531247 <- paste0(PMID_30531247$journal,' ', PMID_30531247$year, ' ', PMID_30531247$month,';', PMID_30531247$volume,'(', PMID_30531247$number,'):', PMID_30531247$pages)

PubMed_30531247 <- paste0(PubMedString, PMID_30531247$eprint)

doi_30531247 <- paste0(doiString, PMID_30531247$doi)

dimensionBadge_30531247 <- paste0(dimensionString1, PMID_30531247$doi,dimensionString2)

altmetricBadge_30531247 <- paste0(altmetricString1, PMID_30531247$doi, altmetricString2 )

addthis_inline_30531247 <- paste0(addthis_String1, PMID_30531247$title , " PMID: 30531247 " , addthis_String2)

Sys.sleep(1)


```

<details open> <summary>
- **`r PMID_30531247$title`**
</summary> 

*`r citation_30531247`*

`r PubMed_30531247`

`r addthis_inline_30531247`

`r PMID_30531247$abstract`

<!-- `r doi_30531247` -->

`r dimensionBadge_30531247`

`r altmetricBadge_30531247`

</details>

---

```{r 30272364, include=FALSE}

PMID_30272364 <- RefManageR::ReadPubMed('30272364', database = 'PubMed')

citation_30272364 <- paste0(PMID_30272364$journal,' ', PMID_30272364$year, ' ', PMID_30272364$month,';', PMID_30272364$volume,'(', PMID_30272364$number,'):', PMID_30272364$pages)

PubMed_30272364 <- paste0(PubMedString, PMID_30272364$eprint)

doi_30272364 <- paste0(doiString, PMID_30272364$doi)

dimensionBadge_30272364 <- paste0(dimensionString1, PMID_30272364$doi,dimensionString2)

altmetricBadge_30272364 <- paste0(altmetricString1, PMID_30272364$doi, altmetricString2 )

addthis_inline_30272364 <- paste0(addthis_String1, PMID_30272364$title , " PMID: 30272364 " , addthis_String2)

Sys.sleep(1)


```

<details open> <summary>
- **`r PMID_30272364$title`**
</summary> 

*`r citation_30272364`*

`r PubMed_30272364`

`r addthis_inline_30272364`

`r PMID_30272364$abstract`

<!-- `r doi_30272364` -->

`r dimensionBadge_30272364`

`r altmetricBadge_30272364`

</details>



---


<a href="#top" target="_self">Back to top</a>

---

\pagebreak


### Techniques, Research Methods, Liquid Biopsy

---

Techniques, Research Methods, Liquid Biopsy

```{r Techniques & Research Methods Liquid Biopsy, eval=FALSE, include=FALSE}
```


---

```{r 30558725, include=FALSE}

PMID_30558725 <- RefManageR::ReadPubMed('30558725', database = 'PubMed')

citation_30558725 <- paste0(PMID_30558725$journal,' ', PMID_30558725$year, ' ', PMID_30558725$month,';', PMID_30558725$volume,'(', PMID_30558725$number,'):', PMID_30558725$pages)

PubMed_30558725 <- paste0(PubMedString, PMID_30558725$eprint)

doi_30558725 <- paste0(doiString, PMID_30558725$doi)

dimensionBadge_30558725 <- paste0(dimensionString1, PMID_30558725$doi,dimensionString2)

altmetricBadge_30558725 <- paste0(altmetricString1, PMID_30558725$doi, altmetricString2 )

addthis_inline_30558725 <- paste0(addthis_String1, PMID_30558725$title , " PMID: 30558725 " , addthis_String2)

Sys.sleep(1)


```

<details open> <summary>
- **`r PMID_30558725$title`**
</summary> 

*`r citation_30558725`*

`r PubMed_30558725`

`r addthis_inline_30558725`

`r PMID_30558725$abstract`

<!-- `r doi_30558725` -->

`r dimensionBadge_30558725`

`r altmetricBadge_30558725`

</details>

---


```{r 30531240, include=FALSE}

PMID_30531240 <- RefManageR::ReadPubMed('30531240', database = 'PubMed')

citation_30531240 <- paste0(PMID_30531240$journal,' ', PMID_30531240$year, ' ', PMID_30531240$month,';', PMID_30531240$volume,'(', PMID_30531240$number,'):', PMID_30531240$pages)

PubMed_30531240 <- paste0(PubMedString, PMID_30531240$eprint)

doi_30531240 <- paste0(doiString, PMID_30531240$doi)

dimensionBadge_30531240 <- paste0(dimensionString1, PMID_30531240$doi,dimensionString2)

altmetricBadge_30531240 <- paste0(altmetricString1, PMID_30531240$doi, altmetricString2 )

addthis_inline_30531240 <- paste0(addthis_String1, PMID_30531240$title , " PMID: 30531240 " , addthis_String2)

Sys.sleep(1)


```

<details open> <summary>
- **`r PMID_30531240$title`**
</summary> 

*`r citation_30531240`*

`r PubMed_30531240`

`r addthis_inline_30531240`

`r PMID_30531240$abstract`

<!-- `r doi_30531240` -->

`r dimensionBadge_30531240`

`r altmetricBadge_30531240`

</details>

---

```{r 30554606, include=FALSE}

PMID_30554606 <- RefManageR::ReadPubMed('30554606', database = 'PubMed')

citation_30554606 <- paste0(PMID_30554606$journal,' ', PMID_30554606$year, ' ', PMID_30554606$month,';', PMID_30554606$volume,'(', PMID_30554606$number,'):', PMID_30554606$pages)

PubMed_30554606 <- paste0(PubMedString, PMID_30554606$eprint)

doi_30554606 <- paste0(doiString, PMID_30554606$doi)

dimensionBadge_30554606 <- paste0(dimensionString1, PMID_30554606$doi,dimensionString2)

altmetricBadge_30554606 <- paste0(altmetricString1, PMID_30554606$doi, altmetricString2 )

addthis_inline_30554606 <- paste0(addthis_String1, PMID_30554606$title , " PMID: 30554606 " , addthis_String2)

Sys.sleep(1)


```

<details open> <summary>
- **`r PMID_30554606$title`**
</summary> 

*`r citation_30554606`*

`r PubMed_30554606`

`r addthis_inline_30554606`

`r PMID_30554606$abstract`

<!-- `r doi_30554606` -->

`r dimensionBadge_30554606`

`r altmetricBadge_30554606`

</details>


---

```{r 29510146, include=FALSE}

PMID_29510146 <- RefManageR::ReadPubMed('29510146', database = 'PubMed')

citation_29510146 <- paste0(PMID_29510146$journal,' ', PMID_29510146$year, ' ', PMID_29510146$month,';', PMID_29510146$volume,'(', PMID_29510146$number,'):', PMID_29510146$pages)

PubMed_29510146 <- paste0(PubMedString, PMID_29510146$eprint)

doi_29510146 <- paste0(doiString, PMID_29510146$doi)

dimensionBadge_29510146 <- paste0(dimensionString1, PMID_29510146$doi,dimensionString2)

altmetricBadge_29510146 <- paste0(altmetricString1, PMID_29510146$doi, altmetricString2 )

addthis_inline_29510146 <- paste0(addthis_String1, PMID_29510146$title , " PMID: 29510146 " , addthis_String2)

Sys.sleep(1)


```

<details open> <summary>
- **`r PMID_29510146$title`**
</summary> 

*`r citation_29510146`*

`r PubMed_29510146`

`r addthis_inline_29510146`

`r PMID_29510146$abstract`

<!-- `r doi_29510146` -->

`r dimensionBadge_29510146`

`r altmetricBadge_29510146`

</details>


---

```{r 30548962, include=FALSE}

PMID_30548962 <- RefManageR::ReadPubMed('30548962', database = 'PubMed')

citation_30548962 <- paste0(PMID_30548962$journal,' ', PMID_30548962$year, ' ', PMID_30548962$month,';', PMID_30548962$volume,'(', PMID_30548962$number,'):', PMID_30548962$pages)

PubMed_30548962 <- paste0(PubMedString, PMID_30548962$eprint)

doi_30548962 <- paste0(doiString, PMID_30548962$doi)

dimensionBadge_30548962 <- paste0(dimensionString1, PMID_30548962$doi,dimensionString2)

altmetricBadge_30548962 <- paste0(altmetricString1, PMID_30548962$doi, altmetricString2 )

addthis_inline_30548962 <- paste0(addthis_String1, PMID_30548962$title , " PMID: 30548962 " , addthis_String2)

Sys.sleep(1)


```

<details open> <summary>
- **`r PMID_30548962$title`**
</summary> 

*`r citation_30548962`*

`r PubMed_30548962`

`r addthis_inline_30548962`

`r PMID_30548962$abstract`

<!-- `r doi_30548962` -->

`r dimensionBadge_30548962`

`r altmetricBadge_30548962`

</details>

---

```{r 30669703, include=FALSE}

PMID_30669703 <- RefManageR::ReadPubMed('30669703', database = 'PubMed')

citation_30669703 <- paste0(PMID_30669703$journal,' ', PMID_30669703$year, ' ', PMID_30669703$month,';', PMID_30669703$volume,'(', PMID_30669703$number,'):', PMID_30669703$pages)

PubMed_30669703 <- paste0(PubMedString, PMID_30669703$eprint)

doi_30669703 <- paste0(doiString, PMID_30669703$doi)

dimensionBadge_30669703 <- paste0(dimensionString1, PMID_30669703$doi,dimensionString2)

altmetricBadge_30669703 <- paste0(altmetricString1, PMID_30669703$doi, altmetricString2 )

addthis_inline_30669703 <- paste0(addthis_String1, PMID_30669703$title , " PMID: 30669703 " , addthis_String2)

Sys.sleep(1)


```

<details open> <summary>
- **`r PMID_30669703$title`**
</summary> 

*`r citation_30669703`*

`r PubMed_30669703`

`r addthis_inline_30669703`

`r PMID_30669703$abstract`

<!-- `r doi_30669703` -->

`r dimensionBadge_30669703`

`r altmetricBadge_30669703`

</details>

---

<a href="#top" target="_self">Back to top</a>

---

\pagebreak


### Reviews, Opinion Articles


```{r Reviews Opinion Articles, eval=FALSE, include=FALSE}
```




---

```{r 30553775, include=FALSE}

PMID_30553775 <- RefManageR::ReadPubMed('30553775', database = 'PubMed')

citation_30553775 <- paste0(PMID_30553775$journal,' ', PMID_30553775$year, ' ', PMID_30553775$month,';', PMID_30553775$volume,'(', PMID_30553775$number,'):', PMID_30553775$pages)

PubMed_30553775 <- paste0(PubMedString, PMID_30553775$eprint)

doi_30553775 <- paste0(doiString, PMID_30553775$doi)

dimensionBadge_30553775 <- paste0(dimensionString1, PMID_30553775$doi,dimensionString2)

altmetricBadge_30553775 <- paste0(altmetricString1, PMID_30553775$doi, altmetricString2 )

addthis_inline_30553775 <- paste0(addthis_String1, PMID_30553775$title , " PMID: 30553775 " , addthis_String2)

Sys.sleep(1)


```

<details open> <summary>
- **`r PMID_30553775$title`**
</summary> 

*`r citation_30553775`*

`r PubMed_30553775`

`r addthis_inline_30553775`

`r PMID_30553775$abstract`

<!-- `r doi_30553775` -->

`r dimensionBadge_30553775`

`r altmetricBadge_30553775`

</details>


---


```{r 30552236, include=FALSE}

PMID_30552236 <- RefManageR::ReadPubMed('30552236', database = 'PubMed')

citation_30552236 <- paste0(PMID_30552236$journal,' ', PMID_30552236$year, ' ', PMID_30552236$month,';', PMID_30552236$volume,'(', PMID_30552236$number,'):', PMID_30552236$pages)

PubMed_30552236 <- paste0(PubMedString, PMID_30552236$eprint)

doi_30552236 <- paste0(doiString, PMID_30552236$doi)

dimensionBadge_30552236 <- paste0(dimensionString1, PMID_30552236$doi,dimensionString2)

altmetricBadge_30552236 <- paste0(altmetricString1, PMID_30552236$doi, altmetricString2 )

addthis_inline_30552236 <- paste0(addthis_String1, PMID_30552236$title , " PMID: 30552236 " , addthis_String2)

Sys.sleep(1)


```

<details open> <summary>
- **`r PMID_30552236$title`**
</summary> 

*`r citation_30552236`*

`r PubMed_30552236`

`r addthis_inline_30552236`

`r PMID_30552236$abstract`

<!-- `r doi_30552236` -->

`r dimensionBadge_30552236`

`r altmetricBadge_30552236`

</details>



---

```{r 30552237, include=FALSE}

PMID_30552237 <- RefManageR::ReadPubMed('30552237', database = 'PubMed')

citation_30552237 <- paste0(PMID_30552237$journal,' ', PMID_30552237$year, ' ', PMID_30552237$month,';', PMID_30552237$volume,'(', PMID_30552237$number,'):', PMID_30552237$pages)

PubMed_30552237 <- paste0(PubMedString, PMID_30552237$eprint)

doi_30552237 <- paste0(doiString, PMID_30552237$doi)

dimensionBadge_30552237 <- paste0(dimensionString1, PMID_30552237$doi,dimensionString2)

altmetricBadge_30552237 <- paste0(altmetricString1, PMID_30552237$doi, altmetricString2 )

addthis_inline_30552237 <- paste0(addthis_String1, PMID_30552237$title , " PMID: 30552237 " , addthis_String2)

Sys.sleep(1)


```

<details open> <summary>
- **`r PMID_30552237$title`**
</summary> 

*`r citation_30552237`*

`r PubMed_30552237`

`r addthis_inline_30552237`

`r PMID_30552237$abstract`

<!-- `r doi_30552237` -->

`r dimensionBadge_30552237`

`r altmetricBadge_30552237`

</details>

---

```{r 30629027, include=FALSE}

PMID_30629027 <- RefManageR::ReadPubMed('30629027', database = 'PubMed')

citation_30629027 <- paste0(PMID_30629027$journal,' ', PMID_30629027$year, ' ', PMID_30629027$month,';', PMID_30629027$volume,'(', PMID_30629027$number,'):', PMID_30629027$pages)

PubMed_30629027 <- paste0(PubMedString, PMID_30629027$eprint)

doi_30629027 <- paste0(doiString, PMID_30629027$doi)

dimensionBadge_30629027 <- paste0(dimensionString1, PMID_30629027$doi,dimensionString2)

altmetricBadge_30629027 <- paste0(altmetricString1, PMID_30629027$doi, altmetricString2 )

addthis_inline_30629027 <- paste0(addthis_String1, PMID_30629027$title , " PMID: 30629027 " , addthis_String2)

Sys.sleep(1)


```

<details open> <summary>
- **`r PMID_30629027$title`**
</summary> 

*`r citation_30629027`*

`r PubMed_30629027`

`r addthis_inline_30629027`

`r PMID_30629027$abstract`

<!-- `r doi_30629027` -->

`r dimensionBadge_30629027`

`r altmetricBadge_30629027`

</details>

---

```{r 30613834, include=FALSE}

PMID_30613834 <- RefManageR::ReadPubMed('30613834', database = 'PubMed')

citation_30613834 <- paste0(PMID_30613834$journal,' ', PMID_30613834$year, ' ', PMID_30613834$month,';', PMID_30613834$volume,'(', PMID_30613834$number,'):', PMID_30613834$pages)

PubMed_30613834 <- paste0(PubMedString, PMID_30613834$eprint)

doi_30613834 <- paste0(doiString, PMID_30613834$doi)

dimensionBadge_30613834 <- paste0(dimensionString1, PMID_30613834$doi,dimensionString2)

altmetricBadge_30613834 <- paste0(altmetricString1, PMID_30613834$doi, altmetricString2 )

addthis_inline_30613834 <- paste0(addthis_String1, PMID_30613834$title , " PMID: 30613834 " , addthis_String2)

Sys.sleep(1)


```

<details open> <summary>
- **`r PMID_30613834$title`**
</summary> 

*`r citation_30613834`*

`r PubMed_30613834`

`r addthis_inline_30613834`

`r PMID_30613834$abstract`

<!-- `r doi_30613834` -->

`r dimensionBadge_30613834`

`r altmetricBadge_30613834`

</details>

---

```{r 30631752, include=FALSE}

PMID_30631752 <- RefManageR::ReadPubMed('30631752', database = 'PubMed')

citation_30631752 <- paste0(PMID_30631752$journal,' ', PMID_30631752$year, ' ', PMID_30631752$month,';', PMID_30631752$volume,'(', PMID_30631752$number,'):', PMID_30631752$pages)

PubMed_30631752 <- paste0(PubMedString, PMID_30631752$eprint)

doi_30631752 <- paste0(doiString, PMID_30631752$doi)

dimensionBadge_30631752 <- paste0(dimensionString1, PMID_30631752$doi,dimensionString2)

altmetricBadge_30631752 <- paste0(altmetricString1, PMID_30631752$doi, altmetricString2 )

addthis_inline_30631752 <- paste0(addthis_String1, PMID_30631752$title , " PMID: 30631752 " , addthis_String2)

Sys.sleep(1)


```

<details open> <summary>
- **`r PMID_30631752$title`**
</summary> 

*`r citation_30631752`*

`r PubMed_30631752`

`r addthis_inline_30631752`

`r PMID_30631752$abstract`

<!-- `r doi_30631752` -->

`r dimensionBadge_30631752`

`r altmetricBadge_30631752`

</details>

---

```{r 30660727, include=FALSE}

PMID_30660727 <- RefManageR::ReadPubMed('30660727', database = 'PubMed')

citation_30660727 <- paste0(PMID_30660727$journal,' ', PMID_30660727$year, ' ', PMID_30660727$month,';', PMID_30660727$volume,'(', PMID_30660727$number,'):', PMID_30660727$pages)

PubMed_30660727 <- paste0(PubMedString, PMID_30660727$eprint)

doi_30660727 <- paste0(doiString, PMID_30660727$doi)

dimensionBadge_30660727 <- paste0(dimensionString1, PMID_30660727$doi,dimensionString2)

altmetricBadge_30660727 <- paste0(altmetricString1, PMID_30660727$doi, altmetricString2 )

addthis_inline_30660727 <- paste0(addthis_String1, PMID_30660727$title , " PMID: 30660727 " , addthis_String2)

Sys.sleep(1)


```

<details open> <summary>
- **`r PMID_30660727$title`**
</summary> 

*`r citation_30660727`*

`r PubMed_30660727`

`r addthis_inline_30660727`

`r PMID_30660727$abstract`

<!-- `r doi_30660727` -->

`r dimensionBadge_30660727`

`r altmetricBadge_30660727`

</details>

---

<a href="#top" target="_self">Back to top</a>

---

\pagebreak


### Animal Studies


```{r Animal Studies, eval=FALSE, include=FALSE}
```


---

```{r 30579733, include=FALSE}

PMID_30579733 <- RefManageR::ReadPubMed('30579733', database = 'PubMed')

citation_30579733 <- paste0(PMID_30579733$journal,' ', PMID_30579733$year, ' ', PMID_30579733$month,';', PMID_30579733$volume,'(', PMID_30579733$number,'):', PMID_30579733$pages)

PubMed_30579733 <- paste0(PubMedString, PMID_30579733$eprint)

doi_30579733 <- paste0(doiString, PMID_30579733$doi)

dimensionBadge_30579733 <- paste0(dimensionString1, PMID_30579733$doi,dimensionString2)

altmetricBadge_30579733 <- paste0(altmetricString1, PMID_30579733$doi, altmetricString2 )

addthis_inline_30579733 <- paste0(addthis_String1, PMID_30579733$title , " PMID: 30579733 " , addthis_String2)

Sys.sleep(1)


```

<details open> <summary>
- **`r PMID_30579733$title`**
</summary> 

*`r citation_30579733`*

`r PubMed_30579733`

`r addthis_inline_30579733`

`r PMID_30579733$abstract`

<!-- `r doi_30579733` -->

`r dimensionBadge_30579733`

`r altmetricBadge_30579733`

</details>

---

<a href="#top" target="_self">Back to top</a>

---

\pagebreak


### Oncology and serum marker studies


```{r Oncology and serum marker studies, eval=FALSE, include=FALSE}
```


---

```{r 30497874, include=FALSE}

PMID_30497874 <- RefManageR::ReadPubMed('30497874', database = 'PubMed')

citation_30497874 <- paste0(PMID_30497874$journal,' ', PMID_30497874$year, ' ', PMID_30497874$month,';', PMID_30497874$volume,'(', PMID_30497874$number,'):', PMID_30497874$pages)

PubMed_30497874 <- paste0(PubMedString, PMID_30497874$eprint)

doi_30497874 <- paste0(doiString, PMID_30497874$doi)

dimensionBadge_30497874 <- paste0(dimensionString1, PMID_30497874$doi,dimensionString2)

altmetricBadge_30497874 <- paste0(altmetricString1, PMID_30497874$doi, altmetricString2 )

addthis_inline_30497874 <- paste0(addthis_String1, PMID_30497874$title , " PMID: 30497874 " , addthis_String2) 

Sys.sleep(1)

```

<details open> <summary>
- **`r PMID_30497874$title`**
</summary> 

*`r citation_30497874`*

`r PubMed_30497874`

`r addthis_inline_30497874`

`r PMID_30497874$abstract`

<!-- `r doi_30497874` -->

`r dimensionBadge_30497874`

`r altmetricBadge_30497874`

</details>


---

```{r 30569296, include=FALSE}

PMID_30569296 <- RefManageR::ReadPubMed('30569296', database = 'PubMed')

citation_30569296 <- paste0(PMID_30569296$journal,' ', PMID_30569296$year, ' ', PMID_30569296$month,';', PMID_30569296$volume,'(', PMID_30569296$number,'):', PMID_30569296$pages)

PubMed_30569296 <- paste0(PubMedString, PMID_30569296$eprint)

doi_30569296 <- paste0(doiString, PMID_30569296$doi)

dimensionBadge_30569296 <- paste0(dimensionString1, PMID_30569296$doi,dimensionString2)

altmetricBadge_30569296 <- paste0(altmetricString1, PMID_30569296$doi, altmetricString2 )

addthis_inline_30569296 <- paste0(addthis_String1, PMID_30569296$title , " PMID: 30569296 " , addthis_String2)

Sys.sleep(1)


```

<details open> <summary>
- **`r PMID_30569296$title`**
</summary> 

*`r citation_30569296`*

`r PubMed_30569296`

`r addthis_inline_30569296`

`r PMID_30569296$abstract`

<!-- `r doi_30569296` -->

`r dimensionBadge_30569296`

`r altmetricBadge_30569296`

</details>

---

```{r 30575492, include=FALSE}

PMID_30575492 <- RefManageR::ReadPubMed('30575492', database = 'PubMed')

citation_30575492 <- paste0(PMID_30575492$journal,' ', PMID_30575492$year, ' ', PMID_30575492$month,';', PMID_30575492$volume,'(', PMID_30575492$number,'):', PMID_30575492$pages)

PubMed_30575492 <- paste0(PubMedString, PMID_30575492$eprint)

doi_30575492 <- paste0(doiString, PMID_30575492$doi)

dimensionBadge_30575492 <- paste0(dimensionString1, PMID_30575492$doi,dimensionString2)

altmetricBadge_30575492 <- paste0(altmetricString1, PMID_30575492$doi, altmetricString2 )

addthis_inline_30575492 <- paste0(addthis_String1, PMID_30575492$title , " PMID: 30575492 " , addthis_String2)

Sys.sleep(1)


```

<details open> <summary>
- **`r PMID_30575492$title`**
</summary> 

*`r citation_30575492`*

`r PubMed_30575492`

`r addthis_inline_30575492`

`r PMID_30575492$abstract`

<!-- `r doi_30575492` -->

`r dimensionBadge_30575492`

`r altmetricBadge_30575492`

</details>

---

```{r 30575490, include=FALSE}

PMID_30575490 <- RefManageR::ReadPubMed('30575490', database = 'PubMed')

citation_30575490 <- paste0(PMID_30575490$journal,' ', PMID_30575490$year, ' ', PMID_30575490$month,';', PMID_30575490$volume,'(', PMID_30575490$number,'):', PMID_30575490$pages)

PubMed_30575490 <- paste0(PubMedString, PMID_30575490$eprint)

doi_30575490 <- paste0(doiString, PMID_30575490$doi)

dimensionBadge_30575490 <- paste0(dimensionString1, PMID_30575490$doi,dimensionString2)

altmetricBadge_30575490 <- paste0(altmetricString1, PMID_30575490$doi, altmetricString2 )

addthis_inline_30575490 <- paste0(addthis_String1, PMID_30575490$title , " PMID: 30575490 " , addthis_String2)

Sys.sleep(1)


```

<details open> <summary>
- **`r PMID_30575490$title`**
</summary> 

*`r citation_30575490`*

`r PubMed_30575490`

`r addthis_inline_30575490`

`r PMID_30575490$abstract`

<!-- `r doi_30575490` -->

`r dimensionBadge_30575490`

`r altmetricBadge_30575490`

</details>

---

```{r 30617132, include=FALSE}

PMID_30617132 <- RefManageR::ReadPubMed('30617132', database = 'PubMed')

citation_30617132 <- paste0(PMID_30617132$journal,' ', PMID_30617132$year, ' ', PMID_30617132$month,';', PMID_30617132$volume,'(', PMID_30617132$number,'):', PMID_30617132$pages)

PubMed_30617132 <- paste0(PubMedString, PMID_30617132$eprint)

doi_30617132 <- paste0(doiString, PMID_30617132$doi)

dimensionBadge_30617132 <- paste0(dimensionString1, PMID_30617132$doi,dimensionString2)

altmetricBadge_30617132 <- paste0(altmetricString1, PMID_30617132$doi, altmetricString2 )

addthis_inline_30617132 <- paste0(addthis_String1, PMID_30617132$title , " PMID: 30617132 " , addthis_String2)

Sys.sleep(1)


```

<details open> <summary>
- **`r PMID_30617132$title`**
</summary> 

*`r citation_30617132`*

`r PubMed_30617132`

`r addthis_inline_30617132`

`r PMID_30617132$abstract`

<!-- `r doi_30617132` -->

`r dimensionBadge_30617132`

`r altmetricBadge_30617132`

</details>

---





<a href="#top" target="_self">Back to top</a>

---

\pagebreak


### Epidemiology, Screening, Cancer Risk Factors

---

#### Pancreas Epidemiology Screening Cancer Risk Factors

```{r Pancreas Epidemiology Screening Cancer Risk Factors, eval=FALSE, include=FALSE}
```


---

```{r 30558720, include=FALSE}

PMID_30558720 <- RefManageR::ReadPubMed('30558720', database = 'PubMed')

citation_30558720 <- paste0(PMID_30558720$journal,' ', PMID_30558720$year, ' ', PMID_30558720$month,';', PMID_30558720$volume,'(', PMID_30558720$number,'):', PMID_30558720$pages)

PubMed_30558720 <- paste0(PubMedString, PMID_30558720$eprint)

doi_30558720 <- paste0(doiString, PMID_30558720$doi)

dimensionBadge_30558720 <- paste0(dimensionString1, PMID_30558720$doi,dimensionString2)

altmetricBadge_30558720 <- paste0(altmetricString1, PMID_30558720$doi, altmetricString2 )

addthis_inline_30558720 <- paste0(addthis_String1, PMID_30558720$title , " PMID: 30558720 " , addthis_String2)

Sys.sleep(1)


```

<details open> <summary>
- **`r PMID_30558720$title`**
</summary> 

*`r citation_30558720`*

`r PubMed_30558720`

`r addthis_inline_30558720`

`r PMID_30558720$abstract`

<!-- `r doi_30558720` -->

`r dimensionBadge_30558720`

`r altmetricBadge_30558720`

</details>

---

```{r 30558719, include=FALSE}

PMID_30558719 <- RefManageR::ReadPubMed('30558719', database = 'PubMed')

citation_30558719 <- paste0(PMID_30558719$journal,' ', PMID_30558719$year, ' ', PMID_30558719$month,';', PMID_30558719$volume,'(', PMID_30558719$number,'):', PMID_30558719$pages)

PubMed_30558719 <- paste0(PubMedString, PMID_30558719$eprint)

doi_30558719 <- paste0(doiString, PMID_30558719$doi)

dimensionBadge_30558719 <- paste0(dimensionString1, PMID_30558719$doi,dimensionString2)

altmetricBadge_30558719 <- paste0(altmetricString1, PMID_30558719$doi, altmetricString2 )

addthis_inline_30558719 <- paste0(addthis_String1, PMID_30558719$title , " PMID: 30558719 " , addthis_String2)

Sys.sleep(1)


```

<details open> <summary>
- **`r PMID_30558719$title`**
</summary> 

*`r citation_30558719`*

`r PubMed_30558719`

`r addthis_inline_30558719`

`r PMID_30558719$abstract`

<!-- `r doi_30558719` -->

`r dimensionBadge_30558719`

`r altmetricBadge_30558719`

</details>

---

```{r 30489447, include=FALSE}

PMID_30489447 <- RefManageR::ReadPubMed('30489447', database = 'PubMed')

citation_30489447 <- paste0(PMID_30489447$journal,' ', PMID_30489447$year, ' ', PMID_30489447$month,';', PMID_30489447$volume,'(', PMID_30489447$number,'):', PMID_30489447$pages)

PubMed_30489447 <- paste0(PubMedString, PMID_30489447$eprint)

doi_30489447 <- paste0(doiString, PMID_30489447$doi)

dimensionBadge_30489447 <- paste0(dimensionString1, PMID_30489447$doi,dimensionString2)

altmetricBadge_30489447 <- paste0(altmetricString1, PMID_30489447$doi, altmetricString2 )

addthis_inline_30489447 <- paste0(addthis_String1, PMID_30489447$title , " PMID: 30489447 " , addthis_String2) 

Sys.sleep(1)

```

<details open> <summary>
- **`r PMID_30489447$title`**
</summary> 

*`r citation_30489447`*

`r PubMed_30489447`

`r addthis_inline_30489447`

`r PMID_30489447$abstract`

<!-- `r doi_30489447` -->

`r dimensionBadge_30489447`

`r altmetricBadge_30489447`

</details>


---



```{r 30519311, include=FALSE}

PMID_30519311 <- RefManageR::ReadPubMed('30519311', database = 'PubMed')

citation_30519311 <- paste0(PMID_30519311$journal,' ', PMID_30519311$year, ' ', PMID_30519311$month,';', PMID_30519311$volume,'(', PMID_30519311$number,'):', PMID_30519311$pages)

PubMed_30519311 <- paste0(PubMedString, PMID_30519311$eprint)

doi_30519311 <- paste0(doiString, PMID_30519311$doi)

dimensionBadge_30519311 <- paste0(dimensionString1, PMID_30519311$doi,dimensionString2)

altmetricBadge_30519311 <- paste0(altmetricString1, PMID_30519311$doi, altmetricString2 )

addthis_inline_30519311 <- paste0(addthis_String1, PMID_30519311$title , " PMID: 30519311 " , addthis_String2) 

Sys.sleep(1)

```

<details open> <summary>
- **`r PMID_30519311$title`**
</summary> 

*`r citation_30519311`*

`r PubMed_30519311`

`r addthis_inline_30519311`

`r PMID_30519311$abstract`

<!-- `r doi_30519311` -->

`r dimensionBadge_30519311`

`r altmetricBadge_30519311`

</details>


---



```{r 30503370, include=FALSE}

PMID_30503370 <- RefManageR::ReadPubMed('30503370', database = 'PubMed')

citation_30503370 <- paste0(PMID_30503370$journal,' ', PMID_30503370$year, ' ', PMID_30503370$month,';', PMID_30503370$volume,'(', PMID_30503370$number,'):', PMID_30503370$pages)

PubMed_30503370 <- paste0(PubMedString, PMID_30503370$eprint)

doi_30503370 <- paste0(doiString, PMID_30503370$doi)

dimensionBadge_30503370 <- paste0(dimensionString1, PMID_30503370$doi,dimensionString2)

altmetricBadge_30503370 <- paste0(altmetricString1, PMID_30503370$doi, altmetricString2 )

addthis_inline_30503370 <- paste0(addthis_String1, PMID_30503370$title , " PMID: 30503370 " , addthis_String2) 

Sys.sleep(1)

```

<details open> <summary>
- **`r PMID_30503370$title`**
</summary> 

*`r citation_30503370`*

`r PubMed_30503370`

`r addthis_inline_30503370`

`r PMID_30503370$abstract`

<!-- `r doi_30503370` -->

`r dimensionBadge_30503370`

`r altmetricBadge_30503370`

</details>


---



```{r 30503637, include=FALSE}

PMID_30503637 <- RefManageR::ReadPubMed('30503637', database = 'PubMed')

citation_30503637 <- paste0(PMID_30503637$journal,' ', PMID_30503637$year, ' ', PMID_30503637$month,';', PMID_30503637$volume,'(', PMID_30503637$number,'):', PMID_30503637$pages)

PubMed_30503637 <- paste0(PubMedString, PMID_30503637$eprint)

doi_30503637 <- paste0(doiString, PMID_30503637$doi)

dimensionBadge_30503637 <- paste0(dimensionString1, PMID_30503637$doi,dimensionString2)

altmetricBadge_30503637 <- paste0(altmetricString1, PMID_30503637$doi, altmetricString2 )

addthis_inline_30503637 <- paste0(addthis_String1, PMID_30503637$title , " PMID: 30503637 " , addthis_String2) 

Sys.sleep(1)

```

<details open> <summary>
- **`r PMID_30503637$title`**
</summary> 

*`r citation_30503637`*

`r PubMed_30503637`

`r addthis_inline_30503637`

`r PMID_30503637$abstract`

<!-- `r doi_30503637` -->

`r dimensionBadge_30503637`

`r altmetricBadge_30503637`

</details>


---


```{r 30531246, include=FALSE}

PMID_30531246 <- RefManageR::ReadPubMed('30531246', database = 'PubMed')

citation_30531246 <- paste0(PMID_30531246$journal,' ', PMID_30531246$year, ' ', PMID_30531246$month,';', PMID_30531246$volume,'(', PMID_30531246$number,'):', PMID_30531246$pages)

PubMed_30531246 <- paste0(PubMedString, PMID_30531246$eprint)

doi_30531246 <- paste0(doiString, PMID_30531246$doi)

dimensionBadge_30531246 <- paste0(dimensionString1, PMID_30531246$doi,dimensionString2)

altmetricBadge_30531246 <- paste0(altmetricString1, PMID_30531246$doi, altmetricString2 )

addthis_inline_30531246 <- paste0(addthis_String1, PMID_30531246$title , " PMID: 30531246 " , addthis_String2)

Sys.sleep(1)


```

<details open> <summary>
- **`r PMID_30531246$title`**
</summary> 

*`r citation_30531246`*

`r PubMed_30531246`

`r addthis_inline_30531246`

`r PMID_30531246$abstract`

<!-- `r doi_30531246` -->

`r dimensionBadge_30531246`

`r altmetricBadge_30531246`

</details>



---

```{r 30538291, include=FALSE}

PMID_30538291 <- RefManageR::ReadPubMed('30538291', database = 'PubMed')

citation_30538291 <- paste0(PMID_30538291$journal,' ', PMID_30538291$year, ' ', PMID_30538291$month,';', PMID_30538291$volume,'(', PMID_30538291$number,'):', PMID_30538291$pages)

PubMed_30538291 <- paste0(PubMedString, PMID_30538291$eprint)

doi_30538291 <- paste0(doiString, PMID_30538291$doi)

dimensionBadge_30538291 <- paste0(dimensionString1, PMID_30538291$doi,dimensionString2)

altmetricBadge_30538291 <- paste0(altmetricString1, PMID_30538291$doi, altmetricString2 )

addthis_inline_30538291 <- paste0(addthis_String1, PMID_30538291$title , " PMID: 30538291 " , addthis_String2)

Sys.sleep(1)


```

<details open> <summary>
- **`r PMID_30538291$title`**
</summary> 

*`r citation_30538291`*

`r PubMed_30538291`

`r addthis_inline_30538291`

`r PMID_30538291$abstract`

<!-- `r doi_30538291` -->

`r dimensionBadge_30538291`

`r altmetricBadge_30538291`

</details>

---

```{r 30580091, include=FALSE}

PMID_30580091 <- RefManageR::ReadPubMed('30580091', database = 'PubMed')

citation_30580091 <- paste0(PMID_30580091$journal,' ', PMID_30580091$year, ' ', PMID_30580091$month,';', PMID_30580091$volume,'(', PMID_30580091$number,'):', PMID_30580091$pages)

PubMed_30580091 <- paste0(PubMedString, PMID_30580091$eprint)

doi_30580091 <- paste0(doiString, PMID_30580091$doi)

dimensionBadge_30580091 <- paste0(dimensionString1, PMID_30580091$doi,dimensionString2)

altmetricBadge_30580091 <- paste0(altmetricString1, PMID_30580091$doi, altmetricString2 )

addthis_inline_30580091 <- paste0(addthis_String1, PMID_30580091$title , " PMID: 30580091 " , addthis_String2)

Sys.sleep(1)


```

<details open> <summary>
- **`r PMID_30580091$title`**
</summary> 

*`r citation_30580091`*

`r PubMed_30580091`

`r addthis_inline_30580091`

`r PMID_30580091$abstract`

<!-- `r doi_30580091` -->

`r dimensionBadge_30580091`

`r altmetricBadge_30580091`

</details>


---

```{r 30589831, include=FALSE}

PMID_30589831 <- RefManageR::ReadPubMed('30589831', database = 'PubMed')

citation_30589831 <- paste0(PMID_30589831$journal,' ', PMID_30589831$year, ' ', PMID_30589831$month,';', PMID_30589831$volume,'(', PMID_30589831$number,'):', PMID_30589831$pages)

PubMed_30589831 <- paste0(PubMedString, PMID_30589831$eprint)

doi_30589831 <- paste0(doiString, PMID_30589831$doi)

dimensionBadge_30589831 <- paste0(dimensionString1, PMID_30589831$doi,dimensionString2)

altmetricBadge_30589831 <- paste0(altmetricString1, PMID_30589831$doi, altmetricString2 )

addthis_inline_30589831 <- paste0(addthis_String1, PMID_30589831$title , " PMID: 30589831 " , addthis_String2)

Sys.sleep(1)


```

<details open> <summary>
- **`r PMID_30589831$title`**
</summary> 

*`r citation_30589831`*

`r PubMed_30589831`

`r addthis_inline_30589831`

`r PMID_30589831$abstract`

<!-- `r doi_30589831` -->

`r dimensionBadge_30589831`

`r altmetricBadge_30589831`

</details>


---

```{r 30603118, include=FALSE}

PMID_30603118 <- RefManageR::ReadPubMed('30603118', database = 'PubMed')

citation_30603118 <- paste0(PMID_30603118$journal,' ', PMID_30603118$year, ' ', PMID_30603118$month,';', PMID_30603118$volume,'(', PMID_30603118$number,'):', PMID_30603118$pages)

PubMed_30603118 <- paste0(PubMedString, PMID_30603118$eprint)

doi_30603118 <- paste0(doiString, PMID_30603118$doi)

dimensionBadge_30603118 <- paste0(dimensionString1, PMID_30603118$doi,dimensionString2)

altmetricBadge_30603118 <- paste0(altmetricString1, PMID_30603118$doi, altmetricString2 )

addthis_inline_30603118 <- paste0(addthis_String1, PMID_30603118$title , " PMID: 30603118 " , addthis_String2)

Sys.sleep(1)


```

<details open> <summary>
- **`r PMID_30603118$title`**
</summary> 

*`r citation_30603118`*

`r PubMed_30603118`

`r addthis_inline_30603118`

`r PMID_30603118$abstract`

<!-- `r doi_30603118` -->

`r dimensionBadge_30603118`

`r altmetricBadge_30603118`

</details>

---

#### Bile Duct Epidemiology Screening Cancer Risk Factors

```{r Bile Duct Epidemiology Screening Cancer Risk Factors, eval=FALSE, include=FALSE}
```


---

```{r 30497878, include=FALSE}

PMID_30497878 <- RefManageR::ReadPubMed('30497878', database = 'PubMed')

citation_30497878 <- paste0(PMID_30497878$journal,' ', PMID_30497878$year, ' ', PMID_30497878$month,';', PMID_30497878$volume,'(', PMID_30497878$number,'):', PMID_30497878$pages)

PubMed_30497878 <- paste0(PubMedString, PMID_30497878$eprint)

doi_30497878 <- paste0(doiString, PMID_30497878$doi)

dimensionBadge_30497878 <- paste0(dimensionString1, PMID_30497878$doi,dimensionString2)

altmetricBadge_30497878 <- paste0(altmetricString1, PMID_30497878$doi, altmetricString2 )

addthis_inline_30497878 <- paste0(addthis_String1, PMID_30497878$title , " PMID: 30497878 " , addthis_String2) 

Sys.sleep(1)

```

<details open> <summary>
- **`r PMID_30497878$title`**
</summary> 

*`r citation_30497878`*

`r PubMed_30497878`

`r addthis_inline_30497878`

`r PMID_30497878$abstract`

<!-- `r doi_30497878` -->

`r dimensionBadge_30497878`

`r altmetricBadge_30497878`

</details>


---



```{r 30505597, include=FALSE}

PMID_30505597 <- RefManageR::ReadPubMed('30505597', database = 'PubMed')

citation_30505597 <- paste0(PMID_30505597$journal,' ', PMID_30505597$year, ' ', PMID_30505597$month,';', PMID_30505597$volume,'(', PMID_30505597$number,'):', PMID_30505597$pages)

PubMed_30505597 <- paste0(PubMedString, PMID_30505597$eprint)

doi_30505597 <- paste0(doiString, PMID_30505597$doi)

dimensionBadge_30505597 <- paste0(dimensionString1, PMID_30505597$doi,dimensionString2)

altmetricBadge_30505597 <- paste0(altmetricString1, PMID_30505597$doi, altmetricString2 )

addthis_inline_30505597 <- paste0(addthis_String1, PMID_30505597$title , " PMID: 30505597 " , addthis_String2) 

Sys.sleep(1)

```

<details open> <summary>
- **`r PMID_30505597$title`**
</summary> 

*`r citation_30505597`*

`r PubMed_30505597`

`r addthis_inline_30505597`

`r PMID_30505597$abstract`

<!-- `r doi_30505597` -->

`r dimensionBadge_30505597`

`r altmetricBadge_30505597`

</details>

---

```{r 30539494, include=FALSE}

PMID_30539494 <- RefManageR::ReadPubMed('30539494', database = 'PubMed')

citation_30539494 <- paste0(PMID_30539494$journal,' ', PMID_30539494$year, ' ', PMID_30539494$month,';', PMID_30539494$volume,'(', PMID_30539494$number,'):', PMID_30539494$pages)

PubMed_30539494 <- paste0(PubMedString, PMID_30539494$eprint)

doi_30539494 <- paste0(doiString, PMID_30539494$doi)

dimensionBadge_30539494 <- paste0(dimensionString1, PMID_30539494$doi,dimensionString2)

altmetricBadge_30539494 <- paste0(altmetricString1, PMID_30539494$doi, altmetricString2 )

addthis_inline_30539494 <- paste0(addthis_String1, PMID_30539494$title , " PMID: 30539494 " , addthis_String2)

Sys.sleep(1)


```

<details open> <summary>
- **`r PMID_30539494$title`**
</summary> 

*`r citation_30539494`*

`r PubMed_30539494`

`r addthis_inline_30539494`

`r PMID_30539494$abstract`

<!-- `r doi_30539494` -->

`r dimensionBadge_30539494`

`r altmetricBadge_30539494`

</details>


---

```{r 30466151, include=FALSE}

PMID_30466151 <- RefManageR::ReadPubMed('30466151', database = 'PubMed')

citation_30466151 <- paste0(PMID_30466151$journal,' ', PMID_30466151$year, ' ', PMID_30466151$month,';', PMID_30466151$volume,'(', PMID_30466151$number,'):', PMID_30466151$pages)

PubMed_30466151 <- paste0(PubMedString, PMID_30466151$eprint)

doi_30466151 <- paste0(doiString, PMID_30466151$doi)

dimensionBadge_30466151 <- paste0(dimensionString1, PMID_30466151$doi,dimensionString2)

altmetricBadge_30466151 <- paste0(altmetricString1, PMID_30466151$doi, altmetricString2 )

addthis_inline_30466151 <- paste0(addthis_String1, PMID_30466151$title , " PMID: 30466151 " , addthis_String2)

Sys.sleep(1)


```

<details open> <summary>
- **`r PMID_30466151$title`**
</summary> 

*`r citation_30466151`*

`r PubMed_30466151`

`r addthis_inline_30466151`

`r PMID_30466151$abstract`

<!-- `r doi_30466151` -->

`r dimensionBadge_30466151`

`r altmetricBadge_30466151`

</details>

---

```{r 30488679, include=FALSE}

PMID_30488679 <- RefManageR::ReadPubMed('30488679', database = 'PubMed')

citation_30488679 <- paste0(PMID_30488679$journal,' ', PMID_30488679$year, ' ', PMID_30488679$month,';', PMID_30488679$volume,'(', PMID_30488679$number,'):', PMID_30488679$pages)

PubMed_30488679 <- paste0(PubMedString, PMID_30488679$eprint)

doi_30488679 <- paste0(doiString, PMID_30488679$doi)

dimensionBadge_30488679 <- paste0(dimensionString1, PMID_30488679$doi,dimensionString2)

altmetricBadge_30488679 <- paste0(altmetricString1, PMID_30488679$doi, altmetricString2 )

addthis_inline_30488679 <- paste0(addthis_String1, PMID_30488679$title , " PMID: 30488679 " , addthis_String2) 

Sys.sleep(1)

```

<details open> <summary>
- **`r PMID_30488679$title`**
</summary> 

*`r citation_30488679`*

`r PubMed_30488679`

`r addthis_inline_30488679`

`r PMID_30488679$abstract`

<!-- `r doi_30488679` -->

`r dimensionBadge_30488679`

`r altmetricBadge_30488679`

</details>

---

```{r 30645774, include=FALSE}

PMID_30645774 <- RefManageR::ReadPubMed('30645774', database = 'PubMed')

citation_30645774 <- paste0(PMID_30645774$journal,' ', PMID_30645774$year, ' ', PMID_30645774$month,';', PMID_30645774$volume,'(', PMID_30645774$number,'):', PMID_30645774$pages)

PubMed_30645774 <- paste0(PubMedString, PMID_30645774$eprint)

doi_30645774 <- paste0(doiString, PMID_30645774$doi)

dimensionBadge_30645774 <- paste0(dimensionString1, PMID_30645774$doi,dimensionString2)

altmetricBadge_30645774 <- paste0(altmetricString1, PMID_30645774$doi, altmetricString2 )

addthis_inline_30645774 <- paste0(addthis_String1, PMID_30645774$title , " PMID: 30645774 " , addthis_String2)

Sys.sleep(1)


```

<details open> <summary>
- **`r PMID_30645774$title`**
</summary> 

*`r citation_30645774`*

`r PubMed_30645774`

`r addthis_inline_30645774`

`r PMID_30645774$abstract`

<!-- `r doi_30645774` -->

`r dimensionBadge_30645774`

`r altmetricBadge_30645774`

</details>

---

#### PanNET Epidemiology Screening Cancer Risk Factors

```{r PanNET Epidemiology Screening Cancer Risk Factors, eval=FALSE, include=FALSE}
```


---

```{r 30589832, include=FALSE}

PMID_30589832 <- RefManageR::ReadPubMed('30589832', database = 'PubMed')

citation_30589832 <- paste0(PMID_30589832$journal,' ', PMID_30589832$year, ' ', PMID_30589832$month,';', PMID_30589832$volume,'(', PMID_30589832$number,'):', PMID_30589832$pages)

PubMed_30589832 <- paste0(PubMedString, PMID_30589832$eprint)

doi_30589832 <- paste0(doiString, PMID_30589832$doi)

dimensionBadge_30589832 <- paste0(dimensionString1, PMID_30589832$doi,dimensionString2)

altmetricBadge_30589832 <- paste0(altmetricString1, PMID_30589832$doi, altmetricString2 )

addthis_inline_30589832 <- paste0(addthis_String1, PMID_30589832$title , " PMID: 30589832 " , addthis_String2)

Sys.sleep(1)


```

<details open> <summary>
- **`r PMID_30589832$title`**
</summary> 

*`r citation_30589832`*

`r PubMed_30589832`

`r addthis_inline_30589832`

`r PMID_30589832$abstract`

<!-- `r doi_30589832` -->

`r dimensionBadge_30589832`

`r altmetricBadge_30589832`

</details>

---

```{r 30519109, include=FALSE}

PMID_30519109 <- RefManageR::ReadPubMed('30519109', database = 'PubMed')

citation_30519109 <- paste0(PMID_30519109$journal,' ', PMID_30519109$year, ' ', PMID_30519109$month,';', PMID_30519109$volume,'(', PMID_30519109$number,'):', PMID_30519109$pages)

PubMed_30519109 <- paste0(PubMedString, PMID_30519109$eprint)

doi_30519109 <- paste0(doiString, PMID_30519109$doi)

dimensionBadge_30519109 <- paste0(dimensionString1, PMID_30519109$doi,dimensionString2)

altmetricBadge_30519109 <- paste0(altmetricString1, PMID_30519109$doi, altmetricString2 )

addthis_inline_30519109 <- paste0(addthis_String1, PMID_30519109$title , " PMID: 30519109 " , addthis_String2) 

Sys.sleep(1)

```

<details open> <summary>
- **`r PMID_30519109$title`**
</summary> 

*`r citation_30519109`*

`r PubMed_30519109`

`r addthis_inline_30519109`

`r PMID_30519109$abstract`

<!-- `r doi_30519109` -->

`r dimensionBadge_30519109`

`r altmetricBadge_30519109`

</details>

---



#### Ampulla of Vater Epidemiology Screening Cancer Risk Factors

```{r Ampulla of Vater Epidemiology Screening Cancer Risk Factors, eval=FALSE, include=FALSE}
```

---


```{r 30488680, include=FALSE}

PMID_30488680 <- RefManageR::ReadPubMed('30488680', database = 'PubMed')

citation_30488680 <- paste0(PMID_30488680$journal,' ', PMID_30488680$year, ' ', PMID_30488680$month,';', PMID_30488680$volume,'(', PMID_30488680$number,'):', PMID_30488680$pages)

PubMed_30488680 <- paste0(PubMedString, PMID_30488680$eprint)

doi_30488680 <- paste0(doiString, PMID_30488680$doi)

dimensionBadge_30488680 <- paste0(dimensionString1, PMID_30488680$doi,dimensionString2)

altmetricBadge_30488680 <- paste0(altmetricString1, PMID_30488680$doi, altmetricString2 )

addthis_inline_30488680 <- paste0(addthis_String1, PMID_30488680$title , " PMID: 30488680 " , addthis_String2) 

Sys.sleep(1)

```

<details open> <summary>
- **`r PMID_30488680$title`**
</summary> 

*`r citation_30488680`*

`r PubMed_30488680`

`r addthis_inline_30488680`

`r PMID_30488680$abstract`

<!-- `r doi_30488680` -->

`r dimensionBadge_30488680`

`r altmetricBadge_30488680`

</details>



---





---






<a href="#top" target="_self">Back to top</a>

---

\pagebreak
