---
title: "Pancreatobiliary Pathology Society Journal Watch"
output:
  pdf_document:
    toc: yes
    number_sections: yes
    latex_engine: xelatex
    keep_tex: yes
  html_document: 
    keep_md: yes
  html_notebook:
    code_folding: none
    fig_caption: yes
    highlight: null
    theme: paper
date: "Last Update on `r format(Sys.Date())`"
subtitle: 'September - October 2020'
header-includes:
- \renewcommand{\linethickness}{0.05em}
- \usepackage{booktabs}
- \usepackage{sectsty} \allsectionsfont{\nohang\centering \emph}
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(cache = TRUE)
```



```{r library, include=FALSE}
suppressPackageStartupMessages(library("tidyverse"))
suppressPackageStartupMessages(library("readxl"))
suppressPackageStartupMessages(library("RefManageR"))

```



<style type="text/css">

h1{
  text-align: center;
}
h2{
  text-align: center;
}
h3{
  text-align: center;
}
h4{
  text-align: center;
}
h4.date{
  text-align: center;
}

</style>


---

# PBPath Journal Watch Articles {.tabset .tabset-fade .tabset-pills #pbpath_jw}


```{r strings , include=FALSE}
PubMedString <- "PubMed: https://www.ncbi.nlm.nih.gov/pubmed/?term="

doiString <- "doi: https://doi.org/"

```



---

**Welcome to the PBPath Journal Watch!** 



This bi-monthly journal watch features exciting recently published pancreas and biliary pathology articles that will provide up to date medical knowledge in our field. These articles will be showcased in several convenient categories, including surgical pathology, cytopathology, molecular pathology, pancreas, gallbladder, bile ducts, and ampulla among others. The articles in each category are in no particular order. See the list of journals we search regularly [here](http://pbpath.org/pbpath-journal-watch/). Previous months’ issues may be found in our *[archive](http://pbpath.org/journal-watch-archive/)* and you may see [drafts of the upcoming issue here](http://pbpath.org/journal-watch-upcoming-issue/).  

We encourage members to actively participate by recommending new articles and providing feedback using the [forms provided below.](#feedback){target="_self"}  

**We hope that you will enjoy the new PBPath Journal Watch!**

<a href="#top" target="_self">Back to top</a>

---

\pagebreak


## Pancreas {#pancreas}



---

```{r pancreas 33177357, include=FALSE}

PMID_33177357 <- RefManageR::ReadPubMed('33177357', database = 'PubMed')

citation_33177357 <- paste0(PMID_33177357$journal,' ', PMID_33177357$year, ' ', PMID_33177357$month,';', PMID_33177357$volume,'(', PMID_33177357$number,'):', PMID_33177357$pages)

PubMed_33177357 <- paste0(PubMedString, PMID_33177357$eprint)

doi_33177357 <- paste0(doiString, PMID_33177357$doi)

Sys.sleep(2)

```

<details open> <summary>
- **`r PMID_33177357$title`**
</summary> 

*`r citation_33177357`*

`r PubMed_33177357`

`r PMID_33177357$abstract`

`r doi_33177357`

</details>

---




---

```{r pancreas 33177340, include=FALSE}

PMID_33177340 <- RefManageR::ReadPubMed('33177340', database = 'PubMed')

citation_33177340 <- paste0(PMID_33177340$journal,' ', PMID_33177340$year, ' ', PMID_33177340$month,';', PMID_33177340$volume,'(', PMID_33177340$number,'):', PMID_33177340$pages)

PubMed_33177340 <- paste0(PubMedString, PMID_33177340$eprint)

doi_33177340 <- paste0(doiString, PMID_33177340$doi)

Sys.sleep(2)

```

<details open> <summary>
- **`r PMID_33177340$title`**
</summary> 

*`r citation_33177340`*

`r PubMed_33177340`

`r PMID_33177340$abstract`

`r doi_33177340`

</details>

---




---

```{r pancreas 33176750, include=FALSE}

PMID_33176750 <- RefManageR::ReadPubMed('33176750', database = 'PubMed')

citation_33176750 <- paste0(PMID_33176750$journal,' ', PMID_33176750$year, ' ', PMID_33176750$month,';', PMID_33176750$volume,'(', PMID_33176750$number,'):', PMID_33176750$pages)

PubMed_33176750 <- paste0(PubMedString, PMID_33176750$eprint)

doi_33176750 <- paste0(doiString, PMID_33176750$doi)

Sys.sleep(2)

```

<details open> <summary>
- **`r PMID_33176750$title`**
</summary> 

*`r citation_33176750`*

`r PubMed_33176750`

`r PMID_33176750$abstract`

`r doi_33176750`

</details>

---




---

```{r pancreas 33174146, include=FALSE}

PMID_33174146 <- RefManageR::ReadPubMed('33174146', database = 'PubMed')

citation_33174146 <- paste0(PMID_33174146$journal,' ', PMID_33174146$year, ' ', PMID_33174146$month,';', PMID_33174146$volume,'(', PMID_33174146$number,'):', PMID_33174146$pages)

PubMed_33174146 <- paste0(PubMedString, PMID_33174146$eprint)

doi_33174146 <- paste0(doiString, PMID_33174146$doi)

Sys.sleep(2)

```

<details open> <summary>
- **`r PMID_33174146$title`**
</summary> 

*`r citation_33174146`*

`r PubMed_33174146`

`r PMID_33174146$abstract`

`r doi_33174146`

</details>

---



---

```{r pancreas 33136337, include=FALSE}

PMID_33136337 <- RefManageR::ReadPubMed('33136337', database = 'PubMed')

citation_33136337 <- paste0(PMID_33136337$journal,' ', PMID_33136337$year, ' ', PMID_33136337$month,';', PMID_33136337$volume,'(', PMID_33136337$number,'):', PMID_33136337$pages)

PubMed_33136337 <- paste0(PubMedString, PMID_33136337$eprint)

doi_33136337 <- paste0(doiString, PMID_33136337$doi)

Sys.sleep(2)

```

<details open> <summary>
- **`r PMID_33136337$title`**
</summary> 

*`r citation_33136337`*

`r PubMed_33136337`

`r PMID_33136337$abstract`

`r doi_33136337`

</details>

---


---

```{r pancreas 33128119, include=FALSE}

PMID_33128119 <- RefManageR::ReadPubMed('33128119', database = 'PubMed')

citation_33128119 <- paste0(PMID_33128119$journal,' ', PMID_33128119$year, ' ', PMID_33128119$month,';', PMID_33128119$volume,'(', PMID_33128119$number,'):', PMID_33128119$pages)

PubMed_33128119 <- paste0(PubMedString, PMID_33128119$eprint)

doi_33128119 <- paste0(doiString, PMID_33128119$doi)

Sys.sleep(2)

```

<details open> <summary>
- **`r PMID_33128119$title`**
</summary> 

*`r citation_33128119`*

`r PubMed_33128119`

`r PMID_33128119$abstract`

`r doi_33128119`

</details>

---





---

```{r pancreas 33122528, include=FALSE}

PMID_33122528 <- RefManageR::ReadPubMed('33122528', database = 'PubMed')

citation_33122528 <- paste0(PMID_33122528$journal,' ', PMID_33122528$year, ' ', PMID_33122528$month,';', PMID_33122528$volume,'(', PMID_33122528$number,'):', PMID_33122528$pages)

PubMed_33122528 <- paste0(PubMedString, PMID_33122528$eprint)

doi_33122528 <- paste0(doiString, PMID_33122528$doi)

Sys.sleep(2)

```

<details open> <summary>
- **`r PMID_33122528$title`**
</summary> 

*`r citation_33122528`*

`r PubMed_33122528`

`r PMID_33122528$abstract`

`r doi_33122528`

</details>

---


---

```{r pancreas 33122524, include=FALSE}

PMID_33122524 <- RefManageR::ReadPubMed('33122524', database = 'PubMed')

citation_33122524 <- paste0(PMID_33122524$journal,' ', PMID_33122524$year, ' ', PMID_33122524$month,';', PMID_33122524$volume,'(', PMID_33122524$number,'):', PMID_33122524$pages)

PubMed_33122524 <- paste0(PubMedString, PMID_33122524$eprint)

doi_33122524 <- paste0(doiString, PMID_33122524$doi)

Sys.sleep(2)

```

<details open> <summary>
- **`r PMID_33122524$title`**
</summary> 

*`r citation_33122524`*

`r PubMed_33122524`

`r PMID_33122524$abstract`

`r doi_33122524`

</details>

---





---

```{r pancreas 33097588, include=FALSE}

PMID_33097588 <- RefManageR::ReadPubMed('33097588', database = 'PubMed')

citation_33097588 <- paste0(PMID_33097588$journal,' ', PMID_33097588$year, ' ', PMID_33097588$month,';', PMID_33097588$volume,'(', PMID_33097588$number,'):', PMID_33097588$pages)

PubMed_33097588 <- paste0(PubMedString, PMID_33097588$eprint)

doi_33097588 <- paste0(doiString, PMID_33097588$doi)

Sys.sleep(2)

```

<details open> <summary>
- **`r PMID_33097588$title`**
</summary> 

*`r citation_33097588`*

`r PubMed_33097588`

`r PMID_33097588$abstract`

`r doi_33097588`

</details>

---



---

```{r pancreas 33097431, include=FALSE}

PMID_33097431 <- RefManageR::ReadPubMed('33097431', database = 'PubMed')

citation_33097431 <- paste0(PMID_33097431$journal,' ', PMID_33097431$year, ' ', PMID_33097431$month,';', PMID_33097431$volume,'(', PMID_33097431$number,'):', PMID_33097431$pages)

PubMed_33097431 <- paste0(PubMedString, PMID_33097431$eprint)

doi_33097431 <- paste0(doiString, PMID_33097431$doi)

Sys.sleep(2)

```

<details open> <summary>
- **`r PMID_33097431$title`**
</summary> 

*`r citation_33097431`*

`r PubMed_33097431`

`r PMID_33097431$abstract`

`r doi_33097431`

</details>

---


---

```{r pancreas 33086324, include=FALSE}

PMID_33086324 <- RefManageR::ReadPubMed('33086324', database = 'PubMed')

citation_33086324 <- paste0(PMID_33086324$journal,' ', PMID_33086324$year, ' ', PMID_33086324$month,';', PMID_33086324$volume,'(', PMID_33086324$number,'):', PMID_33086324$pages)

PubMed_33086324 <- paste0(PubMedString, PMID_33086324$eprint)

doi_33086324 <- paste0(doiString, PMID_33086324$doi)

Sys.sleep(2)

```

<details open> <summary>
- **`r PMID_33086324$title`**
</summary> 

*`r citation_33086324`*

`r PubMed_33086324`

`r PMID_33086324$abstract`

`r doi_33086324`

</details>

---



---

```{r pancreas 33082106, include=FALSE}

PMID_33082106 <- RefManageR::ReadPubMed('33082106', database = 'PubMed')

citation_33082106 <- paste0(PMID_33082106$journal,' ', PMID_33082106$year, ' ', PMID_33082106$month,';', PMID_33082106$volume,'(', PMID_33082106$number,'):', PMID_33082106$pages)

PubMed_33082106 <- paste0(PubMedString, PMID_33082106$eprint)

doi_33082106 <- paste0(doiString, PMID_33082106$doi)

Sys.sleep(2)

```

<details open> <summary>
- **`r PMID_33082106$title`**
</summary> 

*`r citation_33082106`*

`r PubMed_33082106`

`r PMID_33082106$abstract`

`r doi_33082106`

</details>

---




---

```{r pancreas 33079429, include=FALSE}

PMID_33079429 <- RefManageR::ReadPubMed('33079429', database = 'PubMed')

citation_33079429 <- paste0(PMID_33079429$journal,' ', PMID_33079429$year, ' ', PMID_33079429$month,';', PMID_33079429$volume,'(', PMID_33079429$number,'):', PMID_33079429$pages)

PubMed_33079429 <- paste0(PubMedString, PMID_33079429$eprint)

doi_33079429 <- paste0(doiString, PMID_33079429$doi)

Sys.sleep(2)

```

<details open> <summary>
- **`r PMID_33079429$title`**
</summary> 

*`r citation_33079429`*

`r PubMed_33079429`

`r PMID_33079429$abstract`

`r doi_33079429`

</details>

---




---

```{r pancreas 33074853, include=FALSE}

PMID_33074853 <- RefManageR::ReadPubMed('33074853', database = 'PubMed')

citation_33074853 <- paste0(PMID_33074853$journal,' ', PMID_33074853$year, ' ', PMID_33074853$month,';', PMID_33074853$volume,'(', PMID_33074853$number,'):', PMID_33074853$pages)

PubMed_33074853 <- paste0(PubMedString, PMID_33074853$eprint)

doi_33074853 <- paste0(doiString, PMID_33074853$doi)

Sys.sleep(2)

```

<details open> <summary>
- **`r PMID_33074853$title`**
</summary> 

*`r citation_33074853`*

`r PubMed_33074853`

`r PMID_33074853$abstract`

`r doi_33074853`

</details>

---





---

```{r pancreas 33069084, include=FALSE}

PMID_33069084 <- RefManageR::ReadPubMed('33069084', database = 'PubMed')

citation_33069084 <- paste0(PMID_33069084$journal,' ', PMID_33069084$year, ' ', PMID_33069084$month,';', PMID_33069084$volume,'(', PMID_33069084$number,'):', PMID_33069084$pages)

PubMed_33069084 <- paste0(PubMedString, PMID_33069084$eprint)

doi_33069084 <- paste0(doiString, PMID_33069084$doi)

Sys.sleep(2)

```

<details open> <summary>
- **`r PMID_33069084$title`**
</summary> 

*`r citation_33069084`*

`r PubMed_33069084`

`r PMID_33069084$abstract`

`r doi_33069084`

</details>

---



---

```{r pancreas 33060017, include=FALSE}

PMID_33060017 <- RefManageR::ReadPubMed('33060017', database = 'PubMed')

citation_33060017 <- paste0(PMID_33060017$journal,' ', PMID_33060017$year, ' ', PMID_33060017$month,';', PMID_33060017$volume,'(', PMID_33060017$number,'):', PMID_33060017$pages)

PubMed_33060017 <- paste0(PubMedString, PMID_33060017$eprint)

doi_33060017 <- paste0(doiString, PMID_33060017$doi)

Sys.sleep(2)

```

<details open> <summary>
- **`r PMID_33060017$title`**
</summary> 

*`r citation_33060017`*

`r PubMed_33060017`

`r PMID_33060017$abstract`

`r doi_33060017`

</details>

---





---

```{r pancreas 33051146, include=FALSE}

PMID_33051146 <- RefManageR::ReadPubMed('33051146', database = 'PubMed')

citation_33051146 <- paste0(PMID_33051146$journal,' ', PMID_33051146$year, ' ', PMID_33051146$month,';', PMID_33051146$volume,'(', PMID_33051146$number,'):', PMID_33051146$pages)

PubMed_33051146 <- paste0(PubMedString, PMID_33051146$eprint)

doi_33051146 <- paste0(doiString, PMID_33051146$doi)

Sys.sleep(2)

```

<details open> <summary>
- **`r PMID_33051146$title`**
</summary> 

*`r citation_33051146`*

`r PubMed_33051146`

`r PMID_33051146$abstract`

`r doi_33051146`

</details>

---



---

```{r pancreas 33046515, include=FALSE}

PMID_33046515 <- RefManageR::ReadPubMed('33046515', database = 'PubMed')

citation_33046515 <- paste0(PMID_33046515$journal,' ', PMID_33046515$year, ' ', PMID_33046515$month,';', PMID_33046515$volume,'(', PMID_33046515$number,'):', PMID_33046515$pages)

PubMed_33046515 <- paste0(PubMedString, PMID_33046515$eprint)

doi_33046515 <- paste0(doiString, PMID_33046515$doi)

Sys.sleep(2)

```

<details open> <summary>
- **`r PMID_33046515$title`**
</summary> 

*`r citation_33046515`*

`r PubMed_33046515`

`r PMID_33046515$abstract`

`r doi_33046515`

</details>

---



---

```{r pancreas 33041332, include=FALSE}

PMID_33041332 <- RefManageR::ReadPubMed('33041332', database = 'PubMed')

citation_33041332 <- paste0(PMID_33041332$journal,' ', PMID_33041332$year, ' ', PMID_33041332$month,';', PMID_33041332$volume,'(', PMID_33041332$number,'):', PMID_33041332$pages)

PubMed_33041332 <- paste0(PubMedString, PMID_33041332$eprint)

doi_33041332 <- paste0(doiString, PMID_33041332$doi)

Sys.sleep(2)

```

<details open> <summary>
- **`r PMID_33041332$title`**
</summary> 

*`r citation_33041332`*

`r PubMed_33041332`

`r PMID_33041332$abstract`

`r doi_33041332`

</details>

---



---

```{r pancreas 33037322, include=FALSE}

PMID_33037322 <- RefManageR::ReadPubMed('33037322', database = 'PubMed')

citation_33037322 <- paste0(PMID_33037322$journal,' ', PMID_33037322$year, ' ', PMID_33037322$month,';', PMID_33037322$volume,'(', PMID_33037322$number,'):', PMID_33037322$pages)

PubMed_33037322 <- paste0(PubMedString, PMID_33037322$eprint)

doi_33037322 <- paste0(doiString, PMID_33037322$doi)

Sys.sleep(2)

```

<details open> <summary>
- **`r PMID_33037322$title`**
</summary> 

*`r citation_33037322`*

`r PubMed_33037322`

`r PMID_33037322$abstract`

`r doi_33037322`

</details>

---



---

```{r pancreas 33028669, include=FALSE}

PMID_33028669 <- RefManageR::ReadPubMed('33028669', database = 'PubMed')

citation_33028669 <- paste0(PMID_33028669$journal,' ', PMID_33028669$year, ' ', PMID_33028669$month,';', PMID_33028669$volume,'(', PMID_33028669$number,'):', PMID_33028669$pages)

PubMed_33028669 <- paste0(PubMedString, PMID_33028669$eprint)

doi_33028669 <- paste0(doiString, PMID_33028669$doi)

Sys.sleep(2)

```

<details open> <summary>
- **`r PMID_33028669$title`**
</summary> 

*`r citation_33028669`*

`r PubMed_33028669`

`r PMID_33028669$abstract`

`r doi_33028669`

</details>

---




---

```{r pancreas 33028596, include=FALSE}

PMID_33028596 <- RefManageR::ReadPubMed('33028596', database = 'PubMed')

citation_33028596 <- paste0(PMID_33028596$journal,' ', PMID_33028596$year, ' ', PMID_33028596$month,';', PMID_33028596$volume,'(', PMID_33028596$number,'):', PMID_33028596$pages)

PubMed_33028596 <- paste0(PubMedString, PMID_33028596$eprint)

doi_33028596 <- paste0(doiString, PMID_33028596$doi)

Sys.sleep(2)

```

<details open> <summary>
- **`r PMID_33028596$title`**
</summary> 

*`r citation_33028596`*

`r PubMed_33028596`

`r PMID_33028596$abstract`

`r doi_33028596`

</details>

---



---

```{r pancreas 33009500, include=FALSE}

PMID_33009500 <- RefManageR::ReadPubMed('33009500', database = 'PubMed')

citation_33009500 <- paste0(PMID_33009500$journal,' ', PMID_33009500$year, ' ', PMID_33009500$month,';', PMID_33009500$volume,'(', PMID_33009500$number,'):', PMID_33009500$pages)

PubMed_33009500 <- paste0(PubMedString, PMID_33009500$eprint)

doi_33009500 <- paste0(doiString, PMID_33009500$doi)

Sys.sleep(2)

```

<details open> <summary>
- **`r PMID_33009500$title`**
</summary> 

*`r citation_33009500`*

`r PubMed_33009500`

`r PMID_33009500$abstract`

`r doi_33009500`

</details>

---



---

```{r pancreas 33005981, include=FALSE}

PMID_33005981 <- RefManageR::ReadPubMed('33005981', database = 'PubMed')

citation_33005981 <- paste0(PMID_33005981$journal,' ', PMID_33005981$year, ' ', PMID_33005981$month,';', PMID_33005981$volume,'(', PMID_33005981$number,'):', PMID_33005981$pages)

PubMed_33005981 <- paste0(PubMedString, PMID_33005981$eprint)

doi_33005981 <- paste0(doiString, PMID_33005981$doi)

Sys.sleep(2)

```

<details open> <summary>
- **`r PMID_33005981$title`**
</summary> 

*`r citation_33005981`*

`r PubMed_33005981`

`r PMID_33005981$abstract`

`r doi_33005981`

</details>

---



---

```{r pancreas 32967636, include=FALSE}

PMID_32967636 <- RefManageR::ReadPubMed('32967636', database = 'PubMed')

citation_32967636 <- paste0(PMID_32967636$journal,' ', PMID_32967636$year, ' ', PMID_32967636$month,';', PMID_32967636$volume,'(', PMID_32967636$number,'):', PMID_32967636$pages)

PubMed_32967636 <- paste0(PubMedString, PMID_32967636$eprint)

doi_32967636 <- paste0(doiString, PMID_32967636$doi)

Sys.sleep(2)

```

<details open> <summary>
- **`r PMID_32967636$title`**
</summary> 

*`r citation_32967636`*

`r PubMed_32967636`

`r PMID_32967636$abstract`

`r doi_32967636`

</details>

---




---

```{r pancreas 32948429, include=FALSE}

PMID_32948429 <- RefManageR::ReadPubMed('32948429', database = 'PubMed')

citation_32948429 <- paste0(PMID_32948429$journal,' ', PMID_32948429$year, ' ', PMID_32948429$month,';', PMID_32948429$volume,'(', PMID_32948429$number,'):', PMID_32948429$pages)

PubMed_32948429 <- paste0(PubMedString, PMID_32948429$eprint)

doi_32948429 <- paste0(doiString, PMID_32948429$doi)

Sys.sleep(2)

```

<details open> <summary>
- **`r PMID_32948429$title`**
</summary> 

*`r citation_32948429`*

`r PubMed_32948429`

`r PMID_32948429$abstract`

`r doi_32948429`

</details>

---





---

```{r pancreas 32934105, include=FALSE}

PMID_32934105 <- RefManageR::ReadPubMed('32934105', database = 'PubMed')

citation_32934105 <- paste0(PMID_32934105$journal,' ', PMID_32934105$year, ' ', PMID_32934105$month,';', PMID_32934105$volume,'(', PMID_32934105$number,'):', PMID_32934105$pages)

PubMed_32934105 <- paste0(PubMedString, PMID_32934105$eprint)

doi_32934105 <- paste0(doiString, PMID_32934105$doi)

Sys.sleep(2)

```

<details open> <summary>
- **`r PMID_32934105$title`**
</summary> 

*`r citation_32934105`*

`r PubMed_32934105`

`r PMID_32934105$abstract`

`r doi_32934105`

</details>

---




---

```{r pancreas 32933947, include=FALSE}

PMID_32933947 <- RefManageR::ReadPubMed('32933947', database = 'PubMed')

citation_32933947 <- paste0(PMID_32933947$journal,' ', PMID_32933947$year, ' ', PMID_32933947$month,';', PMID_32933947$volume,'(', PMID_32933947$number,'):', PMID_32933947$pages)

PubMed_32933947 <- paste0(PubMedString, PMID_32933947$eprint)

doi_32933947 <- paste0(doiString, PMID_32933947$doi)

Sys.sleep(2)

```

<details open> <summary>
- **`r PMID_32933947$title`**
</summary> 

*`r citation_32933947`*

`r PubMed_32933947`

`r PMID_32933947$abstract`

`r doi_32933947`

</details>

---



---

```{r pancreas 32897998, include=FALSE}

PMID_32897998 <- RefManageR::ReadPubMed('32897998', database = 'PubMed')

citation_32897998 <- paste0(PMID_32897998$journal,' ', PMID_32897998$year, ' ', PMID_32897998$month,';', PMID_32897998$volume,'(', PMID_32897998$number,'):', PMID_32897998$pages)

PubMed_32897998 <- paste0(PubMedString, PMID_32897998$eprint)

doi_32897998 <- paste0(doiString, PMID_32897998$doi)

Sys.sleep(2)

```

<details open> <summary>
- **`r PMID_32897998$title`**
</summary> 

*`r citation_32897998`*

`r PubMed_32897998`

`r PMID_32897998$abstract`

`r doi_32897998`

</details>

---



---

```{r pancreas 32813226, include=FALSE}

PMID_32813226 <- RefManageR::ReadPubMed('32813226', database = 'PubMed')

citation_32813226 <- paste0(PMID_32813226$journal,' ', PMID_32813226$year, ' ', PMID_32813226$month,';', PMID_32813226$volume,'(', PMID_32813226$number,'):', PMID_32813226$pages)

PubMed_32813226 <- paste0(PubMedString, PMID_32813226$eprint)

doi_32813226 <- paste0(doiString, PMID_32813226$doi)

Sys.sleep(2)

```

<details open> <summary>
- **`r PMID_32813226$title`**
</summary> 

*`r citation_32813226`*

`r PubMed_32813226`

`r PMID_32813226$abstract`

`r doi_32813226`

</details>

---




---

```{r pancreas 32457408, include=FALSE}

PMID_32457408 <- RefManageR::ReadPubMed('32457408', database = 'PubMed')

citation_32457408 <- paste0(PMID_32457408$journal,' ', PMID_32457408$year, ' ', PMID_32457408$month,';', PMID_32457408$volume,'(', PMID_32457408$number,'):', PMID_32457408$pages)

PubMed_32457408 <- paste0(PubMedString, PMID_32457408$eprint)

doi_32457408 <- paste0(doiString, PMID_32457408$doi)

Sys.sleep(2)

```

<details open> <summary>
- **`r PMID_32457408$title`**
</summary> 

*`r citation_32457408`*

`r PubMed_32457408`

`r PMID_32457408$abstract`

`r doi_32457408`

</details>

---




---

```{r pancreas 32424767, include=FALSE}

PMID_32424767 <- RefManageR::ReadPubMed('32424767', database = 'PubMed')

citation_32424767 <- paste0(PMID_32424767$journal,' ', PMID_32424767$year, ' ', PMID_32424767$month,';', PMID_32424767$volume,'(', PMID_32424767$number,'):', PMID_32424767$pages)

PubMed_32424767 <- paste0(PubMedString, PMID_32424767$eprint)

doi_32424767 <- paste0(doiString, PMID_32424767$doi)

Sys.sleep(2)

```

<details open> <summary>
- **`r PMID_32424767$title`**
</summary> 

*`r citation_32424767`*

`r PubMed_32424767`

`r PMID_32424767$abstract`

`r doi_32424767`

</details>

---



---

```{r pancreas 32358589, include=FALSE}

PMID_32358589 <- RefManageR::ReadPubMed('32358589', database = 'PubMed')

citation_32358589 <- paste0(PMID_32358589$journal,' ', PMID_32358589$year, ' ', PMID_32358589$month,';', PMID_32358589$volume,'(', PMID_32358589$number,'):', PMID_32358589$pages)

PubMed_32358589 <- paste0(PubMedString, PMID_32358589$eprint)

doi_32358589 <- paste0(doiString, PMID_32358589$doi)

Sys.sleep(2)

```

<details open> <summary>
- **`r PMID_32358589$title`**
</summary> 

*`r citation_32358589`*

`r PubMed_32358589`

`r PMID_32358589$abstract`

`r doi_32358589`

</details>

---




---

```{r pancreas 32350415, include=FALSE}

PMID_32350415 <- RefManageR::ReadPubMed('32350415', database = 'PubMed')

citation_32350415 <- paste0(PMID_32350415$journal,' ', PMID_32350415$year, ' ', PMID_32350415$month,';', PMID_32350415$volume,'(', PMID_32350415$number,'):', PMID_32350415$pages)

PubMed_32350415 <- paste0(PubMedString, PMID_32350415$eprint)

doi_32350415 <- paste0(doiString, PMID_32350415$doi)

Sys.sleep(2)

```

<details open> <summary>
- **`r PMID_32350415$title`**
</summary> 

*`r citation_32350415`*

`r PubMed_32350415`

`r PMID_32350415$abstract`

`r doi_32350415`

</details>

---




---

```{r pancreas 32307617, include=FALSE}

PMID_32307617 <- RefManageR::ReadPubMed('32307617', database = 'PubMed')

citation_32307617 <- paste0(PMID_32307617$journal,' ', PMID_32307617$year, ' ', PMID_32307617$month,';', PMID_32307617$volume,'(', PMID_32307617$number,'):', PMID_32307617$pages)

PubMed_32307617 <- paste0(PubMedString, PMID_32307617$eprint)

doi_32307617 <- paste0(doiString, PMID_32307617$doi)

Sys.sleep(2)

```

<details open> <summary>
- **`r PMID_32307617$title`**
</summary> 

*`r citation_32307617`*

`r PubMed_32307617`

`r PMID_32307617$abstract`

`r doi_32307617`

</details>

---





---

<a href="#top" target="_self">Back to top</a>

---

\pagebreak



## Gallbladder {#gallbladder}




---

```{r gallbladder 33060404, include=FALSE}

PMID_33060404 <- RefManageR::ReadPubMed('33060404', database = 'PubMed')

citation_33060404 <- paste0(PMID_33060404$journal,' ', PMID_33060404$year, ' ', PMID_33060404$month,';', PMID_33060404$volume,'(', PMID_33060404$number,'):', PMID_33060404$pages)

PubMed_33060404 <- paste0(PubMedString, PMID_33060404$eprint)

doi_33060404 <- paste0(doiString, PMID_33060404$doi)

Sys.sleep(2)

```

<details open> <summary>
- **`r PMID_33060404$title`**
</summary> 

*`r citation_33060404`*

`r PubMed_33060404`

`r PMID_33060404$abstract`

`r doi_33060404`

</details>

---




---

```{r gallbladder 33016162, include=FALSE}

PMID_33016162 <- RefManageR::ReadPubMed('33016162', database = 'PubMed')

citation_33016162 <- paste0(PMID_33016162$journal,' ', PMID_33016162$year, ' ', PMID_33016162$month,';', PMID_33016162$volume,'(', PMID_33016162$number,'):', PMID_33016162$pages)

PubMed_33016162 <- paste0(PubMedString, PMID_33016162$eprint)

doi_33016162 <- paste0(doiString, PMID_33016162$doi)

Sys.sleep(2)

```

<details open> <summary>
- **`r PMID_33016162$title`**
</summary> 

*`r citation_33016162`*

`r PubMed_33016162`

`r PMID_33016162$abstract`

`r doi_33016162`

</details>

---




---

```{r gallbladder 32991930, include=FALSE}

PMID_32991930 <- RefManageR::ReadPubMed('32991930', database = 'PubMed')

citation_32991930 <- paste0(PMID_32991930$journal,' ', PMID_32991930$year, ' ', PMID_32991930$month,';', PMID_32991930$volume,'(', PMID_32991930$number,'):', PMID_32991930$pages)

PubMed_32991930 <- paste0(PubMedString, PMID_32991930$eprint)

doi_32991930 <- paste0(doiString, PMID_32991930$doi)

Sys.sleep(2)

```

<details open> <summary>
- **`r PMID_32991930$title`**
</summary> 

*`r citation_32991930`*

`r PubMed_32991930`

`r PMID_32991930$abstract`

`r doi_32991930`

</details>

---




---

```{r gallbladder 32925194, include=FALSE}

PMID_32925194 <- RefManageR::ReadPubMed('32925194', database = 'PubMed')

citation_32925194 <- paste0(PMID_32925194$journal,' ', PMID_32925194$year, ' ', PMID_32925194$month,';', PMID_32925194$volume,'(', PMID_32925194$number,'):', PMID_32925194$pages)

PubMed_32925194 <- paste0(PubMedString, PMID_32925194$eprint)

doi_32925194 <- paste0(doiString, PMID_32925194$doi)

Sys.sleep(2)

```

<details open> <summary>
- **`r PMID_32925194$title`**
</summary> 

*`r citation_32925194`*

`r PubMed_32925194`

`r PMID_32925194$abstract`

`r doi_32925194`

</details>

---




---

```{r gallbladder 32895766, include=FALSE}

PMID_32895766 <- RefManageR::ReadPubMed('32895766', database = 'PubMed')

citation_32895766 <- paste0(PMID_32895766$journal,' ', PMID_32895766$year, ' ', PMID_32895766$month,';', PMID_32895766$volume,'(', PMID_32895766$number,'):', PMID_32895766$pages)

PubMed_32895766 <- paste0(PubMedString, PMID_32895766$eprint)

doi_32895766 <- paste0(doiString, PMID_32895766$doi)

Sys.sleep(2)

```

<details open> <summary>
- **`r PMID_32895766$title`**
</summary> 

*`r citation_32895766`*

`r PubMed_32895766`

`r PMID_32895766$abstract`

`r doi_32895766`

</details>

---




---

```{r gallbladder 32891647, include=FALSE}

PMID_32891647 <- RefManageR::ReadPubMed('32891647', database = 'PubMed')

citation_32891647 <- paste0(PMID_32891647$journal,' ', PMID_32891647$year, ' ', PMID_32891647$month,';', PMID_32891647$volume,'(', PMID_32891647$number,'):', PMID_32891647$pages)

PubMed_32891647 <- paste0(PubMedString, PMID_32891647$eprint)

doi_32891647 <- paste0(doiString, PMID_32891647$doi)

Sys.sleep(2)

```

<details open> <summary>
- **`r PMID_32891647$title`**
</summary> 

*`r citation_32891647`*

`r PubMed_32891647`

`r PMID_32891647$abstract`

`r doi_32891647`

</details>

---






---

```{r gallbladder 32447492, include=FALSE}

PMID_32447492 <- RefManageR::ReadPubMed('32447492', database = 'PubMed')

citation_32447492 <- paste0(PMID_32447492$journal,' ', PMID_32447492$year, ' ', PMID_32447492$month,';', PMID_32447492$volume,'(', PMID_32447492$number,'):', PMID_32447492$pages)

PubMed_32447492 <- paste0(PubMedString, PMID_32447492$eprint)

doi_32447492 <- paste0(doiString, PMID_32447492$doi)

Sys.sleep(2)

```

<details open> <summary>
- **`r PMID_32447492$title`**
</summary> 

*`r citation_32447492`*

`r PubMed_32447492`

`r PMID_32447492$abstract`

`r doi_32447492`

</details>

---






---

<a href="#top" target="_self">Back to top</a>

---

\pagebreak


## Bile Ducts {#bileducts}




---

```{r bileducts 33129823, include=FALSE}

PMID_33129823 <- RefManageR::ReadPubMed('33129823', database = 'PubMed')

citation_33129823 <- paste0(PMID_33129823$journal,' ', PMID_33129823$year, ' ', PMID_33129823$month,';', PMID_33129823$volume,'(', PMID_33129823$number,'):', PMID_33129823$pages)

PubMed_33129823 <- paste0(PubMedString, PMID_33129823$eprint)

doi_33129823 <- paste0(doiString, PMID_33129823$doi)

Sys.sleep(2)

```

<details open> <summary>
- **`r PMID_33129823$title`**
</summary> 

*`r citation_33129823`*

`r PubMed_33129823`

`r PMID_33129823$abstract`

`r doi_33129823`

</details>

---



---

```{r bileducts 32909295, include=FALSE}

PMID_32909295 <- RefManageR::ReadPubMed('32909295', database = 'PubMed')

citation_32909295 <- paste0(PMID_32909295$journal,' ', PMID_32909295$year, ' ', PMID_32909295$month,';', PMID_32909295$volume,'(', PMID_32909295$number,'):', PMID_32909295$pages)

PubMed_32909295 <- paste0(PubMedString, PMID_32909295$eprint)

doi_32909295 <- paste0(doiString, PMID_32909295$doi)

Sys.sleep(2)

```

<details open> <summary>
- **`r PMID_32909295$title`**
</summary> 

*`r citation_32909295`*

`r PubMed_32909295`

`r PMID_32909295$abstract`

`r doi_32909295`

</details>

---




---

```{r bileducts 32473032, include=FALSE}

PMID_32473032 <- RefManageR::ReadPubMed('32473032', database = 'PubMed')

citation_32473032 <- paste0(PMID_32473032$journal,' ', PMID_32473032$year, ' ', PMID_32473032$month,';', PMID_32473032$volume,'(', PMID_32473032$number,'):', PMID_32473032$pages)

PubMed_32473032 <- paste0(PubMedString, PMID_32473032$eprint)

doi_32473032 <- paste0(doiString, PMID_32473032$doi)

Sys.sleep(2)

```

<details open> <summary>
- **`r PMID_32473032$title`**
</summary> 

*`r citation_32473032`*

`r PubMed_32473032`

`r PMID_32473032$abstract`

`r doi_32473032`

</details>

---




---

```{r bileducts 32457409, include=FALSE}

PMID_32457409 <- RefManageR::ReadPubMed('32457409', database = 'PubMed')

citation_32457409 <- paste0(PMID_32457409$journal,' ', PMID_32457409$year, ' ', PMID_32457409$month,';', PMID_32457409$volume,'(', PMID_32457409$number,'):', PMID_32457409$pages)

PubMed_32457409 <- paste0(PubMedString, PMID_32457409$eprint)

doi_32457409 <- paste0(doiString, PMID_32457409$doi)

Sys.sleep(2)

```

<details open> <summary>
- **`r PMID_32457409$title`**
</summary> 

*`r citation_32457409`*

`r PubMed_32457409`

`r PMID_32457409$abstract`

`r doi_32457409`

</details>

---




---

```{r bileducts 32296928, include=FALSE}

PMID_32296928 <- RefManageR::ReadPubMed('32296928', database = 'PubMed')

citation_32296928 <- paste0(PMID_32296928$journal,' ', PMID_32296928$year, ' ', PMID_32296928$month,';', PMID_32296928$volume,'(', PMID_32296928$number,'):', PMID_32296928$pages)

PubMed_32296928 <- paste0(PubMedString, PMID_32296928$eprint)

doi_32296928 <- paste0(doiString, PMID_32296928$doi)

Sys.sleep(2)

```

<details open> <summary>
- **`r PMID_32296928$title`**
</summary> 

*`r citation_32296928`*

`r PubMed_32296928`

`r PMID_32296928$abstract`

`r doi_32296928`

</details>

---




---

<a href="#top" target="_self">Back to top</a>

---

\pagebreak


# Feedback {#feedback}


[Google Feedback Form](https://docs.google.com/forms/d/e/1FAIpQLSeD3Z9J6Y7eMmiyM12f_SfAmHUlykb1zxZcwO6lg7cebGYQIQ/viewform)  


<script id="dsq-count-scr" src="//pbpath-org.disqus.com/count.js" async></script>
<div id="disqus_thread"></div>
<script>

/**
*  RECOMMENDED CONFIGURATION VARIABLES: EDIT AND UNCOMMENT THE SECTION BELOW TO INSERT DYNAMIC VALUES FROM YOUR PLATFORM OR CMS.
*  LEARN WHY DEFINING THESE VARIABLES IS IMPORTANT: https://disqus.com/admin/universalcode/#configuration-variables*/
/*
var disqus_config = function () {
this.page.url = PAGE_URL;  // Replace PAGE_URL with your page's canonical URL variable
this.page.identifier = PAGE_IDENTIFIER; // Replace PAGE_IDENTIFIER with your page's unique identifier variable
};
*/
(function() { // DON'T EDIT BELOW THIS LINE
var d = document, s = d.createElement('script');
s.src = 'https://pbpath-org.disqus.com/embed.js';
s.setAttribute('data-timestamp', +new Date());
(d.head || d.body).appendChild(s);
})();
</script>
<noscript>Please enable JavaScript to view the <a href="https://disqus.com/?ref_noscript">comments powered by Disqus.</a></noscript>
                            


---

<a href="#top" target="_self">Back to top</a>

---

\pagebreak


