---
title: "Pancreatobiliary Pathology Society Journal Watch"
output:
  html_notebook:
    code_folding: none
    fig_caption: yes
    highlight: null
    theme: paper
  pdf_document: 
    toc: yes
    number_sections: yes
    latex_engine: xelatex
    keep_tex: yes
  html_document:
    df_print: paged
date: "Last Update on `r format(Sys.Date())`"
subtitle: Recent Articles that will be Selected
header-includes:
- \renewcommand{\linethickness}{0.05em}
- \usepackage{booktabs}
- \usepackage{sectsty} \allsectionsfont{\nohang\centering \emph}
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(cache = TRUE)
```


```{r library, include=FALSE}
suppressPackageStartupMessages(library("tidyverse"))
suppressPackageStartupMessages(library("readxl"))
suppressPackageStartupMessages(library("RefManageR"))

```


```{r data load, include=FALSE}
articles <- readRDS("~/JournalWatchPBPath/articles.rds")
```


<style type="text/css">

h1{
  text-align: center;
}
h2{
  text-align: center;
}
h3{
  text-align: center;
}
h4{
  text-align: center;
}
h4.date{
  text-align: center;
}

</style>



<!-- Open all links in new tab-->  
<base target="_blank"/>  



---

# PBPath Journal Watch Articles {.tabset .tabset-fade .tabset-pills #pbpath_jw}


```{r strings , include=FALSE}
PubMedString <- "PubMed: https://www.ncbi.nlm.nih.gov/pubmed/?term="

doiString <- "doi: https://doi.org/"

```



---

**Wellcome to the PBPath Journal Watch!** 

[![DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.3635440.svg)](https://doi.org/10.5281/zenodo.3635440)

https://doi.org/10.5281/zenodo.3635440

https://osf.io/3d67y/

This bi-monthly journal watch features exciting recently published pancreas and biliary pathology articles that will provide up to date medical knowledge in our field. These articles will be showcased in several convenient categories, including surgical pathology, cytopathology, and molecular pathology among others. The articles in each category are in no particular order. See the list of journals we search regularly [here](http://pbpath.org/pbpath-journal-watch/). Previous months’ issues may be found in our *[archive](http://pbpath.org/journal-watch-archive/)* and you may see [drafts of the upcoming issue here](http://pbpath.org/journal-watch-upcoming-issue/).  

We encourage members to actively participate by recommending new articles and providing feedback using the [forms provided below.](#feedback){target="_self"}  

**We hope that you will enjoy the new PBPath Journal Watch!**


\pagebreak





```{r PMID, include=FALSE}
pancreas_recent_PMID <-
    readr::read_csv(file      = "~/AutoJournalWatch/data/PMIDList_pancreas.csv",
                    col_names = c("PMID"),
                    cols(PMID = col_character()))

gallbladder_recent_PMID <-
    readr::read_csv(file      = "~/AutoJournalWatch/data/PMIDList_gallbladder.csv",
                    col_names = c("PMID"),
                    cols(PMID = col_character()))

bileducts_recent_PMID <-
    readr::read_csv(file      = "~/AutoJournalWatch/data/PMIDList_bileducts.csv",
                    col_names = c("PMID"),
                    cols(PMID = col_character()))

ampulla_recent_PMID <-
    readr::read_csv(file      = "~/AutoJournalWatch/data/PMIDList_ampulla.csv",
                    col_names = c("PMID"),
                    cols(PMID = col_character()))
```



## Pancreas {#pancreas}



```{r OKM pancreas, include=FALSE}
PMID_OKM_pancreas <- pancreas_recent_PMID$PMID %>% 
t() %>%
paste0("[uid] OR ", collapse = "") # add OR between PMID List

PMID_OKM_pancreas <- gsub(" OR $", "" , PMID_OKM_pancreas) # to remove last OR

PubMed_Link_pancreas <- paste0("To see these articles in <a href = https://www.ncbi.nlm.nih.gov/pubmed/?term='",PMID_OKM_pancreas,"'> PubMed, click here </a>")

```


`r PubMed_Link_pancreas`




```{r pancreasRecent,  child='~/JournalWatchPBPath/_pancreasRecent.Rmd'}
```

---

<a href="#top" target="_self">Back to top</a>

---

\pagebreak



## Gallbladder {#gallbladder}




```{r include=FALSE}
PMID_OKM_gallbladder <- gallbladder_recent_PMID$PMID %>% 
t() %>%
paste0("[uid] OR ", collapse = "") # add OR between PMID List

PMID_OKM_gallbladder <- gsub(" OR $", "" , PMID_OKM_gallbladder) # to remove last OR
```



```{r gallbladderRecent,  child='~/JournalWatchPBPath/_gallbladderRecent.Rmd'}
```


---

<a href="#top" target="_self">Back to top</a>

---

\pagebreak


## Bile Ducts {#bileducts}




```{r include=FALSE}
PMID_OKM_bileducts <- bileducts_recent_PMID$PMID %>% 
t() %>%
paste0("[uid] OR ", collapse = "") # add OR between PMID List

PMID_OKM_bileducts <- gsub(" OR $", "" , PMID_OKM_bileducts) # to remove last OR
```





```{r bileductsRecent,  child='~/JournalWatchPBPath/_bileductsRecent.Rmd'}
```



---

<a href="#top" target="_self">Back to top</a>

---

\pagebreak

## Ampulla {#ampulla}



```{r include=FALSE}
PMID_OKM_ampulla <- ampulla_recent_PMID$PMID %>% 
t() %>%
paste0("[uid] OR ", collapse = "") # add OR between PMID List

PMID_OKM_ampulla <- gsub(" OR $", "" , PMID_OKM_ampulla) # to remove last OR

```




```{r ampullaRecent,  child='~/JournalWatchPBPath/_ampullaRecent.Rmd'}
```



---

<a href="#top" target="_self">Back to top</a>

---

\pagebreak



---

<a href="#top" target="_self">Back to top</a>

---

\pagebreak


# Feedback {#feedback}


[Google Feedback Form](https://docs.google.com/forms/d/e/1FAIpQLSeD3Z9J6Y7eMmiyM12f_SfAmHUlykb1zxZcwO6lg7cebGYQIQ/viewform)  


<script id="dsq-count-scr" src="//pbpath-org.disqus.com/count.js" async></script>
<div id="disqus_thread"></div>
<script>

/**
*  RECOMMENDED CONFIGURATION VARIABLES: EDIT AND UNCOMMENT THE SECTION BELOW TO INSERT DYNAMIC VALUES FROM YOUR PLATFORM OR CMS.
*  LEARN WHY DEFINING THESE VARIABLES IS IMPORTANT: https://disqus.com/admin/universalcode/#configuration-variables*/
/*
var disqus_config = function () {
this.page.url = PAGE_URL;  // Replace PAGE_URL with your page's canonical URL variable
this.page.identifier = PAGE_IDENTIFIER; // Replace PAGE_IDENTIFIER with your page's unique identifier variable
};
*/
(function() { // DON'T EDIT BELOW THIS LINE
var d = document, s = d.createElement('script');
s.src = 'https://pbpath-org.disqus.com/embed.js';
s.setAttribute('data-timestamp', +new Date());
(d.head || d.body).appendChild(s);
})();
</script>
<noscript>Please enable JavaScript to view the <a href="https://disqus.com/?ref_noscript">comments powered by Disqus.</a></noscript>
                            


---

<a href="#top" target="_self">Back to top</a>

---

\pagebreak


